### 2021-01-03 code/data-analysis/factor-analysis.Rmd
Codes for cleaning pm component data

---
title: "Air Quality Data from EPA AQS"
author: "Fatemeh Kazemi"
date: "01-01-2021"
output:
  html_document:
    df_print: paged
---

### Last Edit: 12-31-2020

### This program:
  (1) Run factor anlaysis

```{r load packages}
library(tidyverse)
library(here)
library(psych) # for factor analysis

```

```{r Load datasets}
load(here('data','processed', 'comp-sel.RDa'))
```

```{r - preliminary factor analysis}
# All eligible monitors
fit <- factanal(dt.comp.sel %>% select(AS:OC), 8, rotation="varimax")
factor.loadings <- rbind(fit$loadings)
save(factor.loadings, file = here('output','table','factor-loadings.RDa'))

factor.scores <- factor.scores(dt.comp.sel %>% select(AS:OC), fit)
dt.comp.fac <- cbind(dt.comp.sel, factor.scores$scores)
save(dt.comp.fac, file = here('data', 'processed', 'comp-fac.RDa'))

# Removing EC from factor analysis
fit <- factanal(dt.comp.sel %>% select(AS:ZN, OC), 8, rotation="varimax")
factor.loadings.ex.ec <- rbind(fit$loadings)
save(factor.loadings.ex.ec, file = here('output','table','factor-loadings-ex-ec.RDa'))

factor.scores <- factor.scores(dt.comp.sel %>% select(AS:ZN, OC), fit)
dt.comp.fac.ex.ec <- cbind(dt.comp.sel, factor.scores$scores)
save(dt.comp.fac.ex.ec, file = here('data', 'processed', 'comp-fac-ex-ec.RDa'))
```

### 2021-01-03 code/data-processors/air-data-processor.Rmd
Codes for cleaning pm component data

---
title: "Air Quality Data - PM2.5 Components"
author: "Fatemeh Kazemi"
date: "12-27-2020"
output:
  html_document:
    df_print: paged
---

### This program:
  (1) Downloads and cleans EPA AQS Sites Description Files
  (2) Downloads and cleans PM2.5 Speciation data measured by EPA 
  (3) Cleans PM2.5 component data - Imrpove Network
  (4) Cleans PM2.5 components data - CSN Network
  (5) Combines all available PM2.5 Components data
  (6) Choose a subset of monitors on the basis of data availability
  (7) Smooth data with 4df per year to fill small gaps
      i. Do not smooth over more than 90 days of missing data
      ii. Divide data into coherent pieces instead
  (8) Calculates yearly average of PM components by site and month
      i. Require at least 350 values to compute yearly average from smoothed data

```{r load packages}
library(tidyverse)
library(here)
library(lubridate)
library(naniar) # for replacing -999 with NA
```

```{r Call Functions}
source(here('code','data-processors','epa-air-data-download-function.R'))
source(here('code','data-processors','air-data-processor-function.R'))
source(here('code','data-processors','air-data-smooth-mvavg-function.R'))
```

```{r load data}
load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\state-region.RDa')
```

```{r - AQS Sites Information}
### AQS Sites - Extract Location setting, land use,
### ... Latitude and Longitude for each site
### https://aqs.epa.gov/aqsweb/airdata/FileFormats.html#_site_description_file

temp <- tempfile()
download.file("https://aqs.epa.gov/aqsweb/airdata/aqs_sites.zip", temp)

aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
  filter(
    #remove monitors closed before 2000
    year(as.Date(Site.Closed.Date)) >= 2000 | Site.Closed.Date == "",
    !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
                       "Guam", "Country Of Mexico","Canada") #remove non-CONUS states
    ) %>%  
  transmute(
    Site.ID = as.factor(sprintf("%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                as.numeric(as.character(State.Code)),
                                County.Code, Site.Number)), 
    State.Code = as.factor(sprintf("%02d", as.numeric(as.character(State.Code)))),
    County.Code = as.factor(sprintf("%03d", County.Code)),
    Latitude,
    Longitude, 
    State = state.abb[match(State.Name,state.name)],
    State = as.factor(ifelse(State.Name == "District Of Columbia","DC", State)),
    Land.Use,
    Location.Setting = as.factor(ifelse(Location.Setting == "URBAN AND CENTER CITY",
                                        "URBAN",
                                        as.character(Location.Setting)))
    ) %>% 
  merge(state.region[, c("State", "Region.IV")])

save(aqs.sites, file = here('data', 'processed', 'aqs-sites.RDa'))

aqs.sites %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())
```

```{r - Parameters' Code and Symbol}
Code.to.Sym <- tribble(
  ~Parameter.Code, ~Parameter.Symbol,
   88103, "AS",
   88111, "CA",
   88114, "CU",
   88115, "CL",
   88126, "FE",
   88128, "PB",
   88132, "MN",
   88136, "NI",
   88140, "MG",
   88154, "SE",
   88164, "V",
   88165, "SI",
   88167, "ZN",
   88180, "K",
   88184, "NA",
   88306, "NO3",
   88403, "SO4",
   88305, "OC.TOT",
   88307, "EC.TOT",
   88320, "OC.TOR",
   88321, "EC.TOR"
   ) %>% 
  mutate(Parameter.Symbol = as.factor(Parameter.Symbol))
```

```{r EPA AQS Data Download}
dt.spec.raw <- EPA_AQS_download (period = "daily", Index = "SPEC",
                        start = 2000, end = 2008, 
                        Code.Sym = Code.to.Sym)
save(dt.spec.raw, file = here('data', 'processed', 'spec-raw.RDa'))
```

```{r check carbon}
### EC
carbon.ec <- dt.spec.raw %>% 
  select(Site.ID, POC, Monitor.ID, Parameter.Symbol, Date, Arithmetic.Mean) %>% 
  pivot_wider(names_sort = T,
              names_from = c(Parameter.Symbol),
              values_from = c(Arithmetic.Mean)) %>% 
  arrange(Site.ID, POC, Date) %>%
  select(Site.ID, POC, Monitor.ID, EC.TOR, EC.TOT)

ec.c<- carbon.ec[complete.cases(carbon.ec),] #405 simultaneous TOR & TOT
ec.c %>% group_by(Site.ID) %>% 
  summarise(n = n()) # 11 Sites ~40 each

summary(lm(EC.TOR ~ EC.TOT, ec.c))
# TOR = 1.182 * TOT + 0.087 Adj.R2 = 0.862

### OC
carbon.ec <- dt.spec.raw %>% 
  select(Site.ID, POC, Monitor.ID, Parameter.Symbol, Date, Arithmetic.Mean) %>% 
  pivot_wider(names_sort = T,
              names_from = c(Parameter.Symbol),
              values_from = c(Arithmetic.Mean)) %>% 
  arrange(Site.ID, POC, Date.Local) %>%
  select(Site.ID, POC, Monitor.ID, OC.TOR, OC.TOT)

oc.c<- carbon.oc[complete.cases(carbon.oc),] #405 simultaneous TOR & TOT
oc.c %>% group_by(Site.ID) %>% 
  summarise(n = n())

summary(lm(OC.TOR ~ OC.TOT, oc.c))
# TOR = 0.917 * TOT + 0.579 Adj.R2 = 0.824
```

```{r change spec data to wide format - combine TOR & TOT carbons}
dt.spec.w <- dt.spec.raw %>% 
  select(-Parameter.Code) %>% 
  pivot_wider(names_sort = T,
              names_from = c(Parameter.Symbol),
              values_from = c(Arithmetic.Mean)) %>% 
  # for 405 cases with two methods use TOR for EC & OC
  mutate(EC = ifelse(!is.na(EC.TOR), EC.TOR, EC.TOT), 
         OC = ifelse(!is.na(OC.TOR), OC.TOR, OC.TOT)) %>% 
  select(-EC.TOR, -EC.TOT, -OC.TOR, -OC.TOT) %>% 
  arrange(Site.ID, POC, Date)

save(dt.spec.w, file = here('data', 'processed', 'spec-wide.RDa'))
```

```{r Improve Data cleaning}
# EC 88307 -> TOT
# OC 88320 -> TOR
dt.imprv.raw = data.frame()
for (i in seq(2000,2008,1)){
  dt0 <- read.delim(here('data','raw','improve',paste0('improve_',i,'.txt')), sep = ',')
  dt.imprv.raw <- rbind(dt.imprv.raw, dt0)
}
colnames(dt.imprv.raw) <- colnames(dt.imprv.raw) %>% str_remove("f.Value")

#replace -999 with NA
dt.imprv.raw <- dt.imprv.raw %>% 
  replace_with_na(replace = list("AS"= -999,
                                 "CA"= -999,
                                 "EC"= -999,
                                 "OC"= -999,
                                 "CL"= -999,
                                 "CU"= -999,
                                 "FE"= -999,
                                 "PB"= -999,
                                 "MG"= -999,
                                 "MN"= -999,
                                 "NI"= -999,
                                 "NO3"= -999,
                                 "K"= -999,
                                 "SE"= -999,
                                 "SI"= -999,
                                 "NA"= -999,
                                 "SO4"= -999,
                                 "V"= -999,
                                 "ZN"= -999)) %>% 
  arrange(EPACode, POC, Date)

# correct EPACode (Site.ID)
dt.imprv.raw <- dt.imprv.raw %>% 
  filter(!EPACode == '.') %>% 
  mutate(EPACode = str_pad(EPACode, 9, pad = "0"))%>% 
  filter(# remove non-CONUS States
    !str_sub(EPACode,1,2) %in% c('02', '15') & str_sub(EPACode,1,2) < '60'
    ) %>% 
  mutate(Date = mdy(Date),
         Site.ID = paste(str_sub(EPACode,1,2), str_sub(EPACode,3,5),
                         str_sub(EPACode,6,9), sep = "-"),
         Monitor.ID = as.factor(sprintf("%02d-%03d-%04d-%02d",
                                     as.numeric(str_sub(EPACode,1,2)),
                                     as.numeric(str_sub(EPACode,3,5)),
                                     as.numeric(str_sub(EPACode,6,9)),
                                     POC))) %>% 
  select(Site.ID, POC, Monitor.ID, Date, everything(), -EPACode) %>% 
  arrange(Site.ID, POC, Date)

save(dt.imprv.raw, file = here('data', 'processed', 'improve-raw.RDa'))

# find the diff bw spec & improve
monitor.spec <- dt.spec.w %>% distinct(Monitor.ID)
monitor.imprv <- dt.imprv.raw %>% distinct(Monitor.ID) 
monitor.diff <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID) %>% 
  as.data.frame() # imrove has 39 Monitor.ID that spec does not have
colnames(monitor.diff) <- 'Monitor.ID'

dt.new <- merge(dt.imprv.raw, monitor.diff)
dt.comp.w <- rbind(dt.spec.w, dt.new) %>% 
  arrange(Site.ID, POC, Date)

save(dt.comp.w, file = here('data', 'processed', 'comp-wide.RDa'))
monitor.comp <- dt.comp.w %>% distinct(Monitor.ID) #698
site.comp <- dt.comp.w %>% distinct(Site.ID) #574
```

```{r CSN Data cleaning}
# EC 88307 -> TOT
# OC 88320 -> TOR
dt.csn.raw = data.frame()
for (i in seq(2000,2008,1)){
  dt0 <- read.delim(here('data','raw','csn',paste0('csn_',i,'.txt')), sep = ',')
  dt.csn.raw <- rbind(dt.csn.raw, dt0)
}
colnames(dt.csn.raw) <- colnames(dt.csn.raw) %>% str_remove("f.Value")

dt.csn.raw <- dt.csn.raw %>% 
  arrange(EPACode, POC, Date)

# correct EPACode (Site.ID)
dt.csn.raw <- dt.csn.raw %>% 
  mutate(EPACode = str_pad(EPACode, 9, pad = "0"))%>% 
  filter(# remove non-CONUS States
    !str_sub(EPACode,1,2) %in% c('02', '15') & str_sub(EPACode,1,2) < '60'
    ) %>% 
  mutate(Date = mdy(Date),
         Site.ID = paste(str_sub(EPACode,1,2), str_sub(EPACode,3,5),
                         str_sub(EPACode,6,9), sep = "-"),
         Monitor.ID = as.factor(sprintf("%02d-%03d-%04d-%02d",
                                     as.numeric(str_sub(EPACode,1,2)),
                                     as.numeric(str_sub(EPACode,3,5)),
                                     as.numeric(str_sub(EPACode,6,9)),
                                     POC))) %>% 
  select(Site.ID, POC, Monitor.ID, Date, everything(), -EPACode) %>% 
  arrange(Site.ID, POC, Date)

save(dt.csn.raw, file = here('data', 'processed', 'csn-raw.RDa'))

monitor.spec <- dt.spec.w %>% distinct(Monitor.ID)
monitor.csn <- dt.csn.raw %>% distinct(Monitor.ID) 
monitor.diff <- setdiff(monitor.csn$Monitor.ID, monitor.spec$Monitor.ID) %>% 
  as.data.frame()
# no difference between two dataset!
# csn dataset is not adding any new information
```

```{r EPA AQS Process}
dt.comp.c <- dt.comp.w[complete.cases(dt.comp.w),]
monitor.comp <- dt.comp.c %>% distinct(Monitor.ID) # 698 -> 530
site.comp <- dt.comp.c %>% distinct(Site.ID) #574 -> 486

dt.comp.sel <- Air_Daily_Process(dt = dt.comp.c, d = 4, m = 9, y = 4)

# pick the POC with larger number of measurement
site.POC.larger <- dt.comp.sel %>% 
  group_by(Site.ID, POC) %>% 
  summarise(n = n()) %>% 
  group_by(Site.ID) %>% 
  filter(n == max (n)) %>% 
  select(Site.ID, POC)

dt.comp.sel <- merge(dt.comp.sel, site.POC.larger) 
monitor.comp <- dt.comp.sel %>% distinct(Monitor.ID) # 698 -> 530 -> 346
site.comp <- dt.comp.sel %>% distinct(Site.ID) #574 -> 486 -> 346
dt.comp.sel$POC <- dt.comp.sel$Monitor.ID <- NULL
save(dt.comp.sel, file = here('data', 'processed', 'comp-selected.RDa'))
```

```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
load(here('data', 'processed', 'comp-selected.RDa'))

dt.air <- dt.comp.sel %>% 
  pivot_longer(cols = AS:OC,
               names_to = "Parameter.Symbol",
               values_to = "Value") %>% 
  arrange(Site.ID, Parameter.Symbol, Date)

site.para <- dt.air %>% 
  distinct(Site.ID, Parameter.Symbol)

smooth.out <- mapply(smoothed.yr, site.para$Site.ID, site.para$Parameter.Symbol)
para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
                           Parameter.Symbol=unlist(smooth.out[2,]),
                           Date=unlist(smooth.out[3,]), 
                           para.1yr=unlist(smooth.out[4,]))

dt.comp.1yr <- para.monthly %>% 
  mutate(Year = floor(Date -0.01),
         Month = (Date - Year)*12) %>% 
  select(-Date) %>% 
  pivot_wider(names_sort = T,
              names_from = c(Parameter.Symbol),
              values_from = c(para.1yr)) %>% 
  arrange(Site.ID, Year, Month)

save(dt.comp.1yr, file = here('data', 'processed', 'comp-1yr.RDa'))

site.comp <- dt.comp.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 346
  merge(aqs.sites)
save(site.comp, file = here('data', 'processed', 'site-comp.RDa'))

site.comp %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())
#Location.Setting  n
#                  2			
#RURAL	           202			
#SUBURBAN	         69			
#URBAN	           73	
```

### 2021-01-03 code/data-processors/air-data-processor-function.R

@@ -1,0 +1,42 @@
+### Author: Fatemeh Kazemi - 01-01-2021
+
+library(tidyverse)
+library(lubridate)
+
+# Air_Daily_Process function
+### Function *** Air_Daily_Process ***
+### Processes Daily data 
+### Chooses a subset of monitors on the basis of: 
+### ... A minimum for number of :
+### ... Daily measurements per Month,
+### ... Months with minimum daily measurements per Year
+### ... Years with minimum Month and Day
+
+# Function Arguments: 
+# d : minimum number of days per month
+# m : minimum numbers of month per year
+# y : minimum numbers of years per period
+# Packages: tidyverse; data.table
+
+Air_Daily_Process <- function(dt, d, m, y) {
+  # identify qualified monitors and merged it with dt (daily dataset)
+  dt.c <- dt %>%
+    mutate(Year = year(Date),
+           Month = month(Date)) %>% 
+    group_by(Monitor.ID, Year, Month) %>%
+    summarize(n_Day = length(unique(Date))) %>%
+    filter(n_Day >= d
+    ) %>% #monitors wt at least -d- days each month 
+    group_by(Monitor.ID, Year) %>%
+    summarize(n_Month = length(unique(Month))) %>%
+    filter(n_Month >= m
+    ) %>% #monitors wt at least -m- month each year
+    group_by(Monitor.ID) %>%
+    summarize(n_Year = length(unique(Year))) %>%
+    filter(n_Year >= y
+    ) %>% #monitors wt at least -y- year in start-end period
+    merge(dt
+    ) %>% 
+    select(-n_Year)
+  return(dt.c)
+}

### 2021-01-03 code/data-processors/air-data-smooth-mvavg-function.R

@@ -1,0 +1,69 @@
+### Author:  Sonja Greven, 17 June 2009 
+### Modified: Fatemeh Kazemi, 27 Dec 2020
+
+library(tidyverse)
+library(lubridate)
+library(mgcv)
+
+# Smooth
+# dt.air: contains air quality data by monitor site and day
+#    Site.ID:
+#    Parameter.Symbol
+#    Value:
+#    Date:
+
+#dt <-  dt.air
+#si  <-  unique(sort(dt.air$Site.ID))
+#pr <-  unique(sort(dt.air$Parameter.Symbol))
+#si <- "01-073-0023"
+#pr <- "AS"
+#c <- 1
+
+smoothed.yr <- function(si, pr){ 
+
+    dt <- dt.air %>% 
+    filter(Site.ID == si & Parameter.Symbol == pr) %>%
+    select(Site.ID, Parameter.Symbol, Value, Date) %>% 
+    mutate(year = year(Date),
+           month = month(Date),
+           date2 = as.numeric(as.Date(Date))) %>% 
+    arrange(date2)
+  
+  gaps <- dt$date2[2:nrow(dt)]-dt$date2[1:(nrow(dt)-1)]
+  cuts <- c(0,which(gaps>90),nrow(dt))  #cut data into coherent bits with gaps <=90 days
+  n.bits <- length(cuts)-1
+  rows <- max(dt$year+dt$month/12)*12-12*min(dt$year+dt$month/12)+1
+  results <- data.frame(Site.ID=rep(si,rows), Parameter.Symbol=rep(pr,rows), 
+                        Date=rep(NA,rows),mvavg.1yr=rep(NA,rows))
+  rows <- 0
+
+  for (c in 1:n.bits){
+    dt1 <- dt[(cuts[c]+1):cuts[c+1],]
+    if (nrow(dt1)>10){ #only try smoothing with at least 11 values
+      df <- ceiling((max(dt1$date2)- min(dt1$date2))/365*4) #4 df per year
+      if (df<6){print(paste("Site.ID: ",si,", Para: ",pr,", c: ",c,", df: ",df,sep=""))}
+      gres <- gam(Value~s(date2,fx=TRUE,k=df+1),data=dt1)
+      
+      pred.data <- as.data.frame(seq(min(dt1$date2),max(dt1$date2)))
+      colnames(pred.data) <- c("date2")
+      pred.data$smooth <- predict(gres,pred.data)
+      pred.data$year <- year(as.Date(pred.data$date2, origin = "1970-01-01"))
[…]

### 2021-01-03 code/data-processors/epa-air-data-download-function.R

@@ -1,0 +1,56 @@
+### Author: Fatemeh Kazemi - 01-01-2021
+
+# EPA_AQS_download Function
+# Function Arguments: 
+# period : hourly/daily
+# Index : list of file index to download
+# start : start year 
+# end : end year
+# Code.Sym : list of parameters code and symbol ...
+# ... ~Parameter.Code ~Parameter.Symbol
+# Packages: tidyverse, lubridate
+
+library(tidyverse)
+library(lubridate)
+
+EPA_AQS_download <- function(period, Index, start, end,
+                             Code.Sym) {
+  dt = data.frame()
+  for (i in Index) {
+    for (t in start:end) {
+      temp <- tempfile()
+      download.file(paste("https://aqs.epa.gov/aqsweb/airdata/",period,"_",i,"_",t
+                          ,".zip",sep = ""),temp)
+      dt0 <- read.csv(unz(temp, paste(period,"_",i,"_",t,".csv", sep = ""))) %>% 
+        filter(Parameter.Code %in% Code.Sym$Parameter.Code) %>% 
+        mutate(State.Code = as.factor(State.Code))
+      dt <- rbind(dt, dt0)
+    }
+  }
+  
+  dt <- dt %>% 
+    filter(!State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
+                              "Country Of Mexico","Canada") #remove nonCONUS
+    ) %>%
+    transmute(
+      #unique ID for each Site: ss-ccc-nnnn
+      Site.ID = as.factor(sprintf("%02d-%03d-%04d",
+                                  as.numeric(as.character(State.Code)),
+                                  County.Code, Site.Num)),
+      POC,
+      #unique ID for each Monitor: ss-ccc-nnnn-pp
+      Monitor.ID = as.factor(sprintf("%02d-%03d-%04d-%02d",
+                                     as.numeric(as.character(State.Code)),
+                                     County.Code, Site.Num, POC)),
+      Parameter.Code,
+      Date = ymd(Date.Local),
+      Arithmetic.Mean,
+    ) %>%
+    merge(Code.Sym
+    ) %>%
+    select(Site.ID, POC, Monitor.ID, Parameter.Symbol, everything()) %>% 
+    arrange(Site.ID, POC, Parameter.Symbol, Date) 
+  return(dt)
+}
+
+

### 2021-01-03 code/data-processors/air-data-processor.Rmd
Update air-data-processor.Rmd
Added Cross-walk files

@@
 library(here)
-library(lubridate)
-library(naniar) # for replacing -999 with NA
+#library(lubridate)
+#library(naniar) # for replacing -999 with NA
 ```
@@
 load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\state-region.RDa')
+load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\site-zip.RDa')
 ```
@@
     ) %>% 
-  merge(state.region[, c("State", "Region.IV")])
+  merge(dt.state.region[, c("State", "Region.IV")])
 
@@
 ```
+
+```{r Zipcodes in x-mile bufferzone of Monitoring Sites}
+load(here('data', 'processed', 'comp-1yr.RDa'))
+
+dt.comp <- dt.comp.1yr %>% 
+  select(Site.ID, Year, Month) %>% 
+  mutate(psuedo = 100)
+
+dt.comp <- dt.comp %>% 
+  inner_join(dt.site.zip, by = c("Site.ID", "Year")) %>% 
+  arrange(Zip.Code, Year, Dist)
+
+# pick the site with shorter distance
+site.dist.shorter <- dt.comp %>% 
+  group_by(Zip.Code, Year) %>% 
+  filter(Dist == min (Dist)) %>% 
+  arrange(Zip.Code, Year)
+
+dt.comp.site.zip.bz6 <- dt.comp %>% 
+  filter(Dist <= 6)
+dt.comp.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4351
+dt.comp.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #286
+
+dt.comp.site.zip.bz12  <- dt.comp %>% 
+  filter(Dist <= 12)
+dt.comp.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8454
+dt.comp.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #331
+
+dt.comp.site.zip.bz24  <- dt.comp %>% 
+  filter(Dist <= 24)
+dt.comp.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15856
+dt.comp.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #344
+```
+
+```{r}
+save(dt.comp.cms, file = here('data', 'processed', 'comp-cms.RDa'))
+
+```

### 2021-01-03 code/data-processors/air-data-processor.Rmd
create 6, 12, 24 mile buffers around sites

--- 2021-01-03 code/data-processors/air-data-processor.Rmd
@@
 
-aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
+dt.aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
   filter(
@@
     ) %>% 
-  merge(state.region[, c("State", "Region.IV")])
+  merge(dt.state.region[, c("State", "Region.IV")])
 
-save(aqs.sites, file = here('data', 'processed', 'aqs-sites.RDa'))
+save(dt.aqs.sites, file = here('data', 'processed', 'aqs-sites.RDa'))
 
-aqs.sites %>% 
+dt.aqs.sites %>% 
   group_by(Location.Setting) %>% 
@@
 ### EC
-carbon.ec <- dt.spec.raw %>% 
+dt.carbon.ec <- dt.spec.raw %>% 
   select(Site.ID, POC, Monitor.ID, Parameter.Symbol, Date, Arithmetic.Mean) %>% 
@@
 
-ec.c<- carbon.ec[complete.cases(carbon.ec),] #405 simultaneous TOR & TOT
+ec.c<- dt.carbon.ec[complete.cases(dt.carbon.ec),] #405 simultaneous TOR & TOT
 ec.c %>% group_by(Site.ID) %>% 
@@
 ### OC
-carbon.ec <- dt.spec.raw %>% 
+dt.carbon.oc <- dt.spec.raw %>% 
   select(Site.ID, POC, Monitor.ID, Parameter.Symbol, Date, Arithmetic.Mean) %>% 
@@
 
-oc.c<- carbon.oc[complete.cases(carbon.oc),] #405 simultaneous TOR & TOT
+oc.c<- dt.carbon.oc[complete.cases(dt.carbon.oc),] #405 simultaneous TOR & TOT
 oc.c %>% group_by(Site.ID) %>% 
@@
 
-site.comp <- dt.comp.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 346
-  merge(aqs.sites)
-save(site.comp, file = here('data', 'processed', 'site-comp.RDa'))
+dt.site.comp <- dt.comp.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 346
+  merge(dt.aqs.sites)
+save(dt.site.comp, file = here('data', 'processed', 'site-comp.RDa'))
 
-site.comp %>% 
+dt.site.comp %>% 
   group_by(Location.Setting) %>% 
@@
 ```
+
+```{r Zipcodes in x-mile bufferzone of Monitoring Sites}
+load(here('data', 'processed', 'comp-1yr.RDa'))
+
+dt.comp <- dt.comp.1yr %>% 
+  select(Site.ID, Year, Month) %>% 
+  mutate(psuedo = 100)
+
+# joining zipcodes to monitoring sites
+dt.comp <- dt.comp %>% 
+  inner_join(dt.site.zip, by = c("Site.ID", "Year")) %>% 
+  arrange(Zip.Code, Year, Dist)
+
+# pick the site with shorter distance to zipcode centroeid
+dt.site.dist.shorter <- dt.comp %>% 
+  group_by(Zip.Code, Year) %>% 
+  filter(Dist == min (Dist)) %>% 
+  arrange(Zip.Code, Year) %>% 
+  as.data.frame()
+
+# 6-mile bufferzone around monitoring site
+dt.comp.site.zip.bz6 <- dt.site.dist.shorter %>% 
+  filter(Dist <= 6) %>% 
+  select(Zip.Code, Year, Month, Site.ID, psuedo)
+
+save(dt.comp.site.zip.bz6, file = here('data', 'processed', 'comp-site-zip-bz6.RDa'))
+write.csv(dt.comp.site.zip.bz6, file = here('data', 'processed', 'comp-site-zip-bz6.csv'))
+
+# Count number of zipcodes and sites
+dt.comp.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4351
+dt.comp.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #277
+
+# 12-mile bufferzone around monitoring site
+dt.comp.site.zip.bz12  <- dt.site.dist.shorter %>% 
+  filter(Dist <= 12) %>% 
+  select(Zip.Code, Year, Month, Site.ID, psuedo)
+
+save(dt.comp.site.zip.bz12, file = here('data', 'processed', 'comp-site-zip-bz12.RDa'))
+write.csv(dt.comp.site.zip.bz12, file = here('data', 'processed', 'comp-site-zip-bz12.csv'))
+
+# Count number of zipcodes and sites
+dt.comp.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8454
+dt.comp.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #328
+
+# 24-mile bufferzone around monitoring site
+dt.comp.site.zip.bz24  <- dt.site.dist.shorter %>% 
+  filter(Dist <= 24) %>% 
+  select(Zip.Code, Year, Month, Site.ID, psuedo)
+
+save(dt.comp.site.zip.bz24, file = here('data', 'processed', 'comp-site-zip-bz24.RDa'))
+write.csv(dt.comp.site.zip.bz24, file = here('data', 'processed', 'comp-site-zip-bz24.csv'))
+
+# Count number of zipcodes and sites
+dt.comp.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15856
+dt.comp.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #341
+```

### 2021-01-10 code/data-analysis/factor-analysis.Rmd
Double checked Air quality data processing

@@
 ```{r Load datasets}
-load(here('data','processed', 'comp-sel.RDa'))
+load(here('data','processed', 'pmc-selected.RDa'))
 ```
@@
 # All eligible monitors
-fit <- factanal(dt.comp.sel %>% select(AS:OC), 8, rotation="varimax")
+fit <- factanal(dt.pmc.sel %>% select(AS:OC), 8, rotation="varimax")
 factor.loadings <- rbind(fit$loadings)
@@
 
-factor.scores <- factor.scores(dt.comp.sel %>% select(AS:OC), fit)
-dt.comp.fac <- cbind(dt.comp.sel, factor.scores$scores)
-save(dt.comp.fac, file = here('data', 'processed', 'comp-fac.RDa'))
+factor.scores <- factor.scores(dt.pmc.sel %>% select(AS:OC), fit)
+dt.pmc.fac <- cbind(dt.pmc.sel, factor.scores$scores)
+save(dt.pmc.fac, file = here('data', 'processed', 'pmc-fac.RDa'))
 
 # Removing EC from factor analysis
-fit <- factanal(dt.comp.sel %>% select(AS:ZN, OC), 8, rotation="varimax")
+fit <- factanal(dt.pmc.sel %>% select(AS:ZN, OC), 8, rotation="varimax")
 factor.loadings.ex.ec <- rbind(fit$loadings)
@@
 
-factor.scores <- factor.scores(dt.comp.sel %>% select(AS:ZN, OC), fit)
-dt.comp.fac.ex.ec <- cbind(dt.comp.sel, factor.scores$scores)
-save(dt.comp.fac.ex.ec, file = here('data', 'processed', 'comp-fac-ex-ec.RDa'))
+factor.scores <- factor.scores(dt.pmc.sel %>% select(AS:ZN, OC), fit)
+dt.pmc.fac.ex.ec <- cbind(dt.pmc.sel, factor.scores$scores)
+save(dt.pmc.fac.ex.ec, file = here('data', 'processed', 'pmc-fac-ex-ec.RDa'))
 ```

### 2021-01-10 code/data-processors/air-data-processor.Rmd
Double checked Air quality data processing

@@
   (2) Downloads and cleans PM2.5 Speciation data measured by EPA
-  (3) Cleans PM2.5 component data - Imrpove Network
-  (4) Cleans PM2.5 components data - CSN Network
+      i. https://aqs.epa.gov/aqsweb/airdata/download_files.html#Daily
+  (3) Cleans PM2.5 Components data - IMPROVE Network
+      i. http://views.cira.colostate.edu/fed/QueryWizard/
+  (4) Cleans PM2.5 Components data - CSN Network
+      i. http://views.cira.colostate.edu/fed/QueryWizard/
   (5) Combines all available PM2.5 Components data
   (6) Choose a subset of monitors on the basis of data availability
-  (7) Smooth data with 4df per year to fill small gaps
-      i. Do not smooth over more than 90 days of missing data
-      ii. Divide data into coherent pieces instead
-  (8) Calculates yearly average of PM components by site and month
+      i. 4days - 9month- 4years
+  (7) Smooths data with 4df per year to fill small gaps
+      i.Does not smooth over more than 90 days of missing data
+      ii. Divides data into coherent pieces instead
+  (8) Calculates yearly average of PM2.5 Comonents by site and month
       i. Require at least 350 values to compute yearly average from smoothed data
+  (9) Uses cross-walk files bw Sites and Zipcodes to assign the measurements from
+      Sites to the Zipcodes in their x-mile bufferzone
+ (10) Merge it with CMS data (on NEU Cluster) to find the Sites which have
+      population living in their x-mile bufferzone
+ (11) Runs Factor Analysis (another Rm file) for the subset of Sites with population
+      living round them (Sites identified in Step10)
+
+### Note:
+  1. In data merged with CMS, bufferzone is 12-mile unless specified
 
@@
 library(here)
-#library(lubridate)
-#library(naniar) # for replacing -999 with NA
+library(lubridate)
+library(naniar) # for replacing -999 with NA
 ```
@@
 ```{r EPA AQS Data Download}
-dt.spec.raw <- EPA_AQS_download (period = "daily", Index = "SPEC",
+dt.spec.raw <- EPA.AQS.download (period = "daily", Index = "SPEC",
                         start = 2000, end = 2008, 
@@
 save(dt.spec.raw, file = here('data', 'processed', 'spec-raw.RDa'))
+#Monitor.ID: Site.ID-POC
 ```
@@
 dt.carbon.ec <- dt.spec.raw %>% 
-  select(Site.ID, POC, Monitor.ID, Parameter.Symbol, Date, Arithmetic.Mean) %>% 
+  select(-Parameter.Code) %>% 
   pivot_wider(names_sort = T,
@@
 ec.c %>% group_by(Site.ID) %>% 
-  summarise(n = n()) # 11 Sites ~40 each
+  summarise(n = n()) # 11 Sites ~ 33-40 each
 
-summary(lm(EC.TOR ~ EC.TOT, ec.c))
-# TOR = 1.182 * TOT + 0.087 Adj.R2 = 0.862
+summary(lm(EC.TOT ~ EC.TOR, ec.c))
+# TOT = 0.730 * TOR + 0.037 Adj.R2 = 0.862
+
+ec.c %>% merge(dt.aqs.sites) %>% 
+  distinct(Site.ID, Location.Setting) %>% 
+  group_by(Location.Setting) %>% 
+  summarise(n = n()) # > Urban and Suburban
 
@@
 dt.carbon.oc <- dt.spec.raw %>% 
-  select(Site.ID, POC, Monitor.ID, Parameter.Symbol, Date, Arithmetic.Mean) %>% 
+  select(-Parameter.Code) %>% 
   pivot_wider(names_sort = T,
@@
               values_from = c(Arithmetic.Mean)) %>% 
-  arrange(Site.ID, POC, Date.Local) %>%
+  arrange(Site.ID, POC, Date) %>%
   select(Site.ID, POC, Monitor.ID, OC.TOR, OC.TOT)
@@
 oc.c %>% group_by(Site.ID) %>% 
-  summarise(n = n())
+  summarise(n = n()) # 11 Sites ~ 33-40 each
 
-summary(lm(OC.TOR ~ OC.TOT, oc.c))
-# TOR = 0.917 * TOT + 0.579 Adj.R2 = 0.824
+summary(lm(OC.TOT ~ OC.TOR, oc.c))
+# TOT = 0.899 * TOR + 0.167 Adj.R2 = 0.824
+
+oc.c %>% merge(dt.aqs.sites) %>% 
+  distinct(Site.ID, Location.Setting) %>% 
+  group_by(Location.Setting) %>% 
+  summarise(n = n()) # > Urban and Suburban
+
+# For both EC & OC the sites with both methods (TOR & TOT) are in Urban and Sub...
+# ...Urban area > We use the TOT since most of the Urbans use TOT
 ```
@@
               values_from = c(Arithmetic.Mean)) %>% 
-  # for 405 cases with two methods use TOR for EC & OC
-  mutate(EC = ifelse(!is.na(EC.TOR), EC.TOR, EC.TOT), 
-         OC = ifelse(!is.na(OC.TOR), OC.TOR, OC.TOT)) %>% 
+  # for 405 cases with two methods for EC and OC (TOR & TOT), use TOT 
+  mutate(EC = ifelse(!is.na(EC.TOT), EC.TOT, EC.TOR), 
+         OC = ifelse(!is.na(OC.TOT), OC.TOT, OC.TOR)) %>% 
   select(-EC.TOR, -EC.TOT, -OC.TOR, -OC.TOT) %>% 
@@
 
-```{r Improve Data cleaning}
+```{r IMPROVE Data cleaning}
 # EC 88307 -> TOT
@@
 
-# correct EPACode (Site.ID)
 dt.imprv.raw <- dt.imprv.raw %>% 
-  filter(!EPACode == '.') %>% 
+  filter(!EPACode == '.') %>% #correct EPACode (Site.ID)
   mutate(EPACode = str_pad(EPACode, 9, pad = "0"))%>% 
@@
   mutate(Date = mdy(Date),
-         Site.ID = paste(str_sub(EPACode,1,2), str_sub(EPACode,3,5),
-                         str_sub(EPACode,6,9), sep = "-"),
+         Site.ID = as.factor(paste(str_sub(EPACode,1,2), str_sub(EPACode,3,5),
+                         str_sub(EPACode,6,9), sep = "-")),
          Monitor.ID = as.factor(sprintf("%02d-%03d-%04d-%02d",
@@
 
+#remove rows with all components missing
+dt.imprv.raw <- dt.imprv.raw[rowSums(is.na(dt.imprv.raw)) != (ncol(dt.imprv.raw)-4), ]
+
 save(dt.imprv.raw, file = here('data', 'processed', 'improve-raw.RDa'))
@@
 monitor.diff <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID) %>% 
-  as.data.frame() # imrove has 39 Monitor.ID that spec does not have
+  as.data.frame() 
 colnames(monitor.diff) <- 'Monitor.ID'
+# improve has 32 Monitor.ID that spec does not have
+
+site.spec <- dt.spec.w %>% distinct(Site.ID)
+site.imprv <- dt.imprv.raw %>% distinct(Site.ID) 
+site.diff <- setdiff(site.imprv$Site.ID, site.spec$Site.ID) %>% 
+  as.data.frame()
+colnames(site.diff) <- 'Site.ID'
+# improve has 28 Site.ID that spec does not have
 
 dt.new <- merge(dt.imprv.raw, monitor.diff)
-dt.comp.w <- rbind(dt.spec.w, dt.new) %>% 
+dt.pmc.w <- rbind(dt.spec.w, dt.new) %>% 
   arrange(Site.ID, POC, Date)
 
-save(dt.comp.w, file = here('data', 'processed', 'comp-wide.RDa'))
-monitor.comp <- dt.comp.w %>% distinct(Monitor.ID) #698
-site.comp <- dt.comp.w %>% distinct(Site.ID) #574
+save(dt.pmc.w, file = here('data', 'processed', 'pmc-wide.RDa'))
+monitor.pmc <- dt.pmc.w %>% distinct(Monitor.ID) #691
+site.pmc <- dt.pmc.w %>% distinct(Site.ID) #574
 ```
@@
 
-# correct EPACode (Site.ID)
 dt.csn.raw <- dt.csn.raw %>% 
+  #correct EPACode (eq. to Site.ID)
   mutate(EPACode = str_pad(EPACode, 9, pad = "0"))%>% 
@@
 # no difference between two dataset!
-# csn dataset is not adding any new information
+# csn is not adding any new information to spec
 ```
 
-```{r EPA AQS Process}
-dt.comp.c <- dt.comp.w[complete.cases(dt.comp.w),]
-monitor.comp <- dt.comp.c %>% distinct(Monitor.ID) # 698 -> 530
-site.comp <- dt.comp.c %>% distinct(Site.ID) #574 -> 486
+```{r label Sites based on the Carbon Method they used - TOR/TOT}
+#speciation sites
+dt.site.carbon.method <- dt.spec.raw %>% 
+  select(-Parameter.Code) %>% 
+  pivot_wider(names_from = c(Parameter.Symbol),
+              values_from = c(Arithmetic.Mean)) %>% 
+  filter(!is.na(EC.TOR) | !is.na(EC.TOT)) %>% 
+  mutate(Method = ifelse(!is.na(EC.TOR), "TOR", "TOT")) %>% 
+  select(Site.ID, Method) %>% 
+  arrange(Site.ID, desc(Method)) %>% #if site has both > keep TOT
+  distinct(Site.ID, .keep_all = T)
 
-dt.comp.sel <- Air_Daily_Process(dt = dt.comp.c, d = 4, m = 9, y = 4)
+#improve sites added to speciation sites
+dt.site.carbon.method <- site.diff %>% 
+  mutate(Method = "EC.TOT-OC.TOR") %>% 
+  add_row(dt.site.carbon.method) %>% 
+  arrange(as.character(Site.ID))
 
-# pick the POC with larger number of measurement
-site.POC.larger <- dt.comp.sel %>% 
+save(dt.site.carbon.method, file = here('data', 'processed', 'site-carbon-method.RDa'))
+
+dt.site.carbon.method %>% group_by(Method) %>% 
+  summarise(n = n())
+```
+
+```{r Air quality data Process}
+map(dt.pmc.w, ~sum(is.na(.)))
+
+#sites with measurements for all components - spec & improve
+dt.pmc.c <- dt.pmc.w[complete.cases(dt.pmc.w),] 
+monitor.pmc <- dt.pmc.c %>% distinct(Monitor.ID) # 698 -> 530 
+site.pmc <- dt.pmc.c %>% distinct(Site.ID) #574 -> 486
+
+# Find sites with at least 4day, 9month and 4 year
+# Using Air_Daily_Process function
+dt.pmc.sel <- Air.Daily.Process(dt = dt.pmc.c, d = 4, m = 9, y = 4)
+
+# POC: Parameter Occurrence Code ...
+# ... more than one instrument measured a component at one site
+# pick the POC(instrument) with larger number of measurements
+site.POC.larger <- dt.pmc.sel %>% 
   group_by(Site.ID, POC) %>% 
@@
 
-dt.comp.sel <- merge(dt.comp.sel, site.POC.larger) 
-monitor.comp <- dt.comp.sel %>% distinct(Monitor.ID) # 698 -> 530 -> 346
-site.comp <- dt.comp.sel %>% distinct(Site.ID) #574 -> 486 -> 346
-dt.comp.sel$POC <- dt.comp.sel$Monitor.ID <- NULL
-save(dt.comp.sel, file = here('data', 'processed', 'comp-selected.RDa'))
+dt.pmc.sel <- merge(dt.pmc.sel, site.POC.larger) 
+monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 698 -> 530 -> 346
+site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 486 -> 346
+dt.pmc.sel$POC <- dt.pmc.sel$Monitor.ID <- NULL
+save(dt.pmc.sel, file = here('data', 'processed', 'pmc-selected.RDa'))
 ```
@@
 ```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
-load(here('data', 'processed', 'comp-selected.RDa'))
-
-dt.air <- dt.comp.sel %>% 
+dt.air <- dt.pmc.sel %>% 
   pivot_longer(cols = AS:OC,
@@
 
-smooth.out <- mapply(smoothed.yr, site.para$Site.ID, site.para$Parameter.Symbol)
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, site.para$Site.ID, site.para$Parameter.Symbol)
 para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
@@
 
-dt.comp.1yr <- para.monthly %>% 
+dt.pmc.1yr <- para.monthly %>% 
   mutate(Year = floor(Date -0.01),
@@
 
-save(dt.comp.1yr, file = here('data', 'processed', 'comp-1yr.RDa'))
+save(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.RDa'))
+write.csv(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.csv'))
 
-dt.site.comp <- dt.comp.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 346
+dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 346
   merge(dt.aqs.sites)
-save(dt.site.comp, file = here('data', 'processed', 'site-comp.RDa'))
+save(dt.site.pmc, file = here('data', 'processed', 'site-pmc.RDa'))
 
-dt.site.comp %>% 
+dt.site.pmc %>% 
   group_by(Location.Setting) %>% 
@@
 #URBAN	           73
+
+dt.pmc.1yr %>% 
+  distinct(Site.ID, Year) %>% 
+  group_by(Site.ID) %>% 
+  summarise(n = n()) %>% filter(n > 3) %>% 
+  nrow() #346: all  #339: with 4+ years
 ```
@@
 ```{r Zipcodes in x-mile bufferzone of Monitoring Sites}
-load(here('data', 'processed', 'comp-1yr.RDa'))
-
-dt.comp <- dt.comp.1yr %>% 
+dt.pmc <- dt.pmc.1yr %>% 
   select(Site.ID, Year, Month) %>% 
@@
 # joining zipcodes to monitoring sites
-dt.comp <- dt.comp %>% 
+dt.pmc <- dt.pmc %>% 
   inner_join(dt.site.zip, by = c("Site.ID", "Year")) %>% 
@@
 
-# pick the site with shorter distance to zipcode centroeid
-dt.site.dist.shorter <- dt.comp %>% 
+# for each zipcode, pick the site with shorter distance to zipcode centroeid
+dt.site.dist.shorter <- dt.pmc %>% 
   group_by(Zip.Code, Year) %>% 
@@
 # 6-mile bufferzone around monitoring site
-dt.comp.site.zip.bz6 <- dt.site.dist.shorter %>% 
+dt.pmc.site.zip.bz6 <- dt.site.dist.shorter %>% 
   filter(Dist <= 6) %>% 
@@
 
-save(dt.comp.site.zip.bz6, file = here('data', 'processed', 'comp-site-zip-bz6.RDa'))
-write.csv(dt.comp.site.zip.bz6, file = here('data', 'processed', 'comp-site-zip-bz6.csv'))
+save(dt.pmc.site.zip.bz6, file = here('data', 'processed', 'pmc-site-zip-bz6.RDa'))
+write.csv(dt.pmc.site.zip.bz6, file = here('data', 'processed', 'pmc-site-zip-bz6.csv'))
 
 # Count number of zipcodes and sites
-dt.comp.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4351
-dt.comp.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #277
+dt.pmc.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4351
+dt.pmc.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #346 > 277
 
 # 12-mile bufferzone around monitoring site
-dt.comp.site.zip.bz12  <- dt.site.dist.shorter %>% 
+dt.pmc.site.zip.bz12  <- dt.site.dist.shorter %>% 
   filter(Dist <= 12) %>% 
@@
 
-save(dt.comp.site.zip.bz12, file = here('data', 'processed', 'comp-site-zip-bz12.RDa'))
-write.csv(dt.comp.site.zip.bz12, file = here('data', 'processed', 'comp-site-zip-bz12.csv'))
+save(dt.pmc.site.zip.bz12, file = here('data', 'processed', 'pmc-site-zip-bz12.RDa'))
+write.csv(dt.pmc.site.zip.bz12, file = here('data', 'processed', 'pmc-site-zip-bz12.csv'))
 
 # Count number of zipcodes and sites
-dt.comp.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8454
-dt.comp.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #328
+dt.pmc.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8454
+dt.pmc.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #346 > 328
 
 # 24-mile bufferzone around monitoring site
-dt.comp.site.zip.bz24  <- dt.site.dist.shorter %>% 
+dt.pmc.site.zip.bz24  <- dt.site.dist.shorter %>% 
   filter(Dist <= 24) %>% 
@@
 
-save(dt.comp.site.zip.bz24, file = here('data', 'processed', 'comp-site-zip-bz24.RDa'))
-write.csv(dt.comp.site.zip.bz24, file = here('data', 'processed', 'comp-site-zip-bz24.csv'))
+save(dt.pmc.site.zip.bz24, file = here('data', 'processed', 'pmc-site-zip-bz24.RDa'))
+write.csv(dt.pmc.site.zip.bz24, file = here('data', 'processed', 'pmc-site-zip-bz24.csv'))
 
 # Count number of zipcodes and sites
-dt.comp.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15856
-dt.comp.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #341
+dt.pmc.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15856
+dt.pmc.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #346 > 341
+
+# pmc-site-zip-bz12.csv was uploaded on NEU Cluster to be merged with CMS data
+# It has 328 sites with 8454 zipcodes around them
 ```
+
+```{r Post mergeing with CMS Data}
+dt.site.ndi.bz12 <- read.csv(here('data', 'raw', 'site_pmc_ndi_bz12.csv')) %>% 
+  rename(Site.ID = Site_ID)
+
+# 325 out of 328 sites have population living in their 12-mile bufferzone
+dt.site.ndi.bz12 %>% 
+  group_by(Site.ID) %>% 
+  summarise(n = n()) %>% filter(n > 0) %>% 
+  nrow() # 325 > 317 > 316 > 308: with 4+ years
+
+# TOT/TOR Method in different location.set
+dt.site.ndi.bz12 %>% 
+  distinct(Site.ID) %>% 
+  left_join(dt.site.carbon.method) %>% 
+  left_join(dt.aqs.sites) %>% 
+  group_by(Location.Setting, Method) %>% 
+  summarise(n = n())
+
+# urban and suburban: TOT >> TOR
+# rural:              TOR >> TOT
+# improve sites only in rural
+
+dt.site.ndi.bz12 %>% 
+  distinct(Site.ID) %>% 
+  left_join(dt.aqs.sites) %>% 
+  group_by(Location.Setting) %>% 
+  summarise(n = n())
+# urban 72
+# suburban 69
+# rural 182
+```

### 2021-01-10 code/data-processors/air-data-processor-function.R

@@ -18,7 +18,7 @@ library(lubridate)
 # y : minimum numbers of years per period
 # Packages: tidyverse; data.table
 
-Air_Daily_Process <- function(dt, d, m, y) {
+Air.Daily.Process <- function(dt, d, m, y) {
   # identify qualified monitors and merged it with dt (daily dataset)
   dt.c <- dt %>%
     mutate(Year = year(Date),

### 2021-01-10 code/data-processors/air-data-smooth-mvavg-function.R

@@ -5,6 +5,10 @@ library(tidyverse)
 library(lubridate)
 library(mgcv)
 
+# Smoothed.Year Function
+# Smooths data with 4df per year to fill small gaps
+# Does not smooth over more than 90 days of missing data
+# Divides data into coherent pieces instead
 # Smooth
 # dt.air: contains air quality data by monitor site and day
 #    Site.ID:
@@ -12,14 +16,7 @@ library(mgcv)
 #    Value:
 #    Date:
 
-#dt <-  dt.air
-#si  <-  unique(sort(dt.air$Site.ID))
-#pr <-  unique(sort(dt.air$Parameter.Symbol))
-#si <- "01-073-0023"
-#pr <- "AS"
-#c <- 1
-
-smoothed.yr <- function(si, pr){ 
+Smoothed.Year <- function(si, pr){ 
 
     dt <- dt.air %>% 
     filter(Site.ID == si & Parameter.Symbol == pr) %>%
@@ -41,7 +38,7 @@ smoothed.yr <- function(si, pr){
     dt1 <- dt[(cuts[c]+1):cuts[c+1],]
     if (nrow(dt1)>10){ #only try smoothing with at least 11 values
       df <- ceiling((max(dt1$date2)- min(dt1$date2))/365*4) #4 df per year
-      if (df<6){print(paste("Site.ID: ",si,", Para: ",pr,", c: ",c,", df: ",df,sep=""))}
+      if (df<4){print(paste("Site.ID: ",si,", Para: ",pr,", c: ",c,", df: ",df,sep=""))}
       gres <- gam(Value~s(date2,fx=TRUE,k=df+1),data=dt1)
       
       pred.data <- as.data.frame(seq(min(dt1$date2),max(dt1$date2)))

### 2021-01-10 code/data-processors/epa-air-data-download-function.R

@@ -13,7 +13,7 @@
 library(tidyverse)
 library(lubridate)
 
-EPA_AQS_download <- function(period, Index, start, end,
+EPA.AQS.download <- function(period, Index, start, end,
                              Code.Sym) {
   dt = data.frame()
   for (i in Index) {

### 2021-01-11 code/data-processors/air-data-processor.Rmd
added daily PM data based on closest zipcode

@@
 load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\state-region.RDa')
-load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\site-zip.RDa')
 ```
@@
 monitor.imprv <- dt.imprv.raw %>% distinct(Monitor.ID) 
-monitor.diff <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID) %>% 
+monitor.diff.imprv <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID) %>% 
   as.data.frame() 
-colnames(monitor.diff) <- 'Monitor.ID'
+colnames(monitor.diff.imprv) <- 'Monitor.ID'
 # improve has 32 Monitor.ID that spec does not have
@@
 site.imprv <- dt.imprv.raw %>% distinct(Site.ID) 
-site.diff <- setdiff(site.imprv$Site.ID, site.spec$Site.ID) %>% 
+site.diff.imprv <- setdiff(site.imprv$Site.ID, site.spec$Site.ID) %>% 
   as.data.frame()
-colnames(site.diff) <- 'Site.ID'
+colnames(site.diff.imprv) <- 'Site.ID'
 # improve has 28 Site.ID that spec does not have
-
-dt.new <- merge(dt.imprv.raw, monitor.diff)
-dt.pmc.w <- rbind(dt.spec.w, dt.new) %>% 
-  arrange(Site.ID, POC, Date)
-
-save(dt.pmc.w, file = here('data', 'processed', 'pmc-wide.RDa'))
-monitor.pmc <- dt.pmc.w %>% distinct(Monitor.ID) #691
-site.pmc <- dt.pmc.w %>% distinct(Site.ID) #574
 ```
@@
 monitor.csn <- dt.csn.raw %>% distinct(Monitor.ID) 
-monitor.diff <- setdiff(monitor.csn$Monitor.ID, monitor.spec$Monitor.ID) %>% 
+monitor.diff.csn <- setdiff(monitor.csn$Monitor.ID, monitor.spec$Monitor.ID) %>% 
   as.data.frame()
@@
 # csn is not adding any new information to spec
+```
+
+```{r add new component data to epa data}
+# Only IMROVE had new data
+# CSN was same as epa
+dt.new <- merge(dt.imprv.raw, monitor.diff.imprv)
+dt.pmc.w <- rbind(dt.spec.w, dt.new) %>% 
+  arrange(Site.ID, POC, Date)
+
+save(dt.pmc.w, file = here('data', 'processed', 'pmc-wide.RDa'))
+monitor.pmc <- dt.pmc.w %>% distinct(Monitor.ID) #691
+site.pmc <- dt.pmc.w %>% distinct(Site.ID) #574
 ```
@@
 #improve sites added to speciation sites
-dt.site.carbon.method <- site.diff %>% 
+dt.site.carbon.method <- site.diff.imprv %>% 
   mutate(Method = "EC.TOT-OC.TOR") %>% 
@@
   summarise(n = n())
+# TOR 167
+# TOT 326
+# EC.TOT-OC.TOR 28
+```
+
+```{r Adding Daily PM data to pmc daily data}
+load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\site-zip-closest-bz12.RDa')
+
+# closest zipcode to each site in each year in 12-mile bufferzone
+dt.site.close.zip.pmc <- site.pmc %>% 
+  merge(dt.site.zip.closest.bz12) %>% 
+  arrange(Site.ID, Year)
+
+save(dt.site.close.zip.pmc, file = here('data', 'processed', 'site-close-zip-pmc.RDa'))
+write.csv(dt.site.close.zip.pmc, file = here('data', 'processed', 'site-close-zip-pmc.csv'))
+
+dt.site.close.zip.pmc %>% distinct(Site.ID) %>% nrow() #560
+# 560 out of 574 sites have zipcodes in their 12-mile buffer
+
+# site-close-zip-pmc.csv was uploaded on NEU Cluster to be merged with daily zipcode level
+# ... PM data.
+
+# daily PM value for each site based on closest zipcode value
+dt.pm.daily <- read.csv(here('data','processed','pm_pmc_daily.csv')) %>% 
+  transmute(Site.ID = Site_ID,
+            Date = mdy(chardate),
+            PM)
+
+dt.pmc.pm.w <- dt.pmc.w %>% 
+  merge(dt.pm.daily)
+
+save(dt.pmc.pm.w, file = here('data', 'processed', 'pmc-pm-wide.RDa'))
 ```
@@
 ```{r Air quality data Process}
-map(dt.pmc.w, ~sum(is.na(.)))
+map(dt.pmc.pm.w, ~sum(is.na(.)))
 
 #sites with measurements for all components - spec & improve
-dt.pmc.c <- dt.pmc.w[complete.cases(dt.pmc.w),] 
-monitor.pmc <- dt.pmc.c %>% distinct(Monitor.ID) # 698 -> 530 
-site.pmc <- dt.pmc.c %>% distinct(Site.ID) #574 -> 486
+dt.pmc.c <- dt.pmc.pm.w[complete.cases(dt.pmc.pm.w),] 
+monitor.pmc <- dt.pmc.c %>% distinct(Monitor.ID) # 698 -> 530  -> 515
+site.pmc <- dt.pmc.c %>% distinct(Site.ID) #574 -> 486 -> 471
 
@@
 dt.pmc.sel <- merge(dt.pmc.sel, site.POC.larger) 
-monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 698 -> 530 -> 346
-site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 486 -> 346
+monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 698 -> 530 -> 346 -> 318
+site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 486 -> 346 -> 318
 dt.pmc.sel$POC <- dt.pmc.sel$Monitor.ID <- NULL
@@
 dt.air <- dt.pmc.sel %>% 
-  pivot_longer(cols = AS:OC,
+  pivot_longer(cols = AS:PM,
                names_to = "Parameter.Symbol",
@@
 
-dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 346
+dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 318
   merge(dt.aqs.sites)
@@
 #                  2			
-#RURAL	           202			
-#SUBURBAN	         69			
-#URBAN	           73
+#RURAL	           177			
+#SUBURBAN	         67			
+#URBAN	           72
 
@@
   summarise(n = n()) %>% filter(n > 3) %>% 
-  nrow() #346: all  #339: with 4+ years
+  nrow() #318: all  #311: with 4+ years
 ```
@@
   mutate(psuedo = 100)
+
+load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\site-zip.RDa')
 
@@
 # Count number of zipcodes and sites
-dt.pmc.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4351
-dt.pmc.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #346 > 277
+dt.pmc.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4253
+dt.pmc.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #318 > 270
 
@@
 # Count number of zipcodes and sites
-dt.pmc.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8454
-dt.pmc.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #346 > 328
+dt.pmc.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8313
+dt.pmc.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #318 > 316
 
@@
 # Count number of zipcodes and sites
-dt.pmc.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15856
-dt.pmc.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #346 > 341
+dt.pmc.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15601
+dt.pmc.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #318 > 317
 

### 2021-01-17 code/data-processors/air-data-processor.Rmd
Added new tests

@@
       i. Require at least 350 values to compute yearly average from smoothed data
-  (9) Uses cross-walk files bw Sites and Zipcodes to assign the measurements from
-      Sites to the Zipcodes in their x-mile bufferzone
+  (9) Uses cross-walk files between Sites and Zipcodes to assign the measurements
+      from Sites to the Zipcodes in their x-mile bufferzone
  (10) Merge it with CMS data (on NEU Cluster) to find the Sites which have
@@
 library(lubridate)
-library(naniar) # for replacing -999 with NA
+#library(naniar) # for replacing -999 with NA
 ```
@@
 ```{r EPA AQS Data Download}
+#Using EPA.AQS.download Function
 dt.spec.raw <- EPA.AQS.download (period = "daily", Index = "SPEC",
@@
                         Code.Sym = Code.to.Sym)
-save(dt.spec.raw, file = here('data', 'processed', 'spec-raw.RDa'))
+save(dt.spec.raw, file = here('data', 'raw', 'spec-raw.RDa'))
 #Monitor.ID: Site.ID-POC
+
+dt.spec.raw %>% distinct(Site.ID) %>% nrow() #546
+dt.spec.raw %>% 
+  mutate(Year = year(Date)) %>% 
+  distinct(Site.ID, Year) %>% 
+  group_by(Year) %>% 
+  summarise(n = n())
+
+dt.test <- Air.Daily.Process(dt = dt.spec.raw, d = 4, m = 9, y = 4)
+
+dt.test2 <- dt.test %>% 
+  select(-Parameter.Code) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(Arithmetic.Mean)) %>% 
+  # for 405 cases with two methods for EC and OC (TOR & TOT), use TOT 
+  mutate(EC = ifelse(!is.na(EC.TOT), EC.TOT, EC.TOR), 
+         OC = ifelse(!is.na(OC.TOT), OC.TOT, OC.TOR)) %>% 
+  select(-EC.TOR, -EC.TOT, -OC.TOR, -OC.TOT) %>% 
+  arrange(Site.ID, POC, Date)
 ```
@@
 
-# For both EC & OC the sites with both methods (TOR & TOT) are in Urban and Sub...
-# ...Urban area > We use the TOT since most of the Urbans use TOT
+# For both EC & OC the sites with both methods (TOR & TOT) are in Urban and ...
+# ...Sub-Urban area > We use the TOT since most of the Urbans use TOT
 ```
@@
 save(dt.spec.w, file = here('data', 'processed', 'spec-wide.RDa'))
+
+dt.spec.w %>% distinct(Monitor.ID) %>% nrow() #659
+dt.spec.w %>% distinct(Site.ID) %>% nrow() #546
 ```
@@
 
-save(dt.imprv.raw, file = here('data', 'processed', 'improve-raw.RDa'))
+save(dt.imprv.raw, file = here('data', 'raw', 'improve-raw.RDa'))
+
+dt.imprv.raw.l <- dt.imprv.raw %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter.Symbol",
+               values_to = "Arithmetic.Mean",
+               values_drop_na = T)
+
+dt.test3 <- Air.Daily.Process(dt = dt.imprv.raw.l, d = 4, m = 9, y = 4)
+
+dt.test4 <- dt.test3 %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(Arithmetic.Mean)) %>% 
+    arrange(Site.ID, POC, Date)
 
@@
 
-save(dt.csn.raw, file = here('data', 'processed', 'csn-raw.RDa'))
+save(dt.csn.raw, file = here('data', 'raw', 'csn-raw.RDa'))
 
@@
 
-```{r add new component data to epa data}
+```{r add new component data to spec data}
 # Only IMROVE had new data
-# CSN was same as epa
+# CSN was same as spec
 dt.new <- merge(dt.imprv.raw, monitor.diff.imprv)
@@
 save(dt.pmc.w, file = here('data', 'processed', 'pmc-wide.RDa'))
-monitor.pmc <- dt.pmc.w %>% distinct(Monitor.ID) #691
-site.pmc <- dt.pmc.w %>% distinct(Site.ID) #574
+
+monitor.pmc <- dt.pmc.w %>% distinct(Monitor.ID) #659 > 691
+site.pmc <- dt.pmc.w %>% distinct(Site.ID) #546 > 574
 ```
@@
 
-dt.site.close.zip.pmc %>% distinct(Site.ID) %>% nrow() #560
+dt.site.close.zip.pmc %>% distinct(Site.ID) %>% nrow() #574 > 560
 # 560 out of 574 sites have zipcodes in their 12-mile buffer
@@
 save(dt.pmc.pm.w, file = here('data', 'processed', 'pmc-pm-wide.RDa'))
+
+dt.pmc.pm.w %>% distinct(Site.ID) %>% nrow() # 574 > 560 > 558
+dt.pmc.pm.w %>% distinct(Monitor.ID) %>% nrow()#691 > 673
+
+dt.pmc.w[complete.cases(dt.pmc.w),] %>% nrow() #264,927
 ```
@@
 #sites with measurements for all components - spec & improve
-dt.pmc.c <- dt.pmc.pm.w[complete.cases(dt.pmc.pm.w),] 
-monitor.pmc <- dt.pmc.c %>% distinct(Monitor.ID) # 698 -> 530  -> 515
-site.pmc <- dt.pmc.c %>% distinct(Site.ID) #574 -> 486 -> 471
+dt.pmc.c <- dt.pmc.pm.w[complete.cases(dt.pmc.pm.w),] #241,624
+monitor.pmc <- dt.pmc.c %>% distinct(Monitor.ID) # 691 > 673 > 515
+site.pmc <- dt.pmc.c %>% distinct(Site.ID) # 574 > 558 > 471
 
 # Find sites with at least 4day, 9month and 4 year
-# Using Air_Daily_Process function
+# Using Air.Daily.Process function
 dt.pmc.sel <- Air.Daily.Process(dt = dt.pmc.c, d = 4, m = 9, y = 4)
+
+monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 691 > 673 > 515 > 331
+site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 558 > 471 > 318
 
@@
 dt.pmc.sel <- merge(dt.pmc.sel, site.POC.larger) 
-monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 698 -> 530 -> 346 -> 318
-site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 486 -> 346 -> 318
+monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 691 > 673 > 515 > 331 > 318
+site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 558 > 471 > 318 > 318
 dt.pmc.sel$POC <- dt.pmc.sel$Monitor.ID <- NULL
@@
   mutate(Year = floor(Date -0.01),
-         Month = (Date - Year)*12) %>% 
+         Month = round((Date - Year)*12)) %>% 
   select(-Date) %>% 
@@
 
-dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 486 -> 346 -> 318
+dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 558 > 471 > 318 > 318
   merge(dt.aqs.sites)
@@
   nrow() #318: all  #311: with 4+ years
+
+check <- dt.pmc.1yr %>% 
+  group_by(Site.ID) %>% 
+  summarise(n = n()) %>% 
+  arrange(n)
+
+summary(check$n)
 ```
@@
 ```{r Zipcodes in x-mile bufferzone of Monitoring Sites}
+# remove components for now to make the dataset smaller
 dt.pmc <- dt.pmc.1yr %>% 
@@
 # pmc-site-zip-bz12.csv was uploaded on NEU Cluster to be merged with CMS data
-# It has 328 sites with 8454 zipcodes around them
+# It has 316 sites with 8313 zipcodes around them
 ```

### 2021-01-17 code/data-processors/air-data-processor-function.R

@@ -23,15 +23,15 @@ Air.Daily.Process <- function(dt, d, m, y) {
   dt.c <- dt %>%
     mutate(Year = year(Date),
            Month = month(Date)) %>% 
-    group_by(Monitor.ID, Year, Month) %>%
+    group_by(Parameter.Symbol, Monitor.ID, Year, Month) %>%
     summarize(n_Day = length(unique(Date))) %>%
     filter(n_Day >= d
     ) %>% #monitors wt at least -d- days each month 
-    group_by(Monitor.ID, Year) %>%
+    group_by(Parameter.Symbol, Monitor.ID, Year) %>%
     summarize(n_Month = length(unique(Month))) %>%
     filter(n_Month >= m
     ) %>% #monitors wt at least -m- month each year
-    group_by(Monitor.ID) %>%
+    group_by(Parameter.Symbol, Monitor.ID) %>%
     summarize(n_Year = length(unique(Year))) %>%
     filter(n_Year >= y
     ) %>% #monitors wt at least -y- year in start-end period

### 2021-01-17 code/data-processors/epa-air-data-download-function.R

@@ -1,8 +1,11 @@
 ### Author: Fatemeh Kazemi - 01-01-2021
 
+# Function that Downloads and cleans air quality data measured by EPA 
+# https://aqs.epa.gov/aqsweb/airdata/download_files.html
+
 # EPA_AQS_download Function
 # Function Arguments: 
-# period : hourly/daily
+# period : daily
 # Index : list of file index to download
 # start : start year 
 # end : end year
@@ -23,7 +26,9 @@ EPA.AQS.download <- function(period, Index, start, end,
                           ,".zip",sep = ""),temp)
       dt0 <- read.csv(unz(temp, paste(period,"_",i,"_",t,".csv", sep = ""))) %>% 
         filter(Parameter.Code %in% Code.Sym$Parameter.Code) %>% 
-        mutate(State.Code = as.factor(State.Code))
+        mutate(State.Code = as.factor(sprintf("%02d", 
+                                              as.numeric(as.character(State.Code))))
+               )
       dt <- rbind(dt, dt0)
     }
   }

### 2021-01-18 code/data-processors/air-data-processor.Rmd
update pm daily mergeing method avg of all zipcodes in 12-mile buffer

@@
 library(lubridate)
-#library(naniar) # for replacing -999 with NA
+library(naniar) # for replacing -999 with NA
 ```
@@
 ```{r load data}
-load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\state-region.RDa')
+dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
+load(paste0(dirUSSpatial,'state-region.RDa'))
+load(paste0(dirUSSpatial,'site-zip-closest-bz12.RDa'))
+load(paste0(dirUSSpatial,'site-zip.RDa'))
 ```
@@
     ) %>% 
-  merge(dt.state.region[, c("State", "Region.IV")])
+  merge(dt.state.region[, c("State", "Region.IV")]) %>% 
+  arrange(Site.ID)
 
@@
 #Monitor.ID: Site.ID-POC
+```
 
+```{r EPA AQS Data Exploration}
+dt.spec.raw %>% distinct(Monitor.ID) %>% nrow() #659
 dt.spec.raw %>% distinct(Site.ID) %>% nrow() #546
+
+# number of sites per year
 dt.spec.raw %>% 
@@
 
-dt.test <- Air.Daily.Process(dt = dt.spec.raw, d = 4, m = 9, y = 4)
-
-dt.test2 <- dt.test %>% 
-  select(-Parameter.Code) %>% 
-  pivot_wider(names_sort = T,
-              names_from = c(Parameter.Symbol),
-              values_from = c(Arithmetic.Mean)) %>% 
-  # for 405 cases with two methods for EC and OC (TOR & TOT), use TOT 
-  mutate(EC = ifelse(!is.na(EC.TOT), EC.TOT, EC.TOR), 
-         OC = ifelse(!is.na(OC.TOT), OC.TOT, OC.TOR)) %>% 
-  select(-EC.TOR, -EC.TOT, -OC.TOR, -OC.TOT) %>% 
-  arrange(Site.ID, POC, Date)
+# number of monitors per year
+dt.spec.raw %>% 
+  mutate(Year = year(Date)) %>% 
+  distinct(Monitor.ID, Year) %>% 
+  group_by(Year) %>% 
+  summarise(n = n())
 ```
@@
 
-dt.imprv.raw.l <- dt.imprv.raw %>% 
-  pivot_longer(cols = AS:ZN,
-               names_to = "Parameter.Symbol",
-               values_to = "Arithmetic.Mean",
-               values_drop_na = T)
-
-dt.test3 <- Air.Daily.Process(dt = dt.imprv.raw.l, d = 4, m = 9, y = 4)
-
-dt.test4 <- dt.test3 %>% 
-  pivot_wider(names_sort = T,
-              names_from = c(Parameter.Symbol),
-              values_from = c(Arithmetic.Mean)) %>% 
-    arrange(Site.ID, POC, Date)
-
 # find the diff bw spec & improve
-monitor.spec <- dt.spec.w %>% distinct(Monitor.ID)
-monitor.imprv <- dt.imprv.raw %>% distinct(Monitor.ID) 
+monitor.spec <- dt.spec.w %>% distinct(Monitor.ID) #659
+monitor.imprv <- dt.imprv.raw %>% distinct(Monitor.ID) #189
 monitor.diff.imprv <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID) %>% 
-  as.data.frame() 
+  as.data.frame() #32
 colnames(monitor.diff.imprv) <- 'Monitor.ID'
@@
 
-site.spec <- dt.spec.w %>% distinct(Site.ID)
-site.imprv <- dt.imprv.raw %>% distinct(Site.ID) 
+site.spec <- dt.spec.w %>% distinct(Site.ID) #546
+site.imprv <- dt.imprv.raw %>% distinct(Site.ID) #172
 site.diff.imprv <- setdiff(site.imprv$Site.ID, site.spec$Site.ID) %>% 
-  as.data.frame()
+  as.data.frame() #28
 colnames(site.diff.imprv) <- 'Site.ID'
@@
 
-monitor.spec <- dt.spec.w %>% distinct(Monitor.ID)
-monitor.csn <- dt.csn.raw %>% distinct(Monitor.ID) 
+monitor.spec <- dt.spec.w %>% distinct(Monitor.ID) #659
+monitor.csn <- dt.csn.raw %>% distinct(Monitor.ID) #195
 monitor.diff.csn <- setdiff(monitor.csn$Monitor.ID, monitor.spec$Monitor.ID) %>% 
-  as.data.frame()
+  as.data.frame() #0
 # no difference between two dataset!
@@
   summarise(n = n())
+# TOT 326
 # TOR 167
-# TOT 326
 # EC.TOT-OC.TOR 28
@@
 ```{r Adding Daily PM data to pmc daily data}
-load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\site-zip-closest-bz12.RDa')
+# available site-year pmc
+site.yr.pmc <- dt.pmc.w %>% 
+  mutate(Year = year(Date)) %>% 
+  distinct(Site.ID, Year) #3394
 
-# closest zipcode to each site in each year in 12-mile bufferzone
-dt.site.close.zip.pmc <- site.pmc %>% 
-  merge(dt.site.zip.closest.bz12) %>% 
-  arrange(Site.ID, Year)
+# all zipcodes in 12-mile bufferzone of each site each year
+dt.pmc.site.all.zip.bz12  <- site.yr.pmc %>% 
+  inner_join(dt.site.zip) %>% 
+  arrange(Site.ID, Year, Dist) %>% 
+  filter(Dist <=12) %>% 
+  select(-Zip.Type, -Dist)
 
-save(dt.site.close.zip.pmc, file = here('data', 'processed', 'site-close-zip-pmc.RDa'))
-write.csv(dt.site.close.zip.pmc, file = here('data', 'processed', 'site-close-zip-pmc.csv'))
+save(dt.pmc.site.all.zip.bz12, file = here('data', 'processed', 'pmc-site-all-zip-bz12.RDa'))
+write.csv(dt.pmc.site.all.zip.bz12, file = here('data', 'processed', 'pmc-site-all-zip-bz12.csv'))
 
-dt.site.close.zip.pmc %>% distinct(Site.ID) %>% nrow() #574 > 560
-# 560 out of 574 sites have zipcodes in their 12-mile buffer
+dt.pmc.site.all.zip.bz12 %>% distinct(Site.ID) %>% nrow() #574 > 558
+# 558 out of 574 sites have zipcodes in their 12-mile buffer
 
@@
             Date = mdy(chardate),
-            PM)
+            PM) %>% 
+  arrange(Site.ID, Date)
 
@@
 
-dt.pmc.pm.w %>% distinct(Site.ID) %>% nrow() # 574 > 560 > 558
+dt.pmc.pm.w %>% distinct(Site.ID) %>% nrow() # 574 > 558
 dt.pmc.pm.w %>% distinct(Monitor.ID) %>% nrow()#691 > 673
@@
 #sites with measurements for all components - spec & improve
-dt.pmc.c <- dt.pmc.pm.w[complete.cases(dt.pmc.pm.w),] #241,624
+dt.pmc.c <- dt.pmc.pm.w[complete.cases(dt.pmc.pm.w),] #243,098
 monitor.pmc <- dt.pmc.c %>% distinct(Monitor.ID) # 691 > 673 > 515
@@
 
-monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 691 > 673 > 515 > 331
-site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 558 > 471 > 318
+monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 691 > 673 > 515 > 336
+site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 558 > 471 > 322
 
@@
 dt.pmc.sel <- merge(dt.pmc.sel, site.POC.larger) 
-monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 691 > 673 > 515 > 331 > 318
-site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 558 > 471 > 318 > 318
+monitor.pmc <- dt.pmc.sel %>% distinct(Monitor.ID) # 691 > 673 > 515 > 336 > 322
+site.pmc <- dt.pmc.sel %>% distinct(Site.ID) #574 -> 558 > 471 > 322
 dt.pmc.sel$POC <- dt.pmc.sel$Monitor.ID <- NULL
@@
   mutate(psuedo = 100)
-
-load('C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\site-zip.RDa')
 

### 2021-01-18 code/data-processors/air-data-processor-function.R

@@ -23,15 +23,15 @@ Air.Daily.Process <- function(dt, d, m, y) {
   dt.c <- dt %>%
     mutate(Year = year(Date),
            Month = month(Date)) %>% 
-    group_by(Parameter.Symbol, Monitor.ID, Year, Month) %>%
+    group_by(Monitor.ID, Year, Month) %>%
     summarize(n_Day = length(unique(Date))) %>%
     filter(n_Day >= d
     ) %>% #monitors wt at least -d- days each month 
-    group_by(Parameter.Symbol, Monitor.ID, Year) %>%
+    group_by(Monitor.ID, Year) %>%
     summarize(n_Month = length(unique(Month))) %>%
     filter(n_Month >= m
     ) %>% #monitors wt at least -m- month each year
-    group_by(Parameter.Symbol, Monitor.ID) %>%
+    group_by(Monitor.ID) %>%
     summarize(n_Year = length(unique(Year))) %>%
     filter(n_Year >= y
     ) %>% #monitors wt at least -y- year in start-end period

### 2021-01-22 code/data-analysis/config-file-generator.Rmd
PMC and CMS Merge Config file generator factor analysis output data cleaning forest plot

---
title: "Config File Generator"
output: html_notebook
---

### This program:
  (1) Generates configuration files for Java for different combinations of 
      i. pollutant
      ii. cause of death
      iii. model

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r List of PM Components}
pmc <- c("Yr_AS","Yr_CA","Yr_CL","Yr_CU","Yr_EC","Yr_FE","Yr_K",
       "Yr_MG","Yr_MN","Yr_NA","Yr_NI","Yr_NO3","Yr_OC","Yr_PB",
       "Yr_PM","Yr_SE","Yr_SI","Yr_SO4","Yr_V","Yr_ZN")
```

```{r List of Factors}
fac <- c("Factor1","Factor2","Factor3","Factor4",
         "Factor5","Factor6","Factor7","Factor8")
```

```{r List of Carbons}
carbon <- c("Yr_EC", "Yr_OC")
```

```{r List of Causes of Death}
cuz <- c("allcuz","nacc","acc","cvd","ihd","chf","cbv","resp","copd","pneu","canc","lungc")
```

```{r Config file - Base Model}
config.base <- c("# data path
data_path=/scratch/fatemehkp/projects/data/analysis/dataset

# loader settings
# separated symbol for the given data
sep=,
# the predictors are included in the model
predictors=exposure
# stratas
stratas=StrID, SiteID
# death
death=no_death_outcome
# life
life=no_enrollee

# optimizer settings
# whether considering ties for death, default false
isTies=false
# if given multiple cores, set isParallelism as true
isParallelism=true
# whether penalizing the weight
l2=false
# if penalizing the weight, set the strength, otherwise it is useless.
l2Strength=1

# the application class name
survival.class=CoxPH
")
```

```{r Config file - SES Adj. Model}
config.ses <- c("# data path
data_path=/scratch/fatemehkp/projects/data/analysis/dataset

# loader settings
# separated symbol for the given data
sep=,
# the predictors are included in the model
predictors=exposure, ses
# stratas
stratas=StrID, SiteID
# death
death=no_death_outcome
# life
life=no_enrollee

# optimizer settings
# whether considering ties for death, default false
isTies=false
# if given multiple cores, set isParallelism as true
isParallelism=true
# whether penalizing the weight
l2=false
# if penalizing the weight, set the strength, otherwise it is useless.
l2Strength=1

# the application class name
survival.class=CoxPH
")
```

```{r base model for components}
dataname <- "ndi-pmc.csv"
expo <- pmc

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.base, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-base', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for components}
dataname <- "ndi-pmc.csv"
expo <- pmc

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','pmc-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r base model for factors}
dataname <- "ndi-fac.csv"
expo <- fac

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.base, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-base', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors}
dataname <- "ndi-fac.csv"
expo <- fac

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r base model for factors excluding EC}
dataname <- "ndi-fac-ex-ec.csv"
expo <- fac

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.base, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-ex-ec-base', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors excluding EC}
dataname <- "ndi-fac-ex-ec.csv"
expo <- fac

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','fac-ex-ec-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for Carbons}
dataname <- "ndi-carbon.csv"
expo <- carbon

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','carbon-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for TOT Carbons}
dataname <- "ndi-carbon-tot.csv"
expo <- carbon

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','tot-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for TOR Carbons}
dataname <- "ndi-carbon-tor.csv"
expo <- carbon

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.ses, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    for (j in seq(1,length(cuz),1)){
      w <- gsub("outcome", cuz[j], z)
      cat(w, file=f, sep="\n")
      k=j+length(cuz)*(i-1)
      writeLines(w, here('config-files','tor-ses', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r under work - parse output}
result = matrix(nrow=1,ncol=4,byrow = TRUE) 
colnames(result) <- c("Expo","Outcome","Beta","SE")

for (i in seq(1,240,1)){
  test <- readLines(here('output','85.txt'))
  important_line2 <- test[min(grep("^death", test))]
  dt <- dt %>% 
    mutate(cuz = gsub(".*death_", "", important_line2))
  important_line <- test[min(grep("^Factor", test))]
  Expo <- gsub("\t.*", "", important_line)
  Coef <- sub(".*\t(.*)\t.*","\\1", important_line)
  SE <- gsub(".*\t", "", important_line)
}

```

### 2021-01-22 code/data-analysis/factor-analysis.Rmd
PMC and CMS Merge Config file generator factor analysis output data cleaning forest plot

@@
 ### This program:
-  (1) Run factor anlaysis
+  (1) Run factor analysis
 
@@
 library(psych) # for factor analysis
-
 ```
@@
 ```{r Load datasets}
-load(here('data','processed', 'pmc-selected.RDa'))
+load(here('data','processed', 'pmc-daily.RDa'))
+```
+
+```{r Call functions}
+source(here('code','data-processors','air-data-smooth-mvavg-function.R'))
 ```
@@
 # All eligible monitors
-fit <- factanal(dt.pmc.sel %>% select(AS:OC), 8, rotation="varimax")
+fit <- factanal(dt.pmc.daily %>% select(AS:OC), 8, rotation="varimax")
 factor.loadings <- rbind(fit$loadings)
 save(factor.loadings, file = here('output','table','factor-loadings.RDa'))
+#Traffic Soil Metals Biomass Salt Oil Coal Steel
 
-factor.scores <- factor.scores(dt.pmc.sel %>% select(AS:OC), fit)
-dt.pmc.fac <- cbind(dt.pmc.sel, factor.scores$scores)
-save(dt.pmc.fac, file = here('data', 'processed', 'pmc-fac.RDa'))
+factor.scores <- factor.scores(dt.pmc.daily %>% select(AS:OC), fit)
+dt.fac.daily <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores) 
+save(dt.fac.daily, file = here('data', 'processed', 'fac-daily.RDa'))
+```
 
-# Removing EC from factor analysis
-fit <- factanal(dt.pmc.sel %>% select(AS:ZN, OC), 8, rotation="varimax")
+```{r Removing EC from factor analysis}
+fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
 factor.loadings.ex.ec <- rbind(fit$loadings)
 save(factor.loadings.ex.ec, file = here('output','table','factor-loadings-ex-ec.RDa'))
+# Soil Metals Traffic Biomass Coal Salt Oil Steel
 
-factor.scores <- factor.scores(dt.pmc.sel %>% select(AS:ZN, OC), fit)
-dt.pmc.fac.ex.ec <- cbind(dt.pmc.sel, factor.scores$scores)
-save(dt.pmc.fac.ex.ec, file = here('data', 'processed', 'pmc-fac-ex-ec.RDa'))
+factor.scores <- factor.scores(dt.pmc.daily %>% select(AS:ZN, OC), fit)
+dt.fac.daily.ex.ec <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores)
+save(dt.fac.daily.ex.ec, file = here('data', 'processed', 'fac-daily-ex-ec.RDa'))
 ```
+
+```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
+dt.air <- dt.fac.daily %>% 
+  pivot_longer(cols = Factor1:Factor8,
+               names_to = "Parameter.Symbol",
+               values_to = "Value") %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
+
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
+
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, site.para$Site.ID, site.para$Parameter.Symbol)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.1yr=unlist(smooth.out[4,]))
+
+dt.fac.1yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.1yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.fac.1yr, file = here('data', 'processed', 'fac-1yr.RDa'))
+write.csv(dt.fac.1yr, file = here('data', 'processed', 'fac-1yr.csv'), row.names = F)
+```
+
+```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
+dt.air <- dt.fac.daily.ex.ec %>% 
+  pivot_longer(cols = Factor1:Factor8,
+               names_to = "Parameter.Symbol",
+               values_to = "Value") %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
+
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
+
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, site.para$Site.ID, site.para$Parameter.Symbol)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.1yr=unlist(smooth.out[4,]))
+
+dt.fac.ex.ec.1yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.1yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.fac.ex.ec.1yr, file = here('data', 'processed', 'fac-ex-ec-1yr.RDa'))
+write.csv(dt.fac.ex.ec.1yr, file = here('data', 'processed', 'fac-ex-ec-1yr.csv'), row.names = F)
+```

### 2021-01-22 code/data-analysis/output-cleaning.Rmd
PMC and CMS Merge Config file generator factor analysis output data cleaning forest plot

---
title: "Analysis Output files"
output: html_notebook
---

This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.

```{r load packages}
library(tidyverse)
library(here)
```

```{r Load data}
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ex-ec-1yr.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
```

```{r - Parameter/Factor to Index}
### Components
Para.to.Index <- tribble(
  ~Index, ~Parameter,
   "As", "AS",
   "Ca", "CA",
   "Cu", "CU",
   "Cl", "CL",
   "Fe", "FE",
   "Pb", "PB",
   "Mn", "MN",
   "Ni", "NI",
   "Mg", "MG",
   "Se", "SE",
   "V", "V",
   "Si", "SI",
   "Zn", "ZN",
   "K", "K",
   "Na", "NA",
   "NO3", "NO3",
   "SO4", "SO4",
   "OC", "OC",
   "EC", "EC",
   "PM2.5", "PM"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))

### Factors
Factor.to.Index <- tribble(
  ~Index, ~Parameter,
   "Traffic", "Factor1",
   "Soil", "Factor2",
   "Metals", "Factor3",
   "Biomass", "Factor4",
   "Salt", "Factor5",
   "Oil", "Factor6",
   "Coal", "Factor7",
   "Steel", "Factor8"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))

### Factors excluding EC
Factor.ex.ec.to.Index <- tribble(
  ~Index, ~Parameter,
   "Soil", "Factor1",
   "Metals", "Factor2",
   "Traffic", "Factor3",
   "Biomass", "Factor4",
   "Coal", "Factor5",
   "Salt", "Factor6",
   "Oil", "Factor7",
   "Steel", "Factor8"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))
```

```{r Outcome to Cause }
Outcome.to.Cause <- tribble(
  ~Cause, ~Outcome,
  "All-Cause", "allcuz",
  "Non-Accidental", "nacc",
  "Accidental", "acc",
  "Cardiovascular", "cvd",
  "IHD", "ihd",
  "CHF", "chf",
  "CBV", "cbv",
  "Respiratory", "resp",
  "COPD", "copd",
  "Pneumonia", "pneu",
  "Cancer", "canc",
  "Lung Cancer", "lungc"
)
```

```{r calculating IQRS}
### Components
pmc.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.pmc.1yr) %>% 
  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
  pivot_longer(cols = AS:ZN,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter))

save(pmc.1yr.iqr, file = here('data','processed','pmc-1yr-iqr.RDa'))

### Factors
fac.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.fac.1yr) %>% 
  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

save(fac.1yr.iqr, file = here('data','processed','fac-1yr-iqr.RDa'))

### Factors excluding EC
fac.ex.ec.1yr.iqr <- dt.pmc.site.ndi %>% 
  select(Site.ID) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
  pivot_longer(cols = Factor1:Factor8,
               names_to = "Parameter",
               values_to = "IQR")%>% 
  mutate(Parameter = as.factor(Parameter))

save(fac.ex.ec.1yr.iqr, file = here('data','processed','fac-ex-ec-1yr-iqr.RDa'))

### Carbons
dt.carbon <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, EC, OC)

dt.site <- dt.pmc.site.ndi %>% 
  filter(!Method == "EC.TOT-OC.TOR") %>% 
  select(Site.ID, Method)

carbon.1yr.iqr <- dt.site %>% 
  select(Site.ID) %>% 
  inner_join(dt.carbon) %>% 
  summarise_at(vars(EC:OC), ~IQR(.x)) %>% 
  pivot_longer(cols = EC:OC,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter))

save(carbon.1yr.iqr, file = here('data','processed','carbon-1yr-iqr.RDa'))

carbon.method.1yr.iqr <- dt.site %>% 
  inner_join(dt.carbon) %>% 
  group_by(Method) %>% 
  summarise_at(vars(EC:OC), ~IQR(.x)) %>% 
  pivot_longer(cols = EC:OC,
               names_to = "Parameter",
               values_to = "IQR") %>% 
  mutate(Parameter = as.factor(Parameter)) %>% 
  arrange(Parameter)

save(carbon.method.1yr.iqr, file = here('data','processed','carbon-method-1yr-iqr.RDa'))
```

```{r Output PMC Base}
out.pmc.base <- read.csv(here('output','analysis','pmc_base.csv')) %>% 
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge(pmc.1yr.iqr) %>% 
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.pmc.base, file = here('output','analysis','out-pmc-base.RDa'))
```

```{r Output PMC SES-Adj}
out.pmc.ses <- read.csv(here('output','analysis','pmc_ses.csv')) %>% 
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge(pmc.1yr.iqr) %>% 
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.pmc.ses, file = here('output','analysis','out-pmc-ses.RDa'))
```

```{r Output Factors Base}
out.fac.base <- read.csv(here('output','analysis','fac_base.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.fac.base, file = here('output','analysis','out-fac-base.RDa'))
```

```{r Output Factors SES-Adj}
out.fac.ses <- read.csv(here('output','analysis','fac_ses.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.1yr.iqr) %>% 
  merge(Factor.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.fac.ses, file = here('output','analysis','out-fac-ses.RDa'))
```

```{r Output Factors Ex. EC Base}
out.fac.ex.ec.base <- read.csv(here('output','analysis','fac_ex_ec_base.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.ex.ec.1yr.iqr) %>% 
  merge(Factor.ex.ec.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.fac.ex.ec.base, file = here('output','analysis','out-fac-ex-ec-base.RDa'))
```

```{r Output Factors Ex. EC SES-Adj}
out.fac.ex.ec.ses <- read.csv(here('output','analysis','fac_ex_ec_ses.csv')) %>% 
  rename(Parameter = Predictor) %>% 
  merge(fac.ex.ec.1yr.iqr) %>% 
  merge(Factor.ex.ec.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.fac.ex.ec.ses, file = here('output','analysis','out-fac-ex-ec-ses.RDa'))
```

```{r Output Carbon SES-Adj}
out.carbon.ses <- read.csv(here('output','analysis','carbon_ses.csv')) %>% 
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge(carbon.1yr.iqr) %>% 
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.carbon.ses, file = here('output','analysis','out-carbon-ses.RDa'))
```

```{r Output Carbon TOT SES-Adj}
out.carbon.tot.ses <- read.csv(here('output','analysis','tot_ses.csv')) %>% 
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge((carbon.method.1yr.iqr %>% filter(Method == "TOT"))) %>% 
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.carbon.tot.ses, file = here('output','analysis','out-carbon-tot-ses.RDa'))
```

```{r Output Carbon TOR SES-Adj}
out.carbon.tor.ses <- read.csv(here('output','analysis','tot_ses.csv')) %>% 
  mutate(Parameter = gsub(".*Yr_", "", Predictor),
         Parameter = as.factor(Parameter)) %>% 
  merge((carbon.method.1yr.iqr %>% filter(Method == "TOR"))) %>% 
  merge(Para.to.Index) %>% 
  merge(Outcome.to.Cause) %>% 
  mutate(HR = round(exp(Coef * IQR),3),
         HR.L = round(exp((Coef-1.96*std) * IQR),3),
         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
  arrange(Config) %>% 
  select(Index, Cause, HR, HR.L, HR.U)

save(out.carbon.tor.ses, file = here('output','analysis','out-carbon-tor-ses.RDa'))
```

### 2021-01-22 code/data-processors/air-data-processor.Rmd
PMC and CMS Merge Config file generator factor analysis output data cleaning forest plot

@@
 
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
 ```{r load packages}
@@
 save(dt.pmc.site.all.zip.bz12, file = here('data', 'processed', 'pmc-site-all-zip-bz12.RDa'))
-write.csv(dt.pmc.site.all.zip.bz12, file = here('data', 'processed', 'pmc-site-all-zip-bz12.csv'))
+write.csv(dt.pmc.site.all.zip.bz12, file = here('data', 'processed', 'pmc-site-all-zip-bz12.csv'), row.names = F)
 
@@
 save(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.RDa'))
-write.csv(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.csv'))
+write.csv(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.csv'), row.names = F)
 
-dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 558 > 471 > 318 > 318
+dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 558 > 471 > 322
   merge(dt.aqs.sites)
@@
 #                  2			
-#RURAL	           177			
-#SUBURBAN	         67			
-#URBAN	           72
+#RURAL	           178			
+#SUBURBAN	         69		
+#URBAN	           73
 
@@
   summarise(n = n()) %>% filter(n > 3) %>% 
-  nrow() #318: all  #311: with 4+ years
+  nrow() #322: all  #315: with 4+ years
 
@@
 
-summary(check$n)
+summary(check$n) # 23 to 97
 ```
@@
 save(dt.pmc.site.zip.bz6, file = here('data', 'processed', 'pmc-site-zip-bz6.RDa'))
-write.csv(dt.pmc.site.zip.bz6, file = here('data', 'processed', 'pmc-site-zip-bz6.csv'))
+write.csv(dt.pmc.site.zip.bz6, file = here('data', 'processed', 'pmc-site-zip-bz6.csv'),
+          row.names = F)
 
 # Count number of zipcodes and sites
-dt.pmc.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4253
-dt.pmc.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #318 > 270
+dt.pmc.site.zip.bz6 %>% distinct(Zip.Code) %>% nrow() #4348
+dt.pmc.site.zip.bz6 %>% distinct(Site.ID) %>% nrow() #322 > 274
 
@@
 save(dt.pmc.site.zip.bz12, file = here('data', 'processed', 'pmc-site-zip-bz12.RDa'))
-write.csv(dt.pmc.site.zip.bz12, file = here('data', 'processed', 'pmc-site-zip-bz12.csv'))
+write.csv(dt.pmc.site.zip.bz12, file = here('data', 'processed', 'pmc-site-zip-bz12.csv'),
+          row.names = F)
 
 # Count number of zipcodes and sites
-dt.pmc.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8313
-dt.pmc.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #318 > 316
+dt.pmc.site.zip.bz12 %>% distinct(Zip.Code) %>% nrow() #8446
+dt.pmc.site.zip.bz12 %>% distinct(Site.ID) %>% nrow() #322 > 320
 
@@
 save(dt.pmc.site.zip.bz24, file = here('data', 'processed', 'pmc-site-zip-bz24.RDa'))
-write.csv(dt.pmc.site.zip.bz24, file = here('data', 'processed', 'pmc-site-zip-bz24.csv'))
+write.csv(dt.pmc.site.zip.bz24, file = here('data', 'processed', 'pmc-site-zip-bz24.csv'),
+          row.names = F)
 
 # Count number of zipcodes and sites
-dt.pmc.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15601
-dt.pmc.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #318 > 317
+dt.pmc.site.zip.bz24 %>% distinct(Zip.Code) %>% nrow() #15778
+dt.pmc.site.zip.bz24 %>% distinct(Site.ID) %>% nrow() #322 > 321
 
 # pmc-site-zip-bz12.csv was uploaded on NEU Cluster to be merged with CMS data
-# It has 316 sites with 8313 zipcodes around them
+# It has 320 sites with 8446 zipcodes around them
 ```
@@
 ```{r Post mergeing with CMS Data}
-dt.site.ndi.bz12 <- read.csv(here('data', 'raw', 'site_pmc_ndi_bz12.csv')) %>% 
-  rename(Site.ID = Site_ID)
+dt.pmc.site.ndi <- read.csv(here('data', 'processed', 'site_pmc_ndi.csv')) %>% 
+  rename(Site.ID = Site_ID) %>% 
+  left_join(dt.aqs.sites) %>% 
+  left_join(dt.site.carbon.method)
+# 317 out of 320 sites have population living in their 12-mile bufferzone
 
-# 325 out of 328 sites have population living in their 12-mile bufferzone
-dt.site.ndi.bz12 %>% 
-  group_by(Site.ID) %>% 
-  summarise(n = n()) %>% filter(n > 0) %>% 
-  nrow() # 325 > 317 > 316 > 308: with 4+ years
+save(dt.pmc.site.ndi, file = here('data', 'processed', 'pmc-site-ndi.RDa'))
+write.csv(dt.pmc.site.ndi, file = here('data', 'processed', 'pmc-site-ndi.csv'),
+          row.names = F)
 
 # TOT/TOR Method in different location.set
-dt.site.ndi.bz12 %>% 
-  distinct(Site.ID) %>% 
-  left_join(dt.site.carbon.method) %>% 
-  left_join(dt.aqs.sites) %>% 
+dt.pmc.site.ndi %>% 
   group_by(Location.Setting, Method) %>% 
@@
 
-dt.site.ndi.bz12 %>% 
-  distinct(Site.ID) %>% 
-  left_join(dt.aqs.sites) %>% 
+dt.pmc.site.ndi %>% 
   group_by(Location.Setting) %>% 
@@
 # suburban 69
-# rural 182
+# rural 174
+# ...   2
 ```
+
+```{r}
+dt.pmc.daily <- dt.pmc.site.ndi %>% 
+  select(Site.ID) %>% 
+  merge(dt.pmc.sel)
+
+save(dt.pmc.daily, file = here('data', 'processed', 'pmc-daily.RDa'))
+```
+
+```{r}
+test <- dt.pmc.daily %>% 
+  group_by(Site.ID) %>% 
+  nest() %>% 
+  mutate(model = map(data, ~lm(PM ~ AS, data = .)),
+         resid = map(model, residuals)) %>% 
+  unnest(data, resid)
+#208037
+test2 <- unlist(unlist(test$model))
+test2 <- residuals(test$model[[3]])
+
+d <- dt.pmc.daily %>% 
+  filter(Site.ID == "01-073-0023")
+
+model <- lm(data = d, PM ~AS)
+
+residuals(model)
+
+d <- data.frame(state=rep(c('NY', 'CA'), c(10, 10)),
+                                 year=rep(1:10, 2),
+                                 response=c(rnorm(10), rnorm(10)))
+
+d %>% 
+  group_by(state) %>% 
+  nest() %>% 
+  mutate(model = map(data, ~lm(response ~ year, data = .)))
+```

### 2021-01-22 code/data-processors/cms-data-processor.Rmd
PMC and CMS Merge Config file generator factor analysis output data cleaning forest plot

---
title: "Air Quality and CMS Data"
author: "Fatemeh Kazemi"
date: "1/18/2021"
output: html_document
---

### This program:
  (1) Merges CMS(ndi) data with pmc and ses data

### Note:
  1. In data merged with CMS, bufferzone is 12-mile unless specified
  2. Exposure window is one year unless specified

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}
library(tidyverse)
library(here)
```

```{r load data}
dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
load(here('data','processed','pmc-1yr.RDa'))
load(here('data','processed','fac-1yr.RDa'))
load(here('data','processed','fac-ex-ec-1yr.RDa'))
load(here('data','processed','master-ndi-pmc.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))
```

```{r Import and save CMS(/ndi) data}
dt.master.ndi.pmc <- read.csv(here('data', 'processed','master_ndi_pmc.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc, file = here('data', 'processed', 'master-ndi-pmc.RDa'))

dt.master.ndi.pmc.race <- read.csv(here('data', 'processed','master_ndi_pmc_race.csv')) %>%
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.race, file = here('data', 'processed', 'master-ndi-pmc-race.RDa'))
```

```{r PMC}
dt.pmc <- dt.pmc.1yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.pmc <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc.csv'),
          row.names = F)

dt.ndi.pmc.race <- dt.master.ndi.pmc.race %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>% 
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.race, file = here('data', 'processed', 'ndi-pmc-race.csv'),
          row.names = F)
```

```{r Factors}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.fac <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac, file = here('data', 'processed', 'ndi-fac.csv'),
          row.names = F)

dt.ndi.fac.race <- dt.master.ndi.fac.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.race, file = here('data', 'processed', 'ndi-fac-race.csv'),
          row.names = F)
```

```{r Factors Excluding EC}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.fac.ex.ec <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.ex.ec, file = here('data', 'processed', 'ndi-fac-ex-ec.csv'),
          row.names = F)

dt.ndi.fac.ex.ec.race <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.race, file = here('data', 'processed', 'ndi-fac-ex-ec-race.csv'),
          row.names = F)
```

```{r Carbons}
dt.carbon <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, EC, OC) %>% 
  rename_at(vars(EC, OC), ~paste("Yr", .x, sep = "_"))

dt.site <- dt.pmc.site.ndi %>% 
  filter(!Method == "EC.TOT-OC.TOR") %>% 
  select(Site.ID, Method)

dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.carbon <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.carbon) %>% 
  inner_join(dt.site) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID) %>% 
  select(-Method)

write.csv(dt.ndi.carbon, file = here('data', 'processed', 'ndi-carbon.csv'),
          row.names = F)

dt.ndi.carbon.tot <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.carbon) %>% 
  inner_join(dt.site) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID) %>% 
  filter(Method == "TOT") %>% 
  select(-Method)

write.csv(dt.ndi.carbon.tot, file = here('data', 'processed', 'ndi-carbon-tot.csv'),
          row.names = F)

dt.ndi.carbon.tor <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.carbon) %>% 
  inner_join(dt.site) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID) %>% 
  filter(Method == "TOR") %>% 
  select(-Method)

write.csv(dt.ndi.carbon.tor, file = here('data', 'processed', 'ndi-carbon-tor.csv'),
          row.names = F)
```

### 2021-01-22 code/data-viz/plot-results.Rmd
PMC and CMS Merge Config file generator factor analysis output data cleaning forest plot

---
title: "PM Component Paper Plots"
author: "Fatemeh Kazemi"
date: "01-19-2021"
---

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
### load packages
  library(tidyverse)
  library(here)
  library(gridExtra)
```

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))

```

```{r - Components Base}
data <- out.pmc.base

cmp <- c("OC", "NO3", "V", "Ni", "SO4", "Se",
         "Zn", "Pb", "Ca", "Si", "PM2.5")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-base.png'), width = 9.5, height = 5.5)
```

```{r - Components SES-Adj}
data <- out.pmc.ses

cmp <- c("OC", "NO3", "V", "Ni", "SO4", "Se",
         "Zn", "Pb", "Ca", "Si", "PM2.5")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','pmc-ses.png'), width = 9.5, height = 5.5)
```

```{r - Factor Base}
data <- out.fac.base

So <- c("Steel", "Coal", "Oil", "Salt", 
         "Biomass", "Metals", "Soil", "Traffic")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-base.png'), width = 9.5, height = 5.5)
```

```{r - Factor SES-Adj}
data <- out.fac.ses

So <- c("Steel", "Coal", "Oil", "Salt", 
         "Biomass", "Metals", "Soil", "Traffic")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ses.png'), width = 9.5, height = 5.5)
```

```{r - Factor Ex. EC Base}
data <- out.fac.ex.ec.base

So <- c("Steel", "Oil", "Salt", "Coal", 
         "Biomass","Traffic", "Metals", "Soil")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ex-ec-base.png'), width = 9.5, height = 5.5)
```

```{r - Factor EX. EC SES-Adj}
data <- out.fac.ex.ec.ses

So <- c("Steel", "Oil", "Salt", "Coal", 
         "Biomass","Traffic", "Metals", "Soil")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia",
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )
# #610038
plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
  xlab("") +
  ylab("") +
  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave(here('output', 'plot','fac-ex-ec-ses.png'), width = 9.5, height = 5.5)
```

```{r - Components - PM Residual}
data <- read_excel('Comp_PMResi.xlsx')

cmp <- c("-OC", "-NO3", "-V", "-Ni", "-SO4", "-Se",
         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
         "Respiratory", "Pneumonia",
         "Cancer","Lung Cancer") # "CHF", "COPD",

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
         )

plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
               color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) +
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 4, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave("CMP_PMResi_1114.jpeg", width = 9.5, height = 5.5)
```

```{r - Components PM Residual - Region}
data <- read_excel('Comp_PMResi_Region.xlsx')

cmp <- c("PM2.5",  "-Si", "-Ca", "-Pb", "-Zn",
         "-Se", "-SO4", "-Ni", "-V", "-NO3", "-OC"
         )
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
         "Respiratory", "Pneumonia",
         "Cancer","Lung Cancer") # "CHF", "COPD",

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("NE", "S", "MW", "W")
plot_cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs,
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10,face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_PMResi_Region_1113.jpeg", p, width = 9.5, height = 12)
```

```{r - Factor - PM Residual}
data <- read_excel('Fac_PMResi.xlsx')

So <- c("-Traffic", "-Oil", "-Coal", 
         "-Metals","-Soil", "PM2.5") # "-Steel", "-Salt", "-Biomass", 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
         "Respiratory", "Pneumonia",
         "Cancer","Lung Cancer") # "CHF", "COPD",

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_cols <- c("red")

ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
              color =plot_cols, size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
             color =plot_cols, size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +

facet_wrap( ~ Cause, ncol = 4, scales = "fixed") +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  ) +
ggsave("Fac_PMResi_1114.jpeg", width = 9.5, height = 4.5)
```

```{r - Components Region}
data <- read_excel('Comp_Region.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("NE", "S", "MW", "W")
plot_cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10,face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_Region_1113.jpeg", p, width = 9.5, height = 12)
```

```{r Factors Region}
data <- read_excel('Fac_Region.xlsx')

So <- c("Soil", "Metals",  
        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",

cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("NE", "S", "MW", "W")
plot_cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("Fac_Region_1113.jpeg", p, width = 9.5, height = 7)
```

```{r - Components Race}
data <- read_excel('Comp_Race.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("White", "Hispanic", "Black", "Asian")
plot_cols <- c("red", "orange", "blue", "seagreen")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_Race_1113.jpeg", p, width = 9.5, height = 12)
```

```{r Factors Race}
data <- read_excel('Fac_Race.xlsx')

So <- c("Soil", "Metals",  
        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",

cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("White", "Hispanic", "Black", "Asian")
plot_cols <- c("red", "orange", "blue", "seagreen")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units ='in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("Fac_Race_1113.jpeg", p, width = 9.5, height = 7)
```

```{r Components Urban}
data <- read_excel('Comp_Urban.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("Non-urban", "Urban")
plot_cols <- c("red", "blue")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "fixed", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_Urban_1113.jpeg", p, width = 9.5, height = 10)
```

```{r Factors Urban}
data <- read_excel('Fac_Urban.xlsx')

So <- c("Soil", "Metals",  
        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",

cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("Non-urban", "Urban")
plot_cols <- c("red", "blue")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units ='in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("Fac_Urban_1113.jpeg", p, width = 9.5, height = 6)
```

```{r Components SES-Urban}
data <- read_excel('Comp_SESUrban.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("High", "Middle", "Low")
plot_cols <-  c("seagreen", "blue", "red")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_SESUrban_1113.jpeg", p, width = 9.5, height = 11)
```

```{r Factors SES-Urban}
data <- read_excel('Fac_SESUrban.xlsx')

So <- c("Soil", "Metals",  
        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",

cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("High", "Middle", "Low")
plot_cols <-  c("seagreen", "blue", "red")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units ='in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("Fac_SESUrban_1113.jpeg", p, width = 9.5, height = 7)
```

```{r - Components BRFSS}
data <- read_excel('Comp_BRFSS.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("BRFSS-Adjusted", "Base")
plot_cols <- c("red", "blue")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_BRFSS_1113.jpeg", p, width = 9.5, height = 10)
```

```{r Factors BRFSS}
data <- read_excel('Fac_BRFSS.xlsx')

So <- c("Soil", "Metals",  
        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",

cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% So,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("BRFSS-Adjusted", "Base")
plot_cols <- c("red", "blue")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units ='in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("Fac_BRFSS_1113.jpeg", p, width = 9.5, height = 7)
```

```{r Components Buffer}
data <- read_excel('Comp_Buffer.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("24-miles", "12-miles", "6-miles") 
plot_cols <- c("red", "blue", "seagreen")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_Buffer_1113.jpeg", p, width = 9.5, height = 10)
```

```{r Components Mvavg}
data <- read_excel('Comp_Mvavg.xlsx')

cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
          "Ni", "V", "NO3", "OC") 
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

data <- data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp),
         Tag = as.factor(Tag)
         )

data <- data %>% 
  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))

plot_labs <- c("5-yr", "4-yr","3-yr","2-yr","1-yr")
plot_cols <- c("red","orange","purple","blue","seagreen")

p <- grid.arrange(
ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
  geom_vline(xintercept = 1, linetype = 2, color = "black") +
  xlab("") +
  ylab("") +
  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                size = 0.25, show.legend = F) + 
  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
             size = 1.5, show.legend = F) + 
  scale_shape_manual(values = c(16, 1, 16), guide = F) +
  scale_color_manual(
    labels = plot_labs, 
    values = plot_cols) +

facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
               shrink = T, space = 'fixed') +
  theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "slategray2"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')) +
  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
nrow = 2)

ggsave("CMP_Mvavg_1113.jpeg", p, width = 9.5, height = 10)
```

### 2021-01-24 code/data-analysis/config-file-generator.Rmd
dataset and config files for residual, effect modification and brfss data processing for bufferzone size

@@
 
+```{r load packages}
+library(tidyverse)
+library(here)
+```
+
 ```{r List of PM Components}
@@
 
+```{r List of PM Components Residuals}
+pmcres <- c("PM_AS","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
+            "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")
+```
+
+```{r List of Factors Residuals}
+facres <- c("PM_Factor1","PM_Factor2","PM_Factor3","PM_Factor4",
+            "PM_Factor5","PM_Factor6","PM_Factor7","PM_Factor8")
+```
+
 ```{r List of Carbons}
 carbon <- c("Yr_EC", "Yr_OC")
+```
+
+```{r List of PM Components Sub}
+pmc.sub <- c("AS","CA","CL","NA","NI","NO3","OC",
+             "PB","PM","SI","SO4","V","ZN")
+```
+
+```{r List of PM Components Yr Sub}
+pmc.sub.yr <- c("Yr_AS","Yr_CA","Yr_CL","Yr_NA","Yr_NI","Yr_NO3","Yr_OC",
+             "Yr_PB","Yr_PM","Yr_SI","Yr_SO4","Yr_V","Yr_ZN")
 ```
@@
 predictors=exposure, ses
+# stratas
+stratas=StrID, SiteID
+# death
+death=no_death_outcome
+# life
+life=no_enrollee
+
+# optimizer settings
+# whether considering ties for death, default false
+isTies=false
+# if given multiple cores, set isParallelism as true
+isParallelism=true
+# whether penalizing the weight
+l2=false
+# if penalizing the weight, set the strength, otherwise it is useless.
+l2Strength=1
+
+# the application class name
+survival.class=CoxPH
+")
+```
+
+```{r Config file - EM Models}
+config.em <- c("# data path
+data_path=/scratch/fatemehkp/projects/data/analysis/dataset
+
+# loader settings
+# separated symbol for the given data
+sep=,
+# the predictors are included in the model
+predictors=Yr_exposure, subg, subg_exposure, ses
+# stratas
+stratas=StrID, SiteID
+# death
+death=no_death_outcome
+# life
+life=no_enrollee
+
+# optimizer settings
+# whether considering ties for death, default false
+isTies=false
+# if given multiple cores, set isParallelism as true
+isParallelism=true
+# whether penalizing the weight
+l2=false
+# if penalizing the weight, set the strength, otherwise it is useless.
+l2Strength=1
+
+# the application class name
+survival.class=CoxPH
+")
+```
+
+```{r Config file - BRFSS Models}
+config.brfss <- c("# data path
+data_path=/scratch/fatemehkp/projects/data/analysis/dataset
+
+# loader settings
+# separated symbol for the given data
+sep=,
+# the predictors are included in the model
+predictors=Yr_exposure, ses, BMI, Race, Smoke, Diabt, Asthma, Drink
 # stratas
@@
 
-```{r ses adj. model for Carbons}
-dataname <- "ndi-carbon.csv"
-expo <- carbon
-
-for (i in seq(1,length(expo),1)){
-  filenames <- c( tempfile())
-  for( f in  filenames ){
-    cat(config.ses, file=f)
-    x <- readLines(f)
-    y <- gsub("dataset", dataname, x)
-    z <- gsub("exposure", expo[i], y)
-    for (j in seq(1,length(cuz),1)){
-      w <- gsub("outcome", cuz[j], z)
-      cat(w, file=f, sep="\n")
-      k=j+length(cuz)*(i-1)
-      writeLines(w, here('config-files','carbon-ses', paste(k,'.txt', sep = "")))
-    }
-  }
-  file.remove(f)
-  }
-```
-
 ```{r ses adj. model for TOT Carbons}
@@
 
+```{r ses adj. model for components residuals}
+dataname <- "ndi-pmc-residual.csv"
+expo <- pmcres
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-resid', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors excluding EC Residual}
+dataname <- "ndi-fac-ex-ec-residual.csv"
+expo <- facres
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-resid', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - race Asian}
+dataname <- "ndi-pmc-raceA.csv"
+expo <- pmc.sub
+subg <- "rA"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-race-A', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - race Black}
+dataname <- "ndi-pmc-raceB.csv"
+expo <- pmc.sub
+subg <- "rB"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-race-B', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - race Hispanic}
+dataname <- "ndi-pmc-raceH.csv"
+expo <- pmc.sub
+subg <- "rH"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-race-H', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - race White}
+dataname <- "ndi-pmc-raceW.csv"
+expo <- pmc.sub
+subg <- "rW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-race-W', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - race Asian}
+dataname <- "ndi-fac-raceA.csv"
+expo <- fac
+subg <- "rA"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-race-A', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - race Black}
+dataname <- "ndi-fac-raceB.csv"
+expo <- fac
+subg <- "rB"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-race-B', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - race Hispanic}
+dataname <- "ndi-fac-raceH.csv"
+expo <- fac
+subg <- "rH"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-race-H', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - race White}
+dataname <- "ndi-fac-raceW.csv"
+expo <- fac
+subg <- "rW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-race-W', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Urban}
+dataname <- "ndi-pmc-urban.csv"
+expo <- pmc.sub
+subg <- "urb"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-urban', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Rural}
+dataname <- "ndi-pmc-rural.csv"
+expo <- pmc.sub
+subg <- "rur"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-rural', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Urban ses Low}
+dataname <- "ndi-pmc-urban-sesL.csv"
+expo <- pmc.sub
+subg <- "sesL"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-urban-sesL', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Urban ses Middle}
+dataname <- "ndi-pmc-urban-sesM.csv"
+expo <- pmc.sub
+subg <- "sesM"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-urban-sesM', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Urban ses High}
+dataname <- "ndi-pmc-urban-sesH.csv"
+expo <- pmc.sub
+subg <- "sesH"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-urban-sesH', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - West}
+dataname <- "ndi-pmc-west.csv"
+expo <- pmc.sub
+subg <- "rW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-west', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Midwest}
+dataname <- "ndi-pmc-midwest.csv"
+expo <- pmc.sub
+subg <- "rMW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-midwest', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - South}
+dataname <- "ndi-pmc-south.csv"
+expo <- pmc.sub
+subg <- "rS"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-south', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Northeast}
+dataname <- "ndi-pmc-northeast.csv"
+expo <- pmc.sub
+subg <- "rNE"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-northeast', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Age LE75}
+dataname <- "ndi-pmc-ageLE75.csv"
+expo <- pmc.sub
+subg <- "aLE75"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-ageLE75', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Age M75}
+dataname <- "ndi-pmc-ageM75.csv"
+expo <- pmc.sub
+subg <- "aM75"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-ageM75', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Female}
+dataname <- "ndi-pmc-sexF.csv"
+expo <- pmc.sub
+subg <- "sexF"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-sexF', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - Male}
+dataname <- "ndi-pmc-sexM.csv"
+expo <- pmc.sub
+subg <- "sexM"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-sexM', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - sites with BRFSS data}
+dataname <- "ndi-pmc-brfss.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-brfss-0', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - adj. BRFSS data}
+dataname <- "ndi-pmc-brfss.csv"
+expo <- pmc.sub
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.brfss, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-brfss', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
 ```{r under work - parse output}

### 2021-01-24 code/data-analysis/factor-analysis.Rmd
dataset and config files for residual, effect modification and brfss data processing for bufferzone size

@@
 ```
+
+```{r residuals of PM vs. Factors}
+dt.pm.daily <- dt.pmc.daily %>% 
+  select(Site.ID, Date, PM)
+
+dt.fac.ex.ec.residual <- dt.fac.daily.ex.ec %>% 
+  merge(dt.pm.daily) %>% 
+  group_by(Site.ID) %>% 
+  nest() %>% 
+  mutate(PM_Factor1 = map(map(data, ~lm(PM ~ Factor1, data = .)), residuals),
+         PM_Factor2 = map(map(data, ~lm(PM ~ Factor2, data = .)), residuals),
+         PM_Factor3 = map(map(data, ~lm(PM ~ Factor3, data = .)), residuals),
+         PM_Factor4 = map(map(data, ~lm(PM ~ Factor4, data = .)), residuals),
+         PM_Factor5 = map(map(data, ~lm(PM ~ Factor5, data = .)), residuals),
+         PM_Factor6  = map(map(data, ~lm(PM ~ Factor6,  data = .)), residuals),
+         PM_Factor7 = map(map(data, ~lm(PM ~ Factor7, data = .)), residuals),
+         PM_Factor8 = map(map(data, ~lm(PM ~ Factor8, data = .)), residuals)
+         ) %>% 
+  unnest(c(data, PM_Factor1:PM_Factor8)) %>% 
+  select(-(Factor1:Factor8), -PM)
+
+save(dt.fac.ex.ec.residual, file = here('data', 'processed', 'fac-ex-ec-residual.RDa'))
+```
+
+```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
+dt.air <- dt.fac.ex.ec.residual %>% 
+  pivot_longer(cols = PM_Factor1:PM_Factor8,
+               names_to = "Parameter.Symbol",
+               values_to = "Value") %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
+
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
+
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, site.para$Site.ID, site.para$Parameter.Symbol)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.1yr=unlist(smooth.out[4,]))
+
+dt.fac.ex.ec.residual.1yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.1yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.fac.ex.ec.residual.1yr, file = here('data', 'processed', 'fac-ex-ec-residual-1yr.RDa'))
+
+```

### 2021-01-24 code/data-processors/air-data-processor.Rmd
dataset and config files for residual, effect modification and brfss data processing for bufferzone size

@@
 source(here('code','data-processors','air-data-smooth-mvavg-function.R'))
+#source('air-data-smooth-mvavg-function.R') # for Cluster
 ```
@@
 load(paste0(dirUSSpatial,'state-region.RDa'))
-load(paste0(dirUSSpatial,'site-zip-closest-bz12.RDa'))
 load(paste0(dirUSSpatial,'site-zip.RDa'))
+load(here('data','processed','aqs-sites.RDa'))
 ```
@@
 
-# daily PM value for each site based on closest zipcode value
+# daily PM value for each site based on zipcodes in 12-mile value
 dt.pm.daily <- read.csv(here('data','processed','pm_pmc_daily.csv')) %>% 
@@
 
-```{r Air quality data Process}
+```{r Air quality data Process - eligible sites}
 map(dt.pmc.pm.w, ~sum(is.na(.)))
@@
 save(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.RDa'))
-write.csv(dt.pmc.1yr, file = here('data', 'processed', 'pmc-1yr.csv'), row.names = F)
 
@@
 
+summary(dt.pmc.site.ndi$Location.Setting) 
+fix(dt.pmc.site.ndi) # changed blanks to 'RURAL'
+
 save(dt.pmc.site.ndi, file = here('data', 'processed', 'pmc-site-ndi.RDa'))
@@
 
-```{r}
+```{r - daily data for eligible sites}
 dt.pmc.daily <- dt.pmc.site.ndi %>% 
@@
 
-```{r}
-test <- dt.pmc.daily %>% 
+```{r residuals of PM vs. Components}
+dt.pmc.residual <- dt.pmc.daily %>% 
   group_by(Site.ID) %>% 
   nest() %>% 
-  mutate(model = map(data, ~lm(PM ~ AS, data = .)),
-         resid = map(model, residuals)) %>% 
-  unnest(data, resid)
-#208037
-test2 <- unlist(unlist(test$model))
-test2 <- residuals(test$model[[3]])
+  mutate(PM_AS = map(map(data, ~lm(PM ~ AS, data = .)), residuals),
+         PM_CA = map(map(data, ~lm(PM ~ CA, data = .)), residuals),
+         PM_CL = map(map(data, ~lm(PM ~ CL, data = .)), residuals),
+         PM_CU = map(map(data, ~lm(PM ~ CU, data = .)), residuals),
+         PM_FE = map(map(data, ~lm(PM ~ FE, data = .)), residuals),
+         PM_K  = map(map(data, ~lm(PM ~ K,  data = .)), residuals),
+         PM_MG = map(map(data, ~lm(PM ~ MG, data = .)), residuals),
+         PM_MN = map(map(data, ~lm(PM ~ MN, data = .)), residuals),
+         PM_NA = map(map(data, ~lm(PM ~ `NA`, data = .)), residuals),
+         PM_NI = map(map(data, ~lm(PM ~ NI, data = .)), residuals),
+         PM_NO3 = map(map(data, ~lm(PM ~ NO3, data = .)), residuals),
+         PM_PB = map(map(data, ~lm(PM ~ PB, data = .)), residuals),
+         PM_SE = map(map(data, ~lm(PM ~ SE, data = .)), residuals),
+         PM_SI  = map(map(data, ~lm(PM ~ SI,  data = .)), residuals),
+         PM_SO4 = map(map(data, ~lm(PM ~ SO4, data = .)), residuals),
+         PM_V = map(map(data, ~lm(PM ~ V, data = .)), residuals),
+         PM_ZN = map(map(data, ~lm(PM ~ ZN, data = .)), residuals),
+         PM_EC  = map(map(data, ~lm(PM ~ EC,  data = .)), residuals),
+         PM_OC = map(map(data, ~lm(PM ~ OC, data = .)), residuals)
+         ) %>% 
+  unnest(c(data, PM_AS:PM_OC)) %>% 
+  select(-(AS:PM))
 
-d <- dt.pmc.daily %>% 
-  filter(Site.ID == "01-073-0023")
+save(dt.pmc.residual, file = here('data', 'processed', 'pmc-residual.RDa'))
+```
 
-model <- lm(data = d, PM ~AS)
+```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
+dt.air <- dt.pmc.residual %>% 
+  pivot_longer(cols = PM_AS:PM_OC,
+               names_to = "Parameter.Symbol",
+               values_to = "Value") %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
 
-residuals(model)
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
 
-d <- data.frame(state=rep(c('NY', 'CA'), c(10, 10)),
-                                 year=rep(1:10, 2),
-                                 response=c(rnorm(10), rnorm(10)))
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, site.para$Site.ID, site.para$Parameter.Symbol)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.1yr=unlist(smooth.out[4,]))
 
-d %>% 
-  group_by(state) %>% 
-  nest() %>% 
-  mutate(model = map(data, ~lm(response ~ year, data = .)))
+dt.pmc.residual.1yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.1yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.pmc.residual.1yr, file = here('data', 'processed', 'pmc-residual-1yr.RDa'))
 ```

### 2021-01-24 code/data-processors/cms-data-processor.Rmd
dataset and config files for residual, effect modification and brfss data processing for bufferzone size

@@
 load(paste0(dirUSSpatial,'ses-site-bz12.RDa'))
+load(paste0(dirUSSpatial,'ses-site-bz6.RDa'))
+load(paste0(dirUSSpatial,'ses-site-bz24.RDa'))
+load(paste0(dirUSSpatial,'brfss-site.RDa'))
+load(here('data','processed','master-ndi-pmc.RDa'))
+load(here('data','processed','master-ndi-pmc-race.RDa'))
+load(here('data','processed','pmc-site-ndi.RDa'))
 load(here('data','processed','pmc-1yr.RDa'))
@@
 load(here('data','processed','fac-ex-ec-1yr.RDa'))
-load(here('data','processed','master-ndi-pmc.RDa'))
-load(here('data','processed','pmc-site-ndi.RDa'))
+load(here('data','processed','pmc-residual-1yr.RDa'))
+load(here('data','processed','fac-ex-ec-residual-1yr.RDa'))
 ```
@@
 save(dt.master.ndi.pmc.race, file = here('data', 'processed', 'master-ndi-pmc-race.RDa'))
+
+dt.master.ndi.pmc.bz6 <- read.csv(here('data', 'processed','master_ndi_pmc_bz6.csv')) %>% 
+  rename(Site.ID = Site_ID,
+         Year = year,
+         Month = MONTH,
+         age = ENROLLEE_AGE)
+save(dt.master.ndi.pmc.bz6, file = here('data', 'processed', 'master-ndi-pmc-bz6.RDa'))
+
+dt.master.ndi.pmc.bz12 <- read.csv(here('data', 'processed','master_ndi_pmc_bz12.csv')) %>% 
+  rename(Site.ID = Site_ID,
+         Year = year,
+         Month = MONTH,
+         age = ENROLLEE_AGE)
+save(dt.master.ndi.pmc.bz12, file = here('data', 'processed', 'master-ndi-pmc-bz12.RDa'))
+
+dt.master.ndi.pmc.bz24 <- read.csv(here('data', 'processed','master_ndi_pmc_bz24.csv')) %>% 
+  rename(Site.ID = Site_ID,
+         Year = year,
+         Month = MONTH,
+         age = ENROLLEE_AGE)
+save(dt.master.ndi.pmc.bz24, file = here('data', 'processed', 'master-ndi-pmc-bz24.RDa'))
 ```
@@
           row.names = F)
-
-dt.ndi.pmc.race <- dt.master.ndi.pmc.race %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.pmc.race, file = here('data', 'processed', 'ndi-pmc-race.csv'),
-          row.names = F)
 ```
@@
           row.names = F)
-
-dt.ndi.fac.race <- dt.master.ndi.fac.pmc %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>% 
-  inner_join(dt.fac.1yr) %>% 
-  inner_join(dt.ses) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.fac.race, file = here('data', 'processed', 'ndi-fac-race.csv'),
-          row.names = F)
 ```
@@
 write.csv(dt.ndi.fac.ex.ec, file = here('data', 'processed', 'ndi-fac-ex-ec.csv'),
-          row.names = F)
-
-dt.ndi.fac.ex.ec.race <- dt.master.ndi.pmc %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
-  inner_join(dt.ses) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.fac.race, file = here('data', 'processed', 'ndi-fac-ex-ec-race.csv'),
           row.names = F)
@@
 ```
+
+```{r PMC Residual}
+cmp.sub <- c("PM_AS","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
+            "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")
+
+dt.pmc <- dt.pmc.residual.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.residual <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.residual, file = here('data', 'processed', 'ndi-pmc-residual.csv'),
+          row.names = F)
+```
+
+```{r Factors Excluding EC Residual}
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.fac.ex.ec.residual <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_enrollee:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>%  
+  inner_join(dt.fac.ex.ec.residual.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.fac.ex.ec.residual, 
+          file = here('data', 'processed', 'ndi-fac-ex-ec-residual.csv'),
+          row.names = F)
+```
+
+```{r PMC race}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+### Race Asian
+dt.raceA <- dt.master.ndi.pmc.race %>%
+  mutate(race = ifelse(!race == "A", "O", "A")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceA <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceA, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.pmc.raceA <- dt.raceA %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rA = ifelse(race == "A", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.raceA[ ,paste0("rA_",cmp)] <- 
+      dt.ndi.pmc.raceA[ ,cmp] * dt.ndi.pmc.raceA$rA
+}
+
+dt.ndi.pmc.raceA <- dt.ndi.pmc.raceA %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rA, everything())
+
+write.csv(dt.ndi.pmc.raceA, file = here('data', 'processed', 'ndi-pmc-raceA.csv'),
+          row.names = F)
+
+### Race Black
+dt.raceB <- dt.master.ndi.pmc.race %>%
+  mutate(race = ifelse(!race == "B", "O", "B")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceB <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceB, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.pmc.raceB <- dt.raceB %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rB = ifelse(race == "B", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.raceB[ ,paste0("rB_",cmp)] <- 
+      dt.ndi.pmc.raceB[ ,cmp] * dt.ndi.pmc.raceB$rB
+}
+
+dt.ndi.pmc.raceB <- dt.ndi.pmc.raceB %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rB, everything())
+
+write.csv(dt.ndi.pmc.raceB, file = here('data', 'processed', 'ndi-pmc-raceB.csv'),
+          row.names = F)
+
+### Race Hispanic
+dt.raceH <- dt.master.ndi.pmc.race %>%
+  mutate(race = ifelse(!race == "H", "O", "H")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceH <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceH, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.pmc.raceH <- dt.raceH %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rH = ifelse(race == "H", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.raceH[ ,paste0("rH_",cmp)] <- 
+      dt.ndi.pmc.raceH[ ,cmp] * dt.ndi.pmc.raceH$rH
+}
+
+dt.ndi.pmc.raceH <- dt.ndi.pmc.raceH %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rH, everything())
+
+write.csv(dt.ndi.pmc.raceH, file = here('data', 'processed', 'ndi-pmc-raceH.csv'),
+          row.names = F)
+
+### Race White
+dt.raceW <- dt.master.ndi.pmc.race %>%
+  mutate(race = ifelse(!race == "W", "O", "W")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceW <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceW, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.pmc.raceW <- dt.raceW %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rW = ifelse(race == "W", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.raceW[ ,paste0("rW_",cmp)] <- 
+      dt.ndi.pmc.raceW[ ,cmp] * dt.ndi.pmc.raceW$rW
+}
+
+dt.ndi.pmc.raceW <- dt.ndi.pmc.raceW %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rW, everything())
+
+write.csv(dt.ndi.pmc.raceW, file = here('data', 'processed', 'ndi-pmc-raceW.csv'),
+          row.names = F)
+```
+
+```{r Factor race}
+fac <- c("Factor1","Factor2","Factor3","Factor4",
+         "Factor5","Factor6","Factor7","Factor8")
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+### Race Asian
+dt.raceA <- dt.master.ndi.pmc.race %>%
+  mutate(race = ifelse(!race == "A", "O", "A")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceA <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceA, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.fac.raceA <- dt.raceA %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rA = ifelse(race == "A", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.raceA[ ,paste0("rA_",cmp)] <- 
+      dt.ndi.fac.raceA[ ,cmp] * dt.ndi.fac.raceA$rA
+}
+
+dt.ndi.fac.raceA <- dt.ndi.fac.raceA %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rA, everything())
+
+write.csv(dt.ndi.fac.raceA, file = here('data', 'processed', 'ndi-fac-raceA.csv'),
+          row.names = F)
+
+### Race Black
+dt.raceB <- dt.master.ndi.fac.race %>%
+  mutate(race = ifelse(!race == "B", "O", "B")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceB <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceB, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.fac.raceB <- dt.raceB %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rB = ifelse(race == "B", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.raceB[ ,paste0("rB_",cmp)] <- 
+      dt.ndi.fac.raceB[ ,cmp] * dt.ndi.fac.raceB$rB
+}
+
+dt.ndi.fac.raceB <- dt.ndi.fac.raceB %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rB, everything())
+
+write.csv(dt.ndi.fac.raceB, file = here('data', 'processed', 'ndi-fac-raceB.csv'),
+          row.names = F)
+
+### Race Hispanic
+dt.raceH <- dt.master.ndi.fac.race %>%
+  mutate(race = ifelse(!race == "H", "O", "H")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceH <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceH, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.fac.raceH <- dt.raceH %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rH = ifelse(race == "H", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.raceH[ ,paste0("rH_",cmp)] <- 
+      dt.ndi.fac.raceH[ ,cmp] * dt.ndi.fac.raceH$rH
+}
+
+dt.ndi.fac.raceH <- dt.ndi.fac.raceH %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rH, everything())
+
+write.csv(dt.ndi.fac.raceH, file = here('data', 'processed', 'ndi-fac-raceH.csv'),
+          row.names = F)
+
+### Race White
+dt.raceW <- dt.master.ndi.fac.race %>%
+  mutate(race = ifelse(!race == "W", "O", "W")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.raceW <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceW, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+dt.ndi.fac.raceW <- dt.raceW %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(rW = ifelse(race == "W", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.raceW[ ,paste0("rW_",cmp)] <- 
+      dt.ndi.fac.raceW[ ,cmp] * dt.ndi.fac.raceW$rW
+}
+
+dt.ndi.fac.raceW <- dt.ndi.fac.raceW %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rW, everything())
+
+write.csv(dt.ndi.fac.raceW, file = here('data', 'processed', 'ndi-fac-raceW.csv'),
+          row.names = F)
+```
+
+```{r PMC urbanicity}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.site <- dt.pmc.site.ndi %>% 
+  select(Site.ID, Location.Setting)
+
+### Urban and Suburban
+dt.ndi.pmc.urban <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(urb = ifelse(!Location.Setting == "RURAL", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Location.Setting)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.urban[ ,paste0("urb_",cmp)] <- 
+      dt.ndi.pmc.urban[ ,cmp] * dt.ndi.pmc.urban$urb
+}
+
+dt.ndi.pmc.urban <- dt.ndi.pmc.urban %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, urb, everything())
+
+write.csv(dt.ndi.pmc.urban, file = here('data', 'processed', 'ndi-pmc-urban.csv'),
+          row.names = F)
+
+### Rural
+dt.ndi.pmc.rural <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rur = ifelse(Location.Setting == "RURAL", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Location.Setting)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.rural[ ,paste0("rur_",cmp)] <- 
+      dt.ndi.pmc.rural[ ,cmp] * dt.ndi.pmc.rural$rur
+}
+
+dt.ndi.pmc.rural <- dt.ndi.pmc.rural %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rur, everything())
+
+write.csv(dt.ndi.pmc.rural, file = here('data', 'processed', 'ndi-pmc-rural.csv'),
+          row.names = F)
+```
+
+```{r r PMC urban SES Categories}
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.site.urban <- dt.pmc.site.ndi %>% 
+  filter(!Location.Setting == "RURAL") %>% 
+  select(Site.ID)
+
+dt.site.urban.ses.cat <- dt.site.urban %>% 
+  inner_join(dt.ses)
+
+qtl <- dt.site.urban.ses.cat %>% 
+  summarise(qtl = quantile(ses, c(0.33, 0.66)))
+
+dt.site.urban.ses.cat <- dt.site.urban.ses.cat %>% 
+  mutate(ses.cat = ifelse(ses < qtl[1,], "Low",
+                          ifelse(ses >qtl[1,] & ses < qtl[2,], "Mid", "High")))
+
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+### Low Income
+dt.ndi.pmc.urban.ses <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.site.urban.ses.cat) %>%  
+  mutate(sesL = ifelse(ses.cat == "Low", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -ses.cat)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.urban.ses[ ,paste0("sesL_",cmp)] <- 
+      dt.ndi.pmc.urban.ses[ ,cmp] * dt.ndi.pmc.urban.ses$sesL
+}
+
+dt.ndi.pmc.urban.sesL <- dt.ndi.pmc.urban.ses %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sesL, everything())
+
+write.csv(dt.ndi.pmc.urban.sesL, file = here('data', 'processed', 'ndi-pmc-urban-sesL.csv'),
+          row.names = F)
+
+### Middle Income
+dt.ndi.pmc.urban.ses <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.site.urban.ses.cat) %>%  
+  mutate(sesM = ifelse(ses.cat == "Mid", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -ses.cat)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.urban.ses[ ,paste0("sesM_",cmp)] <- 
+      dt.ndi.pmc.urban.ses[ ,cmp] * dt.ndi.pmc.urban.ses$sesM
+}
+
+dt.ndi.pmc.urban.sesM <- dt.ndi.pmc.urban.ses %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sesM, everything())
+
+write.csv(dt.ndi.pmc.urban.sesM, file = here('data', 'processed', 'ndi-pmc-urban-sesM.csv'),
+          row.names = F)
+
+### High Income
+dt.ndi.pmc.urban.ses <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.site.urban.ses.cat) %>%  
+  mutate(sesH = ifelse(ses.cat == "Mid", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -ses.cat)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.urban.ses[ ,paste0("sesH_",cmp)] <- 
+      dt.ndi.pmc.urban.ses[ ,cmp] * dt.ndi.pmc.urban.ses$sesH
+}
+
+dt.ndi.pmc.urban.sesH <- dt.ndi.pmc.urban.ses %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sesH, everything())
+
+write.csv(dt.ndi.pmc.urban.sesH, file = here('data', 'processed', 'ndi-pmc-urban-sesH.csv'),
+          row.names = F)
+```
+
+```{r PMC Region}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.site <- dt.pmc.site.ndi %>% 
+  select(Site.ID, Region.IV)
+
+### West = 1
+dt.ndi.pmc.west <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rW = ifelse(Region.IV == 1, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.west[ ,paste0("rW_",cmp)] <- 
+      dt.ndi.pmc.west[ ,cmp] * dt.ndi.pmc.west$rW
+}
+
+dt.ndi.pmc.west <- dt.ndi.pmc.west %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rW, everything())
+
+write.csv(dt.ndi.pmc.west, file = here('data', 'processed', 'ndi-pmc-west.csv'),
+          row.names = F)
+
+### Midwest = 2
+dt.ndi.pmc.midwest <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rMW = ifelse(Region.IV == 2, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.midwest[ ,paste0("rMW_",cmp)] <- 
+      dt.ndi.pmc.midwest[ ,cmp] * dt.ndi.pmc.midwest$rMW
+}
+
+dt.ndi.pmc.midwest <- dt.ndi.pmc.midwest %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rMW, everything())
+
+write.csv(dt.ndi.pmc.midwest, file = here('data', 'processed', 'ndi-pmc-midwest.csv'),
+          row.names = F)
+
+### South = 3
+dt.ndi.pmc.south <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rS = ifelse(Region.IV == 3, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.south[ ,paste0("rS_",cmp)] <- 
+      dt.ndi.pmc.south[ ,cmp] * dt.ndi.pmc.south$rS
+}
+
+dt.ndi.pmc.south <- dt.ndi.pmc.south %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rS, everything())
+
+write.csv(dt.ndi.pmc.south, file = here('data', 'processed', 'ndi-pmc-south.csv'),
+          row.names = F)
+
+### Northeast = 4
+dt.ndi.pmc.northeast <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rNE = ifelse(Region.IV == 4, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.northeast[ ,paste0("rNE_",cmp)] <- 
+      dt.ndi.pmc.northeast[ ,cmp] * dt.ndi.pmc.northeast$rNE
+}
+
+dt.ndi.pmc.northeast <- dt.ndi.pmc.northeast %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rNE, everything())
+
+write.csv(dt.ndi.pmc.northeast, file = here('data', 'processed', 'ndi-pmc-northeast.csv'),
+          row.names = F)
+```
+
+```{r PMC Age}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+### Age 
+dt.age <- dt.master.ndi.pmc %>%
+  mutate(age = ifelse(age <= 75, "LE", "M")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.age <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+### LE 75
+dt.ndi.pmc.ageLE75 <- dt.age %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aLE75 = ifelse(age == "LE", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.ageLE75[ ,paste0("aLE75_",cmp)] <- 
+      dt.ndi.pmc.ageLE75[ ,cmp] * dt.ndi.pmc.ageLE75$aLE75
+}
+
+dt.ndi.pmc.ageLE75 <- dt.ndi.pmc.ageLE75 %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aLE75, everything())
+
+write.csv(dt.ndi.pmc.ageLE75, file = here('data', 'processed', 'ndi-pmc-ageLE75.csv'),
+          row.names = F)
+
+### M 75
+dt.ndi.pmc.ageM75 <- dt.age %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aM75 = ifelse(age == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.ageM75[ ,paste0("aM75_",cmp)] <- 
+      dt.ndi.pmc.ageM75[ ,cmp] * dt.ndi.pmc.ageM75$aM75
+}
+
+dt.ndi.pmc.ageM75 <- dt.ndi.pmc.ageM75 %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aM75, everything())
+
+write.csv(dt.ndi.pmc.ageM75, file = here('data', 'processed', 'ndi-pmc-ageM75.csv'),
+          row.names = F)
+```
+
+```{r PMC Sex}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.sex <- dt.master.ndi.pmc %>% 
+    select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses)
+
+### Female
+dt.ndi.pmc.sexF <- dt.sex %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(sexF = ifelse(sex == "F", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.sexF[ ,paste0("sexF_",cmp)] <- 
+      dt.ndi.pmc.sexF[ ,cmp] * dt.ndi.pmc.sexF$sexF
+}
+
+dt.ndi.pmc.sexF <- dt.ndi.pmc.sexF %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexF, everything())
+
+write.csv(dt.ndi.pmc.sexF, file = here('data', 'processed', 'ndi-pmc-sexF.csv'),
+          row.names = F)
+
+### Male
+dt.ndi.pmc.sexM <- dt.sex %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(sexM = ifelse(sex == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.sexM[ ,paste0("sexM_",cmp)] <- 
+      dt.ndi.pmc.sexM[ ,cmp] * dt.ndi.pmc.sexM$sexM
+}
+
+dt.ndi.pmc.sexM <- dt.ndi.pmc.sexM %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexM, everything())
+
+write.csv(dt.ndi.pmc.sexM, file = here('data', 'processed', 'ndi-pmc-sexM.csv'),
+          row.names = F)
+```
+
+```{r PMC BRFSS}
+dt.pmc <- dt.pmc.1yr %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.brfss <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.brfss.site) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.brfss, file = here('data', 'processed', 'ndi-pmc-brfss.csv'),
+          row.names = F)
+```
+
+```{r PMC BZ 6}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub) %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz6 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc.bz6 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-bz6.csv'),
+          row.names = F)
+```
+
+```{r PMC BZ 12}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub) %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc.bz12 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-bz12.csv'),
+          row.names = F)
+```
+
+```{r PMC BZ 24}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub) %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz24 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc.bz24 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-bz24.csv'),
+          row.names = F)
+```

### 2021-01-25 code/data-analysis/factor-analysis.Rmd
1 to 5yr mvavg modify smooth function

@@
 #using smoothed.yr function
-smooth.out <- mapply(Smoothed.Year, site.para$Site.ID, site.para$Parameter.Symbol)
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 0.99, 350)
 para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),

### 2021-01-25 code/data-processors/air-data-processor.Rmd
1 to 5yr mvavg modify smooth function

@@
 # It has 320 sites with 8446 zipcodes around them
+# 317 out of 320 sites have population living in their 12-mile bufferzone
+
+# pmc-site-zip-bz6.csv was uploaded on NEU Cluster to be merged with CMS data
+# 271 out of 274 sites have population living in their 6-mile bufferzone
+# We extended the bufferzone around these 271 sites to 12- and 24- miles too
 ```
@@
 ```
+
+```{r Smoothing Data & Caluculating 1 to 5-yr mvavg for each month}
+cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+dt.air <- dt.pmc.daily %>% 
+  select(Site.ID, Date, cmp.sub) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter.Symbol",
+               values_to = "Value") %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
+
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
+
+#using smoothed.yr function
+# 5 years
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 4.99, 1750)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.yr=unlist(smooth.out[4,]))
+
+dt.pmc.5yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.pmc.5yr, file = here('data', 'processed', 'pmc-sub-5yr.RDa'))
+
+# 4 years
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 3.99, 1400)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.yr=unlist(smooth.out[4,]))
+
+dt.pmc.4yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.pmc.4yr, file = here('data', 'processed', 'pmc-sub-4yr.RDa'))
+
+dt.pmc.4yr.5yr <- dt.pmc.5yr %>% 
+  select(Site.ID, Year, Month) %>% 
+  inner_join(dt.pmc.4yr)
+
+save(dt.pmc.4yr.5yr, file = here('data', 'processed', 'pmc-sub-4yr-5yr.RDa'))
+
+# 3 years
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 2.99, 1050)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.yr=unlist(smooth.out[4,]))
+
+dt.pmc.3yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.pmc.3yr, file = here('data', 'processed', 'pmc-sub-3yr.RDa'))
+
+dt.pmc.3yr.5yr <- dt.pmc.5yr %>% 
+  select(Site.ID, Year, Month) %>% 
+  inner_join(dt.pmc.3yr)
+
+save(dt.pmc.3yr.5yr, file = here('data', 'processed', 'pmc-sub-3yr-5yr.RDa'))
+
+# 2 years
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 1.99, 700)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.yr=unlist(smooth.out[4,]))
+
+dt.pmc.2yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.pmc.2yr, file = here('data', 'processed', 'pmc-sub-2yr.RDa'))
+
+dt.pmc.2yr.5yr <- dt.pmc.5yr %>% 
+  select(Site.ID, Year, Month) %>% 
+  inner_join(dt.pmc.2yr)
+
+save(dt.pmc.2yr.5yr, file = here('data', 'processed', 'pmc-sub-2yr-5yr.RDa'))
+
+# 1 year
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 0.99, 350)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.yr=unlist(smooth.out[4,]))
+
+dt.pmc.1yr <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.pmc.1yr, file = here('data', 'processed', 'pmc-sub-1yr.RDa'))
+
+dt.pmc.1yr.5yr <- dt.pmc.5yr %>% 
+  select(Site.ID, Year, Month) %>% 
+  inner_join(dt.pmc.1yr)
+
+save(dt.pmc.1yr.5yr, file = here('data', 'processed', 'pmc-sub-1yr-5yr.RDa'))
+
+dt.pmc.5yr %>% distinct(Site.ID, Year) %>% nrow() #263 -  820
+dt.pmc.4yr %>% distinct(Site.ID, Year) %>% nrow() #303 - 1128
+dt.pmc.3yr %>% distinct(Site.ID, Year) %>% nrow() #314 - 1442
+dt.pmc.2yr %>% distinct(Site.ID, Year) %>% nrow() #317 - 1745
+dt.pmc.1yr %>% distinct(Site.ID, Year) %>% nrow() #317 - 2074
+```

### 2021-01-25 code/data-processors/cms-data-processor.Rmd
1 to 5yr mvavg modify smooth function

@@
 load(here('data','processed','fac-ex-ec-residual-1yr.RDa'))
+load(here('data','processed','pmc-sub-5yr.RDa'))
+load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
+load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
+load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
+load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
 ```
@@
 ```
+
+```{r PMC - 5yr}
+dt.pmc <- dt.pmc.5yr %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 4yr}
+dt.pmc <- dt.pmc.4yr.5yr %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-4yr-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 3yr}
+dt.pmc <- dt.pmc.3yr.5yr %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-3yr-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 2yr}
+dt.pmc <- dt.pmc.2yr.5yr %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-2yr-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 1yr}
+dt.pmc <- dt.pmc.1yr.5yr %>% 
+  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-1yr-5yr.csv'),
+          row.names = F)
+```

### 2021-01-25 code/data-processors/air-data-smooth-mvavg-function.R

@@ -16,7 +16,7 @@ library(mgcv)
 #    Value:
 #    Date:
 
-Smoothed.Year <- function(si, pr){ 
+Smoothed.Year <- function(si, pr, s, n){ 
 
     dt <- dt.air %>% 
     filter(Site.ID == si & Parameter.Symbol == pr) %>%
@@ -31,7 +31,7 @@ Smoothed.Year <- function(si, pr){
   n.bits <- length(cuts)-1
   rows <- max(dt$year+dt$month/12)*12-12*min(dt$year+dt$month/12)+1
   results <- data.frame(Site.ID=rep(si,rows), Parameter.Symbol=rep(pr,rows), 
-                        Date=rep(NA,rows),mvavg.1yr=rep(NA,rows))
+                        Date=rep(NA,rows),mvavg.yr=rep(NA,rows))
   rows <- 0
 
   for (c in 1:n.bits){
@@ -51,16 +51,16 @@ Smoothed.Year <- function(si, pr){
       dtdate <- unique(pred.data$date)
       
       average1 <- function(dat){
-        av <- subset(pred.data,pred.data$date<=dat+0.01 & pred.data$date >dat-0.99)
-        if (nrow(av)>=350){mean.value <- mean(av$smooth)}else{mean.value <- NA}
+        av <- subset(pred.data,pred.data$date<=dat+0.01 & pred.data$date >dat-s)
+        if (nrow(av)>=n){mean.value <- mean(av$smooth)}else{mean.value <- NA}
         return(mean.value)
       }
       smoothed.yr <- sapply(dtdate,average1)
       
       results[(rows+1):(rows+length(dtdate)),"Date"] <- dtdate
-      results[(rows+1):(rows+length(dtdate)),"mvavg.1yr"] <- smoothed.yr
+      results[(rows+1):(rows+length(dtdate)),"mvavg.yr"] <- smoothed.yr
       rows <- rows + length(dtdate)
     }}
-  results <- results[!is.na(results$mvavg.1yr),]
+  results <- results[!is.na(results$mvavg.yr),]
   return(results)
 }

### 2021-01-25 code/data-processors/air-data-processor.Rmd
import different buffersize cms data add indentation

@@
 ```{r load data}
-dirUSSpatial <- 'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
+dirUSSpatial <- 
+  'C:\\Users\\fkazem01\\Box\\Projects\\USA Spatial\\data\\processed\\'
 load(paste0(dirUSSpatial,'state-region.RDa'))
@@
     !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
-                       "Guam", "Country Of Mexico","Canada") #remove non-CONUS states
+                       "Guam", "Country Of Mexico","Canada") 
+    #remove non-CONUS states
     ) %>%  
   transmute(
-    Site.ID = as.factor(sprintf("%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
+    Site.ID = as.factor(sprintf(
+      "%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                 as.numeric(as.character(State.Code)),
@@
     Land.Use,
-    Location.Setting = as.factor(ifelse(Location.Setting == "URBAN AND CENTER CITY",
-                                        "URBAN",
+    Location.Setting = as.factor(
+      ifelse(Location.Setting == "URBAN AND CENTER CITY", "URBAN",
              as.character(Location.Setting)))
@@
 for (i in seq(2000,2008,1)){
-  dt0 <- read.delim(here('data','raw','improve',paste0('improve_',i,'.txt')), sep = ',')
+  dt0 <- read.delim(
+    here('data','raw','improve',paste0('improve_',i,'.txt')), sep = ',')
   dt.imprv.raw <- rbind(dt.imprv.raw, dt0)
@@
 monitor.imprv <- dt.imprv.raw %>% distinct(Monitor.ID) #189
-monitor.diff.imprv <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID) %>% 
+monitor.diff.imprv <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID
+                              ) %>% 
   as.data.frame() #32
@@
 
-save(dt.site.carbon.method, file = here('data', 'processed', 'site-carbon-method.RDa'))
+save(dt.site.carbon.method, 
+     file = here('data', 'processed', 'site-carbon-method.RDa'))
 
@@
 
-save(dt.pmc.site.all.zip.bz12, file = here('data', 'processed', 'pmc-site-all-zip-bz12.RDa'))
-write.csv(dt.pmc.site.all.zip.bz12, file = here('data', 'processed', 'pmc-site-all-zip-bz12.csv'), row.names = F)
+save(dt.pmc.site.all.zip.bz12, 
+     file = here('data', 'processed', 'pmc-site-all-zip-bz12.RDa'))
+write.csv(dt.pmc.site.all.zip.bz12, 
+          file = here('data', 'processed', 'pmc-site-all-zip-bz12.csv'), 
+          row.names = F)
 
@@
 
-# site-close-zip-pmc.csv was uploaded on NEU Cluster to be merged with daily zipcode level
-# ... PM data.
+# site-close-zip-pmc.csv was uploaded on NEU Cluster to be merged with ...
+# ... daily zipcode level PM data.
 
@@
 
-save(dt.pmc.site.zip.bz6, file = here('data', 'processed', 'pmc-site-zip-bz6.RDa'))
-write.csv(dt.pmc.site.zip.bz6, file = here('data', 'processed', 'pmc-site-zip-bz6.csv'),
+save(dt.pmc.site.zip.bz6, 
+     file = here('data', 'processed', 'pmc-site-zip-bz6.RDa'))
+write.csv(dt.pmc.site.zip.bz6, 
+          file = here('data', 'processed', 'pmc-site-zip-bz6.csv'),
           row.names = F)
@@
 
-save(dt.pmc.site.zip.bz12, file = here('data', 'processed', 'pmc-site-zip-bz12.RDa'))
-write.csv(dt.pmc.site.zip.bz12, file = here('data', 'processed', 'pmc-site-zip-bz12.csv'),
+save(dt.pmc.site.zip.bz12, 
+     file = here('data', 'processed', 'pmc-site-zip-bz12.RDa'))
+write.csv(dt.pmc.site.zip.bz12, 
+          file = here('data', 'processed', 'pmc-site-zip-bz12.csv'),
           row.names = F)
@@
 
-save(dt.pmc.site.zip.bz24, file = here('data', 'processed', 'pmc-site-zip-bz24.RDa'))
-write.csv(dt.pmc.site.zip.bz24, file = here('data', 'processed', 'pmc-site-zip-bz24.csv'),
+save(dt.pmc.site.zip.bz24, 
+     file = here('data', 'processed', 'pmc-site-zip-bz24.RDa'))
+write.csv(dt.pmc.site.zip.bz24, 
+          file = here('data', 'processed', 'pmc-site-zip-bz24.csv'),
           row.names = F)
@@
 save(dt.pmc.site.ndi, file = here('data', 'processed', 'pmc-site-ndi.RDa'))
-write.csv(dt.pmc.site.ndi, file = here('data', 'processed', 'pmc-site-ndi.csv'),
+write.csv(dt.pmc.site.ndi, 
+          file = here('data', 'processed', 'pmc-site-ndi.csv'),
           row.names = F)
@@
 
-save(dt.pmc.residual.1yr, file = here('data', 'processed', 'pmc-residual-1yr.RDa'))
+save(dt.pmc.residual.1yr, 
+     file = here('data', 'processed', 'pmc-residual-1yr.RDa'))
 ```

### 2021-01-25 code/data-processors/cms-data-processor.Rmd
import different buffersize cms data add indentation

@@
 ```{r Import and save CMS(/ndi) data}
-dt.master.ndi.pmc <- read.csv(here('data', 'processed','master_ndi_pmc.csv')) %>% 
+# bz = 12
+dt.master.ndi.pmc <- read.csv(
+  here('data', 'processed','master_ndi_pmc.csv')) %>% 
   rename(Site.ID = Site_ID,
@@
          age = ENROLLEE_AGE)
-save(dt.master.ndi.pmc, file = here('data', 'processed', 'master-ndi-pmc.RDa'))
-
-dt.master.ndi.pmc.race <- read.csv(here('data', 'processed','master_ndi_pmc_race.csv')) %>%
+save(dt.master.ndi.pmc, 
+     file = here('data', 'processed', 'master-ndi-pmc.RDa'))
+
+# bz =12 - race
+dt.master.ndi.pmc.race <- read.csv(
+  here('data', 'processed','master_ndi_pmc_race.csv')) %>%
   rename(Site.ID = Site_ID,
@@
          age = ENROLLEE_AGE)
-save(dt.master.ndi.pmc.race, file = here('data', 'processed', 'master-ndi-pmc-race.RDa'))
-
-dt.master.ndi.pmc.bz6 <- read.csv(here('data', 'processed','master_ndi_pmc_bz6.csv')) %>% 
+save(dt.master.ndi.pmc.race, 
+     file = here('data', 'processed', 'master-ndi-pmc-race.RDa'))
+
+# bz = 6
+dt.master.ndi.pmc.bz6 <- read.csv(
+  here('data', 'processed','master_ndi_pmc_bz6.csv')) %>% 
   rename(Site.ID = Site_ID,
@@
          age = ENROLLEE_AGE)
-save(dt.master.ndi.pmc.bz6, file = here('data', 'processed', 'master-ndi-pmc-bz6.RDa'))
-
-dt.master.ndi.pmc.bz12 <- read.csv(here('data', 'processed','master_ndi_pmc_bz12.csv')) %>% 
+save(dt.master.ndi.pmc.bz6, 
+     file = here('data', 'processed', 'master-ndi-pmc-bz6.RDa'))
+
+# bz = 12 of sites of bz =6
+dt.master.ndi.pmc.bz12 <- read.csv(
+  here('data', 'processed','master_ndi_pmc_bz12.csv')) %>% 
   rename(Site.ID = Site_ID,
@@
          age = ENROLLEE_AGE)
-save(dt.master.ndi.pmc.bz12, file = here('data', 'processed', 'master-ndi-pmc-bz12.RDa'))
-
-dt.master.ndi.pmc.bz24 <- read.csv(here('data', 'processed','master_ndi_pmc_bz24.csv')) %>% 
+save(dt.master.ndi.pmc.bz12, 
+     file = here('data', 'processed', 'master-ndi-pmc-bz12.RDa'))
+
+# bz = 24 of sites of bz =6
+dt.master.ndi.pmc.bz24 <- read.csv(
+  here('data', 'processed','master_ndi_pmc_bz24.csv')) %>% 
   rename(Site.ID = Site_ID,
@@
          age = ENROLLEE_AGE)
-save(dt.master.ndi.pmc.bz24, file = here('data', 'processed', 'master-ndi-pmc-bz24.RDa'))
+save(dt.master.ndi.pmc.bz24, 
+     file = here('data', 'processed', 'master-ndi-pmc-bz24.RDa'))
 ```
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc.csv'),
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.fac, file = here('data', 'processed', 'ndi-fac.csv'),
+write.csv(dt.ndi.fac, 
+          file = here('data', 'processed', 'ndi-fac.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.fac.ex.ec, file = here('data', 'processed', 'ndi-fac-ex-ec.csv'),
+write.csv(dt.ndi.fac.ex.ec, 
+          file = here('data', 'processed', 'ndi-fac-ex-ec.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.carbon, file = here('data', 'processed', 'ndi-carbon.csv'),
+write.csv(dt.ndi.carbon, 
+          file = here('data', 'processed', 'ndi-carbon.csv'), 
           row.names = F)
@@
 
-write.csv(dt.ndi.carbon.tot, file = here('data', 'processed', 'ndi-carbon-tot.csv'),
+write.csv(dt.ndi.carbon.tot, 
+          file = here('data', 'processed', 'ndi-carbon-tot.csv'), 
           row.names = F)
@@
 
-write.csv(dt.ndi.carbon.tor, file = here('data', 'processed', 'ndi-carbon-tor.csv'),
+write.csv(dt.ndi.carbon.tor, 
+          file = here('data', 'processed', 'ndi-carbon-tor.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.residual, file = here('data', 'processed', 'ndi-pmc-residual.csv'),
+write.csv(dt.ndi.pmc.residual, 
+          file = here('data', 'processed', 'ndi-pmc-residual.csv'), 
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.raceA, file = here('data', 'processed', 'ndi-pmc-raceA.csv'),
+write.csv(dt.ndi.pmc.raceA, 
+          file = here('data', 'processed', 'ndi-pmc-raceA.csv'),
           row.names = F)
@@
 
-dt.raceB <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceB, sum) %>%
+dt.raceB <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceB, sum) %>%
   arrange(Site.ID, Year, Month, age, sex, race)
@@
 
-write.csv(dt.ndi.pmc.raceB, file = here('data', 'processed', 'ndi-pmc-raceB.csv'),
+write.csv(dt.ndi.pmc.raceB, 
+          file = here('data', 'processed', 'ndi-pmc-raceB.csv'),
           row.names = F)
@@
 
-dt.raceH <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceH, sum) %>%
+dt.raceH <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceH, sum) %>%
   arrange(Site.ID, Year, Month, age, sex, race)
@@
 
-write.csv(dt.ndi.pmc.raceH, file = here('data', 'processed', 'ndi-pmc-raceH.csv'),
+write.csv(dt.ndi.pmc.raceH, 
+          file = here('data', 'processed', 'ndi-pmc-raceH.csv'),
           row.names = F)
@@
 
-dt.raceW <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceW, sum) %>%
+dt.raceW <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceW, sum) %>%
   arrange(Site.ID, Year, Month, age, sex, race)
@@
 
-write.csv(dt.ndi.pmc.raceW, file = here('data', 'processed', 'ndi-pmc-raceW.csv'),
+write.csv(dt.ndi.pmc.raceW, 
+          file = here('data', 'processed', 'ndi-pmc-raceW.csv'),
           row.names = F)
@@
 
-dt.raceA <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceA, sum) %>%
+dt.raceA <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.raceA, sum) %>%
   arrange(Site.ID, Year, Month, age, sex, race)
@@
 
-write.csv(dt.ndi.fac.raceA, file = here('data', 'processed', 'ndi-fac-raceA.csv'),
+write.csv(dt.ndi.fac.raceA, 
+          file = here('data', 'processed', 'ndi-fac-raceA.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.fac.raceB, file = here('data', 'processed', 'ndi-fac-raceB.csv'),
+write.csv(dt.ndi.fac.raceB, 
+          file = here('data', 'processed', 'ndi-fac-raceB.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.fac.raceH, file = here('data', 'processed', 'ndi-fac-raceH.csv'),
+write.csv(dt.ndi.fac.raceH, 
+          file = here('data', 'processed', 'ndi-fac-raceH.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.fac.raceW, file = here('data', 'processed', 'ndi-fac-raceW.csv'),
+write.csv(dt.ndi.fac.raceW, 
+          file = here('data', 'processed', 'ndi-fac-raceW.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.urban, file = here('data', 'processed', 'ndi-pmc-urban.csv'),
+write.csv(dt.ndi.pmc.urban, 
+          file = here('data', 'processed', 'ndi-pmc-urban.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.rural, file = here('data', 'processed', 'ndi-pmc-rural.csv'),
+write.csv(dt.ndi.pmc.rural, 
+          file = here('data', 'processed', 'ndi-pmc-rural.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.urban.sesL, file = here('data', 'processed', 'ndi-pmc-urban-sesL.csv'),
+write.csv(dt.ndi.pmc.urban.sesL, 
+          file = here('data', 'processed', 'ndi-pmc-urban-sesL.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.urban.sesM, file = here('data', 'processed', 'ndi-pmc-urban-sesM.csv'),
+write.csv(dt.ndi.pmc.urban.sesM, 
+          file = here('data', 'processed', 'ndi-pmc-urban-sesM.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.urban.sesH, file = here('data', 'processed', 'ndi-pmc-urban-sesH.csv'),
+write.csv(dt.ndi.pmc.urban.sesH, 
+          file = here('data', 'processed', 'ndi-pmc-urban-sesH.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.west, file = here('data', 'processed', 'ndi-pmc-west.csv'),
+write.csv(dt.ndi.pmc.west, 
+          file = here('data', 'processed', 'ndi-pmc-west.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.midwest, file = here('data', 'processed', 'ndi-pmc-midwest.csv'),
+write.csv(dt.ndi.pmc.midwest, 
+          file = here('data', 'processed', 'ndi-pmc-midwest.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.south, file = here('data', 'processed', 'ndi-pmc-south.csv'),
+write.csv(dt.ndi.pmc.south, 
+          file = here('data', 'processed', 'ndi-pmc-south.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.northeast, file = here('data', 'processed', 'ndi-pmc-northeast.csv'),
+write.csv(dt.ndi.pmc.northeast, 
+          file = here('data', 'processed', 'ndi-pmc-northeast.csv'),
           row.names = F)
@@
 
-dt.age <- aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
+dt.age <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
   arrange(Site.ID, Year, Month, age, sex, race)
@@
 
-write.csv(dt.ndi.pmc.ageLE75, file = here('data', 'processed', 'ndi-pmc-ageLE75.csv'),
+write.csv(dt.ndi.pmc.ageLE75, 
+          file = here('data', 'processed', 'ndi-pmc-ageLE75.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.ageM75, file = here('data', 'processed', 'ndi-pmc-ageM75.csv'),
+write.csv(dt.ndi.pmc.ageM75, 
+          file = here('data', 'processed', 'ndi-pmc-ageM75.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.sexF, file = here('data', 'processed', 'ndi-pmc-sexF.csv'),
+write.csv(dt.ndi.pmc.sexF, 
+          file = here('data', 'processed', 'ndi-pmc-sexF.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.sexM, file = here('data', 'processed', 'ndi-pmc-sexM.csv'),
+write.csv(dt.ndi.pmc.sexM, 
+          file = here('data', 'processed', 'ndi-pmc-sexM.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc.brfss, file = here('data', 'processed', 'ndi-pmc-brfss.csv'),
+write.csv(dt.ndi.pmc.brfss, 
+          file = here('data', 'processed', 'ndi-pmc-brfss.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-bz6.csv'),
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-bz6.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-bz12.csv'),
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-bz12.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-bz24.csv'),
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-bz24.csv'),
           row.names = F)
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-5yr.csv'),
-          row.names = F)
-```
-
-```{r PMC - 4yr}
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 4yr - 5yr}
 dt.pmc <- dt.pmc.4yr.5yr %>% 
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-4yr-5yr.csv'),
-          row.names = F)
-```
-
-```{r PMC - 3yr}
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-4yr-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 3yr - 5yr}
 dt.pmc <- dt.pmc.3yr.5yr %>% 
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-3yr-5yr.csv'),
-          row.names = F)
-```
-
-```{r PMC - 2yr}
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-3yr-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 2yr - 5yr}
 dt.pmc <- dt.pmc.2yr.5yr %>% 
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-2yr-5yr.csv'),
-          row.names = F)
-```
-
-```{r PMC - 1yr}
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-2yr-5yr.csv'),
+          row.names = F)
+```
+
+```{r PMC - 1yr - 5yr}
 dt.pmc <- dt.pmc.1yr.5yr %>% 
@@
 
-write.csv(dt.ndi.pmc, file = here('data', 'processed', 'ndi-pmc-1yr-5yr.csv'),
-          row.names = F)
-```
+write.csv(dt.ndi.pmc, 
+          file = here('data', 'processed', 'ndi-pmc-1yr-5yr.csv'),
+          row.names = F)
+```

### 2021-01-25 code/data-processors/air-data-smooth-mvavg-function.R

@@ -27,7 +27,8 @@ Smoothed.Year <- function(si, pr, s, n){
     arrange(date2)
   
   gaps <- dt$date2[2:nrow(dt)]-dt$date2[1:(nrow(dt)-1)]
-  cuts <- c(0,which(gaps>90),nrow(dt))  #cut data into coherent bits with gaps <=90 days
+  #cut data into coherent bits with gaps <=90 days
+  cuts <- c(0,which(gaps>90),nrow(dt))  
   n.bits <- length(cuts)-1
   rows <- max(dt$year+dt$month/12)*12-12*min(dt$year+dt$month/12)+1
   results <- data.frame(Site.ID=rep(si,rows), Parameter.Symbol=rep(pr,rows), 
@@ -38,7 +39,8 @@ Smoothed.Year <- function(si, pr, s, n){
     dt1 <- dt[(cuts[c]+1):cuts[c+1],]
     if (nrow(dt1)>10){ #only try smoothing with at least 11 values
       df <- ceiling((max(dt1$date2)- min(dt1$date2))/365*4) #4 df per year
-      if (df<4){print(paste("Site.ID: ",si,", Para: ",pr,", c: ",c,", df: ",df,sep=""))}
+      if (df<4){print(
+        paste("Site.ID: ",si,", Para: ",pr,", c: ",c,", df: ",df,sep=""))}
       gres <- gam(Value~s(date2,fx=TRUE,k=df+1),data=dt1)
       
       pred.data <- as.data.frame(seq(min(dt1$date2),max(dt1$date2)))

### 2021-01-26 code/data-analysis/config-file-generator.Rmd
import different buffersize cms data add indentation
cms and config data for each bz plots for all cmps

@@
 title: "Config File Generator"
-output: html_notebook
+output: 
 ---
@@
 
+```{r ses adj. model for components - 5yr}
+dataname <- "ndi-pmc-5yr.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-5yr', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - 4yr-5yr}
+dataname <- "ndi-pmc-4yr-5yr.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-4yr', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - 3yr-5yr}
+dataname <- "ndi-pmc-3yr-5yr.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-3yr', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - 2yr-5yr}
+dataname <- "ndi-pmc-2yr-5yr.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-2yr', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - 1yr-5yr}
+dataname <- "ndi-pmc-1yr-5yr.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-1yr', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - bz 6}
+dataname <- "ndi-pmc-bz6.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-bz6', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - bz 12}
+dataname <- "ndi-pmc-bz12.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-bz12', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - bz 24}
+dataname <- "ndi-pmc-bz24.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','pmc-bz24', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
 ```{r under work - parse output}

### 2021-01-26 code/data-processors/cms-data-processor.Rmd
cms and config data for each bz plots for all cmps

@@
 load(here('data','processed','master-ndi-pmc-race.RDa'))
+load(here('data','processed','master-ndi-pmc-bz6.RDa'))
+load(here('data','processed','master-ndi-pmc-bz12.RDa'))
+load(here('data','processed','master-ndi-pmc-bz24.RDa'))
 load(here('data','processed','pmc-site-ndi.RDa'))
@@
 
-dt.ndi.pmc <- dt.master.ndi.pmc.bz6 %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
-         -no_death_uri, -no_death_ards) %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.pmc, 
+dt.ndi.pmc.bz6 <- dt.master.ndi.pmc.bz6 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz6, 
           file = here('data', 'processed', 'ndi-pmc-bz6.csv'),
@@
 
-dt.ndi.pmc <- dt.master.ndi.pmc.bz12 %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
-         -no_death_uri, -no_death_ards) %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.pmc, 
+dt.ndi.pmc.bz12 <- dt.master.ndi.pmc.bz12 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz12, 
           file = here('data', 'processed', 'ndi-pmc-bz12.csv'),
@@
 
-dt.ndi.pmc <- dt.master.ndi.pmc.bz24 %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
-         -no_death_uri, -no_death_ards) %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.pmc, 
+dt.ndi.pmc.bz24 <- dt.master.ndi.pmc.bz24 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz24, 
           file = here('data', 'processed', 'ndi-pmc-bz24.csv'),

### 2021-01-26 code/data-viz/plot-results.Rmd
cms and config data for each bz plots for all cmps

@@
 
-cmp <- c("OC", "NO3", "V", "Ni", "SO4", "Se",
+cmp <- c("Mn","Fe","V", "Ni","Cl", "Na", "SO4", "Se","Cu", "K", "OC", "NO3", 
          "Zn", "Pb", "Ca", "Si", "PM2.5")
@@
   ) +
-ggsave(here('output', 'plot','pmc-base.png'), width = 9.5, height = 5.5)
+ggsave(here('output', 'plot','pmc-base.png'), width = 9.5, height = 7.5)
 ```
@@
   ) +
-ggsave(here('output', 'plot','pmc-ses.png'), width = 9.5, height = 5.5)
+ggsave(here('output', 'plot','pmc-ses.png'), width = 9.5, height = 7.5)
 ```

### 2021-01-29 code/data-analysis/config-file-generator.Rmd
added SE to all datasets - created config file for fac-EM runs- cleaned outputs- plot outputs

@@
 ```{r List of PM Components Residuals}
-pmcres <- c("PM_AS","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
+pmcres <- c("PM_SE","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
             "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")
@@
 ```{r List of PM Components Sub}
-pmc.sub <- c("AS","CA","CL","NA","NI","NO3","OC",
+pmc.sub <- c("SE","CA","CL","NA","NI","NO3","OC",
              "PB","PM","SI","SO4","V","ZN")
@@
 ```{r List of PM Components Yr Sub}
-pmc.sub.yr <- c("Yr_AS","Yr_CA","Yr_CL","Yr_NA","Yr_NI","Yr_NO3","Yr_OC",
+pmc.sub.yr <- c("Yr_SE","Yr_CA","Yr_CL","Yr_NA","Yr_NI","Yr_NO3","Yr_OC",
              "Yr_PB","Yr_PM","Yr_SI","Yr_SO4","Yr_V","Yr_ZN")
@@
 cuz <- c("allcuz","nacc","acc","cvd","ihd","chf","cbv","resp","copd","pneu","canc","lungc")
+```
+
+```{r List of Causes of Death}
+cuz.sub <- c("allcuz","cvd","ihd","chf","cbv","resp","copd","pneu","canc","lungc")
 ```
@@
 
-```{r Config file - BRFSS Models}
-config.brfss <- c("# data path
+```{r Config file - EM Models 2}
+config.em.2 <- c("# data path
 data_path=/scratch/fatemehkp/projects/data/analysis/dataset
@@
 # the predictors are included in the model
-predictors=Yr_exposure, ses, BMI, Race, Smoke, Diabt, Asthma, Drink
+predictors=exposure, subg, subg_exposure, ses
 # stratas
@@
 
+```{r Config file - BRFSS Models}
+config.brfss <- c("# data path
+data_path=/scratch/fatemehkp/projects/data/analysis/dataset
+
+# loader settings
+# separated symbol for the given data
+sep=,
+# the predictors are included in the model
+predictors=exposure, ses, BMI, Race, Smoke, Diabt, Asthma, Drink
+# stratas
+stratas=StrID, SiteID
+# death
+death=no_death_outcome
+# life
+life=no_enrollee
+
+# optimizer settings
+# whether considering ties for death, default false
+isTies=false
+# if given multiple cores, set isParallelism as true
+isParallelism=true
+# whether penalizing the weight
+l2=false
+# if penalizing the weight, set the strength, otherwise it is useless.
+l2Strength=1
+
+# the application class name
+survival.class=CoxPH
+")
+```
+
 ```{r base model for components}
@@
   for( f in  filenames ){
-    cat(config.em, file=f)
+    cat(config.em.2, file=f)
     x <- readLines(f)
@@
 
+```{r ses adj. model for factors - age LE75}
+dataname <- "ndi-fac-ageLE75.csv"
+expo <- fac
+subg <- "aLE75"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-ageLE75', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - age M75}
+dataname <- "ndi-fac-ageM75.csv"
+expo <- fac
+subg <- "aM75"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-ageM75', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
 ```{r ses adj. model for components - Female}
@@
       writeLines(w, here('config-files','pmc-sexM', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - sex F}
+dataname <- "ndi-fac-sexF.csv"
+expo <- fac
+subg <- "sexF"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-sexF', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - sex M}
+dataname <- "ndi-fac-sexM.csv"
+expo <- fac
+subg <- "sexM"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz),1)){
+      w <- gsub("outcome", cuz[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz)*(i-1)
+      writeLines(w, here('config-files','fac-sexM', paste(k,'.txt', sep = "")))
     }
@@
 dataname <- "ndi-pmc-brfss.csv"
-expo <- pmc.sub
+expo <- pmc.sub.yr
 
@@
       writeLines(w, here('config-files','pmc-bz24', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components residuals - West}
+dataname <- "ndi-pmc-res-west.csv"
+expo <- pmcres
+subg <- "rW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','pmc-resid-west', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components residuals - Midwest}
+dataname <- "ndi-pmc-res-midwest.csv"
+expo <- pmcres
+subg <- "rMW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','pmc-resid-midwest', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components residuals - South}
+dataname <- "ndi-pmc-res-south.csv"
+expo <- pmcres
+subg <- "rS"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','pmc-resid-South', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components residuals - Northeast}
+dataname <- "ndi-pmc-res-northeast.csv"
+expo <- pmcres
+subg <- "rNE"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','pmc-resid-northeast', paste(k,'.txt', sep = "")))
     }

### 2021-01-29 code/data-analysis/output-cleaning.Rmd
added SE to all datasets - created config file for fac-EM runs- cleaned outputs- plot outputs

@@
 title: "Analysis Output files"
-output: html_notebook
 ---
-
-This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.
-
-Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.
 
@@
 load(here('data','processed','pmc-site-ndi.RDa'))
+load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
+load(here('data','processed','pmc-sub-2yr-5yr.RDa'))
+load(here('data','processed','pmc-sub-3yr-5yr.RDa'))
+load(here('data','processed','pmc-sub-4yr-5yr.RDa'))
+load(here('data','processed','pmc-sub-5yr.RDa'))
 ```
@@
 
-save(pmc.1yr.iqr, file = here('data','processed','pmc-1yr-iqr.RDa'))
-
 ### Factors
@@
 
-save(fac.1yr.iqr, file = here('data','processed','fac-1yr-iqr.RDa'))
-
 ### Factors excluding EC
@@
   mutate(Parameter = as.factor(Parameter))
-
-save(fac.ex.ec.1yr.iqr, file = here('data','processed','fac-ex-ec-1yr-iqr.RDa'))
 
@@
 
-save(carbon.1yr.iqr, file = here('data','processed','carbon-1yr-iqr.RDa'))
-
 carbon.method.1yr.iqr <- dt.site %>% 
@@
 
-save(carbon.method.1yr.iqr, file = here('data','processed','carbon-method-1yr-iqr.RDa'))
+### Components - urbanicity
+pmc.1yr.locset.iqr <- dt.pmc.site.ndi %>% 
+   mutate(Loc.Set = ifelse(!Location.Setting == "RURAL", "urban","rural")) %>% 
+  select(Site.ID, Loc.Set) %>% 
+  inner_join(dt.pmc.1yr) %>% 
+  group_by(Loc.Set) %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Components - region
+pmc.1yr.region.iqr <- dt.pmc.site.ndi %>% 
+  select(Site.ID, Region.IV) %>% 
+  inner_join(dt.pmc.1yr) %>% 
+  group_by(Region.IV) %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Components - 5yr
+pmc.5yr.iqr <- dt.pmc.5yr %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Components - 4yr
+pmc.4yr.5yr.iqr <- dt.pmc.4yr.5yr %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Components - 3yr
+pmc.3yr.5yr.iqr <- dt.pmc.3yr.5yr %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Components - 2yr
+pmc.2yr.5yr.iqr <- dt.pmc.2yr.5yr %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Components - 1yr
+pmc.1yr.5yr.iqr <- dt.pmc.1yr.5yr %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter))
 ```
@@
 ```
+
+```{r Output PMC Residuals}
+PM.IQR <- as.double(pmc.1yr.iqr[pmc.1yr.iqr$Parameter == 'PM', 'IQR'])
+load(here('output','analysis','out-pmc-ses.RDa'))
+PM <- out.pmc.ses %>% 
+  filter(Index == "PM2.5")
+
+out.pmc.resid <- read.csv(here('output','analysis','pmc_resid.csv')) %>% 
+  mutate(Parameter = gsub(".*PM_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(Para.to.Index) %>% 
+  mutate(Index = paste0('-', Index)) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * PM.IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * PM.IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * PM.IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, HR, HR.L, HR.U) %>% 
+  add_row(PM)
+
+save(out.pmc.resid, file = here('output','analysis','out-pmc-resid.RDa'))
+```
+
+```{r Output Factors Residuals}
+PM.IQR <- as.double(pmc.1yr.iqr[pmc.1yr.iqr$Parameter == 'PM', 'IQR'])
+load(here('output','analysis','out-pmc-ses.RDa'))
+PM <- out.pmc.ses %>% 
+  filter(Index == "PM2.5")
+
+out.fac.resid <- read.csv(here('output','analysis','fac_resid.csv')) %>% 
+  mutate(Parameter = gsub(".*PM_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(Factor.ex.ec.to.Index) %>% 
+  mutate(Index = paste0('-', Index)) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * PM.IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * PM.IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * PM.IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, HR, HR.L, HR.U) %>% 
+  add_row(PM)
+
+save(out.fac.resid, file = here('output','analysis','out-fac-resid.RDa'))
+```
+
+```{r Output PMC Race}
+out.pmc.race = data.frame()
+for (i in c("A", "B", "H", "W")){
+  dt <- read.csv(here('output','analysis',paste('pmc_race',i,'.csv', sep= ""))) %>% 
+    mutate(Race = i)
+  out.pmc.race  <-  rbind(out.pmc.race, dt)
+}
+
+out.pmc.race <- out.pmc.race %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Race, HR, HR.L, HR.U)
+
+save(out.pmc.race, file = here('output','analysis','out-pmc-race.RDa'))
+```
+
+```{r Output PMC Urbanicity}
+out.pmc.urbanicity = data.frame()
+for (i in c("urban", "rural")){
+  dt <- read.csv(here('output','analysis',paste('pmc_',i,'.csv', sep= ""))) %>% 
+    mutate(Loc.Set = i)
+  out.pmc.urbanicity  <-  rbind(out.pmc.urbanicity, dt)
+}
+
+out.pmc.urbanicity <- out.pmc.urbanicity %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Loc.Set, HR, HR.L, HR.U)
+
+save(out.pmc.urbanicity, file = here('output','analysis','out-pmc-urbanicity.RDa'))
+```
+
+```{r Output PMC Urban - SES}
+out.pmc.sescat = data.frame()
+for (i in c("L", "M", "H")){
+  dt <- read.csv(here('output','analysis',paste('pmc_urban_ses',i,'.csv', sep= ""))) %>% 
+    mutate(SES.Cat = i)
+  out.pmc.sescat  <-  rbind(out.pmc.sescat, dt)
+}
+
+out.pmc.sescat <- out.pmc.sescat %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, SES.Cat, HR, HR.L, HR.U)
+
+save(out.pmc.sescat, file = here('output','analysis','out-pmc-sescat.RDa'))
+```
+
+```{r Output PMC Region}
+out.pmc.region = data.frame()
+for (i in c("west", "midwest", "south", "northeast")){
+  dt <- read.csv(here('output','analysis',paste('pmc_',i,'.csv', sep= ""))) %>% 
+    mutate(Region = i)
+  out.pmc.region  <-  rbind(out.pmc.region, dt)
+}
+
+out.pmc.region <- out.pmc.region %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Region, HR, HR.L, HR.U)
+
+save(out.pmc.region, file = here('output','analysis','out-pmc-region.RDa'))
+```
+
+```{r Output PMC Age}
+out.pmc.age = data.frame()
+for (i in c("LE75", "M75")){
+  dt <- read.csv(here('output','analysis',paste('pmc_age',i,'.csv', sep= ""))) %>% 
+    mutate(Age = i)
+  out.pmc.age  <-  rbind(out.pmc.age, dt)
+}
+
+out.pmc.age <- out.pmc.age %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Age, HR, HR.L, HR.U)
+
+save(out.pmc.age, file = here('output','analysis','out-pmc-age.RDa'))
+```
+
+```{r Output PMC Sex}
+out.pmc.sex = data.frame()
+for (i in c("F", "M")){
+  dt <- read.csv(here('output','analysis',paste('pmc_sex',i,'.csv', sep= ""))) %>% 
+    mutate(Sex = i)
+  out.pmc.sex  <-  rbind(out.pmc.sex, dt)
+}
+
+out.pmc.sex <- out.pmc.sex %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Sex, HR, HR.L, HR.U)
+
+save(out.pmc.sex, file = here('output','analysis','out-pmc-sex.RDa'))
+```
+
+```{r Output PMC BRFSS}
+out.pmc.brfss = data.frame()
+for (i in c("brfss0", "brfss")){
+  dt <- read.csv(here('output','analysis',paste('pmc_',i,'.csv', sep= ""))) %>% 
+    mutate(BRFSS = i)
+  out.pmc.brfss  <-  rbind(out.pmc.brfss, dt)
+}
+
+out.pmc.brfss <- out.pmc.brfss %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, BRFSS, HR, HR.L, HR.U)
+
+save(out.pmc.brfss, file = here('output','analysis','out-pmc-brfss.RDa'))
+```
+
+```{r Output PMC bufferzone}
+out.pmc.buffer = data.frame()
+for (i in c("6", "12", "24")){
+  dt <- read.csv(here('output','analysis',paste('pmc_bz',i,'.csv', sep= ""))) %>% 
+    mutate(Buffer = i)
+  out.pmc.buffer  <-  rbind(out.pmc.buffer, dt)
+}
+
+out.pmc.buffer <- out.pmc.buffer %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Buffer, HR, HR.L, HR.U)
+
+save(out.pmc.buffer, file = here('output','analysis','out-pmc-buffer.RDa'))
+```
+
+```{r Output PMC Exposure window}
+out.pmc.expo = data.frame()
+for (i in c("1", "2", "3", "4", "5")){
+  dt <- read.csv(here('output','analysis',paste('pmc_',i,'yr','.csv', sep= ""))) %>% 
+    mutate(Window = i)
+  out.pmc.expo  <-  rbind(out.pmc.expo, dt)
+}
+
+out.pmc.expo <- out.pmc.expo %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Window, HR, HR.L, HR.U)
+
+save(out.pmc.expo, file = here('output','analysis','out-pmc-expo.RDa'))
+```

### 2021-01-29 code/data-processors/air-data-processor.Rmd
added SE to all datasets - created config file for fac-EM runs- cleaned outputs- plot outputs

@@
 ```{r Smoothing Data & Caluculating 1 to 5-yr mvavg for each month}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
-             "PB", "PM", "SI", "SO4", "V", "ZN")
+cmp.sub <- c("CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SE", "SI", "SO4", "V", "ZN")
 dt.air <- dt.pmc.daily %>% 
   select(Site.ID, Date, cmp.sub) %>% 
-  pivot_longer(cols = AS:ZN,
+  pivot_longer(cols = cmp.sub,
                names_to = "Parameter.Symbol",

### 2021-01-29 code/data-processors/cms-data-processor.Rmd
added SE to all datasets - created config file for fac-EM runs- cleaned outputs- plot outputs

@@
 ```{r PMC Residual}
-cmp.sub <- c("PM_AS","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
+cmp.sub <- c("PM_SE","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
             "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")
@@
 ```{r PMC race}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 dt.ndi.pmc.raceA <- dt.ndi.pmc.raceA %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.raceB <- dt.ndi.pmc.raceB %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.raceH <- dt.ndi.pmc.raceH %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.raceW <- dt.ndi.pmc.raceW %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 ```{r PMC urbanicity}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 dt.ndi.pmc.urban <- dt.ndi.pmc.urban %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.rural <- dt.ndi.pmc.rural %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 dt.ndi.pmc.urban.sesL <- dt.ndi.pmc.urban.ses %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.urban.sesM <- dt.ndi.pmc.urban.ses %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.urban.sesH <- dt.ndi.pmc.urban.ses %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 ```{r PMC Region}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 dt.ndi.pmc.west <- dt.ndi.pmc.west %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.midwest <- dt.ndi.pmc.midwest %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.south <- dt.ndi.pmc.south %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.northeast <- dt.ndi.pmc.northeast %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 
+```{r PMC Residual Region}
+cmp.sub <- c("PM_SE","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
+            "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")
+
+dt.pmc <- dt.pmc.residual.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.site <- dt.pmc.site.ndi %>% 
+  select(Site.ID, Region.IV)
+
+### West = 1
+dt.ndi.pmc.west <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rW = ifelse(Region.IV == 1, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.west[ ,paste0("rW_",cmp)] <- 
+      dt.ndi.pmc.west[ ,cmp] * dt.ndi.pmc.west$rW
+}
+
+dt.ndi.pmc.res.west <- dt.ndi.pmc.west %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rW, everything())
+
+write.csv(dt.ndi.pmc.res.west, 
+          file = here('data', 'processed', 'ndi-pmc-res-west.csv'),
+          row.names = F)
+
+### Midwest = 2
+
+dt.ndi.pmc.midwest <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rMW = ifelse(Region.IV == 2, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.midwest[ ,paste0("rMW_",cmp)] <- 
+      dt.ndi.pmc.midwest[ ,cmp] * dt.ndi.pmc.midwest$rMW
+}
+
+dt.ndi.pmc.res.midwest <- dt.ndi.pmc.midwest %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rMW, everything())
+
+write.csv(dt.ndi.pmc.res.midwest, 
+          file = here('data', 'processed', 'ndi-pmc-res-midwest.csv'),
+          row.names = F)
+
+### South = 3
+
+dt.ndi.pmc.south <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rS = ifelse(Region.IV == 3, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.south[ ,paste0("rS_",cmp)] <- 
+      dt.ndi.pmc.south[ ,cmp] * dt.ndi.pmc.south$rS
+}
+
+dt.ndi.pmc.res.south <- dt.ndi.pmc.south %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rS, everything())
+
+write.csv(dt.ndi.pmc.res.south, 
+          file = here('data', 'processed', 'ndi-pmc-res-south.csv'),
+          row.names = F)
+
+### Northeast = 4
+
+dt.ndi.pmc.northeast <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rNE = ifelse(Region.IV == 4, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.northeast[ ,paste0("rNE_",cmp)] <- 
+      dt.ndi.pmc.northeast[ ,cmp] * dt.ndi.pmc.northeast$rNE
+}
+
+dt.ndi.pmc.res.northeast <- dt.ndi.pmc.northeast %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rNE, everything())
+
+write.csv(dt.ndi.pmc.res.northeast, 
+          file = here('data', 'processed', 'ndi-pmc-res-northeast.csv'),
+          row.names = F)
+
+```
+
 ```{r PMC Age}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 dt.ndi.pmc.ageLE75 <- dt.ndi.pmc.ageLE75 %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.ageM75 <- dt.ndi.pmc.ageM75 %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 
+```{r Factor Age}
+fac <- c("Factor1","Factor2","Factor3","Factor4",
+         "Factor5","Factor6","Factor7","Factor8")
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+### Age 
+dt.age <- dt.master.ndi.pmc %>%
+  mutate(age = ifelse(age <= 75, "LE", "M")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards)
+
+dt.age <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+### LE 75
+dt.ndi.fac.ageLE75 <- dt.age %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aLE75 = ifelse(age == "LE", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.ageLE75[ ,paste0("aLE75_",cmp)] <- 
+      dt.ndi.fac.ageLE75[ ,cmp] * dt.ndi.fac.ageLE75$aLE75
+}
+
+dt.ndi.fac.ageLE75 <- dt.ndi.fac.ageLE75 %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aLE75, everything())
+
+write.csv(dt.ndi.fac.ageLE75, 
+          file = here('data', 'processed', 'ndi-fac-ageLE75.csv'),
+          row.names = F)
+
+### M 75
+dt.ndi.fac.ageM75 <- dt.age %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aM75 = ifelse(age == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.ageM75[ ,paste0("aM75_",cmp)] <- 
+      dt.ndi.fac.ageM75[ ,cmp] * dt.ndi.fac.ageM75$aM75
+}
+
+dt.ndi.fac.ageM75 <- dt.ndi.fac.ageM75 %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aM75, everything())
+
+write.csv(dt.ndi.fac.ageM75, 
+          file = here('data', 'processed', 'ndi-fac-ageM75.csv'),
+          row.names = F)
+```
+
 ```{r PMC Sex}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 dt.ndi.pmc.sexF <- dt.sex %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
   mutate(sexF = ifelse(sex == "F", 0,1),
@@
 dt.ndi.pmc.sexF <- dt.ndi.pmc.sexF %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 dt.ndi.pmc.sexM <- dt.sex %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
   mutate(sexM = ifelse(sex == "M", 0,1),
@@
 dt.ndi.pmc.sexM <- dt.ndi.pmc.sexM %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
   rename(SiteID = Site.ID) %>% 
@@
 
+```{r Factor Sex}
+fac <- c("Factor1","Factor2","Factor3","Factor4",
+         "Factor5","Factor6","Factor7","Factor8")
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.sex <- dt.master.ndi.pmc %>% 
+    select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>%  
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses)
+
+### Female
+dt.ndi.fac.sexF <- dt.sex %>% 
+  mutate(sexF = ifelse(sex == "F", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.sexF[ ,paste0("sexF_",cmp)] <- 
+      dt.ndi.fac.sexF[ ,cmp] * dt.ndi.fac.sexF$sexF
+}
+
+dt.ndi.fac.sexF <- dt.ndi.fac.sexF %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexF, everything())
+
+write.csv(dt.ndi.fac.sexF, 
+          file = here('data', 'processed', 'ndi-fac-sexF.csv'),
+          row.names = F)
+
+### Male
+dt.ndi.fac.sexM <- dt.sex %>% 
+  mutate(sexM = ifelse(sex == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.sexM[ ,paste0("sexM_",cmp)] <- 
+      dt.ndi.fac.sexM[ ,cmp] * dt.ndi.fac.sexM$sexM
+}
+
+dt.ndi.fac.sexM <- dt.ndi.fac.sexM %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexM, everything())
+
+write.csv(dt.ndi.fac.sexM, 
+          file = here('data', 'processed', 'ndi-fac-sexM.csv'),
+          row.names = F)
+```
+
 ```{r PMC BRFSS}
 dt.pmc <- dt.pmc.1yr %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))
 
@@
 
+```{r Factor BRFSS}
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.fac.brfss <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>%  
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.brfss.site) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.fac.brfss, 
+          file = here('data', 'processed', 'ndi-fac-brfss.csv'),
+          row.names = F)
+```
+
 ```{r PMC BZ 6}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
   select(Site.ID, Year, Month, cmp.sub) %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))
 
@@
 ```{r PMC BZ 12}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 ```{r PMC BZ 24}
-cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
              "PB", "PM", "SI", "SO4", "V", "ZN")
@@
 dt.pmc <- dt.pmc.5yr %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.5 <- dt.master.ndi.pmc %>% 
   mutate(StrID = paste(age, sex, race)) %>% 
@@
 
-write.csv(dt.ndi.pmc, 
+write.csv(dt.ndi.pmc.5, 
           file = here('data', 'processed', 'ndi-pmc-5yr.csv'),
@@
 dt.pmc <- dt.pmc.4yr.5yr %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.4 <- dt.master.ndi.pmc %>% 
   mutate(StrID = paste(age, sex, race)) %>% 
@@
 
-write.csv(dt.ndi.pmc, 
+write.csv(dt.ndi.pmc.4, 
           file = here('data', 'processed', 'ndi-pmc-4yr-5yr.csv'),
@@
 dt.pmc <- dt.pmc.3yr.5yr %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.3 <- dt.master.ndi.pmc %>% 
   mutate(StrID = paste(age, sex, race)) %>% 
@@
 
-write.csv(dt.ndi.pmc, 
+write.csv(dt.ndi.pmc.3, 
           file = here('data', 'processed', 'ndi-pmc-3yr-5yr.csv'),
@@
 dt.pmc <- dt.pmc.2yr.5yr %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.2 <- dt.master.ndi.pmc %>% 
   mutate(StrID = paste(age, sex, race)) %>% 
@@
 
-write.csv(dt.ndi.pmc, 
+write.csv(dt.ndi.pmc.2, 
           file = here('data', 'processed', 'ndi-pmc-2yr-5yr.csv'),
@@
 dt.pmc <- dt.pmc.1yr.5yr %>% 
-  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.pmc <- dt.master.ndi.pmc %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.1 <- dt.master.ndi.pmc %>% 
   mutate(StrID = paste(age, sex, race)) %>% 
@@
 
-write.csv(dt.ndi.pmc, 
+write.csv(dt.ndi.pmc.1, 
           file = here('data', 'processed', 'ndi-pmc-1yr-5yr.csv'),

### 2021-01-29 code/data-viz/plot-results.Rmd
added SE to all datasets - created config file for fac-EM runs- cleaned outputs- plot outputs

@@
 load(here('output','analysis','out-fac-ses.RDa'))
-
+load(here('output','analysis','out-fac-ex-ec-base.RDa'))
+load(here('output','analysis','out-fac-ex-ec-ses.RDa'))
+load(here('output','analysis','out-pmc-resid.RDa'))
+load(here('output','analysis','out-fac-resid.RDa'))
+load(here('output','analysis','out-pmc-region.RDa'))
+load(here('output','analysis','out-pmc-race.RDa'))
+load(here('output','analysis','out-pmc-urbanicity.RDa'))
+load(here('output','analysis','out-pmc-sescat.RDa'))
+load(here('output','analysis','out-pmc-brfss.RDa'))
+load(here('output','analysis','out-pmc-age.RDa'))
+load(here('output','analysis','out-pmc-sex.RDa'))
+load(here('output','analysis','out-pmc-buffer.RDa'))
+load(here('output','analysis','out-pmc-expo.RDa'))
 ```
@@
          )
-# #610038
-plot_cols <- c("red")
+
+plot_cols <- c("#D71A21")
 
@@
   ) +
-ggsave(here('output', 'plot','pmc-base.png'), width = 9.5, height = 7.5)
+ggsave(here('output', 'plot','pmc-base.png'), width = 6.5, height = 8.5)
 ```
@@
   ) +
-ggsave(here('output', 'plot','pmc-ses.png'), width = 9.5, height = 7.5)
+ggsave(here('output', 'plot','pmc-ses.png'), width = 6.5, height = 8.5)
 ```
@@
   ) +
-ggsave(here('output', 'plot','fac-base.png'), width = 9.5, height = 5.5)
+ggsave(here('output', 'plot','fac-base-ec.png'), width = 6.5, height = 8.5)
 ```
@@
   ) +
-ggsave(here('output', 'plot','fac-ses.png'), width = 9.5, height = 5.5)
+ggsave(here('output', 'plot','fac-ses-ec.png'), width = 6.5, height = 8.5)
 ```
@@
   ) +
-ggsave(here('output', 'plot','fac-ex-ec-base.png'), width = 9.5, height = 5.5)
+ggsave(here('output', 'plot','fac-base.png'), width = 6.5, height = 8.5)
 ```
@@
   ) +
-ggsave(here('output', 'plot','fac-ex-ec-ses.png'), width = 9.5, height = 5.5)
+ggsave(here('output', 'plot','fac-ses.png'), width = 6.5, height = 8.5)
 ```
@@
 ```{r - Components - PM Residual}
-data <- read_excel('Comp_PMResi.xlsx')
-
-cmp <- c("-OC", "-NO3", "-V", "-Ni", "-SO4", "-Se",
+data <- out.pmc.resid
+
+cmp <- c("-V", "-Ni","-Cl", "-Na", "-SO4", "-Se", "-OC", "-NO3", 
          "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
-         "Respiratory", "Pneumonia",
-         "Cancer","Lung Cancer") # "CHF", "COPD",
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
 
@@
 
-plot_cols <- c("red")
+plot_cols <- c("#D71A21")
 
@@
 
-facet_wrap( ~ Cause, ncol = 4, scales = "fixed") +
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
   theme_classic() + 
@@
   ) +
-ggsave("CMP_PMResi_1114.jpeg", width = 9.5, height = 5.5)
+ggsave(here('output', 'plot','pmc-resid.png'), width = 6.5, height = 8.5)
 ```
@@
 ```{r - Factor - PM Residual}
-data <- read_excel('Fac_PMResi.xlsx')
-
-So <- c("-Traffic", "-Oil", "-Coal", 
-         "-Metals","-Soil", "PM2.5") # "-Steel", "-Salt", "-Biomass", 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
-         "Respiratory", "Pneumonia",
-         "Cancer","Lung Cancer") # "CHF", "COPD",
+data <- out.fac.resid
+
+So <- c("-Oil", "-Salt", "-Coal", 
+         "-Traffic", "-Metals", "-Soil", "PM2.5")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
 
@@
 
-facet_wrap( ~ Cause, ncol = 4, scales = "fixed") +
+facet_wrap( ~ Cause, nrow = 2, scales = "fixed") +
   theme_classic() + 
@@
   ) +
-ggsave("Fac_PMResi_1114.jpeg", width = 9.5, height = 4.5)
+ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 8.5)
 ```
@@
 ```{r - Components Region}
-data <- read_excel('Comp_Region.xlsx')
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
-          "Ni", "V", "NO3", "OC") 
+data <- out.pmc.region
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
          Index = factor(Index, levels = cmp),
+         Tag = ifelse(Region == "west", "d",
+                      ifelse(Region == "midwest", "c",
+                             ifelse(Region == "south", "b", "a"))),
          Tag = as.factor(Tag)
@@
   theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
         panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
@@
 
-ggsave("CMP_Region_1113.jpeg", p, width = 9.5, height = 12)
+ggsave(here('output', 'plot','pmc-region.png'),p, width = 6.5, height = 8.5)
 ```
@@
 ```{r - Components Race}
-data <- read_excel('Comp_Race.xlsx')
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
-          "Ni", "V", "NO3", "OC") 
+data <- out.pmc.race
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
          Index = factor(Index, levels = cmp),
+         Tag = ifelse(Race == "A", "d",
+                      ifelse(Race == "B", "c",
+                             ifelse(Race == "H", "b", "a"))),
          Tag = as.factor(Tag)
@@
 
-ggsave("CMP_Race_1113.jpeg", p, width = 9.5, height = 12)
+ggsave(here('output', 'plot','pmc-race.png'),p, width = 6.5, height = 8.5)
+```
+
+```{r - Components Age}
+data <- out.pmc.age
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(Age == "LE75", "b", "a"),
+         Tag = as.factor(Tag)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_labs <- c("> 75 years", "<= 75 years")
+plot_cols <- c("red", "blue")
+
+p <- grid.arrange(
+ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  xlab("") +
+  ylab("") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  theme_classic() + 
+  theme(panel.spacing.x = unit(0.25,'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
+        strip.text.y.left = element_text(angle = 0),
+        strip.background = element_rect(fill = "slategray2"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = 'bottom',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 10, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in')) +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+
+ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  xlab("") +
+  ylab("") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  theme_classic() + 
+  theme(panel.spacing.x = unit(0.25,'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
+        strip.text.y.left = element_text(angle = 0),
+        strip.background = element_rect(fill = "slategray2"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = 'bottom',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 10, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in')) +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+nrow = 2)
+
+ggsave(here('output', 'plot','pmc-age.png'),p, width = 6.5, height = 8.5)
+```
+
+```{r - Components Sex}
+data <- out.pmc.sex
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(Sex == "F", "b", "a"),
+         Tag = as.factor(Tag)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_labs <- c("Male", "Female")
+plot_cols <- c("red", "blue")
+
+p <- grid.arrange(
+ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  xlab("") +
+  ylab("") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  theme_classic() + 
+  theme(panel.spacing.x = unit(0.25,'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
+        strip.text.y.left = element_text(angle = 0),
+        strip.background = element_rect(fill = "slategray2"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = 'bottom',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 10, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in')) +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+
+ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  xlab("") +
+  ylab("") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  theme_classic() + 
+  theme(panel.spacing.x = unit(0.25,'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
+        strip.text.y.left = element_text(angle = 0),
+        strip.background = element_rect(fill = "slategray2"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = 'bottom',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 10, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in')) +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+nrow = 2)
+
+ggsave(here('output', 'plot','pmc-sex.png'),p, width = 6.5, height = 8.5)
 ```
@@
 ```{r Components Urban}
-data <- read_excel('Comp_Urban.xlsx')
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
-          "Ni", "V", "NO3", "OC") 
+data <- out.pmc.urbanicity
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
          Index = factor(Index, levels = cmp),
+         Tag = ifelse(Loc.Set == "urban", "b", "a"),
          Tag = as.factor(Tag)
@@
   theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25, 0, 0.25, 0),'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
         panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
@@
 
-ggsave("CMP_Urban_1113.jpeg", p, width = 9.5, height = 10)
+ggsave(here('output', 'plot','pmc-urbanicity.png'),p, width = 6.5, height = 8.5)
 ```
@@
 ```{r Components SES-Urban}
-data <- read_excel('Comp_SESUrban.xlsx')
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
-          "Ni", "V", "NO3", "OC") 
+data <- out.pmc.sescat
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V")
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
          Index = factor(Index, levels = cmp),
+         Tag = ifelse(SES.Cat == "L", "c",
+                      ifelse(SES.Cat == "M", "b", "a")),
          Tag = as.factor(Tag)
@@
 
-ggsave("CMP_SESUrban_1113.jpeg", p, width = 9.5, height = 11)
+ggsave(here('output', 'plot','pmc-sescat.png'),p, width = 6.5, height = 8.5)
 ```
@@
 ```{r - Components BRFSS}
-data <- read_excel('Comp_BRFSS.xlsx')
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
-          "Ni", "V", "NO3", "OC") 
+data <- out.pmc.brfss
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V")
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
          Index = factor(Index, levels = cmp),
+         Tag = ifelse(BRFSS == "brfss0", "b", "a"),
          Tag = as.factor(Tag)
@@
 
-ggsave("CMP_BRFSS_1113.jpeg", p, width = 9.5, height = 10)
+ggsave(here('output', 'plot','pmc-brfss.png'),p, width = 6.5, height = 8.5)
 ```
@@
 ```{r Components Buffer}
-data <- read_excel('Comp_Buffer.xlsx')
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
-          "Ni", "V", "NO3", "OC") 
+data <- out.pmc.buffer
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V")
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
          Index = factor(Index, levels = cmp),
+         Tag = ifelse(Buffer == 6, "c",
+                      ifelse(Buffer == 12, "b", "a")),
          Tag = as.factor(Tag)
@@
 
-ggsave("CMP_Buffer_1113.jpeg", p, width = 9.5, height = 10)
-```
-
-```{r Components Mvavg}
-data <- read_excel('Comp_Mvavg.xlsx')
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "Se", "SO4", 
-          "Ni", "V", "NO3", "OC") 
+ggsave(here('output', 'plot','pmc-buffer.png'),p, width = 6.5, height = 8.5)
+```
+
+```{r Components Exposure window}
+data <- out.pmc.expo
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V")
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
          Index = factor(Index, levels = cmp),
+         Tag = ifelse(Window == 1, "e",
+                      ifelse(Window == 2, "d",
+                             ifelse(Window == 3, "c",
+                                    ifelse(Window == 4, "b", "a")))),
          Tag = as.factor(Tag)
@@
 
-ggsave("CMP_Mvavg_1113.jpeg", p, width = 9.5, height = 10)
-```
+ggsave(here('output', 'plot','pmc-expo.png'),p, width = 6.5, height = 8.5)
+```

### 2021-01-30 code/data-analysis/config-file-generator.Rmd
new analysis - configs - clean outputs - plots

@@
 
+```{r ses adj. model for factors - age LE75}
+dataname <- "ndi-fac-ageLE75.csv"
+expo <- fac
+subg <- "aLE75"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','fac-ageLE75', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
 ```{r ses adj. model for factors - race Asian}
@@
     s <- gsub("subg", subg, z)
-    for (j in seq(1,length(cuz),1)){
-      w <- gsub("outcome", cuz[j], s)
-      cat(w, file=f, sep="\n")
-      k=j+length(cuz)*(i-1)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
       writeLines(w, here('config-files','fac-ageLE75', paste(k,'.txt', sep = "")))
@@
     s <- gsub("subg", subg, z)
-    for (j in seq(1,length(cuz),1)){
-      w <- gsub("outcome", cuz[j], s)
-      cat(w, file=f, sep="\n")
-      k=j+length(cuz)*(i-1)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
       writeLines(w, here('config-files','fac-ageM75', paste(k,'.txt', sep = "")))
@@
     s <- gsub("subg", subg, z)
-    for (j in seq(1,length(cuz),1)){
-      w <- gsub("outcome", cuz[j], s)
-      cat(w, file=f, sep="\n")
-      k=j+length(cuz)*(i-1)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
       writeLines(w, here('config-files','fac-sexF', paste(k,'.txt', sep = "")))
@@
     s <- gsub("subg", subg, z)
-    for (j in seq(1,length(cuz),1)){
-      w <- gsub("outcome", cuz[j], s)
-      cat(w, file=f, sep="\n")
-      k=j+length(cuz)*(i-1)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
       writeLines(w, here('config-files','fac-sexM', paste(k,'.txt', sep = "")))

### 2021-01-30 code/data-analysis/output-cleaning.Rmd
new analysis - configs - clean outputs - plots

@@
 ```{r calculating IQRS}
+
 ### Components
@@
 pmc.5yr.iqr <- dt.pmc.5yr %>% 
-  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
-  pivot_longer(cols = AS:ZN,
+  summarise_at(vars(CA:SE), ~IQR(.x)) %>% 
+  pivot_longer(cols = CA:SE,
                names_to = "Parameter",
@@
 pmc.4yr.5yr.iqr <- dt.pmc.4yr.5yr %>% 
-  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
-  pivot_longer(cols = AS:ZN,
+  summarise_at(vars(CA:SE), ~IQR(.x)) %>% 
+  pivot_longer(cols = CA:SE,
                names_to = "Parameter",
@@
 pmc.3yr.5yr.iqr <- dt.pmc.3yr.5yr %>% 
-  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
-  pivot_longer(cols = AS:ZN,
+  summarise_at(vars(CA:SE), ~IQR(.x)) %>% 
+  pivot_longer(cols = CA:SE,
                names_to = "Parameter",
@@
 pmc.2yr.5yr.iqr <- dt.pmc.2yr.5yr %>% 
-  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
-  pivot_longer(cols = AS:ZN,
+  summarise_at(vars(CA:SE), ~IQR(.x)) %>% 
+  pivot_longer(cols = CA:SE,
                names_to = "Parameter",
@@
 pmc.1yr.5yr.iqr <- dt.pmc.1yr.5yr %>% 
-  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
-  pivot_longer(cols = AS:ZN,
+  summarise_at(vars(CA:SE), ~IQR(.x)) %>% 
+  pivot_longer(cols = CA:SE,
                names_to = "Parameter",
@@
 ```{r Output PMC Base}
-out.pmc.base <- read.csv(here('output','analysis','pmc_base.csv')) %>% 
+out.pmc.base <- read.csv(here('output','analysis','pmc-base.csv')) %>% 
   mutate(Parameter = gsub(".*Yr_", "", Predictor),
@@
 ```{r Output PMC SES-Adj}
-out.pmc.ses <- read.csv(here('output','analysis','pmc_ses.csv')) %>% 
+out.pmc.ses <- read.csv(here('output','analysis','pmc-ses.csv')) %>% 
   mutate(Parameter = gsub(".*Yr_", "", Predictor),
@@
 ```{r Output Factors Base}
-out.fac.base <- read.csv(here('output','analysis','fac_base.csv')) %>% 
+out.fac.base.ec <- read.csv(here('output','analysis','fac-base.csv')) %>% 
   rename(Parameter = Predictor) %>% 
@@
 
-save(out.fac.base, file = here('output','analysis','out-fac-base.RDa'))
+save(out.fac.base.ec, file = here('output','analysis','out-fac-base-ec.RDa'))
 ```
@@
 ```{r Output Factors SES-Adj}
-out.fac.ses <- read.csv(here('output','analysis','fac_ses.csv')) %>% 
+out.fac.ses.ec <- read.csv(here('output','analysis','fac-ses.csv')) %>% 
   rename(Parameter = Predictor) %>% 
@@
 
-save(out.fac.ses, file = here('output','analysis','out-fac-ses.RDa'))
+save(out.fac.ses.ec, file = here('output','analysis','out-fac-ses-ec.RDa'))
 ```
@@
 ```{r Output Factors Ex. EC Base}
-out.fac.ex.ec.base <- read.csv(here('output','analysis','fac_ex_ec_base.csv')) %>% 
+out.fac.base <- read.csv(here('output','analysis','fac-ex-ec-base.csv')) %>% 
   rename(Parameter = Predictor) %>% 
@@
 
-save(out.fac.ex.ec.base, file = here('output','analysis','out-fac-ex-ec-base.RDa'))
+save(out.fac.base, file = here('output','analysis','out-fac-base.RDa'))
 ```
@@
 ```{r Output Factors Ex. EC SES-Adj}
-out.fac.ex.ec.ses <- read.csv(here('output','analysis','fac_ex_ec_ses.csv')) %>% 
+out.fac.ses <- read.csv(here('output','analysis','fac-ex-ec-ses.csv')) %>% 
   rename(Parameter = Predictor) %>% 
@@
 
-save(out.fac.ex.ec.ses, file = here('output','analysis','out-fac-ex-ec-ses.RDa'))
+save(out.fac.ses, file = here('output','analysis','out-fac-ses.RDa'))
 ```
@@
 ```{r Output Carbon SES-Adj}
-out.carbon.ses <- read.csv(here('output','analysis','carbon_ses.csv')) %>% 
+out.carbon.ses <- read.csv(here('output','analysis','carbon-ses.csv')) %>% 
   mutate(Parameter = gsub(".*Yr_", "", Predictor),
@@
 ```{r Output Carbon TOT SES-Adj}
-out.carbon.tot.ses <- read.csv(here('output','analysis','tot_ses.csv')) %>% 
+out.carbon.tot.ses <- read.csv(here('output','analysis','tot-ses.csv')) %>% 
   mutate(Parameter = gsub(".*Yr_", "", Predictor),
@@
 ```{r Output Carbon TOR SES-Adj}
-out.carbon.tor.ses <- read.csv(here('output','analysis','tot_ses.csv')) %>% 
+out.carbon.tor.ses <- read.csv(here('output','analysis','tot-ses.csv')) %>% 
   mutate(Parameter = gsub(".*Yr_", "", Predictor),
@@
 
-out.pmc.resid <- read.csv(here('output','analysis','pmc_resid.csv')) %>% 
+out.pmc.resid <- read.csv(here('output','analysis','pmc-resid.csv')) %>% 
   mutate(Parameter = gsub(".*PM_", "", Predictor),
@@
 
-out.fac.resid <- read.csv(here('output','analysis','fac_resid.csv')) %>% 
+out.fac.resid <- read.csv(here('output','analysis','fac-resid.csv')) %>% 
   mutate(Parameter = gsub(".*PM_", "", Predictor),
@@
 
+```{r Output PMC Age}
+out.pmc.age = data.frame()
+for (i in c("LE75", "M75")){
+  dt <- read.csv(here('output','analysis',paste('pmc-age',i,'.csv', sep= ""))) %>% 
+    mutate(Age = i)
+  out.pmc.age  <-  rbind(out.pmc.age, dt)
+}
+
+out.pmc.age <- out.pmc.age %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Age, HR, HR.L, HR.U)
+
+save(out.pmc.age, file = here('output','analysis','out-pmc-age.RDa'))
+```
+
+```{r Output Factor Age}
+out.fac.age = data.frame()
+for (i in c("LE75", "M75")){
+  dt <- read.csv(here('output','analysis',paste('fac-age',i,'.csv', sep= ""))) %>% 
+    mutate(Age = i)
+  out.fac.age  <-  rbind(out.fac.age, dt)
+}
+
+out.fac.age <- out.fac.age %>% 
+  rename(Parameter = Predictor) %>% 
+  merge(fac.1yr.iqr) %>% 
+  merge(Factor.ex.ec.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Age, HR, HR.L, HR.U)
+
+save(out.fac.age, file = here('output','analysis','out-fac-age.RDa'))
+```
+
+```{r Output PMC Sex}
+out.pmc.sex = data.frame()
+for (i in c("F", "M")){
+  dt <- read.csv(here('output','analysis',paste('pmc-sex',i,'.csv', sep= ""))) %>% 
+    mutate(Sex = i)
+  out.pmc.sex  <-  rbind(out.pmc.sex, dt)
+}
+
+out.pmc.sex <- out.pmc.sex %>% 
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.1yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Sex, HR, HR.L, HR.U)
+
+save(out.pmc.sex, file = here('output','analysis','out-pmc-sex.RDa'))
+```
+
+```{r Output Factor Sex}
+out.fac.sex = data.frame()
+for (i in c("F", "M")){
+  dt <- read.csv(here('output','analysis',paste('fac-sex',i,'.csv', sep= ""))) %>% 
+    mutate(Sex = i)
+  out.fac.sex  <-  rbind(out.fac.sex, dt)
+}
+
+out.fac.sex <- out.fac.sex %>% 
+  rename(Parameter = Predictor) %>% 
+  merge(fac.1yr.iqr) %>% 
+  merge(Factor.ex.ec.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Sex, HR, HR.L, HR.U)
+
+save(out.fac.sex, file = here('output','analysis','out-fac-sex.RDa'))
+```
+
 ```{r Output PMC Race}
@@
 for (i in c("A", "B", "H", "W")){
-  dt <- read.csv(here('output','analysis',paste('pmc_race',i,'.csv', sep= ""))) %>% 
+  dt <- read.csv(here('output','analysis',paste('pmc-race',i,'.csv', sep= ""))) %>% 
     mutate(Race = i)
@@
 
+```{r Output Factor Race}
+out.fac.race = data.frame()
+for (i in c("A", "B", "H", "W")){
+  dt <- read.csv(here('output','analysis',paste('fac-race',i,'.csv', sep= ""))) %>% 
+    mutate(Race = i)
+  out.fac.race  <-  rbind(out.fac.race, dt)
+}
+
+out.fac.race <- out.fac.race %>% 
+  rename(Parameter = Predictor) %>% 
+  merge(fac.1yr.iqr) %>% 
+  merge(Factor.ex.ec.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Race, HR, HR.L, HR.U)
+
+save(out.fac.race, file = here('output','analysis','out-fac-race.RDa'))
+```
+
 ```{r Output PMC Urbanicity}
@@
 for (i in c("urban", "rural")){
-  dt <- read.csv(here('output','analysis',paste('pmc_',i,'.csv', sep= ""))) %>% 
+  dt <- read.csv(here('output','analysis',paste('pmc-',i,'.csv', sep= ""))) %>% 
     mutate(Loc.Set = i)
@@
 for (i in c("L", "M", "H")){
-  dt <- read.csv(here('output','analysis',paste('pmc_urban_ses',i,'.csv', sep= ""))) %>% 
+  dt <- read.csv(here('output','analysis',paste('pmc-urban-ses',i,'.csv', sep= ""))) %>% 
     mutate(SES.Cat = i)
@@
 for (i in c("west", "midwest", "south", "northeast")){
-  dt <- read.csv(here('output','analysis',paste('pmc_',i,'.csv', sep= ""))) %>% 
+  dt <- read.csv(here('output','analysis',paste('pmc-',i,'.csv', sep= ""))) %>% 
     mutate(Region = i)
@@
 
-```{r Output PMC Age}
-out.pmc.age = data.frame()
-for (i in c("LE75", "M75")){
-  dt <- read.csv(here('output','analysis',paste('pmc_age',i,'.csv', sep= ""))) %>% 
-    mutate(Age = i)
-  out.pmc.age  <-  rbind(out.pmc.age, dt)
+```{r Output PMC Residual Region}
+PM.IQR <- as.double(pmc.1yr.iqr[pmc.1yr.iqr$Parameter == 'PM', 'IQR'])
+load(here('output','analysis','out-pmc-ses.RDa'))
+PM <- out.pmc.ses %>% 
+  filter(Index == "PM2.5")
+
+out.pmc.resid.region = data.frame()
+for (i in c("west", "midwest", "south", "northeast")){
+  dt <- read.csv(here('output','analysis',paste('pmc-resid-',i,'.csv', sep= ""))) %>% 
+    mutate(Region = i)
+  out.pmc.resid.region  <-  rbind(out.pmc.resid.region, dt)
 }
 
-out.pmc.age <- out.pmc.age %>% 
-  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+out.pmc.resid.region <- out.pmc.resid.region %>%
+  mutate(Parameter = gsub(".*PM_", "", Predictor),
          Parameter = as.factor(Parameter)) %>% 
-  merge(pmc.1yr.iqr) %>% 
   merge(Para.to.Index) %>% 
+  mutate(Index = paste0('-', Index)) %>% 
   merge(Outcome.to.Cause) %>% 
-  mutate(HR = round(exp(Coef * IQR),3),
-         HR.L = round(exp((Coef-1.96*std) * IQR),3),
-         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  mutate(HR = round(exp(Coef * PM.IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * PM.IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * PM.IQR),3)) %>% 
   arrange(Config) %>% 
-  select(Index, Cause, Age, HR, HR.L, HR.U)
+  select(Index, Region, Cause, HR, HR.L, HR.U) %>% 
+  add_row(PM)
 
-save(out.pmc.age, file = here('output','analysis','out-pmc-age.RDa'))
-```
-
-```{r Output PMC Sex}
-out.pmc.sex = data.frame()
-for (i in c("F", "M")){
-  dt <- read.csv(here('output','analysis',paste('pmc_sex',i,'.csv', sep= ""))) %>% 
-    mutate(Sex = i)
-  out.pmc.sex  <-  rbind(out.pmc.sex, dt)
-}
-
-out.pmc.sex <- out.pmc.sex %>% 
-  mutate(Parameter = gsub(".*Yr_", "", Predictor),
-         Parameter = as.factor(Parameter)) %>% 
-  merge(pmc.1yr.iqr) %>% 
-  merge(Para.to.Index) %>% 
-  merge(Outcome.to.Cause) %>% 
-  mutate(HR = round(exp(Coef * IQR),3),
-         HR.L = round(exp((Coef-1.96*std) * IQR),3),
-         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
-  arrange(Config) %>% 
-  select(Index, Cause, Sex, HR, HR.L, HR.U)
-
-save(out.pmc.sex, file = here('output','analysis','out-pmc-sex.RDa'))
+save(out.pmc.resid.region, file = here('output','analysis','out-pmc-resid-region.RDa'))
 ```
@@
 for (i in c("brfss0", "brfss")){
-  dt <- read.csv(here('output','analysis',paste('pmc_',i,'.csv', sep= ""))) %>% 
+  dt <- read.csv(here('output','analysis',paste('pmc-',i,'.csv', sep= ""))) %>% 
     mutate(BRFSS = i)
@@
 for (i in c("6", "12", "24")){
-  dt <- read.csv(here('output','analysis',paste('pmc_bz',i,'.csv', sep= ""))) %>% 
+  dt <- read.csv(here('output','analysis',paste('pmc-bz',i,'.csv', sep= ""))) %>% 
     mutate(Buffer = i)
@@
 for (i in c("1", "2", "3", "4", "5")){
-  dt <- read.csv(here('output','analysis',paste('pmc_',i,'yr','.csv', sep= ""))) %>% 
+  dt <- read.csv(here('output','analysis',paste('pmc-',i,'yr','.csv', sep= ""))) %>% 
     mutate(Window = i)

### 2021-01-30 code/data-processors/cms-data-processor.Rmd
new analysis - configs - clean outputs - plots

@@
 
+```{r PMC Age}
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+### Age 
+dt.age <- dt.master.ndi.pmc %>%
+  mutate(age = ifelse(age <= 75, "LE", "M")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards)
+
+dt.age <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+### LE 75
+dt.ndi.pmc.ageLE75 <- dt.age %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aLE75 = ifelse(age == "LE", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.ageLE75[ ,paste0("aLE75_",cmp)] <- 
+      dt.ndi.pmc.ageLE75[ ,cmp] * dt.ndi.pmc.ageLE75$aLE75
+}
+
+dt.ndi.pmc.ageLE75 <- dt.ndi.pmc.ageLE75 %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aLE75, everything())
+
+write.csv(dt.ndi.pmc.ageLE75, 
+          file = here('data', 'processed', 'ndi-pmc-ageLE75.csv'),
+          row.names = F)
+
+### M 75
+dt.ndi.pmc.ageM75 <- dt.age %>% 
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aM75 = ifelse(age == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.ageM75[ ,paste0("aM75_",cmp)] <- 
+      dt.ndi.pmc.ageM75[ ,cmp] * dt.ndi.pmc.ageM75$aM75
+}
+
+dt.ndi.pmc.ageM75 <- dt.ndi.pmc.ageM75 %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aM75, everything())
+
+write.csv(dt.ndi.pmc.ageM75, 
+          file = here('data', 'processed', 'ndi-pmc-ageM75.csv'),
+          row.names = F)
+```
+
+```{r Factor Age}
+fac <- c("Factor1","Factor2","Factor3","Factor4",
+         "Factor5","Factor6","Factor7","Factor8")
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+### Age 
+dt.age <- dt.master.ndi.pmc %>%
+  mutate(age = ifelse(age <= 75, "LE", "M")) %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards)
+
+dt.age <- 
+  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
+  arrange(Site.ID, Year, Month, age, sex, race)
+
+### LE 75
+dt.ndi.fac.ageLE75 <- dt.age %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aLE75 = ifelse(age == "LE", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.ageLE75[ ,paste0("aLE75_",cmp)] <- 
+      dt.ndi.fac.ageLE75[ ,cmp] * dt.ndi.fac.ageLE75$aLE75
+}
+
+dt.ndi.fac.ageLE75 <- dt.ndi.fac.ageLE75 %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aLE75, everything())
+
+write.csv(dt.ndi.fac.ageLE75, 
+          file = here('data', 'processed', 'ndi-fac-ageLE75.csv'),
+          row.names = F)
+
+### M 75
+dt.ndi.fac.ageM75 <- dt.age %>% 
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  mutate(aM75 = ifelse(age == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.ageM75[ ,paste0("aM75_",cmp)] <- 
+      dt.ndi.fac.ageM75[ ,cmp] * dt.ndi.fac.ageM75$aM75
+}
+
+dt.ndi.fac.ageM75 <- dt.ndi.fac.ageM75 %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, aM75, everything())
+
+write.csv(dt.ndi.fac.ageM75, 
+          file = here('data', 'processed', 'ndi-fac-ageM75.csv'),
+          row.names = F)
+```
+
+```{r PMC Sex}
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
+dt.pmc <- dt.pmc.1yr %>% 
+  select(Site.ID, Year, Month, cmp.sub)
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.sex <- dt.master.ndi.pmc %>% 
+    select(Site.ID:no_death_lungc,
+         -no_death_uri, -no_death_ards) %>%  
+  inner_join(dt.pmc) %>% 
+  inner_join(dt.ses)
+
+### Female
+dt.ndi.pmc.sexF <- dt.sex %>% 
+  mutate(sexF = ifelse(sex == "F", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.sexF[ ,paste0("sexF_",cmp)] <- 
+      dt.ndi.pmc.sexF[ ,cmp] * dt.ndi.pmc.sexF$sexF
+}
+
+dt.ndi.pmc.sexF <- dt.ndi.pmc.sexF %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexF, everything())
+
+write.csv(dt.ndi.pmc.sexF, 
+          file = here('data', 'processed', 'ndi-pmc-sexF.csv'),
+          row.names = F)
+
+### Male
+dt.ndi.pmc.sexM <- dt.sex %>% 
+  mutate(sexM = ifelse(sex == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in cmp.sub){
+    dt.ndi.pmc.sexM[ ,paste0("sexM_",cmp)] <- 
+      dt.ndi.pmc.sexM[ ,cmp] * dt.ndi.pmc.sexM$sexM
+}
+
+dt.ndi.pmc.sexM <- dt.ndi.pmc.sexM %>% 
+  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexM, everything())
+
+write.csv(dt.ndi.pmc.sexM, 
+          file = here('data', 'processed', 'ndi-pmc-sexM.csv'),
+          row.names = F)
+```
+
+```{r Factor Sex}
+fac <- c("Factor1","Factor2","Factor3","Factor4",
+         "Factor5","Factor6","Factor7","Factor8")
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.sex <- dt.master.ndi.pmc %>% 
+    select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>%  
+  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.ses)
+
+### Female
+dt.ndi.fac.sexF <- dt.sex %>% 
+  mutate(sexF = ifelse(sex == "F", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.sexF[ ,paste0("sexF_",cmp)] <- 
+      dt.ndi.fac.sexF[ ,cmp] * dt.ndi.fac.sexF$sexF
+}
+
+dt.ndi.fac.sexF <- dt.ndi.fac.sexF %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexF, everything())
+
+write.csv(dt.ndi.fac.sexF, 
+          file = here('data', 'processed', 'ndi-fac-sexF.csv'),
+          row.names = F)
+
+### Male
+dt.ndi.fac.sexM <- dt.sex %>% 
+  mutate(sexM = ifelse(sex == "M", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race)
+
+for (cmp in fac){
+    dt.ndi.fac.sexM[ ,paste0("sexM_",cmp)] <- 
+      dt.ndi.fac.sexM[ ,cmp] * dt.ndi.fac.sexM$sexM
+}
+
+dt.ndi.fac.sexM <- dt.ndi.fac.sexM %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, sexM, everything())
+
+write.csv(dt.ndi.fac.sexM, 
+          file = here('data', 'processed', 'ndi-fac-sexM.csv'),
+          row.names = F)
+```
+
 ```{r PMC race}
@@
 
-```{r PMC Age}
-cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
-             "PB", "PM", "SI", "SO4", "V", "ZN")
-
-dt.pmc <- dt.pmc.1yr %>% 
-  select(Site.ID, Year, Month, cmp.sub)
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-### Age 
-dt.age <- dt.master.ndi.pmc %>%
-  mutate(age = ifelse(age <= 75, "LE", "M")) %>% 
-  select(Site.ID:no_death_lungc,
-         -no_death_uri, -no_death_ards)
-
-dt.age <- 
-  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
-  arrange(Site.ID, Year, Month, age, sex, race)
-
-### LE 75
-dt.ndi.pmc.ageLE75 <- dt.age %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
-  mutate(aLE75 = ifelse(age == "LE", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in cmp.sub){
-    dt.ndi.pmc.ageLE75[ ,paste0("aLE75_",cmp)] <- 
-      dt.ndi.pmc.ageLE75[ ,cmp] * dt.ndi.pmc.ageLE75$aLE75
-}
-
-dt.ndi.pmc.ageLE75 <- dt.ndi.pmc.ageLE75 %>% 
-  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, aLE75, everything())
-
-write.csv(dt.ndi.pmc.ageLE75, 
-          file = here('data', 'processed', 'ndi-pmc-ageLE75.csv'),
-          row.names = F)
-
-### M 75
-dt.ndi.pmc.ageM75 <- dt.age %>% 
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses) %>% 
-  mutate(aM75 = ifelse(age == "M", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in cmp.sub){
-    dt.ndi.pmc.ageM75[ ,paste0("aM75_",cmp)] <- 
-      dt.ndi.pmc.ageM75[ ,cmp] * dt.ndi.pmc.ageM75$aM75
-}
-
-dt.ndi.pmc.ageM75 <- dt.ndi.pmc.ageM75 %>% 
-  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, aM75, everything())
-
-write.csv(dt.ndi.pmc.ageM75, 
-          file = here('data', 'processed', 'ndi-pmc-ageM75.csv'),
-          row.names = F)
-```
-
-```{r Factor Age}
-fac <- c("Factor1","Factor2","Factor3","Factor4",
-         "Factor5","Factor6","Factor7","Factor8")
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-### Age 
-dt.age <- dt.master.ndi.pmc %>%
-  mutate(age = ifelse(age <= 75, "LE", "M")) %>% 
-  select(Site.ID:no_death_lungc,
-         -no_death_nacc, -no_death_acc,
-         -no_death_uri, -no_death_ards)
-
-dt.age <- 
-  aggregate(. ~ Site.ID + Year + Month + age + sex + race, dt.age, sum) %>%
-  arrange(Site.ID, Year, Month, age, sex, race)
-
-### LE 75
-dt.ndi.fac.ageLE75 <- dt.age %>% 
-  inner_join(dt.fac.1yr) %>% 
-  inner_join(dt.ses) %>% 
-  mutate(aLE75 = ifelse(age == "LE", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in fac){
-    dt.ndi.fac.ageLE75[ ,paste0("aLE75_",cmp)] <- 
-      dt.ndi.fac.ageLE75[ ,cmp] * dt.ndi.fac.ageLE75$aLE75
-}
-
-dt.ndi.fac.ageLE75 <- dt.ndi.fac.ageLE75 %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, aLE75, everything())
-
-write.csv(dt.ndi.fac.ageLE75, 
-          file = here('data', 'processed', 'ndi-fac-ageLE75.csv'),
-          row.names = F)
-
-### M 75
-dt.ndi.fac.ageM75 <- dt.age %>% 
-  inner_join(dt.fac.1yr) %>% 
-  inner_join(dt.ses) %>% 
-  mutate(aM75 = ifelse(age == "M", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in fac){
-    dt.ndi.fac.ageM75[ ,paste0("aM75_",cmp)] <- 
-      dt.ndi.fac.ageM75[ ,cmp] * dt.ndi.fac.ageM75$aM75
-}
-
-dt.ndi.fac.ageM75 <- dt.ndi.fac.ageM75 %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, aM75, everything())
-
-write.csv(dt.ndi.fac.ageM75, 
-          file = here('data', 'processed', 'ndi-fac-ageM75.csv'),
-          row.names = F)
-```
-
-```{r PMC Sex}
-cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
-             "PB", "PM", "SI", "SO4", "V", "ZN")
-
-dt.pmc <- dt.pmc.1yr %>% 
-  select(Site.ID, Year, Month, cmp.sub)
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.sex <- dt.master.ndi.pmc %>% 
-    select(Site.ID:no_death_lungc,
-         -no_death_uri, -no_death_ards) %>%  
-  inner_join(dt.pmc) %>% 
-  inner_join(dt.ses)
-
-### Female
-dt.ndi.pmc.sexF <- dt.sex %>% 
-  mutate(sexF = ifelse(sex == "F", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in cmp.sub){
-    dt.ndi.pmc.sexF[ ,paste0("sexF_",cmp)] <- 
-      dt.ndi.pmc.sexF[ ,cmp] * dt.ndi.pmc.sexF$sexF
-}
-
-dt.ndi.pmc.sexF <- dt.ndi.pmc.sexF %>% 
-  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, sexF, everything())
-
-write.csv(dt.ndi.pmc.sexF, 
-          file = here('data', 'processed', 'ndi-pmc-sexF.csv'),
-          row.names = F)
-
-### Male
-dt.ndi.pmc.sexM <- dt.sex %>% 
-  mutate(sexM = ifelse(sex == "M", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in cmp.sub){
-    dt.ndi.pmc.sexM[ ,paste0("sexM_",cmp)] <- 
-      dt.ndi.pmc.sexM[ ,cmp] * dt.ndi.pmc.sexM$sexM
-}
-
-dt.ndi.pmc.sexM <- dt.ndi.pmc.sexM %>% 
-  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, sexM, everything())
-
-write.csv(dt.ndi.pmc.sexM, 
-          file = here('data', 'processed', 'ndi-pmc-sexM.csv'),
-          row.names = F)
-```
-
-```{r Factor Sex}
-fac <- c("Factor1","Factor2","Factor3","Factor4",
-         "Factor5","Factor6","Factor7","Factor8")
-
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.sex <- dt.master.ndi.pmc %>% 
-    select(Site.ID:no_death_lungc,
-         -no_death_nacc, -no_death_acc,
-         -no_death_uri, -no_death_ards) %>%  
-  inner_join(dt.fac.1yr) %>% 
-  inner_join(dt.ses)
-
-### Female
-dt.ndi.fac.sexF <- dt.sex %>% 
-  mutate(sexF = ifelse(sex == "F", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in fac){
-    dt.ndi.fac.sexF[ ,paste0("sexF_",cmp)] <- 
-      dt.ndi.fac.sexF[ ,cmp] * dt.ndi.fac.sexF$sexF
-}
-
-dt.ndi.fac.sexF <- dt.ndi.fac.sexF %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, sexF, everything())
-
-write.csv(dt.ndi.fac.sexF, 
-          file = here('data', 'processed', 'ndi-fac-sexF.csv'),
-          row.names = F)
-
-### Male
-dt.ndi.fac.sexM <- dt.sex %>% 
-  mutate(sexM = ifelse(sex == "M", 0,1),
-         StrID = paste(age, sex, race)) %>% 
-  select(-age, -sex, -race)
-
-for (cmp in fac){
-    dt.ndi.fac.sexM[ ,paste0("sexM_",cmp)] <- 
-      dt.ndi.fac.sexM[ ,cmp] * dt.ndi.fac.sexM$sexM
-}
-
-dt.ndi.fac.sexM <- dt.ndi.fac.sexM %>% 
-  rename(SiteID = Site.ID) %>% 
-  select(SiteID, Year, Month, StrID, sexM, everything())
-
-write.csv(dt.ndi.fac.sexM, 
-          file = here('data', 'processed', 'ndi-fac-sexM.csv'),
-          row.names = F)
-```
-
 ```{r PMC BRFSS}
@@
 
-```{r Factor BRFSS}
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.fac.brfss <- dt.master.ndi.pmc %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
-         -no_death_nacc, -no_death_acc,
-         -no_death_uri, -no_death_ards) %>%  
-  inner_join(dt.fac.1yr) %>% 
-  inner_join(dt.ses) %>% 
-  inner_join(dt.brfss.site) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.fac.brfss, 
-          file = here('data', 'processed', 'ndi-fac-brfss.csv'),
-          row.names = F)
-```
-
 ```{r PMC BZ 6}

### 2021-01-30 code/data-viz/plot-results.Rmd
new analysis - configs - clean outputs - plots

@@
   library(gridExtra)
-```
-
-```{r Load data}
-load(here('output','analysis','out-pmc-base.RDa'))
-load(here('output','analysis','out-pmc-ses.RDa'))
-load(here('output','analysis','out-fac-base.RDa'))
-load(here('output','analysis','out-fac-ses.RDa'))
-load(here('output','analysis','out-fac-ex-ec-base.RDa'))
-load(here('output','analysis','out-fac-ex-ec-ses.RDa'))
-load(here('output','analysis','out-pmc-resid.RDa'))
-load(here('output','analysis','out-fac-resid.RDa'))
-load(here('output','analysis','out-pmc-region.RDa'))
-load(here('output','analysis','out-pmc-race.RDa'))
-load(here('output','analysis','out-pmc-urbanicity.RDa'))
-load(here('output','analysis','out-pmc-sescat.RDa'))
-load(here('output','analysis','out-pmc-brfss.RDa'))
-load(here('output','analysis','out-pmc-age.RDa'))
-load(here('output','analysis','out-pmc-sex.RDa'))
-load(here('output','analysis','out-pmc-buffer.RDa'))
-load(here('output','analysis','out-pmc-expo.RDa'))
-```
-
-```{r - Components Base}
-data <- out.pmc.base
-
-cmp <- c("Mn","Fe","V", "Ni","Cl", "Na", "SO4", "Se","Cu", "K", "OC", "NO3", 
-         "Zn", "Pb", "Ca", "Si", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#D71A21")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-              color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  theme_classic() + 
+  library(ggthemes)
+```
+
+```{r set theme}
+ggtheme1 <- theme_bw() + 
   theme(panel.spacing.x = unit(0.25, 'lines'),
@@
         strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
+        strip.background = element_rect(fill = "#B9CFED"),
         axis.text.x = element_text(size = 8, color = 'black'),
         axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','pmc-base.png'), width = 6.5, height = 8.5)
-```
-
-```{r - Components SES-Adj}
-data <- out.pmc.ses
-
-cmp <- c("Mn","Fe","V", "Ni","Cl", "Na", "SO4", "Se","Cu", "K", "OC", "NO3", 
-         "Zn", "Pb", "Ca", "Si", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#D71A21")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-              color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25, 'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','pmc-ses.png'), width = 6.5, height = 8.5)
-```
-
-```{r - Factor Base}
-data <- out.fac.base
-
-So <- c("Steel", "Coal", "Oil", "Salt", 
-         "Biomass", "Metals", "Soil", "Traffic")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#D71A21")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
-  xlab("") +
-  ylab("") +
-  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  theme_classic() + 
+  )
+```
+
+```{r}
+ggtheme2 <- theme_classic() + 
   theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','fac-base-ec.png'), width = 6.5, height = 8.5)
-```
-
-```{r - Factor SES-Adj}
-data <- out.fac.ses
-
-So <- c("Steel", "Coal", "Oil", "Salt", 
-         "Biomass", "Metals", "Soil", "Traffic")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#D71A21")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
-  xlab("") +
-  ylab("") +
-  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','fac-ses-ec.png'), width = 6.5, height = 8.5)
-```
-
-```{r - Factor Ex. EC Base}
-data <- out.fac.ex.ec.base
-
-So <- c("Steel", "Oil", "Salt", "Coal", 
-         "Biomass","Traffic", "Metals", "Soil")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#D71A21")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
-  xlab("") +
-  ylab("") +
-  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','fac-base.png'), width = 6.5, height = 8.5)
-```
-
-```{r - Factor EX. EC SES-Adj}
-data <- out.fac.ex.ec.ses
-
-So <- c("Steel", "Oil", "Salt", "Coal", 
-         "Biomass","Traffic", "Metals", "Soil")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#D71A21")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  geom_vline(xintercept = 1.2, linetype = 2, alpha = 0) +
-  xlab("") +
-  ylab("") +
-  #scale_x_continuous(breaks=c(1, 1.1, 1.2)) + 
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','fac-ses.png'), width = 6.5, height = 8.5)
-```
-
-```{r - Components - PM Residual}
-data <- out.pmc.resid
-
-cmp <- c("-V", "-Ni","-Cl", "-Na", "-SO4", "-Se", "-OC", "-NO3", 
-         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#D71A21")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) +
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','pmc-resid.png'), width = 6.5, height = 8.5)
-```
-
-```{r - Components PM Residual - Region}
-data <- read_excel('Comp_PMResi_Region.xlsx')
-
-cmp <- c("PM2.5",  "-Si", "-Ca", "-Pb", "-Zn",
-         "-Se", "-SO4", "-Ni", "-V", "-NO3", "-OC"
-         )
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", 
-         "Respiratory", "Pneumonia",
-         "Cancer","Lung Cancer") # "CHF", "COPD",
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         Tag = as.factor(Tag)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("NE", "S", "MW", "W")
-plot_cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs,
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
         panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
@@
         strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
+        strip.background = element_rect(fill = "#B9CFED"),
         axis.text.x = element_text(size = 8, color = 'black'),
@@
         legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10,face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave("CMP_PMResi_Region_1113.jpeg", p, width = 9.5, height = 12)
-```
-
-```{r - Factor - PM Residual}
-data <- out.fac.resid
-
-So <- c("-Oil", "-Salt", "-Coal", 
-         "-Traffic", "-Metals", "-Soil", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_cols <- c("#D71A21")
+        legend.key.width = unit(0.25, units = 'in'))
+```
+
+```{r Load data}
+load(here('output','analysis','out-pmc-base.RDa'))
+load(here('output','analysis','out-pmc-ses.RDa'))
+load(here('output','analysis','out-fac-base.RDa'))
+load(here('output','analysis','out-fac-ses.RDa'))
+load(here('output','analysis','out-fac-base-ec.RDa'))
+load(here('output','analysis','out-fac-ses-ec.RDa'))
+load(here('output','analysis','out-pmc-resid.RDa'))
+load(here('output','analysis','out-fac-resid.RDa'))
+load(here('output','analysis','out-pmc-age.RDa'))
+load(here('output','analysis','out-fac-age.RDa'))
+load(here('output','analysis','out-pmc-sex.RDa'))
+load(here('output','analysis','out-fac-sex.RDa'))
+load(here('output','analysis','out-pmc-race.RDa'))
+load(here('output','analysis','out-fac-race.RDa'))
+load(here('output','analysis','out-pmc-urbanicity.RDa'))
+load(here('output','analysis','out-pmc-sescat.RDa'))
+load(here('output','analysis','out-pmc-region.RDa'))
+load(here('output','analysis','out-pmc-brfss.RDa'))
+load(here('output','analysis','out-pmc-buffer.RDa'))
+load(here('output','analysis','out-pmc-expo.RDa'))
+```
+
+```{r color code}
+#https://www.schemecolor.com/british-airways-website.php
+```
+
+```{r - Components Base}
+data <- out.pmc.base
+
+cmp <- c("Mn","Fe","V", "Ni","Cl", "Na", "SO4", "Se","Cu", "K", "OC", "NO3", 
+         "Zn", "Pb", "Ca", "Si", "PM2.5")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         )
+
+plot_cols <- c("#EB2226")
 
@@
   geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
+  labs(x = "", y = "") +
   geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
@@
   scale_shape_manual(values = c(16, 1, 16), guide = F) +
-
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+  ggtheme1 +
+ggsave(here('output','plot','pmc-base.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Components SES-Adj}
+data <- out.pmc.ses
+
+cmp <- c("Mn","Fe","V", "Ni","Cl", "Na", "SO4", "Se","Cu", "K", "OC", "NO3", 
+         "Zn", "Pb", "Ca", "Si", "PM2.5")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         )
+
+plot_cols <- c("#EB2226")
+
+ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+              color =plot_cols, size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
+             color =plot_cols, size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+  ggtheme1 +
+ggsave(here('output','plot','pmc-ses.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factor Base Inc EC}
+data <- out.fac.base.ec
+
+So <- c("Steel", "Coal", "Oil", "Salt", 
+         "Biomass", "Metals", "Soil", "Traffic")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% So,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So),
+         sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         )
+
+plot_cols <- c("#EB2226")
+
+ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+               color =plot_cols, size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
+             color =plot_cols, size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+  ggtheme1 +
+ggsave(here('output','plot','fac-base-ec.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factor SES-Adj Inc EC}
+data <- out.fac.ses.ec
+
+So <- c("Steel", "Coal", "Oil", "Salt", 
+         "Biomass", "Metals", "Soil", "Traffic")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% So,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So),
+         sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         )
+
+plot_cols <- c("#EB2226")
+
+ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+               color =plot_cols, size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
+             color =plot_cols, size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+  ggtheme1 +
+ggsave(here('output','plot','fac-ses-ec.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factor Ex. EC Base}
+data <- out.fac.base
+
+So <- c("Steel", "Oil", "Salt", "Coal", 
+         "Biomass","Traffic", "Metals", "Soil")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% So,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So),
+         sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         )
+
+plot_cols <- c("#EB2226")
+
+ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+               color =plot_cols, size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
+             color =plot_cols, size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+  ggtheme1 +
+ggsave(here('output','plot','fac-base.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factor EX. EC SES-Adj}
+data <- out.fac.ses
+
+So <- c("Steel", "Oil", "Salt", "Coal", 
+         "Biomass","Traffic", "Metals", "Soil")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% So,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So),
+         sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         )
+
+plot_cols <- c("#EB2226")
+
+ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+               color =plot_cols, size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
+             color =plot_cols, size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+  ggtheme1 +
+ggsave(here('output','plot','fac-ses.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Components - PM Residual}
+data <- out.pmc.resid
+
+cmp <- c("-V", "-Ni","-Cl", "-Na", "-SO4", "-Se", "-OC", "-NO3", 
+         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         )
+
+plot_cols <- c("#EB2226")
+
+ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+               color =plot_cols, size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
+             color =plot_cols, size = 1.5, show.legend = F) +
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+  ggtheme1 +
+ggsave(here('output','plot','pmc-resid.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factor - PM Residual}
+data <- out.fac.resid
+
+So <- c("-Oil", "-Salt", "-Coal", 
+         "-Traffic", "-Metals", "-Soil", "PM2.5")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia",
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% So,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_cols <- c("#EB2226")
+
+ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+              color =plot_cols, size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
+             color =plot_cols, size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
 facet_wrap( ~ Cause, nrow = 2, scales = "fixed") +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  ) +
-ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 8.5)
+  ggtheme1 +
+ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Components Age}
+data <- out.pmc.age
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(Age == "LE75", "b", "a"),
+         Tag = as.factor(Tag)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_labs <- c("> 75 years", "<= 75 years")
+plot_cols <- c("#EB2226", "#075AAA")
+
+p <- grid.arrange(
+ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+
+ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+nrow = 2)
+
+ggsave(here('output', 'plot','pmc-age.png'),p, width = 6.5, height = 6.5)
+```
+
+```{r - Components Sex}
+data <- out.pmc.sex
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(Sex == "F", "b", "a"),
+         Tag = as.factor(Tag)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_labs <- c("Male", "Female")
+plot_cols <- c("#EB2226", "#075AAA")
+
+p <- grid.arrange(
+ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+
+ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+nrow = 2)
+
+ggsave(here('output', 'plot','pmc-sex.png'),p, width = 6.5, height = 6.5)
+```
+
+```{r - Components Race}
+data <- out.pmc.race
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(Race == "A", "d",
+                      ifelse(Race == "B", "c",
+                             ifelse(Race == "H", "b", "a"))),
+         Tag = as.factor(Tag)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_labs <- c("White", "Hispanic", "Black", "Asian")
+plot_cols <- c("#EB2226", "orange", "#075AAA", "seagreen")
+
+p <- grid.arrange(
+ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+
+ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+nrow = 2)
+
+ggsave(here('output', 'plot','pmc-race.png'),p, width = 6.5, height = 6.5)
+```
+
+```{r Components Urban}
+data <- out.pmc.urbanicity
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V") 
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(Loc.Set == "urban", "b", "a"),
+         Tag = as.factor(Tag)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_labs <- c("Non-urban", "Urban")
+plot_cols <- c("#EB2226", "#075AAA")
+
+p <- grid.arrange(
+ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+
+ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "fixed", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+nrow = 2)
+
+ggsave(here('output', 'plot','pmc-urbanicity.png'),p, width = 6.5, height = 6.5)
+```
+
+```{r Components SES-Urban}
+data <- out.pmc.sescat
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(SES.Cat == "L", "c",
+                      ifelse(SES.Cat == "M", "b", "a")),
+         Tag = as.factor(Tag)
+         )
+
+data <- data %>% 
+  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
+                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+
+plot_labs <- c("High", "Middle", "Low")
+plot_cols <-  c("seagreen", "#075AAA", "#EB2226")
+
+p <- grid.arrange(
+ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = F) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = F) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+
+ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
+       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+  geom_vline(xintercept = 1, linetype = 2, color = "black") +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
+  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+nrow = 2)
+
+ggsave(here('output', 'plot','pmc-sescat.png'),p, width = 6.5, height = 6.5)
 ```
@@
   geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
+  labs(x = "", y = "") +
   geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
@@
                shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
+  ggtheme2 +
   guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
@@
   geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10,face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
   guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
@@
 
-ggsave(here('output', 'plot','pmc-region.png'),p, width = 6.5, height = 8.5)
-```
-
-```{r Factors Region}
-data <- read_excel('Fac_Region.xlsx')
-
-So <- c("Soil", "Metals",  
-        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",
-
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So)
+ggsave(here('output', 'plot','pmc-region.png'),p, width = 6.5, height = 6.5)
+```
+
+```{r - Components BRFSS}
+data <- out.pmc.brfss
+
+cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+         "Na", "Cl", "Ni", "V")
+cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
+         "Respiratory", "COPD", "Pneumonia", 
+         "Cancer", "Lung Cancer")
+
+data <- data %>% 
+  filter(Index %in% cmp,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp),
+         Tag = ifelse(BRFSS == "brfss0", "b", "a"),
+         Tag = as.factor(Tag)
          )
@@
 
-plot_labs <- c("NE", "S", "MW", "W")
-plot_cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")
+plot_labs <- c("BRFSS-Adjusted", "Base")
+plot_cols <- c("#EB2226", "#075AAA")
 
@@
     values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
   guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
@@
   geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
   guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
@@
 
-ggsave("Fac_Region_1113.jpeg", p, width = 9.5, height = 7)
-```
-
-```{r - Components Race}
-data <- out.pmc.race
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         Tag = ifelse(Race == "A", "d",
-                      ifelse(Race == "B", "c",
-                             ifelse(Race == "H", "b", "a"))),
-         Tag = as.factor(Tag)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("White", "Hispanic", "Black", "Asian")
-plot_cols <- c("red", "orange", "blue", "seagreen")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-race.png'),p, width = 6.5, height = 8.5)
-```
-
-```{r - Components Age}
-data <- out.pmc.age
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         Tag = ifelse(Age == "LE75", "b", "a"),
-         Tag = as.factor(Tag)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("> 75 years", "<= 75 years")
-plot_cols <- c("red", "blue")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-age.png'),p, width = 6.5, height = 8.5)
-```
-
-```{r - Components Sex}
-data <- out.pmc.sex
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         Tag = ifelse(Sex == "F", "b", "a"),
-         Tag = as.factor(Tag)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("Male", "Female")
-plot_cols <- c("red", "blue")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-sex.png'),p, width = 6.5, height = 8.5)
-```
-
-```{r Factors Race}
-data <- read_excel('Fac_Race.xlsx')
-
-So <- c("Soil", "Metals",  
-        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",
-
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("White", "Hispanic", "Black", "Asian")
-plot_cols <- c("red", "orange", "blue", "seagreen")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units ='in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave("Fac_Race_1113.jpeg", p, width = 9.5, height = 7)
-```
-
-```{r Components Urban}
-data <- out.pmc.urbanicity
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         Tag = ifelse(Loc.Set == "urban", "b", "a"),
-         Tag = as.factor(Tag)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("Non-urban", "Urban")
-plot_cols <- c("red", "blue")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "fixed", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-urbanicity.png'),p, width = 6.5, height = 8.5)
-```
-
-```{r Factors Urban}
-data <- read_excel('Fac_Urban.xlsx')
-
-So <- c("Soil", "Metals",  
-        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",
-
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("Non-urban", "Urban")
-plot_cols <- c("red", "blue")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units ='in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave("Fac_Urban_1113.jpeg", p, width = 9.5, height = 6)
-```
-
-```{r Components SES-Urban}
-data <- out.pmc.sescat
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         Tag = ifelse(SES.Cat == "L", "c",
-                      ifelse(SES.Cat == "M", "b", "a")),
-         Tag = as.factor(Tag)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("High", "Middle", "Low")
-plot_cols <-  c("seagreen", "blue", "red")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-sescat.png'),p, width = 6.5, height = 8.5)
-```
-
-```{r Factors SES-Urban}
-data <- read_excel('Fac_SESUrban.xlsx')
-
-So <- c("Soil", "Metals",  
-        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",
-
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("High", "Middle", "Low")
-plot_cols <-  c("seagreen", "blue", "red")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units ='in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave("Fac_SESUrban_1113.jpeg", p, width = 9.5, height = 7)
-```
-
-```{r - Components BRFSS}
-data <- out.pmc.brfss
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         Tag = ifelse(BRFSS == "brfss0", "b", "a"),
-         Tag = as.factor(Tag)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("BRFSS-Adjusted", "Base")
-plot_cols <- c("red", "blue")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
 ggsave(here('output', 'plot','pmc-brfss.png'),p, width = 6.5, height = 8.5)
-```
-
-```{r Factors BRFSS}
-data <- read_excel('Fac_BRFSS.xlsx')
-
-So <- c("Soil", "Metals",  
-        "Coal", "Oil", "Traffic") # "-Steel", "-Salt", "-Biomass",
-
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So)
-         )
-
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
-
-plot_labs <- c("BRFSS-Adjusted", "Base")
-plot_cols <- c("red", "blue")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units ='in')) +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave("Fac_BRFSS_1113.jpeg", p, width = 9.5, height = 7)
 ```
@@
 plot_labs <- c("24-miles", "12-miles", "6-miles") 
-plot_cols <- c("red", "blue", "seagreen")
+plot_cols <- c("#EB2226", "#075AAA", "seagreen")
 
@@
   geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
   guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
@@
 plot_labs <- c("5-yr", "4-yr","3-yr","2-yr","1-yr")
-plot_cols <- c("red","orange","purple","blue","seagreen")
+plot_cols <- c("#EB2226","orange","purple","#075AAA","seagreen")
 
@@
   geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  xlab("") +
-  ylab("") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "slategray2"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in')) +
+  labs(x = "", y = "") +
+  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                size = 0.25, show.legend = T) + 
+  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
+             size = 1.5, show.legend = T) + 
+  scale_shape_manual(values = c(16, 1, 16), guide = F) +
+  scale_color_manual(
+    labels = plot_labs, 
+    values = plot_cols) +
+
+facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+  ggtheme2 +
   guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),

### 2021-02-01 code/data-analysis/config-file-generator.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 ```
@@
 
+```{r ses adj. model for factors - urban}
+dataname <- "ndi-fac-urban.csv"
+expo <- fac
+subg <- "urb"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','fac-urban', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - rural}
+dataname <- "ndi-fac-rural.csv"
+expo <- fac
+subg <- "rur"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','fac-rural', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
 ```{r ses adj. model for components - Urban ses Low}
@@
       writeLines(w, here('config-files','pmc-northeast', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - west}
+dataname <- "ndi-fac-west.csv"
+expo <- fac
+subg <- "rW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','fac-west', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - midwest}
+dataname <- "ndi-fac-midwest.csv"
+expo <- fac
+subg <- "rMW"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','fac-midwest', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - south}
+dataname <- "ndi-fac-south.csv"
+expo <- fac
+subg <- "rS"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','fac-south', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for factors - northeast}
+dataname <- "ndi-fac-northeast.csv"
+expo <- fac
+subg <- "rNE"
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.em.2, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    s <- gsub("subg", subg, z)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], s)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','fac-northeast', paste(k,'.txt', sep = "")))
     }

### 2021-02-01 code/data-analysis/factor-analysis.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

@@
   (1) Run factor analysis
+
+```{r}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+```
 
@@
 # Soil Metals Traffic Biomass Coal Salt Oil Steel
+write.csv(factor.loadings.ex.ec,
+          file = here('output','table', 'factor-loadings.csv'))
 

### 2021-02-01 code/data-processors/air-data-processor.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

@@
 # suburban 69
-# rural 174
-# ...   2
+# rural 176
+
+dt.pmc.site.ndi %>% 
+  group_by(Region.IV, Location.Setting) %>% 
+  summarise(n = n())
+#1	102			
+#2	68			
+#3	93			
+#4	54
+
+dt.pmc.site.ndi.bz6 <- read.csv(here('data', 'processed', 'site_pmc_ndi_bz6.csv')) %>% 
+  rename(Site.ID = Site_ID) %>% 
+  left_join(dt.aqs.sites)
+
+dt.pmc.site.ndi.bz6 %>% 
+  group_by(Location.Setting) %>% 
+  summarise(n = n())
 ```
@@
 ```
+
+```{r}
+load(here('data','processed', 'pmc-daily.RDa'))
+load(here('data','processed','pmc-site-ndi.RDa'))
+
+dt.pmc <- dt.pmc.site.ndi %>% 
+  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
+         Region = ifelse(Region.IV == 1, "W",
+                         ifelse(Region.IV == 2, "MW",
+                                ifelse(Region.IV == 3, "S", "NE")))) %>% 
+    select(Site.ID, Region, Loc.Set) %>% 
+  merge(dt.pmc.daily) %>% 
+  pivot_longer(AS:PM,
+               names_to = "Parameter",
+               values_to = "Value")
+
+table.region <- dt.pmc %>% 
+  group_by(Parameter, Region) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
+            STD = sprintf("%0.2f", sd(Value*1000)))
+
+table.urban <- dt.pmc %>% 
+  group_by(Parameter, Loc.Set) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
+            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
+  rename(Region = Loc.Set)
+
+table <- dt.pmc %>% 
+  group_by(Parameter) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
+            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
+  mutate(Region = "US") %>% 
+  as.data.frame() %>% 
+  add_row(table.region) %>% 
+  add_row(table.urban) %>% 
+  pivot_wider(names_from = c(Region),
+              values_from = c(Mean, STD))
+
+write.csv(table,
+          file = here('output','table', 'pmc-daily-summary.csv'),
+          row.names = F)
+
+```

### 2021-02-01 code/data-processors/cms-data-processor.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

@@
 ---
+#####To do for fututre/ not urgent in all
+##### Fix Factor with and wothout EC names####
 
@@
   2. Exposure window is one year unless specified
+  4. In mail analysis (factors and risudal of factors) dt.fac.1yr is factor
+    analysis with EC and datasets are saved as fac.
+  3. In all Effect modification analysis, the fac.ex.ec is saved as fac
 
@@
 dt.ndi.fac.ageLE75 <- dt.age %>% 
-  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.ageM75 <- dt.age %>% 
-  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
          -no_death_uri, -no_death_ards) %>%  
-  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
   inner_join(dt.ses)
@@
   select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
          -no_death_uri, -no_death_ards)
@@
 dt.ndi.fac.raceA <- dt.raceA %>% 
-  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.raceB <- dt.raceB %>% 
-  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.raceH <- dt.raceH %>% 
-  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.raceW <- dt.raceW %>% 
-  inner_join(dt.fac.1yr) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 
+```{r Factor urbanicity}
+#fatemeh
+fac <- c("Factor1","Factor2","Factor3","Factor4",
+         "Factor5","Factor6","Factor7","Factor8")
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.site <- dt.pmc.site.ndi %>% 
+  select(Site.ID, Location.Setting)
+
+### Urban and Suburban
+dt.ndi.fac.urban <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(urb = ifelse(!Location.Setting == "RURAL", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Location.Setting)
+
+for (cmp in fac){
+    dt.ndi.fac.urban[ ,paste0("urb_",cmp)] <- 
+      dt.ndi.fac.urban[ ,cmp] * dt.ndi.fac.urban$urb
+}
+
+dt.ndi.fac.urban <- dt.ndi.fac.urban %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, urb, everything())
+
+write.csv(dt.ndi.fac.urban, 
+          file = here('data', 'processed', 'ndi-fac-urban.csv'),
+          row.names = F)
+
+### Rural
+dt.ndi.fac.rural <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rur = ifelse(Location.Setting == "RURAL", 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Location.Setting)
+
+for (cmp in fac){
+    dt.ndi.fac.rural[ ,paste0("rur_",cmp)] <- 
+      dt.ndi.fac.rural[ ,cmp] * dt.ndi.fac.rural$rur
+}
+
+dt.ndi.fac.rural <- dt.ndi.fac.rural %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rur, everything())
+
+write.csv(dt.ndi.fac.rural, 
+          file = here('data', 'processed', 'ndi-fac-rural.csv'),
+          row.names = F)
+```
+
 ```{r r PMC urban SES Categories}
@@
 
+```{r Factor Region}
+fac <- c("Factor1","Factor2","Factor3","Factor4",
+         "Factor5","Factor6","Factor7","Factor8")
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.site <- dt.pmc.site.ndi %>% 
+  select(Site.ID, Region.IV)
+
+### West = 1
+dt.ndi.fac.west <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rW = ifelse(Region.IV == 1, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in fac){
+    dt.ndi.fac.west[ ,paste0("rW_",cmp)] <- 
+      dt.ndi.fac.west[ ,cmp] * dt.ndi.fac.west$rW
+}
+
+dt.ndi.fac.west <- dt.ndi.fac.west %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rW, everything())
+
+write.csv(dt.ndi.fac.west, 
+          file = here('data', 'processed', 'ndi-fac-west.csv'),
+          row.names = F)
+
+### Midwest = 2
+dt.ndi.fac.midwest <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rMW = ifelse(Region.IV == 2, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in fac){
+    dt.ndi.fac.midwest[ ,paste0("rMW_",cmp)] <- 
+      dt.ndi.fac.midwest[ ,cmp] * dt.ndi.fac.midwest$rMW
+}
+
+dt.ndi.fac.midwest <- dt.ndi.fac.midwest %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rMW, everything())
+
+write.csv(dt.ndi.fac.midwest, 
+          file = here('data', 'processed', 'ndi-fac-midwest.csv'),
+          row.names = F)
+
+### South = 3
+dt.ndi.fac.south <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rS = ifelse(Region.IV == 3, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in fac){
+    dt.ndi.fac.south[ ,paste0("rS_",cmp)] <- 
+      dt.ndi.fac.south[ ,cmp] * dt.ndi.fac.south$rS
+}
+
+dt.ndi.fac.south <- dt.ndi.fac.south %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rS, everything())
+
+write.csv(dt.ndi.fac.south, 
+          file = here('data', 'processed', 'ndi-fac-south.csv'),
+          row.names = F)
+
+### Northeast = 4
+dt.ndi.fac.northeast <- dt.master.ndi.pmc %>% 
+  select(Site.ID:no_death_lungc,
+         -no_death_nacc, -no_death_acc,
+         -no_death_uri, -no_death_ards) %>% 
+  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  inner_join(dt.site) %>% 
+  mutate(rNE = ifelse(Region.IV == 4, 0,1),
+         StrID = paste(age, sex, race)) %>% 
+  select(-age, -sex, -race, -Region.IV)
+
+for (cmp in fac){
+    dt.ndi.fac.northeast[ ,paste0("rNE_",cmp)] <- 
+      dt.ndi.fac.northeast[ ,cmp] * dt.ndi.fac.northeast$rNE
+}
+
+dt.ndi.fac.northeast <- dt.ndi.fac.northeast %>% 
+  rename(SiteID = Site.ID) %>% 
+  select(SiteID, Year, Month, StrID, rNE, everything())
+
+write.csv(dt.ndi.fac.northeast, 
+          file = here('data', 'processed', 'ndi-fac-northeast.csv'),
+          row.names = F)
+```
+
 ```{r PMC Residual Region}
@@
 ```{r PMC BRFSS}
+cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
+             "PB", "PM", "SI", "SO4", "V", "ZN")
+
 dt.pmc <- dt.pmc.1yr %>% 
@@
           row.names = F)
+
+pmc.brfs.count <- dt.ndi.pmc.brfss %>% 
+  distinct(SiteID, Year, Month) %>% 
+  rename(Site_ID = SiteID)
+
+write.csv(pmc.brfs.count, 
+          file = here('data', 'processed', 'pmc-brfss-count.csv'),
+          row.names = F)
+
+dt.pmc.site.ndi.brfs <- dt.ndi.pmc.brfss %>% 
+  rename(Site.ID = SiteID) %>% 
+  distinct(Site.ID) %>% 
+  merge(dt.pmc.site.ndi)
+
+dt.pmc.site.ndi.brfs %>% 
+  group_by(Location.Setting) %>% 
+  summarise(n = n())
+#RURAL	37			
+#SUBURBAN	42			
+#URBAN	56	> 98
 ```

### 2021-02-01 code/data-viz/correlation.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

---
title: "R Notebook"
---

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Load packages}
  library(tidyverse)
  library(here)
  library(corrplot)
  library(RColorBrewer)
```

```{r Load datasets}
load(here('data','processed', 'pmc-daily.RDa'))
load(here('data','processed', 'pmc-site-ndi.RDa'))
```

```{r}
Para.to.Index <- tribble(
  ~Index, ~Parameter,
   "As", "AS",
   "Ca", "CA",
   "Cu", "CU",
   "Cl", "CL",
   "Fe", "FE",
   "Pb", "PB",
   "Mn", "MN",
   "Ni", "NI",
   "Mg", "MG",
   "Se", "SE",
   "V", "V",
   "Si", "SI",
   "Zn", "ZN",
   "K", "K",
   "Na", "NA",
   "NO3", "NO3",
   "SO4", "SO4",
   "OC", "OC",
   "EC", "EC",
   "PM2.5", "PM"
   ) %>% 
  mutate(Index = as.factor(Index),
         Parameter = as.factor(Parameter))
```

```{r}
dt.pmc <- dt.pmc.daily %>% 
  pivot_longer(cols = AS:PM,
               names_to = "Parameter",
               values_to = "Measurement") %>% 
  merge(Para.to.Index) %>% 
  select(-Parameter) %>% 
  pivot_wider(names_from = "Index",
              values_from = "Measurement",
              names_sort = T)

dt.pmc <- dt.pmc.site.ndi %>% 
  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
         Region = ifelse(Region.IV == 1, "W",
                         ifelse(Region.IV == 2, "MW",
                                ifelse(Region.IV == 3, "S", "NE")))) %>% 
    select(Site.ID, Region, Region.IV, Loc.Set) %>% 
  merge(dt.pmc)
```

```{r}
corr <- dt.pmc %>%
  select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
  na.omit %>%
  cor()

jpeg(here('output','plot','corr-us.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
corrplot(corr, type = "lower",  method = 'number',
         tl.col = "black", tl.srt = 45, number.cex=0.65,
         col = rev(brewer.pal(n = 10, name = "RdGy"))) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 14, hjust = 1, face='bold'),
        axis.text.y = element_text(angle = 0, vjust = 1, 
                                   size = 14, hjust = 1, face='bold'),
        legend.title = element_blank())
dev.off()
```

```{r - Region}
dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),]

jpeg(here('output','plot','corr-region.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
for(i in unique(dt.pmc$Region)) {
  data<- subset(dt.pmc, Region==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          axis.text.y = element_text(angle = 0, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          legend.title = element_blank())
}
dev.off()
```

```{r - Urbanicity}
jpeg(here('output','plot','corr-urbanicity.png'), width = 6.5, height = 6.5, units = 'in',
     res = 300)
par(mfrow=c(2,2))
for(i in unique(dt.pmc$Loc.Set)) {
  data<- subset(dt.pmc, Loc.Set==i)
  corr <- data %>%
    select(As,Ca,Cl,Cu,Fe,K,Mg,Mn,Na,Ni,NO3,OC,Pb,Se,Si,SO4,V,Zn,`PM2.5`) %>%
    na.omit %>%
    cor()
  corrplot(corr, type = "lower",
           tl.col = "black", tl.srt = 45, number.cex=0.65,
           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          axis.text.y = element_text(angle = 0, vjust = 1, 
                                     size = 14, hjust = 1, face='bold'),
          legend.title = element_blank())
}
dev.off()
```

### 2021-02-01 code/data-viz/plot-results.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

@@
 
+###color codes: https://www.schemecolor.com/british-airways-website.php
+
 ```{r}
@@
 
-```{r}
-### load packages
+```{r Load packages}
   library(tidyverse)
   library(here)
-  library(gridExtra)
   library(ggthemes)
@@
 
-```{r set theme}
-ggtheme1 <- theme_bw() + 
-  theme(panel.spacing.x = unit(0.25, 'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.background = element_rect(fill = "#B9CFED"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
-  )
-```
-
-```{r}
-ggtheme2 <- theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
-        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
-        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
-        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
-        strip.text.y.left = element_text(angle = 0),
-        strip.background = element_rect(fill = "#B9CFED"),
-        axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        legend.position = 'bottom',
-        legend.title = element_blank(),
-        legend.text = element_text(size = 10, face = "bold"),
-        legend.key.width = unit(0.25, units = 'in'))
+```{r Call Functions}
+source(here('code','data-viz','plot-functions.R'))
 ```
@@
 load(here('output','analysis','out-pmc-urbanicity.RDa'))
+load(here('output','analysis','out-fac-urbanicity.RDa'))
 load(here('output','analysis','out-pmc-sescat.RDa'))
 load(here('output','analysis','out-pmc-region.RDa'))
+load(here('output','analysis','out-pmc-resid-region.RDa'))
+load(here('output','analysis','out-fac-region.RDa'))
 load(here('output','analysis','out-pmc-brfss.RDa'))
@@
 
-```{r color code}
-#https://www.schemecolor.com/british-airways-website.php
+```{r set theme 1 - single group plots}
+ggtheme.single <- theme_bw() + 
+  theme(panel.spacing.x = unit(0.25, 'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.background = element_rect(fill = "#B9CFED"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
+  )
 ```
 
-```{r - Components Base}
-data <- out.pmc.base
+```{r set theme 2 - effect modification, subgroups, multiple groups plots}
+ggtheme.multi.1 <- theme_classic() + 
+  theme(panel.spacing.x = unit(0.25,'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
+        strip.text.y.left = element_text(angle = 0),
+        strip.background = element_rect(fill = "#B9CFED"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = 'bottom',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 10, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in'))
+```
 
-cmp <- c("Mn","Fe","V", "Ni","Cl", "Na", "SO4", "Se","Cu", "K", "OC", "NO3", 
-         "Zn", "Pb", "Ca", "Si", "PM2.5")
+```{r set theme 3 - effect modification, subgroups, multiple groups plots}
+ggtheme.multi.2 <- theme_classic() + 
+  theme(panel.spacing.x = unit(0.25,'lines'),
+        panel.spacing.y = unit(c(0.25),'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
+        strip.text.y.left = element_text(angle = 0),
+        strip.background = element_rect(fill = "#B9CFED"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = 'bottom',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 10, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in'))
+```
+
+```{r}
 cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
@@
 
-data <- data %>% 
-  filter(Index %in% cmp,
+cuz.top.row <-  c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")
+cuz.bot.row <- c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")
+
+cmp.main <- c("Mn", "Fe", "V", "Ni", "Cl", "Na", "SO4", "Se", 
+              "Cu", "K", "OC", "NO3", "Zn", "Pb", "Ca", "Si", "PM2.5")
+cmp.multi <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+               "Ni", "V")
+
+So.main <- c("Steel", "Oil", "Salt", "Coal", 
+         "Biomass", "Traffic", "Metals", "Soil")
+So.multi <- c("Soil", "Metals", "Traffic",
+              "Coal", "Oil")
+
+So.ec <- c("Steel", "Coal", "Oil", "Salt",
+         "Biomass", "Metals", "Soil", "Traffic")
+
+cmp.res <- c("-V", "-Ni","-SO4", "-Se", "-OC", "-NO3", 
+         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
+So.res <- c("-Oil", "-Coal", 
+         "-Traffic", "-Metals", "-Soil", "PM2.5")
+
+cmp.multi.res <- c("PM2.5","-Si", "-Ca", "-Pb", "-Zn", "-NO3", "-OC",
+                   "-Se", "-SO4", "-Ni", "-V")
+```
+
+```{r - Components Base}
+data <- out.pmc.base %>% 
+  filter(Index %in% cmp.main,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         Index = factor(Index, levels = cmp.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-plot_cols <- c("#EB2226")
+plot.cols <- c("#EB2226")
 
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-              color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  ggtheme1 +
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
 ggsave(here('output','plot','pmc-base.png'), width = 6.5, height = 6.5)
@@
 ```{r - Components SES-Adj}
-data <- out.pmc.ses
-
-cmp <- c("Mn","Fe","V", "Ni","Cl", "Na", "SO4", "Se","Cu", "K", "OC", "NO3", 
-         "Zn", "Pb", "Ca", "Si", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.ses %>% 
+  filter(Index %in% cmp.main,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         Index = factor(Index, levels = cmp.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-plot_cols <- c("#EB2226")
+plot.cols <- c("#EB2226")
 
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-              color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  ggtheme1 +
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
 ggsave(here('output','plot','pmc-ses.png'), width = 6.5, height = 6.5)
@@
 
-```{r - Factor Base Inc EC}
-data <- out.fac.base.ec
-
-So <- c("Steel", "Coal", "Oil", "Salt", 
-         "Biomass", "Metals", "Soil", "Traffic")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
+```{r - Factor Base Ex. EC}
+data <- out.fac.base %>% 
+  filter(Index %in% So.main,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-plot_cols <- c("#EB2226")
+plot.cols <- c("#EB2226")
 
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  ggtheme1 +
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','fac-base.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factor SES-Adj Ex. EC}
+data <- out.fac.ses %>% 
+  filter(Index %in% So.main,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','fac-ses.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factor Inc. EC Base}
+data <- out.fac.base.ec %>% 
+  filter(Index %in% So.ec,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.ec),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
 ggsave(here('output','plot','fac-base-ec.png'), width = 6.5, height = 6.5)
@@
 
-```{r - Factor SES-Adj Inc EC}
-data <- out.fac.ses.ec
-
-So <- c("Steel", "Coal", "Oil", "Salt", 
-         "Biomass", "Metals", "Soil", "Traffic")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
+```{r - Factor Inc. EC SES-Adj}
+data <- out.fac.ses.ec %>% 
+  filter(Index %in% So.ec,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         Index = factor(Index, levels = So.ec),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-plot_cols <- c("#EB2226")
+plot.cols <- c("#EB2226")
 
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  ggtheme1 +
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
 ggsave(here('output','plot','fac-ses-ec.png'), width = 6.5, height = 6.5)
@@
 
-```{r - Factor Ex. EC Base}
-data <- out.fac.base
-
-So <- c("Steel", "Oil", "Salt", "Coal", 
-         "Biomass","Traffic", "Metals", "Soil")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
+```{r - Components - PM Residual}
+data <- out.pmc.resid %>% 
+  filter(Index %in% cmp.res,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
+         Index = factor(Index, levels = cmp.res),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-plot_cols <- c("#EB2226")
+plot.cols <- c("#EB2226")
 
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  ggtheme1 +
-ggsave(here('output','plot','fac-base.png'), width = 6.5, height = 6.5)
-```
-
-```{r - Factor EX. EC SES-Adj}
-data <- out.fac.ses
-
-So <- c("Steel", "Oil", "Salt", "Coal", 
-         "Biomass","Traffic", "Metals", "Soil")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#EB2226")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  ggtheme1 +
-ggsave(here('output','plot','fac-ses.png'), width = 6.5, height = 6.5)
-```
-
-```{r - Components - PM Residual}
-data <- out.pmc.resid
-
-cmp <- c("-V", "-Ni","-Cl", "-Na", "-SO4", "-Se", "-OC", "-NO3", 
-         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
-         sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos'))
-         )
-
-plot_cols <- c("#EB2226")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-               color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) +
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
-  ggtheme1 +
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
 ggsave(here('output','plot','pmc-resid.png'), width = 6.5, height = 6.5)
@@
 ```{r - Factor - PM Residual}
-data <- out.fac.resid
-
-So <- c("-Oil", "-Salt", "-Coal", 
-         "-Traffic", "-Metals", "-Soil", "PM2.5")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia",
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% So,
+data <- out.fac.resid %>% 
+  filter(Index %in% So.res,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So)
+         Index = factor(Index, levels = So.res),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.cols <- c("#EB2226")
 
-plot_cols <- c("#EB2226")
-
-ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
-              color =plot_cols, size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Index, shape = as.factor(sig)), 
-             color =plot_cols, size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-facet_wrap( ~ Cause, nrow = 2, scales = "fixed") +
-  ggtheme1 +
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
 ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 6.5)
@@
 ```{r - Components Age}
-data <- out.pmc.age
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.age %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(Age == "LE75", "b", "a"),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("> 75 years", "<= 75 years")
+plot.cols <- c("#EB2226", "#075AAA")
 
-plot_labs <- c("> 75 years", "<= 75 years")
-plot_cols <- c("#EB2226", "#075AAA")
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-age.png'), width = 6.5, height = 7.5)
+```
 
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
+```{r - Factor Age}
+data <- out.fac.age %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Age == "LE75", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
 
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+plot.labs <- c("> 75 years", "<= 75 years")
+plot.cols <- c("#EB2226", "#075AAA")
 
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-age.png'),p, width = 6.5, height = 6.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+ggsave(here('output', 'plot','fac-age.png'), width = 6.5, height = 6.5)
 ```
@@
 ```{r - Components Sex}
-data <- out.pmc.sex
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.sex %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(Sex == "F", "b", "a"),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("Male", "Female")
+plot.cols <- c("#EB2226", "#075AAA")
 
-plot_labs <- c("Male", "Female")
-plot_cols <- c("#EB2226", "#075AAA")
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-sex.png'), width = 6.5, height = 7.5)
+```
 
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+```{r - Factor Sex}
+data <- out.fac.sex %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Sex == "F", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
 
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
+plot.labs <- c("Male", "Female")
+plot.cols <- c("#EB2226", "#075AAA")
 
-ggsave(here('output', 'plot','pmc-sex.png'),p, width = 6.5, height = 6.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+ggsave(here('output', 'plot','fac-sex.png'), width = 6.5, height = 6.5)
 ```
@@
 ```{r - Components Race}
-data <- out.pmc.race
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.race %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(Race == "A", "d",
@@
                              ifelse(Race == "H", "b", "a"))),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("White", "Hispanic", "Black", "Asian")
+plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
 
-plot_labs <- c("White", "Hispanic", "Black", "Asian")
-plot_cols <- c("#EB2226", "orange", "#075AAA", "seagreen")
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-race.png'), width = 6.5, height = 7.5)
+```
 
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+```{r - Factor Race}
+data <- out.fac.race %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Race == "A", "d",
+                      ifelse(Race == "B", "c",
+                             ifelse(Race == "H", "b", "a"))),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
 
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
+plot.labs <- c("White", "Hispanic", "Black", "Asian")
+plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
 
-ggsave(here('output', 'plot','pmc-race.png'),p, width = 6.5, height = 6.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+ggsave(here('output', 'plot','fac-race.png'), width = 6.5, height = 6.5)
 ```
@@
 ```{r Components Urban}
-data <- out.pmc.urbanicity
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.urbanicity %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(Loc.Set == "urban", "b", "a"),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("Rural", "Urban")
+plot.cols <- c("#EB2226", "#075AAA")
 
-plot_labs <- c("Non-urban", "Urban")
-plot_cols <- c("#EB2226", "#075AAA")
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-urbanicity.png'), width = 6.5, height = 7.5)
+```
 
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+```{r - Factor Urbaniity}
+data <- out.fac.urbanicity %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Loc.Set == "urban", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
 
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "fixed", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
+plot.labs <- c("Rural", "Urban")
+plot.cols <- c("#EB2226", "#075AAA")
 
-ggsave(here('output', 'plot','pmc-urbanicity.png'),p, width = 6.5, height = 6.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+ggsave(here('output', 'plot','fac-urbanicity.png'), width = 6.5, height = 6.5)
 ```
@@
 ```{r Components SES-Urban}
-data <- out.pmc.sescat
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.sescat %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(SES.Cat == "L", "c",
                       ifelse(SES.Cat == "M", "b", "a")),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("High", "Middle", "Low")
+plot.cols <-  c("#01742F", "#075AAA", "#EB2226")
 
-plot_labs <- c("High", "Middle", "Low")
-plot_cols <-  c("seagreen", "#075AAA", "#EB2226")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-sescat.png'),p, width = 6.5, height = 6.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-sescat.png'), width = 6.5, height = 7.5)
 ```
@@
 ```{r - Components Region}
-data <- out.pmc.region
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V") 
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.region %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(Region == "west", "d",
@@
                              ifelse(Region == "south", "b", "a"))),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("Northeast", "South", "Midwest", "West")
+plot.cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")
 
-plot_labs <- c("NE", "S", "MW", "W")
-plot_cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
+```
+```{r - Factor Region}
+data <- out.fac.region %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+  Tag = ifelse(Region == "west", "d",
+               ifelse(Region == "midwest", "c",
+                      ifelse(Region == "south", "b", "a"))),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
 
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
+plot.labs <- c("Northeast", "South", "Midwest", "West")
+plot.cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")
 
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+ggsave(here('output', 'plot','fac-region.png'), width = 6.5, height = 6.5)
+```
 
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
+```{r - Components Residual Region}
+data <- out.pmc.resid.region %>% 
+  filter(Index %in% cmp.multi.res,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp.multi.res),
+         Tag = ifelse(Region == "west", "d",
+                      ifelse(Region == "midwest", "c",
+                             ifelse(Region == "south", "b", "a"))),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
 
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
+plot.labs <- c("Northeast", "South", "Midwest", "West")
+plot.cols <- c("#07f900", "#0433ff", "#ffa501", "#a034f0")
 
-ggsave(here('output', 'plot','pmc-region.png'),p, width = 6.5, height = 6.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-resid-region.png'),width = 6.5, height = 7.5)
 ```
@@
 ```{r - Components BRFSS}
-data <- out.pmc.brfss
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.brfss %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(BRFSS == "brfss0", "b", "a"),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("BRFSS-Adjusted", "Base")
+plot.cols <- c("#EB2226", "#075AAA")
 
-plot_labs <- c("BRFSS-Adjusted", "Base")
-plot_cols <- c("#EB2226", "#075AAA")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-brfss.png'),p, width = 6.5, height = 8.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-brfss.png'), width = 6.5, height = 7.5)
 ```
@@
 ```{r Components Buffer}
-data <- out.pmc.buffer
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.buffer %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(Buffer == 6, "c",
                       ifelse(Buffer == 12, "b", "a")),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("24-miles", "12-miles", "6-miles") 
+plot.cols <- c("#EB2226", "#075AAA", "#01742F")
 
-plot_labs <- c("24-miles", "12-miles", "6-miles") 
-plot_cols <- c("#EB2226", "#075AAA", "seagreen")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-buffer.png'),p, width = 6.5, height = 8.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+ggsave(here('output', 'plot','pmc-buffer.png'), width = 6.5, height = 7.5)
 ```
@@
 ```{r Components Exposure window}
-data <- out.pmc.expo
-
-cmp <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
-         "Na", "Cl", "Ni", "V")
-cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
-         "Respiratory", "COPD", "Pneumonia", 
-         "Cancer", "Lung Cancer")
-
-data <- data %>% 
-  filter(Index %in% cmp,
+data <- out.pmc.expo %>% 
+  filter(Index %in% cmp.multi,
          Cause %in% cuz) %>% 
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp),
+         Index = factor(Index, levels = cmp.multi),
          Tag = ifelse(Window == 1, "e",
@@
                                     ifelse(Window == 4, "b", "a")))),
-         Tag = as.factor(Tag)
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
   )
 
-data <- data %>% 
-  mutate(sig = ifelse(HR.U < 1 , '1-prtc',
-                      ifelse((HR.L<=1 & HR.U>=1), '2-null','3-sigpos')))
+plot.labs <- c("5-yr", "4-yr","3-yr","2-yr","1-yr")
+plot.cols <- c("#EB2226","#FF8200","#9D178D","#075AAA","#01742F")
 
-plot_labs <- c("5-yr", "4-yr","3-yr","2-yr","1-yr")
-plot_cols <- c("#EB2226","orange","purple","#075AAA","seagreen")
-
-p <- grid.arrange(
-ggplot(data = filter(data, Cause %in% c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = F) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)), 
-             size = 1.5, show.legend = F) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-
-ggplot(data = filter(data, Cause %in% c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")),
-       aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
-  geom_vline(xintercept = 1, linetype = 2, color = "black") +
-  labs(x = "", y = "") +
-  geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
-                size = 0.25, show.legend = T) + 
-  geom_point(aes(x = HR, y = Tag, color = Tag, shape = as.factor(sig)),
-             size = 1.5, show.legend = T) + 
-  scale_shape_manual(values = c(16, 1, 16), guide = F) +
-  scale_color_manual(
-    labels = plot_labs, 
-    values = plot_cols) +
-
-facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
-               shrink = T, space = 'fixed') +
-  ggtheme2 +
-  guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")),
-nrow = 2)
-
-ggsave(here('output', 'plot','pmc-expo.png'),p, width = 6.5, height = 8.5)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) + 
+ggsave(here('output', 'plot','pmc-expo.png'), width = 6.5, height = 8.5)
 ```

### 2021-02-01 code/data-viz/plot-functions.R

@@ -1,0 +1,72 @@
+### Author: Fatemeh Kazemi - 01-30-2021
+
+# Functions for plotting results of exposure ~ outcome analysis
+# Hazard Ratio (HR) and 95% CI (HR.L, HR.U) (HR.Lower and HR.Upper)
+
+library(tidyverse)
+library(ggpubr)
+
+### Function *** Plot.Single ***
+# Function Arguments: 
+# dt : dataset that contains the HRs for each exposure and outcome
+
+### Single Group Plot Function
+Plot.Single <- function(dt, ggtheme){
+  p <- ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+    geom_vline(xintercept = 1, linetype = 2, color = "black") +
+    labs(x = "", y = "") +
+    geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+                 color = plot.cols, size = 0.25, show.legend = F) + 
+    geom_point(aes(x = HR, y = Index, shape = sig), 
+               color = plot.cols, size = 1.5, show.legend = F) +
+    scale_shape_identity() +
+    facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+    ggtheme
+  return(p)
+}
+
+
+### Function *** Plot.Multi ***
+# Function Arguments: 
+# dt : dataset that contains the HRs for each exposure, outcome and subgroups
+
+### Multiple Group Plot Function
+Plot.Multi <- function(dt, ggtheme) {
+  p1 <- ggplot(data = filter(data, Cause %in% cuz.top.row),
+               aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
+    geom_vline(xintercept = 1, linetype = 2, color = "black") +
+    labs(x = "", y = "") +
+    geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
+                 size = 0.25, show.legend = T) + 
+    geom_point(aes(x = HR, y = Tag, color = Tag, shape = sig), 
+               size = 1.5, show.legend = T) + 
+    scale_shape_identity() +
+    scale_color_manual(
+      labels = plot.labs, 
+      values = plot.cols) +
+    
+    facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
+               shrink = T, space = 'fixed') +
+    ggtheme +
[…]

### 2021-02-03 code/data-processors/air-data-processor.Rmd
black carbon exploration

@@
   mutate(Parameter.Symbol = as.factor(Parameter.Symbol))
+
+Code.to.Sym <- tribble(
+  ~Parameter.Code, ~Parameter.Symbol,
+   88313, "BC",
+   88317, "BC.c"
+   ) %>% 
+  mutate(Parameter.Symbol = as.factor(Parameter.Symbol))
 ```
@@
 #Monitor.ID: Site.ID-POC
+
+dt.bc.raw <- EPA.AQS.download (period = "daily", Index = "SPEC",
+                        start = 2000, end = 2008, 
+                        Code.Sym = Code.to.Sym)
+save(dt.bc.raw, file = here('data', 'raw', 'bc-raw.RDa'))
+
+dt.bc.raw %>% distinct(Monitor.ID) %>% nrow() #29
+dt.bc.raw %>% distinct(Site.ID) %>% nrow() #28
+
+dt.spec.raw <- dt.spec.raw %>% 
+  add_row(dt.bc.raw)
 ```

### 2021-02-07 code/data-processors/air-data-processor.Rmd
function for forest plots for results

@@
 library(here)
-#library(lubridate)
+library(lubridate)
 #library(naniar) # for replacing -999 with NA
@@
     Land.Use,
-    Location.Setting = as.factor(
-      ifelse(Location.Setting == "URBAN AND CENTER CITY", "URBAN",
-             as.character(Location.Setting)))
+    Location.Setting
     ) %>% 
@@
   summarise(n = n())
+
+dt.aqs.sites.ii <- dt.aqs.sites %>% 
+  mutate(Location.Setting = as.factor(
+      ifelse(Location.Setting == "URBAN AND CENTER CITY", "URBAN",
+             as.character(Location.Setting))))
+
+save(dt.aqs.sites.ii, file = here('data', 'processed', 'aqs-sites-ii.RDa'))
 ```
@@
 
-ec.c %>% merge(dt.aqs.sites) %>% 
+ec.c %>% merge(dt.aqs.sites.ii) %>% 
   distinct(Site.ID, Location.Setting) %>% 
@@
 
-oc.c %>% merge(dt.aqs.sites) %>% 
+oc.c %>% merge(dt.aqs.sites.ii) %>% 
   distinct(Site.ID, Location.Setting) %>% 
@@
 dt.site.pmc <- dt.pmc.1yr %>% distinct(Site.ID) %>%  #574 -> 558 > 471 > 322
-  merge(dt.aqs.sites)
+  merge(dt.aqs.sites.ii)
 save(dt.site.pmc, file = here('data', 'processed', 'site-pmc.RDa'))
@@
   rename(Site.ID = Site_ID) %>% 
-  left_join(dt.aqs.sites) %>% 
+  left_join(dt.aqs.sites.ii) %>% 
   left_join(dt.site.carbon.method)
@@
   rename(Site.ID = Site_ID) %>% 
-  left_join(dt.aqs.sites)
+  left_join(dt.aqs.sites.ii)
 

### 2021-02-07 code/data-viz/forest-plots.Rmd
function for forest plots for results

--- 2021-02-01 code/data-viz/plot-results.Rmd
@@
 ```{r Call Functions}
-source(here('code','data-viz','plot-functions.R'))
+source(here('code','data-viz','forest-plot-functions.R'))
 ```
@@
 
-```{r set theme 2 - effect modification, subgroups, multiple groups plots}
+```{r set theme 2 - components - effect modification, subgroups, multiple groups plots}
 ggtheme.multi.1 <- theme_classic() + 
@@
 
-```{r set theme 3 - effect modification, subgroups, multiple groups plots}
+```{r set theme 3 - factors - effect modification, subgroups, multiple groups plots}
 ggtheme.multi.2 <- theme_classic() + 
@@
 ```
+
 ```{r - Factor Region}

### 2021-02-14 code/data-analysis/factor-analysis.Rmd
modified factor data names - shape and color plots - mass apportionemnt

--- 2021-01-25 code/data-analysis/factor-analysis.Rmd
@@
 
+```{r}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+```
+
 ```{r load packages}
@@
   library(psych) # for factor analysis
+  library(lme4) # mixed model
+  library(sjPlot) # tab_model
 ```
@@
 load(here('data','processed', 'pmc-daily.RDa'))
+load(here('data','processed', 'aqs-sites.RDa'))
 ```
@@
 fit <- factanal(dt.pmc.daily %>% select(AS:OC), 8, rotation="varimax")
-factor.loadings <- rbind(fit$loadings)
-save(factor.loadings, file = here('output','table','factor-loadings.RDa'))
+factor.loadings.ec <- rbind(fit$loadings)
+save(factor.loadings.ec, file = here('output','table','factor-loadings-ec.RDa'))
 #Traffic Soil Metals Biomass Salt Oil Coal Steel
@@
 dt.fac.daily <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores) 
-save(dt.fac.daily, file = here('data', 'processed', 'fac-daily.RDa'))
+save(dt.fac.ec.daily, file = here('data', 'processed', 'fac-ec-daily.RDa'))
 ```
@@
 fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
-factor.loadings.ex.ec <- rbind(fit$loadings)
-save(factor.loadings.ex.ec, file = here('output','table','factor-loadings-ex-ec.RDa'))
+factor.loadings <- rbind(fit$loadings)
+save(factor.loadings, file = here('output','table','factor-loadings.RDa'))
 # Soil Metals Traffic Biomass Coal Salt Oil Steel
+write.csv(factor.loadings,
+          file = here('output','table', 'factor-loadings.csv'))
 
 factor.scores <- factor.scores(dt.pmc.daily %>% select(AS:ZN, OC), fit)
-dt.fac.daily.ex.ec <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores)
-save(dt.fac.daily.ex.ec, file = here('data', 'processed', 'fac-daily-ex-ec.RDa'))
+dt.fac.daily <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores)
+save(dt.fac.daily, file = here('data', 'processed', 'fac-daily.RDa'))
 ```
@@
 
-```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
-dt.air <- dt.fac.daily.ex.ec %>% 
+```{r Smoothing Data & Caluculating 1-yr mvavg for each month with EC}
+dt.air <- dt.fac.daily.ec %>% 
   pivot_longer(cols = Factor1:Factor8,
@@
 
-dt.fac.ex.ec.1yr <- para.monthly %>% 
+dt.fac.ec.1yr <- para.monthly %>% 
   mutate(Year = floor(Date -0.01),
@@
 
-save(dt.fac.ex.ec.1yr, file = here('data', 'processed', 'fac-ex-ec-1yr.RDa'))
-write.csv(dt.fac.ex.ec.1yr, file = here('data', 'processed', 'fac-ex-ec-1yr.csv'), row.names = F)
+save(dt.fac.ec.1yr, file = here('data', 'processed', 'fac-ec-1yr.RDa'))
+write.csv(dt.fac.ec.1yr, file = here('data', 'processed', 'fac-ec-1yr.csv'), row.names = F)
 ```
@@
 
-dt.fac.ex.ec.residual <- dt.fac.daily.ex.ec %>% 
+dt.fac.residual <- dt.fac.daily %>% 
   merge(dt.pm.daily) %>% 
@@
 
-save(dt.fac.ex.ec.residual, file = here('data', 'processed', 'fac-ex-ec-residual.RDa'))
+save(dt.fac.residual, file = here('data', 'processed', 'fac-residual.RDa'))
 ```
@@
 ```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
-dt.air <- dt.fac.ex.ec.residual %>% 
+dt.air <- dt.fac.residual %>% 
   pivot_longer(cols = PM_Factor1:PM_Factor8,
@@
 
-dt.fac.ex.ec.residual.1yr <- para.monthly %>% 
+dt.fac.residual.1yr <- para.monthly %>% 
   mutate(Year = floor(Date -0.01),
@@
 
-save(dt.fac.ex.ec.residual.1yr, file = here('data', 'processed', 'fac-ex-ec-residual-1yr.RDa'))
+save(dt.fac.residual.1yr, file = here('data', 'processed', 'fac-residual-1yr.RDa'))
 
 ```
+
+```{r - Single Tracer Mass Regression Model Test}
+# Factor order: Soil Metals Traffic Biomass Coal Salt Oil Steel
+# Soil(Si), Metals(Pb), Traffic(Oc), Biomass(K),
+# Coal(SO4), Salt(Cl), Oil(Ni), Steel(Fe)
+
+### high load
+high.load <- lmer(data = dt.pmc.daily,
+              PM ~ SI + PB + OC + K + SO4 + CL + NI + FE + (1|Site.ID))
+tab_model(high.load, show.se = T, show.ci = F, show.aic = T,
+            show.re.var = F, show.icc = T, show.obs = T, show.ngroups = T,
+          title = "Higher Load Tracers")
+
+### high health impact
+high.health <- lmer(data = dt.pmc.daily,
+              PM ~ SI + PB + NO3 + K + SO4 + CL + NI + FE + (1|Site.ID))
+tab_model(high.health, show.se = T, show.ci = F, show.aic = T, digits = 2,
+            show.re.var = F, show.icc = T, show.obs = T, show.ngroups = T,
+          title = "Higher Health Impact Tracers")
+# Nagative Ni
+
+### high health impact ii
+high.health <- lmer(data = dt.pmc.daily,
+              PM ~ SI + PB + NO3 + K + SO4 + CL + NI + MN + (1|Site.ID))
+tab_model(high.health, show.se = T, show.ci = F, show.aic = T, digits = 2,
+            show.re.var = F, show.icc = T, show.obs = T, show.ngroups = T,
+          title = "Higher Health Impact Tracers - II")
+
+### Thurston
+thurston <- lmer(data = dt.pmc.daily,
+              PM ~ SI + ZN + NO3 + K + SO4 + CL + NI + FE + (1|Site.ID))
+tab_model(thurston, show.se = T, show.ci = F, show.aic = T, digits = 2,
+            show.re.var = F, show.icc = T, show.obs = T, show.ngroups = T,
+          title = "Close to Thurston Tracers")
+# Negative Ni
+```
+
+```{r - Single Tracer Mass Apportionment}
+dt.sites <- dt.aqs.sites %>% 
+  transmute(Site.ID,
+            Latitude,
+            Longitude,
+            Location = ifelse(Location.Setting != "RURAL", "Urban", "Rural"),
+            Region = ifelse(Region.IV == 1, "West",
+                            ifelse(Region.IV == 2, "Midwest",
+                                   ifelse(Region.IV == 3, "South", "Northeast"))))
+
+Sources <- c("Soil", "Metal", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")
+
+so.coef <- function(model, cmp){
+  source = as.numeric(summary(model)$coefficients[,1][cmp])
+  return(source)
+}
+
+dt.mass.app <- dt.pmc.daily %>% 
+  mutate(Soil = so.coef(high.load, 'SI') * SI,
+         Metal = so.coef(high.load, 'PB') * PB,
+         Traffic = so.coef(high.load, 'OC') * OC,
+         Biomass = so.coef(high.load, 'K') * K,
+         Coal = so.coef(high.load, 'SO4') * SO4,
+         Salt = so.coef(high.load, 'CL') * CL,
+         Oil = so.coef(high.load, 'NI') * NI,
+         Steel = so.coef(high.load, 'FE') * FE) %>% 
+  select(Site.ID, Date, PM, Sources) %>% 
+  inner_join(dt.sites) %>% 
+  pivot_longer(cols = c('PM', Sources),
+               names_to = "Source",
+               values_to = "Mass")
+
+save(dt.mass.app, file = here('data', 'processed', 'mass-apportioned.RDa'))
+
+mass.summary.us <- dt.mass.app %>% 
+  group_by(Source) %>% 
+  summarise(Mass.mean = round(mean(Mass),2),
+            Mass.sd = round(sd(Mass),2)) %>% 
+  mutate(Unit = "US")
+
+mass.summary.region <- dt.mass.app %>% 
+  group_by(Source, Region) %>% 
+  summarise(Mass.mean = round(mean(Mass),2),
+            Mass.sd = round(sd(Mass),2)) %>% 
+  rename(Unit = Region)
+
+mass.summary.locset <- dt.mass.app %>% 
+  group_by(Source, Location) %>% 
+  summarise(Mass.mean = round(mean(Mass),2),
+            Mass.sd = round(sd(Mass),2)) %>% 
+rename(Unit = Location)
+
+mass.summary <- mass.summary.us %>% 
+  add_row(mass.summary.region) %>% 
+  add_row(mass.summary.locset)
+
+write.csv(mass.summary,
+          file = here('output','table', 'mass-app-summary.csv'))
+
+dt.mass.map <- dt.mass.app %>% 
+  group_by(Site.ID, Source) %>% 
+  summarise(Mass = mean(Mass)) %>% 
+  pivot_wider(names_from = "Source",
+              values_from = "Mass") %>% 
+  inner_join(dt.sites)
+
+save(dt.mass.map, file = here('data', 'processed', 'mass-map.RDa'))
+write.csv(dt.mass.map, file = here('output','table', 'mass-map.csv'), row.names = F)
+```

### 2021-02-14 code/data-analysis/output-cleaning.Rmd
modified factor data names - shape and color plots - mass apportionemnt

@@
 ---
+
+```{r}
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+```
 
@@
 load(here('data','processed','fac-1yr.RDa'))
-load(here('data','processed','fac-ex-ec-1yr.RDa'))
+load(here('data','processed','fac-ec-1yr.RDa'))
 load(here('data','processed','pmc-site-ndi.RDa'))
@@
 
-### Factors
+### Factors excluding EC
 Factor.to.Index <- tribble(
+  ~Index, ~Parameter,
+   "Soil", "Factor1",
+   "Metals", "Factor2",
+   "Traffic", "Factor3",
+   "Biomass", "Factor4",
+   "Coal", "Factor5",
+   "Salt", "Factor6",
+   "Oil", "Factor7",
+   "Steel", "Factor8"
+   ) %>% 
+  mutate(Index = as.factor(Index),
+         Parameter = as.factor(Parameter))
+
+### Factors Inc. EC
+Factor.ec.to.Index <- tribble(
   ~Index, ~Parameter,
@@
    "Coal", "Factor7",
-   "Steel", "Factor8"
-   ) %>% 
-  mutate(Index = as.factor(Index),
-         Parameter = as.factor(Parameter))
-
-### Factors excluding EC
-Factor.ex.ec.to.Index <- tribble(
-  ~Index, ~Parameter,
-   "Soil", "Factor1",
-   "Metals", "Factor2",
-   "Traffic", "Factor3",
-   "Biomass", "Factor4",
-   "Coal", "Factor5",
-   "Salt", "Factor6",
-   "Oil", "Factor7",
    "Steel", "Factor8"
@@
 ```{r calculating IQRS}
-
 ### Components
@@
 
-### Factors
+### Factors excluding EC
 fac.1yr.iqr <- dt.pmc.site.ndi %>% 
@@
 
-### Factors excluding EC
-fac.ex.ec.1yr.iqr <- dt.pmc.site.ndi %>% 
+### Factors Inc EC
+fac.ec.1yr.iqr <- dt.pmc.site.ndi %>% 
   select(Site.ID) %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.ec.1yr) %>% 
   summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
@@
 
-### Components - urbanicity
-pmc.1yr.locset.iqr <- dt.pmc.site.ndi %>% 
-   mutate(Loc.Set = ifelse(!Location.Setting == "RURAL", "urban","rural")) %>% 
-  select(Site.ID, Loc.Set) %>% 
-  inner_join(dt.pmc.1yr) %>% 
-  group_by(Loc.Set) %>% 
-  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
-  pivot_longer(cols = AS:ZN,
-               names_to = "Parameter",
-               values_to = "IQR") %>% 
-  mutate(Parameter = as.factor(Parameter))
-
-### Components - region
-pmc.1yr.region.iqr <- dt.pmc.site.ndi %>% 
-  select(Site.ID, Region.IV) %>% 
-  inner_join(dt.pmc.1yr) %>% 
-  group_by(Region.IV) %>% 
-  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
-  pivot_longer(cols = AS:ZN,
-               names_to = "Parameter",
-               values_to = "IQR") %>% 
-  mutate(Parameter = as.factor(Parameter))
-
 ### Components - 5yr
-pmc.5yr.iqr <- dt.pmc.5yr %>% 
+pmc.5yr.5yr.iqr <- dt.pmc.5yr %>% 
   summarise_at(vars(CA:SE), ~IQR(.x)) %>% 
@@
                values_to = "IQR") %>% 
-  mutate(Parameter = as.factor(Parameter))
+  mutate(Parameter = as.factor(Parameter),
+         Window = "5")
 
@@
                values_to = "IQR") %>% 
-  mutate(Parameter = as.factor(Parameter))
+  mutate(Parameter = as.factor(Parameter),
+         Window = "4")
 
@@
                values_to = "IQR") %>% 
-  mutate(Parameter = as.factor(Parameter))
+  mutate(Parameter = as.factor(Parameter),
+         Window = "3")
 
@@
                values_to = "IQR") %>% 
-  mutate(Parameter = as.factor(Parameter))
+  mutate(Parameter = as.factor(Parameter),
+         Window = "2")
 
@@
                values_to = "IQR") %>% 
-  mutate(Parameter = as.factor(Parameter))
+  mutate(Parameter = as.factor(Parameter),
+         Window = "1")
+
+# combine 1yr to 5yr
+pmc.xyr.5yr.iqr  <-  pmc.5yr.5yr.iqr %>% 
+  add_row(pmc.4yr.5yr.iqr) %>% 
+  add_row(pmc.3yr.5yr.iqr) %>% 
+  add_row(pmc.2yr.5yr.iqr) %>% 
+  add_row(pmc.1yr.5yr.iqr)
+
 ```
@@
 
-```{r Output Factors Base}
-out.fac.base.ec <- read.csv(here('output','analysis','fac-base.csv')) %>% 
+```{r Output Factors Ex. EC Base}
+out.fac.base <- read.csv(here('output','analysis','fac-base.csv')) %>% 
   rename(Parameter = Predictor) %>% 
@@
   merge(Factor.to.Index) %>% 
-  merge(Outcome.to.Cause) %>% 
-  mutate(HR = round(exp(Coef * IQR),3),
-         HR.L = round(exp((Coef-1.96*std) * IQR),3),
-         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
-  arrange(Config) %>% 
-  select(Index, Cause, HR, HR.L, HR.U)
-
-save(out.fac.base.ec, file = here('output','analysis','out-fac-base-ec.RDa'))
-```
-
-```{r Output Factors SES-Adj}
-out.fac.ses.ec <- read.csv(here('output','analysis','fac-ses.csv')) %>% 
-  rename(Parameter = Predictor) %>% 
-  merge(fac.1yr.iqr) %>% 
-  merge(Factor.to.Index) %>% 
-  merge(Outcome.to.Cause) %>% 
-  mutate(HR = round(exp(Coef * IQR),3),
-         HR.L = round(exp((Coef-1.96*std) * IQR),3),
-         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
-  arrange(Config) %>% 
-  select(Index, Cause, HR, HR.L, HR.U)
-
-save(out.fac.ses.ec, file = here('output','analysis','out-fac-ses-ec.RDa'))
-```
-
-```{r Output Factors Ex. EC Base}
-out.fac.base <- read.csv(here('output','analysis','fac-ex-ec-base.csv')) %>% 
-  rename(Parameter = Predictor) %>% 
-  merge(fac.ex.ec.1yr.iqr) %>% 
-  merge(Factor.ex.ec.to.Index) %>% 
   merge(Outcome.to.Cause) %>% 
@@
 ```{r Output Factors Ex. EC SES-Adj}
-out.fac.ses <- read.csv(here('output','analysis','fac-ex-ec-ses.csv')) %>% 
+out.fac.ses <- read.csv(here('output','analysis','fac-ses.csv')) %>% 
   rename(Parameter = Predictor) %>% 
-  merge(fac.ex.ec.1yr.iqr) %>% 
-  merge(Factor.ex.ec.to.Index) %>% 
+  merge(fac.1yr.iqr) %>% 
+  merge(Factor.to.Index) %>% 
   merge(Outcome.to.Cause) %>% 
@@
 save(out.fac.ses, file = here('output','analysis','out-fac-ses.RDa'))
+```
+
+```{r Output Factors Base}
+out.fac.ec.base <- read.csv(here('output','analysis','fac-ec-base.csv')) %>% 
+  rename(Parameter = Predictor) %>% 
+  merge(fac.ec.1yr.iqr) %>% 
+  merge(Factor.ec.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, HR, HR.L, HR.U)
+
+save(out.fac.ec.base, file = here('output','analysis','out-fac-ec-base.RDa'))
+```
+
+```{r Output Factors SES-Adj}
+out.fac.ec.ses <- read.csv(here('output','analysis','fac-ec-ses.csv')) %>% 
+  rename(Parameter = Predictor) %>% 
+  merge(fac.ec.1yr.iqr) %>% 
+  merge(Factor.ec.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, HR, HR.L, HR.U)
+
+save(out.fac.ec.ses, file = here('output','analysis','out-fac-ec-ses.RDa'))
 ```
@@
          Parameter = as.factor(Parameter)) %>% 
-  merge(Factor.ex.ec.to.Index) %>% 
+  merge(Factor.to.Index) %>% 
   mutate(Index = paste0('-', Index)) %>% 
@@
   merge(fac.1yr.iqr) %>% 
-  merge(Factor.ex.ec.to.Index) %>% 
+  merge(Factor.to.Index) %>% 
   merge(Outcome.to.Cause) %>% 
@@
 save(out.pmc.urbanicity, file = here('output','analysis','out-pmc-urbanicity.RDa'))
+```
+
+```{r Output Factor Urbanicity}
+out.fac.urbanicity = data.frame()
+for (i in c("urban", "rural")){
+  dt <- read.csv(here('output','analysis',paste('fac-',i,'.csv', sep= ""))) %>% 
+    mutate(Loc.Set = i)
+  out.fac.urbanicity  <-  rbind(out.fac.urbanicity, dt)
+}
+
+out.fac.urbanicity <- out.fac.urbanicity %>% 
+  rename(Parameter = Predictor) %>% 
+  merge(fac.1yr.iqr) %>% 
+  merge(Factor.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Loc.Set, HR, HR.L, HR.U)
+
+save(out.fac.urbanicity, file = here('output','analysis','out-fac-urbanicity.RDa'))
 ```
@@
 PM.IQR <- as.double(pmc.1yr.iqr[pmc.1yr.iqr$Parameter == 'PM', 'IQR'])
-load(here('output','analysis','out-pmc-ses.RDa'))
-PM <- out.pmc.ses %>% 
+load(here('output','analysis','out-pmc-region.RDa'))
+PM <- out.pmc.region %>% 
   filter(Index == "PM2.5")
@@
 save(out.pmc.resid.region, file = here('output','analysis','out-pmc-resid-region.RDa'))
+```
+
+```{r Output Factor Region}
+out.fac.region = data.frame()
+for (i in c("west", "midwest", "south", "northeast")){
+  dt <- read.csv(here('output','analysis',paste('fac-',i,'.csv', sep= ""))) %>% 
+    mutate(Region = i)
+  out.fac.region  <-  rbind(out.fac.region, dt)
+}
+
+out.fac.region <- out.fac.region %>% 
+  rename(Parameter = Predictor) %>% 
+  merge(fac.1yr.iqr) %>% 
+  merge(Factor.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, Region, HR, HR.L, HR.U)
+
+save(out.fac.region, file = here('output','analysis','out-fac-region.RDa'))
 ```
@@
          Parameter = as.factor(Parameter)) %>% 
-  merge(pmc.1yr.iqr) %>% 
+  merge(pmc.xyr.5yr.iqr) %>% 
   merge(Para.to.Index) %>% 

### 2021-02-14 code/data-processors/cms-data-processor.Rmd
modified factor data names - shape and color plots - mass apportionemnt

@@
 load(here('data','processed','fac-1yr.RDa'))
-load(here('data','processed','fac-ex-ec-1yr.RDa'))
+load(here('data','processed','fac-ec-1yr.RDa'))
 load(here('data','processed','pmc-residual-1yr.RDa'))
-load(here('data','processed','fac-ex-ec-residual-1yr.RDa'))
+load(here('data','processed','fac-residual-1yr.RDa'))
 load(here('data','processed','pmc-sub-5yr.RDa'))
@@
 
-```{r Factors}
+```{r Factors with EC}
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.fac.ec <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.fac.ec.1yr) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.fac.ec, 
+          file = here('data', 'processed', 'ndi-fac-ec.csv'),
+          row.names = F)
+```
+
+```{r Factors Excluding EC}
 dt.ses <- dt.ses.site.bz12 %>% 
@@
           file = here('data', 'processed', 'ndi-fac.csv'),
-          row.names = F)
-```
-
-```{r Factors Excluding EC}
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.fac.ex.ec <- dt.master.ndi.pmc %>% 
-  mutate(StrID = paste(age, sex, race)) %>% 
-  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
-  inner_join(dt.fac.ex.ec.1yr) %>% 
-  inner_join(dt.ses) %>% 
-  rename(SiteID = Site.ID)
-
-write.csv(dt.ndi.fac.ex.ec, 
-          file = here('data', 'processed', 'ndi-fac-ex-ec.csv'),
           row.names = F)
@@
 
-```{r Factors Excluding EC Residual}
-dt.ses <- dt.ses.site.bz12 %>% 
-  mutate(ses = SES.Zip.Norm) %>% 
-  select(Site.ID, Year, ses)
-
-dt.ndi.fac.ex.ec.residual <- dt.master.ndi.pmc %>% 
+```{r Factors Residual}
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.fac.residual <- dt.master.ndi.pmc %>% 
   mutate(StrID = paste(age, sex, race)) %>% 
@@
          -no_death_uri, -no_death_ards) %>%  
-  inner_join(dt.fac.ex.ec.residual.1yr) %>% 
+  inner_join(dt.fac.residual.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 
-write.csv(dt.ndi.fac.ex.ec.residual, 
-          file = here('data', 'processed', 'ndi-fac-ex-ec-residual.csv'),
+write.csv(dt.ndi.fac.residual, 
+          file = here('data', 'processed', 'ndi-fac-residual.csv'),
           row.names = F)
@@
 dt.ndi.fac.ageLE75 <- dt.age %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.ageM75 <- dt.age %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
          -no_death_uri, -no_death_ards) %>%  
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses)
@@
 dt.ndi.fac.raceA <- dt.raceA %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.raceB <- dt.raceB %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.raceH <- dt.raceH %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
 dt.ndi.fac.raceW <- dt.raceW %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses) %>% 
@@
          -no_death_uri, -no_death_ards) %>% 
-  inner_join(dt.fac.ex.ec.1yr) %>% 
+  inner_join(dt.fac.1yr) %>% 
   inner_join(dt.ses) %>% 

### 2021-02-14 code/data-viz/forest-plots-color-shape.Rmd
modified factor data names - shape and color plots - mass apportionemnt

---
title: "PM Component Paper Plots"
author: "Fatemeh Kazemi"
date: "02-13-2021"
---

### plots subgroups using different colors and shapes
###color codes: https://www.schemecolor.com/british-airways-website.php

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Load packages}
  library(tidyverse)
  library(here)
  library(ggthemes)
```

```{r Call Functions}
source(here('code','data-viz','forest-plot-functions.R'))
```

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-fac-base-ec.RDa'))
load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

```{r set theme 1 - single group plots}
ggtheme.single <- theme_bw() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  )
```

```{r set theme 2 - components - effect modification, subgroups, multiple groups plots}
ggtheme.multi.1 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 3 - factors - effect modification, subgroups, multiple groups plots}
ggtheme.multi.2 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.25,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r}
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

cuz.top.row <-  c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")
cuz.bot.row <- c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")

cmp.main <- c("Mn", "Fe", "V", "Ni", "Cl", "Na", "SO4", "Se", 
              "Cu", "K", "OC", "NO3", "Zn", "Pb", "Ca", "Si", "PM2.5")
cmp.multi <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
               "Ni", "V")

So.main <- c("Steel", "Oil", "Salt", "Coal", 
         "Biomass", "Traffic", "Metals", "Soil")
So.multi <- c("Soil", "Metals", "Traffic",
              "Coal", "Oil")

So.ec <- c("Steel", "Coal", "Oil", "Salt",
         "Biomass", "Metals", "Soil", "Traffic")

cmp.res <- c("-V", "-Ni","-SO4", "-Se", "-OC", "-NO3", 
         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
So.res <- c("-Oil", "-Coal", 
         "-Traffic", "-Metals", "-Soil", "PM2.5")

cmp.multi.res <- c("PM2.5","-Si", "-Ca", "-Pb", "-Zn", "-NO3", "-OC",
                   "-Se", "-SO4", "-Ni", "-V")
```

```{r - Components Base}
data <- out.pmc.base %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','pmc-base.png'), width = 6.5, height = 6.5)
```

```{r - Components SES-Adj}
data <- out.pmc.ses %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','pmc-ses.png'), width = 6.5, height = 6.5)
```

```{r - Factor Base Ex. EC}
data <- out.fac.base %>% 
  filter(Index %in% So.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','fac-base.png'), width = 6.5, height = 6.5)
```

```{r - Factor SES-Adj Ex. EC}
data <- out.fac.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','fac-ses.png'), width = 6.5, height = 6.5)
```

```{r - Components - PM Residual}
data <- out.pmc.resid %>% 
  filter(Index %in% cmp.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','pmc-resid.png'), width = 6.5, height = 6.5)
```

```{r - Factor - PM Residual}
data <- out.fac.resid %>% 
  filter(Index %in% So.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 6.5)
```

```{r - Components Age}
data <- out.pmc.age %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("> 75 years", "<= 75 years")
plot.cols <- c("#EB2226", "#075AAA")
plot.shapes <- c(0,1,15,16)
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-age.png'), width = 6.5, height = 7.5)
```

```{r - Factor Age}
data <- out.fac.age %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("> 75 years", "<= 75 years")
plot.cols <- c("#EB2226", "#075AAA")
plot.shapes <- c(0,1,15,16)
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-age.png'), width = 6.5, height = 6.5)
```

```{r - Components Sex}
data <- out.pmc.sex %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("Male", "Female")
plot.cols <- c("#EB2226", "#075AAA")
plot.shapes <- c(0,1,15,16)
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-sex.png'), width = 6.5, height = 7.5)
```

```{r - Factor Sex}
data <- out.fac.sex %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("Male", "Female")
plot.cols <- c("#EB2226", "#075AAA")
plot.shapes <- c(0,1,15,16)
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-sex.png'), width = 6.5, height = 6.5)
```

```{r - Components Race}
data <- out.pmc.race %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Race == "A", "d",
                      ifelse(Race == "B", "c",
                             ifelse(Race == "H", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"),18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"),17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("White", "Hispanic", "Black", "Asian")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
plot.shapes <- c(0,1,2,5,15,16,17,18)
guide.shapes <- c(15,16,17,18)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n =1) +
ggsave(here('output', 'plot','pmc-race.png'), width = 6.5, height = 7.5)
```

```{r - Factor Race}
data <- out.fac.race %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Race == "A", "dd",
                      ifelse(Race == "B", "cc",
                             ifelse(Race == "H", "bb", "aa"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"),18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"),17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("White", "Hispanic", "Black", "Asian")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
plot.shapes <- c(0,1,2,5,15,16,17,18)
guide.shapes <- c(15,16,17,18)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-race.png'), width = 6.5, height = 6.5)
```

```{r Components Urban}
data <- out.pmc.urbanicity %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Loc.Set == "urban", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Loc.Set == "rural"), 1,
                      ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("Rural", "Urban")
plot.cols <- c("#EB2226", "#075AAA")
plot.shapes <- c(0,1,15,16)
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-urbanicity.png'), width = 6.5, height = 7.5)
```

```{r - Factor Urbaniity}
data <- out.fac.urbanicity %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Loc.Set == "urban", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Loc.Set == "rural"), 1,
                      ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("Rural", "Urban")
plot.cols <- c("#EB2226", "#075AAA")
plot.shapes <- c(0,1,15,16)
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-urbanicity.png'), width = 6.5, height = 6.5)
```

```{r Components SES-Urban}
data <- out.pmc.sescat %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(SES.Cat == "L", "c",
                      ifelse(SES.Cat == "M", "b", "a")),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & SES.Cat == "H"), 2,
                      ifelse((sig == 15 & SES.Cat == "H"),17, sig)),
         sig = ifelse((sig == 0 & SES.Cat == "M"), 1,
                      ifelse((sig == 15 & SES.Cat == "M"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("High", "Middle", "Low")
plot.cols <- c("#01742F", "#FFA42E", "#EB2226")
plot.shapes <- c(0,1,2,15,16,17)
guide.shapes <- c(15,16,17)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-sescat.png'), width = 6.5, height = 7.5)
```

```{r - Components Region}
data <- out.pmc.region %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("Northeast", "South", "Midwest", "West")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
plot.shapes <- c(0,1,2,5,15,16,17,18)
guide.shapes <- c(15,16,17,18)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
```

```{r - Factor Region}
data <- out.fac.region %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
  Tag = ifelse(Region == "west", "d",
               ifelse(Region == "midwest", "c",
                      ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("Northeast", "South", "Midwest", "West")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
plot.shapes <- c(0,1,2,5,15,16,17,18)
guide.shapes <- c(15,16,17,18)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-region.png'), width = 6.5, height = 6.5)
```

```{r - Components Residual Region}
data <- out.pmc.resid.region %>% 
  filter(Index %in% cmp.multi.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi.res),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("Northeast", "South", "Midwest", "West")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
plot.shapes <- c(0,1,2,5,15,16,17,18)
guide.shapes <- c(15,16,17,18)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-resid-region.png'),width = 6.5, height = 7.5)
```

```{r - Components BRFSS}
data <- out.pmc.brfss %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(BRFSS == "brfss0", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & BRFSS == "brfss"), 1,
                      ifelse((sig == 15 & BRFSS == "brfss"),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("BRFSS-Adjusted","Base")
plot.cols <- c("#EB2226", "#075AAA")
plot.shapes <- c(0,1,15,16)
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-brfss.png'), width = 6.5, height = 7.5)
```

```{r Components Buffer}
data <- out.pmc.buffer %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Buffer == 6, "c",
                      ifelse(Buffer == 12, "b", "a")),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Buffer == 24), 2,
                      ifelse((sig == 15 & Buffer == 24),17, sig)),
         sig = ifelse((sig == 0 & Buffer == 12), 1,
                      ifelse((sig == 15 & Buffer == 12),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("24-miles", "12-miles", "6-miles")
plot.cols <- c("#01742F", "#FFA42E", "#EB2226")
plot.shapes <- c(0,1,2,15,16,17)
guide.shapes <- c(15,16,17)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-buffer.png'), width = 6.5, height = 7.5)
```

```{r Components Exposure window}
data <- out.pmc.expo %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Window == 1, "e",
                      ifelse(Window == 2, "d",
                             ifelse(Window == 3, "c",
                                    ifelse(Window == 4, "b", "a")))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Window == 5), 6,
                      ifelse((sig == 15 & Window == 5),25, sig)),
         sig = ifelse((sig == 0 & Window == 4), 5,
                      ifelse((sig == 15 & Window == 4),18, sig)),
         sig = ifelse((sig == 0 & Window == 3), 2,
                      ifelse((sig == 15 & Window == 3),17, sig)),
         sig = ifelse((sig == 0 & Window == 2), 1,
                      ifelse((sig == 15 & Window == 2),16, sig)),
         sig = as.factor(sig)
  )

plot.labs <- c("5-yr", "4-yr","3-yr","2-yr","1-yr")
plot.cols <- c("#EB2226","#FF8200","#9D178D","#075AAA","#01742F")
plot.shapes <- c(0,1,2,5,4,15,16,17,18,8)
guide.shapes <- c(15,16,17,18,8)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
ggsave(here('output', 'plot','pmc-expo.png'), width = 6.5, height = 8.5)
```

### 2021-02-14 code/data-viz/forest-plots-color.Rmd
modified factor data names - shape and color plots - mass apportionemnt

--- 2021-02-07 code/data-viz/forest-plots.Rmd
@@
 
+### plots subgroups using different colors
 ###color codes: https://www.schemecolor.com/british-airways-website.php
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-age.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
 ggsave(here('output', 'plot','fac-age.png'), width = 6.5, height = 6.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-sex.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
 ggsave(here('output', 'plot','fac-sex.png'), width = 6.5, height = 6.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-race.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
 ggsave(here('output', 'plot','fac-race.png'), width = 6.5, height = 6.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-urbanicity.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
 ggsave(here('output', 'plot','fac-urbanicity.png'), width = 6.5, height = 6.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-sescat.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
 ggsave(here('output', 'plot','fac-region.png'), width = 6.5, height = 6.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-resid-region.png'),width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-brfss.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) +
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
 ggsave(here('output', 'plot','pmc-buffer.png'), width = 6.5, height = 7.5)
@@
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1) + 
+Plot.Multi.Color(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
 ggsave(here('output', 'plot','pmc-expo.png'), width = 6.5, height = 8.5)

### 2021-02-14 code/data-viz/forest-plot-functions.R

@@ -6,9 +6,15 @@
 library(tidyverse)
 library(ggpubr)
 
+
+###############################################################################
+##############################  Plot.Single  ##################################
+###############################################################################
+
 ### Function *** Plot.Single ***
 # Function Arguments: 
 # dt : dataset that contains the HRs for each exposure and outcome
+# ggtheme : customized theme
 
 ### Single Group Plot Function
 Plot.Single <- function(dt, ggtheme){
@@ -26,12 +32,20 @@ Plot.Single <- function(dt, ggtheme){
 }
 
 
+###############################################################################
+##############################  Plot.Multi ####################################
+###############################################################################
+
 ### Function *** Plot.Multi ***
+# Plots subgroups with different colors and shapes
 # Function Arguments: 
 # dt : dataset that contains the HRs for each exposure, outcome and subgroups
+# ggtheme : customized theme
+# n : desired number of rows of legends
 
 ### Multiple Group Plot Function
-Plot.Multi <- function(dt, ggtheme) {
+Plot.Multi <- function(dt, ggtheme, n) {
+  
   p1 <- ggplot(data = filter(data, Cause %in% cuz.top.row),
                aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
     geom_vline(xintercept = 1, linetype = 2, color = "black") +
@@ -40,15 +54,18 @@ Plot.Multi <- function(dt, ggtheme) {
                  size = 0.25, show.legend = T) + 
     geom_point(aes(x = HR, y = Tag, color = Tag, shape = sig), 
                size = 1.5, show.legend = T) + 
-    scale_shape_identity() +
+    scale_shape_manual(
+      values = plot.shapes,
+      guide = F) +
     scale_color_manual(
       labels = plot.labs, 
       values = plot.cols) +
-    
     facet_grid(Index ~ Cause,  scales = "free_x", switch = 'y',
                shrink = T, space = 'fixed') +
     ggtheme +
-    guides(colour = guide_legend(nrow = 1, byrow = T, reverse = T, direction = "vertical")) 
+    guides(color = guide_legend(override.aes = list(shape = guide.shapes),
+                                nrow = n, byrow = T, reverse = T, 
+                                direction = "vertical"))
   
[…]

### 2021-02-17 code/data-analysis/factor-analysis.Rmd
smoothing spline for apportioned mass - new mass app combination

@@
 load(here('data','processed', 'aqs-sites.RDa'))
+load(here('data','processed', 'mass-apportioned.RDa'))
 ```
@@
 
-### high load
+### high load -- Comb1
 high.load <- lmer(data = dt.pmc.daily,
@@
 
-### high health impact
-high.health <- lmer(data = dt.pmc.daily,
-              PM ~ SI + PB + NO3 + K + SO4 + CL + NI + FE + (1|Site.ID))
-tab_model(high.health, show.se = T, show.ci = F, show.aic = T, digits = 2,
-            show.re.var = F, show.icc = T, show.obs = T, show.ngroups = T,
-          title = "Higher Health Impact Tracers")
-# Nagative Ni
-
-### high health impact ii
+### high health impact ii - Comb2
 high.health <- lmer(data = dt.pmc.daily,
@@
           title = "Higher Health Impact Tracers - II")
+# CL non sig
 
@@
 
-```{r - Single Tracer Mass Apportionment}
+```{r - Single Tracer Mass Apportionment - function}
 dt.sites <- dt.aqs.sites %>% 
@@
 }
+```
 
-dt.mass.app <- dt.pmc.daily %>% 
+```{r - Single Tracer Mass Apportionment - Combination 1}
+dt.mass.app.c1 <- dt.pmc.daily %>% 
   mutate(Soil = so.coef(high.load, 'SI') * SI,
@@
 
-save(dt.mass.app, file = here('data', 'processed', 'mass-apportioned.RDa'))
+save(dt.mass.app.c1, file = here('data', 'processed', 'mass-apportioned-c1.RDa'))
 
-mass.summary.us <- dt.mass.app %>% 
+mass.summary.us <- dt.mass.app.c1 %>% 
   group_by(Source) %>% 
@@
 
-mass.summary.region <- dt.mass.app %>% 
+mass.summary.region <- dt.mass.app.c1 %>% 
   group_by(Source, Region) %>% 
@@
 
-mass.summary.locset <- dt.mass.app %>% 
+mass.summary.locset <- dt.mass.app.c1 %>% 
   group_by(Source, Location) %>% 
@@
 
-mass.summary <- mass.summary.us %>% 
+mass.summary.c1 <- mass.summary.us %>% 
   add_row(mass.summary.region) %>% 
@@
 
-write.csv(mass.summary,
-          file = here('output','table', 'mass-app-summary.csv'))
+write.csv(mass.summary.c1,
+          file = here('output','table', 'mass-app-summary-c1.csv'))
 
-dt.mass.map <- dt.mass.app %>% 
+dt.mass.map.c1 <- dt.mass.app.c1 %>% 
   group_by(Site.ID, Source) %>% 
@@
 
-save(dt.mass.map, file = here('data', 'processed', 'mass-map.RDa'))
-write.csv(dt.mass.map, file = here('output','table', 'mass-map.csv'), row.names = F)
+save(dt.mass.map.c1, file = here('data', 'processed', 'mass-map-c1.RDa'))
+write.csv(dt.mass.map.c1, file = here('output','table', 'mass-map-c1.csv'), row.names = F)
 ```
+
+```{r Smoothing Data & Caluculating 1-yr mvavg for each month - Combination 1}
+dt.air <- dt.mass.app.c1 %>% 
+  transmute(Site.ID,
+            Parameter.Symbol = Source,
+            Date,
+            Value = Mass) %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
+
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
+
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 0.99, 350)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.1yr=unlist(smooth.out[4,]))
+
+dt.mass.app.1yr.c1 <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.1yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.mass.app.1yr.c1, file = here('data', 'processed', 'mass-app-1yr-c1.RDa'))
+write.csv(dt.mass.app.1yr.c1, file = here('data', 'processed', 'mass-app-1yr-c1.csv'), row.names = F)
+```
+
+```{r - Single Tracer Mass Apportionment - Combination 2}
+dt.mass.app.c2 <- dt.pmc.daily %>% 
+  mutate(Soil = so.coef(high.health, 'SI') * SI,
+         Metal = so.coef(high.health, 'PB') * PB,
+         Traffic = so.coef(high.health, 'NO3') * NO3,
+         Biomass = so.coef(high.health, 'K') * K,
+         Coal = so.coef(high.health, 'SO4') * SO4,
+         Salt = so.coef(high.health, 'CL') * CL,
+         Oil = so.coef(high.health, 'NI') * NI,
+         Steel = so.coef(high.health, 'MN') * MN) %>% 
+  select(Site.ID, Date, PM, Sources) %>% 
+  inner_join(dt.sites) %>% 
+  pivot_longer(cols = c('PM', Sources),
+               names_to = "Source",
+               values_to = "Mass")
+
+save(dt.mass.app.c2, file = here('data', 'processed', 'mass-apportioned-c2.RDa'))
+
+mass.summary.us <- dt.mass.app.c2 %>% 
+  group_by(Source) %>% 
+  summarise(Mass.mean = round(mean(Mass),2),
+            Mass.sd = round(sd(Mass),2)) %>% 
+  mutate(Unit = "US")
+
+mass.summary.region <- dt.mass.app.c2 %>% 
+  group_by(Source, Region) %>% 
+  summarise(Mass.mean = round(mean(Mass),2),
+            Mass.sd = round(sd(Mass),2)) %>% 
+  rename(Unit = Region)
+
+mass.summary.locset <- dt.mass.app.c2 %>% 
+  group_by(Source, Location) %>% 
+  summarise(Mass.mean = round(mean(Mass),2),
+            Mass.sd = round(sd(Mass),2)) %>% 
+rename(Unit = Location)
+
+mass.summary.c2 <- mass.summary.us %>% 
+  add_row(mass.summary.region) %>% 
+  add_row(mass.summary.locset)
+
+write.csv(mass.summary.c2,
+          file = here('output','table', 'mass-app-summary-c2.csv'))
+
+dt.mass.map.c2 <- dt.mass.app.c2 %>% 
+  group_by(Site.ID, Source) %>% 
+  summarise(Mass = mean(Mass)) %>% 
+  pivot_wider(names_from = "Source",
+              values_from = "Mass") %>% 
+  inner_join(dt.sites)
+
+save(dt.mass.map.c2, file = here('data', 'processed', 'mass-map-c2.RDa'))
+write.csv(dt.mass.map.c2, file = here('output','table', 'mass-map-c2.csv'), row.names = F)
+```
+
+```{r Smoothing Data & Caluculating 1-yr mvavg for each month - Combination 2}
+dt.air <- dt.mass.app.c2 %>% 
+  transmute(Site.ID,
+            Parameter.Symbol = Source,
+            Date,
+            Value = Mass) %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
+
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
+
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 0.99, 350)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.1yr=unlist(smooth.out[4,]))
+
+dt.mass.app.1yr.c2 <- para.monthly %>% 
+  mutate(Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.1yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.mass.app.1yr.c2, file = here('data', 'processed', 'mass-app-1yr-c2.RDa'))
+write.csv(dt.mass.app.1yr.c2, file = here('data', 'processed', 'mass-app-1yr-c2.csv'), row.names = F)
+```

### 2021-02-22 code/data-analysis/config-file-generator.Rmd
pm apportioned mass health models

@@
              "Yr_PB","Yr_PM","Yr_SI","Yr_SO4","Yr_V","Yr_ZN")
+```
+
+```{r List of Sources}
+so <- c("Yr_Biomass","Yr_Coal","Yr_Metal","Yr_Oil",
+         "Yr_Salt","Yr_Soil","Yr_Steel","Yr_Traffic")
 ```
@@
 
+```{r ses adj. model for apportioned mass}
+dataname <- "ndi-mass.csv"
+expo <- so
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','mass-ses', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
 ```{r under work - parse output}

### 2021-02-22 code/data-processors/cms-data-processor.Rmd
pm apportioned mass health models

@@
 load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
+load(here('data','processed','mass-app-1yr-c2.RDa'))
 ```
@@
 ```
+
+```{r PM Apportioned Mass}
+dt.mass <- dt.mass.app.1yr.c2 %>% 
+  rename_at(vars(Biomass: Traffic), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.mass <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.mass) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.mass, 
+          file = here('data', 'processed', 'ndi-mass.csv'),
+          row.names = F)
+```

### 2021-02-28 code/data-analysis/output-cleaning.Rmd
visualization

@@
 load(here('data','processed','pmc-sub-5yr.RDa'))
+load(here('data','processed','mass-app-1yr-c2.RDa'))
 ```
@@
   pivot_longer(cols = Factor1:Factor8,
+               names_to = "Parameter",
+               values_to = "IQR")%>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Source Apportioned PM Mass
+mass.1yr.iqr <- dt.pmc.site.ndi %>% 
+  select(Site.ID) %>% 
+  inner_join(dt.mass.app.1yr.c2) %>% 
+  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
+  pivot_longer(cols = Biomass:Traffic,
                names_to = "Parameter",
@@
 save(out.fac.ec.ses, file = here('output','analysis','out-fac-ec-ses.RDa'))
+```
+
+```{r Output App Mass SES-Adj}
+out.mass.ses <- read.csv(here('output','analysis','mass-ses.csv')) %>%
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>%  
+  merge(mass.1yr.iqr) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3),
+         Index = Parameter) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, HR, HR.L, HR.U)
+
+save(out.mass.ses, file = here('output','analysis','out-mass-ses.RDa'))
 ```

### 2021-02-28 code/data-viz/forest-plots-color-shape.Rmd
visualization

@@
 load(here('output','analysis','out-fac-ses.RDa'))
+load(here('output','analysis','out-mass-ses.RDa'))
 load(here('output','analysis','out-fac-base-ec.RDa'))
@@
 
-```{r - Factor Base Ex. EC}
+```{r - Factor Base}
 data <- out.fac.base %>% 
@@
 
-```{r - Factor SES-Adj Ex. EC}
+```{r - Factor SES-Adj}
 data <- out.fac.ses %>% 
@@
 ggsave(here('output','plot','fac-ses.png'), width = 6.5, height = 6.5)
+```
+
+```{r - App Mass SES-Adj}
+data <- out.mass.ses %>% 
+  filter(Index %in% So.main,
+         Cause %in% cuz,
+         HR < 5,
+         HR.U < 5) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','mass-ses.png'), width = 6.5, height = 6.5)
 ```

### 2021-05-25 code/data-viz/forest-plots-color.Rmd
plot, table, map

@@
 
+```{r - Components urban}
+data <- out.pmc.urbanicity %>% 
+  filter(Index %in% cmp.main,
+         Cause %in% cuz,
+         Loc.Set == "urban") %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','pmc-urban.png'), width = 6.5, height = 6.5)
+```
+
+```{r - Factors urban}
+data <- out.fac.urbanicity %>% 
+  filter(Index %in% So.main,
+         Cause %in% cuz,
+         Loc.Set == "urban") %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null # 16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','fac-urban.png'), width = 6.5, height = 6.5)
+```
+
 ```{r Components SES-Urban}

### 2021-05-25 code/data-viz/manuscript-tables.Rmd
plot, table, map

---
title: "Tables for PM2.5 Paper Manuscript"
author: "Fatemeh Kazemi"
date: "3/28/2021"
output:
  html_document:
    df_print: paged
---

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load packages}
library(tidyverse)
library(here)
library(knitr)
library(kableExtra)
```

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
#load(here('output','analysis','out-fac-base-ec.RDa'))
#load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

```{r}
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

cuz.top.row <-  c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")
cuz.bot.row <- c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")

cmp.main <- c("PM2.5", "Si","Ca", "Pb","Zn", "NO3","OC", "K","Cu",
              "Se","SO4", "Na","Cl", "Ni","V", "Fe","Mn")

cmp.multi <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
               "Ni", "V") 
cmp.m2 <- c("PM2.5", "PM2.5", "Si", "Si", "Ca", "Ca", "Pb", "Pb", "Zn", "Zn",
            "NO3", "NO3", "OC", "OC", "Se", "Se", "SO4", "SO4", "Ni", "Ni", "V", "V")

So.main <- c("Soil", "Metals", "Traffic", "Biomass",
             "Coal", "Salt", "Oil", "Steel")

So.multi <- c("Soil", "Metals", "Traffic", "Coal", "Oil")

cmp.res <- c("PM2.5", "-Si","-Ca", "-Pb","-Zn", "-NO3","-OC",
             "-Se","-SO4", "-Ni","-V")

So.res <- c("PM2.5", "-Soil", "-Metals", "-Traffic", "-Coal", "-Oil")

cmp.multi.res <- c("PM2.5","-Si", "-Ca", "-Pb", "-Zn", "-NO3", "-OC",
                   "-Se", "-SO4", "-Ni", "-V")

Race <- c("A", "B", "H", "W")
AgeC <- c("LE75", "M75")
```

# Figure 1a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Biomass", 8, 9) %>% 
    group_rows("Coal", 10, 11) %>%
    group_rows("Salt", 12, 13) %>% 
    group_rows("Oil", 14, 15) %>% 
    group_rows("Steel", 16, 17) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

table_fk(data = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row)
```

# Figure 1a
```{r}
table_fk(data = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row)
```

# Figure 1b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.fac.ses, cmp = So.main, cuz = cuz.top.row)
```

# Figure 1b
```{r}
table_fk(data = out.fac.ses, cmp = So.main, cuz = cuz.bot.row)
```

# Figure 2a
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    group_rows("Soil", 2, 3) %>%   # same result with group 1=
    group_rows("Metals", 4, 5) %>% 
    group_rows("Traffic", 6, 7) %>% 
    group_rows("Coal", 8, 9) %>%
    group_rows("Oil", 10, 11) %>% 
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row)
```

# Figure 2a
```{r}
table_fk(data = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row)
```

# Figure 2b
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
  slice(match(cmp, Index)),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.fac.resid, cmp = So.res, cuz = cuz.top.row)
```

# Figure 2b
```{r}
table_fk(data = out.fac.resid, cmp = So.res, cuz = cuz.bot.row)
```

# Figure x
```{r}
table_fk <- function(data, cmp, cuz, em){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(!Index %in% c("Na", "Cl")) %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
    group_rows("Soil", 3, 6) %>%   # same result with group 1=
    group_rows("Metals", 7, 10) %>% 
    group_rows("Traffic", 11, 14) %>% 
    group_rows("Coal", 15, 18) %>% 
    group_rows("Oil", 19, 22) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 8)
}

table_fk(data = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row)
```

```{r}
table_fk(data = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row)
```

# Figure x2
```{r}
table_fk <- function(data, cmp, cuz){
  opts <- options(knitr.kable.NA = "0")
  kbl(data %>% 
  filter(Index %in% cmp,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz)) %>% 
  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
  select(-(HR:HR.U)) %>% 
  pivot_wider(names_from = "Cause",
              values_from = "HR.Sum") %>% 
    arrange(factor(Index, levels = cmp), Age),
  align = "c", booktabs = TRUE) %>%
    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
    kable_styling() %>% 
    row_spec(0, font_size = 9)
}

table_fk(data = out.fac.age, cmp = So.multi, cuz = cuz.top.row)
```

```{r}
table_fk(data = out.fac.age, cmp = So.multi, cuz = cuz.bot.row)
```

### 2021-05-31 code/data-analysis/factor-analysis.Rmd
update plot lables and shapes

@@
 
-Sources <- c("Soil", "Metal", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")
+Sources <- c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")
 
@@
   mutate(Soil = so.coef(high.load, 'SI') * SI,
-         Metal = so.coef(high.load, 'PB') * PB,
+         Metals = so.coef(high.load, 'PB') * PB,
          Traffic = so.coef(high.load, 'OC') * OC,
@@
   mutate(Soil = so.coef(high.health, 'SI') * SI,
-         Metal = so.coef(high.health, 'PB') * PB,
+         Metals = so.coef(high.health, 'PB') * PB,
          Traffic = so.coef(high.health, 'NO3') * NO3,

### 2021-05-31 code/data-viz/correlation.Rmd
plot, table, map
update plot lables and shapes

@@
 ---
-title: "R Notebook"
+title: "PM Component Paper Correlation Plots"
+author: "Fatemeh Kazemi"
+date: "01-31-2021"
 ---
@@
 ```{r}
+cmp.main.labels <- c("As", "Ca", "Cl", "Cu", "Fe", "K",  "Mg", "Mn", "Na", "Ni",
+                     "$NO[3]^'-'", "OC", "Pb", "Se", "Si",
+                     "$SO[4]^'2-'", "V", "Zn", "$PM[2.5]")
+```
+
+```{r}
 corr <- dt.pmc %>%
@@
 
+colnames(corr) <- cmp.main.labels
+rownames(corr) <- cmp.main.labels
+
 jpeg(here('output','plot','corr-us.png'), width = 6.5, height = 6.5, units = 'in',
@@
 corrplot(corr, type = "lower",  method = 'number',
-         tl.col = "black", tl.srt = 45, number.cex=0.65,
-         col = rev(brewer.pal(n = 10, name = "RdGy"))) +
-  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
-                                   size = 14, hjust = 1, face='bold'),
-        axis.text.y = element_text(angle = 0, vjust = 1, 
-                                   size = 14, hjust = 1, face='bold'),
-        legend.title = element_blank())
+         tl.col = "black", tl.srt = 45, number.cex=0.65, title = "US",mar=c(0,0,1,0),
+         col = rev(brewer.pal(n = 10, name = "RdGy")))
 dev.off()
@@
 ```{r - Region}
-dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),]
+dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),] %>% 
+  mutate(Region = ifelse(Region == "W", "West",
+                         ifelse(Region == "MW", "Midwest",
+                                ifelse(Region == "S", "South", "Northeast"))))
 
@@
     cor()
+  colnames(corr) <- cmp.main.labels
+  rownames(corr) <- cmp.main.labels
   corrplot(corr, type = "lower",
-           tl.col = "black", tl.srt = 45, number.cex=0.65,
-           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) +
-    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
-                                     size = 14, hjust = 1, face='bold'),
-          axis.text.y = element_text(angle = 0, vjust = 1, 
-                                     size = 14, hjust = 1, face='bold'),
-          legend.title = element_blank())
+           tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
+           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0))
 }
@@
 par(mfrow=c(2,2))
+dt.pmc <- dt.pmc %>% arrange(Loc.Set)
 for(i in unique(dt.pmc$Loc.Set)) {
@@
     cor()
+  colnames(corr) <- cmp.main.labels
+  rownames(corr) <- cmp.main.labels
   corrplot(corr, type = "lower",
-           tl.col = "black", tl.srt = 45, number.cex=0.65,
-           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) +
-    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
-                                     size = 14, hjust = 1, face='bold'),
-          axis.text.y = element_text(angle = 0, vjust = 1, 
-                                     size = 14, hjust = 1, face='bold'),
-          legend.title = element_blank())
+           tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
+           col = rev(brewer.pal(n = 10, name = "RdGy")), title =i, mar=c(0,0,1,0)) 
 }

### 2021-05-31 code/data-viz/forest-plots-color-shape.Rmd
update plot lables and shapes

@@
 load(here('output','analysis','out-mass-ses.RDa'))
-load(here('output','analysis','out-fac-base-ec.RDa'))
-load(here('output','analysis','out-fac-ses-ec.RDa'))
+#load(here('output','analysis','out-fac-base-ec.RDa'))
+#load(here('output','analysis','out-fac-ses-ec.RDa'))
 load(here('output','analysis','out-pmc-resid.RDa'))
@@
 ggtheme.single <- theme_bw() + 
-  theme(panel.spacing.x = unit(0.25, 'lines'),
+  theme(panel.spacing.x = unit(0.5, 'lines'),
         panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
@@
 ggtheme.multi.1 <- theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
+  theme(panel.spacing.x = unit(0.5,'lines'),
         panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
@@
 ggtheme.multi.2 <- theme_classic() + 
-  theme(panel.spacing.x = unit(0.25,'lines'),
+  theme(panel.spacing.x = unit(0.5,'lines'),
         panel.spacing.y = unit(c(0.25),'lines'),
@@
               "Cu", "K", "OC", "NO3", "Zn", "Pb", "Ca", "Si", "PM2.5")
+cmp.main.labels <- c("Mn", "Fe", "V", "Ni", "Cl", "Na", expression("SO"[4]^{"2-"}),
+                     "Se", "Cu", "K", "OC", expression("NO"[3]^{"-"}), "Zn", 
+                     "Pb", "Ca", "Si", expression("PM"[2.5]))
+
 cmp.multi <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
+               "Ni", "V")
+cmp.multi.labels <- c(expression("PM"[2.5]),"Si", "Ca", "Pb", "Zn", 
+                      expression("NO"[3]^{"-"}), "OC", "Se", expression("SO"[4]^{"2-"}),
                       "Ni", "V")
@@
          "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
+cmp.res.labels <- c("-V", "-Ni", expression("-SO"[4]^{"2-"}), "-Se", "-OC", 
+                    expression("-NO"[3]^{"-"}), "-Zn", "-Pb", "-Ca", "-Si", 
+                    expression("PM"[2.5]))
+
 So.res <- c("-Oil", "-Coal", 
          "-Traffic", "-Metals", "-Soil", "PM2.5")
+So.res.labels <- c("-Oil", "-Coal", 
+         "-Traffic", "-Metals", "-Soil", expression("PM"[2.5]))
 
@@
                    "-Se", "-SO4", "-Ni", "-V")
+cmp.multi.res.labels <- c(expression("PM"[2.5]),"-Si", "-Ca", "-Pb", "-Zn", 
+                          expression("-NO"[3]^{"-"}), "-OC","-Se",
+                          expression("-SO"[4]^{"2-"}), "-Ni", "-V")
 ```
@@
 plot.cols <- c("#EB2226")
+Index.labels <- cmp.main.labels
 
-Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','pmc-base.png'), width = 6.5, height = 6.5)
+Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','pmc-base.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 plot.cols <- c("#EB2226")
+Index.labels <- cmp.main.labels
 
-Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','pmc-ses.png'), width = 6.5, height = 6.5)
+Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','pmc-ses.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','fac-base.png'), width = 6.5, height = 6.5)
+ggsave(here('output','plot','fac-base.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','fac-ses.png'), width = 6.5, height = 6.5)
+ggsave(here('output','plot','fac-ses.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','mass-ses.png'), width = 6.5, height = 6.5)
+ggsave(here('output','plot','mass-ses.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 plot.cols <- c("#EB2226")
+Index.labels <- cmp.res.labels
 
-Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','pmc-resid.png'), width = 6.5, height = 6.5)
+Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','pmc-resid.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 plot.cols <- c("#EB2226")
+Index.labels <- So.res.labels
 
-Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output', 'plot','fac-resid.png'), width = 6.5, height = 6.5)
+Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output', 'plot','fac-resid.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Age == "M75"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
 
-plot.labs <- c("> 75 years", "<= 75 years")
+levels(data$Index) <- cmp.multi.labels
+
+plot.labs <- c("> 75 years", "65-75 years")
 plot.cols <- c("#EB2226", "#075AAA")
-plot.shapes <- c(0,1,15,16)
 guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-age.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-age.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Age == "M75"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
 
-plot.labs <- c("> 75 years", "<= 75 years")
+plot.labs <- c("> 75 years", "65-75 years")
 plot.cols <- c("#EB2226", "#075AAA")
-plot.shapes <- c(0,1,15,16)
 guide.shapes <- c(15,16)
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-age.png'), width = 6.5, height = 6.5)
+ggsave(here('output', 'plot','fac-age.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Sex == "M"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
+
+levels(data$Index) <- cmp.multi.labels
 
@@
 plot.cols <- c("#EB2226", "#075AAA")
-plot.shapes <- c(0,1,15,16)
 guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-sex.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-sex.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Sex == "M"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
@@
 plot.cols <- c("#EB2226", "#075AAA")
-plot.shapes <- c(0,1,15,16)
 guide.shapes <- c(15,16)
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-sex.png'), width = 6.5, height = 6.5)
+ggsave(here('output', 'plot','fac-sex.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 data <- out.pmc.race %>% 
+  arrange(Index, Cause, Race) %>% 
   filter(Index %in% cmp.multi,
@@
          Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
+         sig = ifelse(HR.U < 1, 15, #15-prtc
                       ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
          sig = ifelse((sig == 0 & Race == "W"), 5,
-                      ifelse((sig == 15 & Race == "W"),18, sig)),
+                      ifelse((sig == 15 & Race == "W"), 18, sig)),
          sig = ifelse((sig == 0 & Race == "H"), 2,
-                      ifelse((sig == 15 & Race == "H"),17, sig)),
+                      ifelse((sig == 15 & Race == "H"), 17, sig)),
          sig = ifelse((sig == 0 & Race == "B"), 1,
-                      ifelse((sig == 15 & Race == "B"),16, sig)),
-         sig = as.factor(sig)
+                      ifelse((sig == 15 & Race == "B"), 16, sig)),
+         sig = as.integer(sig)
   )
+
+levels(data$Index) <- cmp.multi.labels
 
@@
 plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
-plot.shapes <- c(0,1,2,5,15,16,17,18)
 guide.shapes <- c(15,16,17,18)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n =1) +
-ggsave(here('output', 'plot','pmc-race.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n =1) +
+ggsave(here('output', 'plot','pmc-race.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Race == "B"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
@@
 plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
-plot.shapes <- c(0,1,2,5,15,16,17,18)
 guide.shapes <- c(15,16,17,18)
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-race.png'), width = 6.5, height = 6.5)
+ggsave(here('output', 'plot','fac-race.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
 
-```{r Components Urban}
+```{r Components Urbanicity}
 data <- out.pmc.urbanicity %>% 
@@
                       ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
+
+levels(data$Index) <- cmp.multi.labels
 
@@
 plot.cols <- c("#EB2226", "#075AAA")
-plot.shapes <- c(0,1,15,16)
 guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-urbanicity.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-urbanicity.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
 
-```{r - Factor Urbaniity}
+```{r - Factor Urbanicity}
 data <- out.fac.urbanicity %>% 
@@
                       ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
@@
 plot.cols <- c("#EB2226", "#075AAA")
-plot.shapes <- c(0,1,15,16)
 guide.shapes <- c(15,16)
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-urbanicity.png'), width = 6.5, height = 6.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
+ggsave(here('output', 'plot','fac-urbanicity.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+```{r - Components urban}
+data <- out.pmc.urbanicity %>% 
+  filter(Loc.Set == "urban") %>% 
+  filter(Index %in% cmp.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = rev(cmp.multi)),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+Index.labels <- rev(cmp.multi.labels)
+
+Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','pmc-urban.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & SES.Cat == "M"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
 
+levels(data$Index) <- cmp.multi.labels
+
 plot.labs <- c("High", "Middle", "Low")
-plot.cols <- c("#01742F", "#FFA42E", "#EB2226")
-plot.shapes <- c(0,1,2,15,16,17)
+plot.cols <- c("#01742F", "#075AAA", "#EB2226")
 guide.shapes <- c(15,16,17)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-sescat.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-sescat.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Region == "midwest"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
+
+levels(data$Index) <- cmp.multi.labels
 
@@
 plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
-plot.shapes <- c(0,1,2,5,15,16,17,18)
 guide.shapes <- c(15,16,17,18)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-region.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-region.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Region == "midwest"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-region.png'), width = 6.5, height = 6.5)
+ggsave(here('output', 'plot','fac-region.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Region == "midwest"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
+
+levels(data$Index) <- cmp.multi.res.labels
 
@@
 plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
-plot.shapes <- c(0,1,2,5,15,16,17,18)
 guide.shapes <- c(15,16,17,18)
+Index.labels <- cmp.multi.res.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-resid-region.png'),width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-resid-region.jpeg'),width = 7.5, height = 8.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & BRFSS == "brfss"),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
+
+levels(data$Index) <- cmp.multi.labels
 
@@
 plot.cols <- c("#EB2226", "#075AAA")
-plot.shapes <- c(0,1,15,16)
 guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-brfss.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-brfss.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
                       ifelse((sig == 15 & Buffer == 12),16, sig)),
-         sig = as.factor(sig)
+         sig = as.integer(sig)
   )
 
+levels(data$Index) <- cmp.multi.labels
+
 plot.labs <- c("24-miles", "12-miles", "6-miles")
-plot.cols <- c("#01742F", "#FFA42E", "#EB2226")
-plot.shapes <- c(0,1,2,15,16,17)
+plot.cols <- c("#EB2226", "#075AAA", "#01742F")
 guide.shapes <- c(15,16,17)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-buffer.png'), width = 6.5, height = 7.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','pmc-buffer.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
                       ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Window == 5), 6,
-                      ifelse((sig == 15 & Window == 5),25, sig)),
+         sig = ifelse((sig == 0 & Window == 5), 13,
+                      ifelse((sig == 15 & Window == 5), 8, sig)),
          sig = ifelse((sig == 0 & Window == 4), 5,
-                      ifelse((sig == 15 & Window == 4),18, sig)),
+                      ifelse((sig == 15 & Window == 4), 18, sig)),
          sig = ifelse((sig == 0 & Window == 3), 2,
-                      ifelse((sig == 15 & Window == 3),17, sig)),
+                      ifelse((sig == 15 & Window == 3), 17, sig)),
          sig = ifelse((sig == 0 & Window == 2), 1,
-                      ifelse((sig == 15 & Window == 2),16, sig)),
-         sig = as.factor(sig)
+                      ifelse((sig == 15 & Window == 2), 16, sig)),
+         sig = as.integer(sig)
   )
+
+levels(data$Index) <- cmp.multi.labels
 
@@
 plot.cols <- c("#EB2226","#FF8200","#9D178D","#075AAA","#01742F")
-plot.shapes <- c(0,1,2,5,4,15,16,17,18,8)
 guide.shapes <- c(15,16,17,18,8)
+Index.labels <- cmp.multi.labels
 
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
-ggsave(here('output', 'plot','pmc-expo.png'), width = 6.5, height = 8.5)
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
+ggsave(here('output', 'plot','pmc-expo.jpeg'), width = 7.5, height = 9.5, dpi = 600)
 ```

### 2021-05-31 code/data-viz/manuscript-tables.Rmd
update plot lables and shapes

@@
   align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
+    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
     group_rows("Soil", 2, 3) %>%   # same result with group 1=
@@
   align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
+    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
     kable_styling() %>% 
@@
   align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
+    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
     group_rows("Soil", 2, 3) %>%   # same result with group 1=
@@
   align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
+    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
     group_rows("Soil", 3, 6) %>%   # same result with group 1=
@@
   align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
+    kable_classic(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
+    group_rows("Soil", 3, 6) %>%   # same result with group 1=
+    group_rows("Metals", 7, 10) %>% 
+    group_rows("Traffic", 11, 14) %>% 
+    group_rows("Coal", 15, 18) %>% 
+    group_rows("Oil", 19, 22) %>%
     kable_styling() %>% 

### 2021-05-31 code/data-viz/forest-plot-functions.R

@@ -16,9 +16,30 @@ library(ggpubr)
 # dt : dataset that contains the HRs for each exposure and outcome
 # ggtheme : customized theme
 
-### Single Group Plot Function
+
+# Single Group Plot Function - Comp ----------------------------------------------
+Plot.Single.lab <- function(dt, ggtheme){
+  p <- ggplot(dt, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+    geom_vline(xintercept = 1, linetype = 2, color = "black") +
+    labs(x = "", y = "") +
+    geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+                 color = plot.cols, size = 0.25, show.legend = F) + 
+    geom_point(aes(x = HR, y = Index, shape = sig), 
+               color = plot.cols, size = 1.5, show.legend = F) +
+    scale_shape_identity() +
+    scale_y_discrete(labels = Index.labels) +
+    facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+    ggtheme
+  return(p)
+}
+
+
+
+
+
+# Single Group Plot Function - Factor -------------------------------------
 Plot.Single <- function(dt, ggtheme){
-  p <- ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+  p <- ggplot(dt, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
     geom_vline(xintercept = 1, linetype = 2, color = "black") +
     labs(x = "", y = "") +
     geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
@@ -43,20 +64,79 @@ Plot.Single <- function(dt, ggtheme){
 # ggtheme : customized theme
 # n : desired number of rows of legends
 
-### Multiple Group Plot Function
-Plot.Multi <- function(dt, ggtheme, n) {
+
+
+
+# Multiple Group Plot Function - Cmp --------------------------------------
+Plot.Multi.lab <- function(dt, ggtheme, n) {
   
-  p1 <- ggplot(data = filter(data, Cause %in% cuz.top.row),
+  dt$size.m <- ifelse(dt$sig == 18, 2.25, 1.5)
+  
+  p1 <- ggplot(data = filter(dt, Cause %in% cuz.top.row),
                aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
     geom_vline(xintercept = 1, linetype = 2, color = "black") +
[…]

### 2021-06-03 code/data-viz/correlation.Rmd
plots and tables for manuscript

@@
   merge(dt.pmc)
-```
 
-```{r}
 cmp.main.labels <- c("As", "Ca", "Cl", "Cu", "Fe", "K",  "Mg", "Mn", "Na", "Ni",
@@
 
-```{r}
+<br>
+
+### US
+```{r - US, fig.dim=c(6.5, 6.5)}
 corr <- dt.pmc %>%
@@
 corrplot(corr, type = "lower",  method = 'number',
-         tl.col = "black", tl.srt = 45, number.cex=0.65, title = "US",mar=c(0,0,1,0),
+         tl.col = "black", tl.srt = 45, number.cex=0.65, tl.cex = 0.75,
+         title = "US",mar=c(0,0,1,0),
          col = rev(brewer.pal(n = 10, name = "RdGy")))
@@
 
-```{r - Region}
+<br>
+
+### Regions
+```{r - Region, fig.dim=c(6.5, 6.5)}
 dt.pmc<-dt.pmc[order(dt.pmc$Region.IV),] %>% 
@@
 
-```{r - Urbanicity}
+<br>
+
+### Urbanicity
+```{r - Urbanicity, fig.dim=c(6.5,6.5)}
 jpeg(here('output','plot','corr-urbanicity.png'), width = 6.5, height = 6.5, units = 'in',
@@
 par(mfrow=c(2,2))
+dt.pmc$Loc.Set <- as.factor(dt.pmc$Loc.Set)
+dt.pmc$Loc.Set <- relevel(dt.pmc$Loc.Set, ref = "Urban")
 dt.pmc <- dt.pmc %>% arrange(Loc.Set)

### 2021-06-03 code/data-viz/manuscript-figures.Rmd
plots and tables for manuscript

---
title: "Figures for PM2.5 Components Paper Manuscript"
author: "Fatemeh Kazemi"
date: "02-13-2021"
---

### plots subgroups using different colors and shapes
###color codes: https://www.schemecolor.com/british-airways-website.php

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r Load packages}
  library(tidyverse)
  library(here)
  library(ggthemes)
```

```{r Call Functions}
source(here('code','data-viz','forest-plot-functions.R'))
```

```{r Load data}
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

```{r set theme 1 - single group plots}
ggtheme.single <- theme_bw() + 
  theme(panel.spacing.x = unit(0.5, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title.x = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, color = 'black')
  )
```

```{r set theme 2 - components - effect modification, subgroups, multiple groups plots}
ggtheme.multi.1 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.5,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title.x = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 3 - factors - effect modification, subgroups, multiple groups plots}
ggtheme.multi.2 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.5,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title.x = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r}
cuz <- c("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF",
         "Respiratory", "COPD", "Pneumonia", 
         "Cancer", "Lung Cancer")

cuz.top.row <-  c ("All-Cause", "Cardiovascular", "IHD", "CBV", "CHF")
cuz.bot.row <- c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")

cmp.main <- c("Mn", "Fe", "V", "Ni", "Cl", "Na", "SO4", "Se", 
              "Cu", "K", "OC", "NO3", "Zn", "Pb", "Ca", "Si", "PM2.5")
cmp.main.labels <- c("Mn", "Fe", "V", "Ni", "Cl", "Na", expression("SO"[4]^{"2-"}),
                     "Se", "Cu", "K", "OC", expression("NO"[3]^{"-"}), "Zn", 
                     "Pb", "Ca", "Si", expression("PM"[2.5]))

cmp.multi <- c("PM2.5","Si", "Ca", "Pb", "Zn", "NO3", "OC", "Se", "SO4", 
               "Ni", "V")
cmp.multi.labels <- c(expression("PM"[2.5]),"Si", "Ca", "Pb", "Zn", 
                      expression("NO"[3]^{"-"}), "OC", "Se", expression("SO"[4]^{"2-"}),
                      "Ni", "V")

So.main <- c("Steel", "Oil", "Salt", "Coal", 
         "Biomass", "Traffic", "Metals", "Soil")
So.multi <- c("Soil", "Metals", "Traffic",
              "Coal", "Oil")

So.ec <- c("Steel", "Coal", "Oil", "Salt",
         "Biomass", "Metals", "Soil", "Traffic")

cmp.res <- c("-V", "-Ni","-SO4", "-Se", "-OC", "-NO3", 
         "-Zn", "-Pb", "-Ca", "-Si", "PM2.5")
cmp.res.labels <- c("-V", "-Ni", expression("-SO"[4]^{"2-"}), "-Se", "-OC", 
                    expression("-NO"[3]^{"-"}), "-Zn", "-Pb", "-Ca", "-Si", 
                    expression("PM"[2.5]))

So.res <- c("-Oil", "-Coal", 
         "-Traffic", "-Metals", "-Soil", "PM2.5")
So.res.labels <- c("-Oil", "-Coal", 
         "-Traffic", "-Metals", "-Soil", expression("PM"[2.5]))

cmp.multi.res <- c("PM2.5","-Si", "-Ca", "-Pb", "-Zn", "-NO3", "-OC",
                   "-Se", "-SO4", "-Ni", "-V")
cmp.multi.res.labels <- c(expression("PM"[2.5]),"-Si", "-Ca", "-Pb", "-Zn", 
                          expression("-NO"[3]^{"-"}), "-OC","-Se",
                          expression("-SO"[4]^{"2-"}), "-Ni", "-V")
```

<br>

### Figure 1 - Components SES
```{r - Components SES-Adj, fig.dim = c(7.5, 6.5)}
data <- out.pmc.ses %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")
Index.labels <- cmp.main.labels

Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','Figure 1.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure 2 - Factors SES
```{r - Factor SES-Adj, fig.dim = c(7.5, 6.5)}
data <- out.fac.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','Figure 2.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure 3 - PM-Components Residual
```{r - Components - PM Residual, fig.dim = c(7.5, 6.5)}
data <- out.pmc.resid %>% 
  filter(Index %in% cmp.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")
Index.labels <- cmp.res.labels

Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','Figure 3.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure 4 - PM-Factors Residual
```{r - Factor - PM Residual, fig.dim = c(7.5, 6.5)}
data <- out.fac.resid %>% 
  filter(Index %in% So.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")
Index.labels <- So.res.labels

Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output', 'plot','Figure 4.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Components Age
```{r - Components Age, fig.dim = c(7.5, 7.5)}
data <- out.pmc.age %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("> 75 years", "65-75 years")
plot.cols <- c("#EB2226", "#075AAA")
guide.shapes <- c(15,16)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-age.jpeg'), width = 7.5, height = 7.5, dpi = 600)
```

<br>

### Factors Age
```{r - Factor Age, fig.dim = c(7.5, 6.5)}
data <- out.fac.age %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.integer(sig)
  )

plot.labs <- c("> 75 years", "65-75 years")
plot.cols <- c("#EB2226", "#075AAA")
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-age.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Components Sex
```{r - Components Sex, fig.dim = c(7.5, 7.5)}
data <- out.pmc.sex %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("Male", "Female")
plot.cols <- c("#EB2226", "#075AAA")
guide.shapes <- c(15,16)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-sex.jpeg'), width = 7.5, height = 7.5, dpi = 600)
```

<br>

### Factors Sex
```{r - Factor Sex, fig.dim = c(7.5, 6.5)}
data <- out.fac.sex %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.integer(sig)
  )

plot.labs <- c("Male", "Female")
plot.cols <- c("#EB2226", "#075AAA")
guide.shapes <- c(15,16)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','fac-sex.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure x - Components Race
```{r - Components Race, fig.dim = c(7.5, 8.5)}
data <- out.pmc.race %>% 
  arrange(Index, Cause, Race) %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Race == "A", "d",
                      ifelse(Race == "B", "c",
                             ifelse(Race == "H", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1, 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"), 18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"), 17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"), 16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("White", "Hispanic", "Black", "Asian")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
guide.shapes <- c(15,16,17,18)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n =1) +
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
```

<br>

### Figure x - Factors Race
```{r - Factor Race, fig.dim = c(7.5, 6.5)}
data <- out.fac.race %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Race == "A", "dd",
                      ifelse(Race == "B", "cc",
                             ifelse(Race == "H", "bb", "aa"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"),18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"),17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"),16, sig)),
         sig = as.integer(sig)
  )

plot.labs <- c("White", "Hispanic", "Black", "Asian")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
guide.shapes <- c(15,16,17,18)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure x - Components Urban
```{r - Components urban, fig.dim = c(7.5, 6.5)}
data <- out.pmc.urbanicity %>% 
  filter(Loc.Set == "urban") %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = rev(cmp.multi)),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")
Index.labels <- rev(cmp.multi.labels)

Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure x - Factors Urban
```{r - Factor Urban, fig.dim = c(7.5, 6.5)}
data <- out.fac.urbanicity %>%
  filter(Loc.Set == "urban") %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

plot.cols <- c("#EB2226")

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure x - Components SES-urban
```{r Components SES-Urban, fig.dim = c(7.5, 7.5)}
data <- out.pmc.sescat %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(SES.Cat == "L", "c",
                      ifelse(SES.Cat == "M", "b", "a")),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & SES.Cat == "H"), 2,
                      ifelse((sig == 15 & SES.Cat == "H"),17, sig)),
         sig = ifelse((sig == 0 & SES.Cat == "M"), 1,
                      ifelse((sig == 15 & SES.Cat == "M"),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("High", "Middle", "Low")
plot.cols <- c("#01742F", "#075AAA", "#EB2226")
guide.shapes <- c(15,16,17)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 7.5, dpi = 600)
```

<br>

### Figure x - Components Region
```{r - Components Region, fig.dim = c(7.5, 8.5)}
data <- out.pmc.region %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("Northeast", "South", "Midwest", "West")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
guide.shapes <- c(15,16,17,18)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
```

<br>

### Figure x - Factors Region
```{r - Factor Region, fig.dim = c(7.5, 6.5)}
data <- out.fac.region %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
  Tag = ifelse(Region == "west", "d",
               ifelse(Region == "midwest", "c",
                      ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.integer(sig)
  )

plot.labs <- c("Northeast", "South", "Midwest", "West")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
guide.shapes <- c(15,16,17,18)

Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Figure x - Components Residual Region
```{r - Components Residual Region, fig.dim = c(7.5, 8.5)}
data <- out.pmc.resid.region %>% 
  filter(Index %in% cmp.multi.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi.res),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.res.labels

plot.labs <- c("Northeast", "South", "Midwest", "West")
plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
guide.shapes <- c(15,16,17,18)
Index.labels <- cmp.multi.res.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','Figure x.jpeg'),width = 7.5, height = 8.5, dpi = 600)
```

<br>

### Figure x - Components BRFSS
```{r - Components BRFSS, fig.dim = c(7.5, 7.5)}
data <- out.pmc.brfss %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(BRFSS == "brfss0", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & BRFSS == "brfss"), 1,
                      ifelse((sig == 15 & BRFSS == "brfss"),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("BRFSS-Adjusted","Base")
plot.cols <- c("#EB2226", "#075AAA")
guide.shapes <- c(15,16)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 7.5, dpi = 600)
```

<br>

### Figure x - Components Buffer
```{r Components Buffer, fig.dim = c(7.5, 8.5)}
data <- out.pmc.buffer %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Buffer == 6, "c",
                      ifelse(Buffer == 12, "b", "a")),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Buffer == 24), 2,
                      ifelse((sig == 15 & Buffer == 24),17, sig)),
         sig = ifelse((sig == 0 & Buffer == 12), 1,
                      ifelse((sig == 15 & Buffer == 12),16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("24-miles", "12-miles", "6-miles")
plot.cols <- c("#EB2226", "#075AAA", "#01742F")
guide.shapes <- c(15,16,17)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
```

<br>

### Figure x - Components Exposure Window
```{r Components Exposure window, fig.dim = c(7.5, 9.5)}
data <- out.pmc.expo %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Window == 1, "e",
                      ifelse(Window == 2, "d",
                             ifelse(Window == 3, "c",
                                    ifelse(Window == 4, "b", "a")))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Window == 5), 13,
                      ifelse((sig == 15 & Window == 5), 8, sig)),
         sig = ifelse((sig == 0 & Window == 4), 5,
                      ifelse((sig == 15 & Window == 4), 18, sig)),
         sig = ifelse((sig == 0 & Window == 3), 2,
                      ifelse((sig == 15 & Window == 3), 17, sig)),
         sig = ifelse((sig == 0 & Window == 2), 1,
                      ifelse((sig == 15 & Window == 2), 16, sig)),
         sig = as.integer(sig)
  )

levels(data$Index) <- cmp.multi.labels

plot.labs <- c("5-yr", "4-yr","3-yr","2-yr","1-yr")
plot.cols <- c("#EB2226","#FF8200","#9D178D","#075AAA","#01742F")
guide.shapes <- c(15,16,17,18,8)
Index.labels <- cmp.multi.labels

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 9.5, dpi = 600)
```

### 2021-06-03 code/data-viz/manuscript-tables.Rmd
plots and tables for manuscript

--- 2021-05-25 code/data-viz/manuscript-tables.Rmd
@@
 ---
-title: "Tables for PM2.5 Paper Manuscript"
+title: "Tables for PM2.5 Components Paper Manuscript"
 author: "Fatemeh Kazemi"
-date: "3/28/2021"
+date: "05/31/2021"
 output:
@@
 library(here)
-library(knitr)
-library(kableExtra)
+library(flextable)
+library(officer)
+```
+
+```{r Call Functions}
+source(here('code','data-viz','manuscript-table-functions.R'))
 ```
@@
 ```{r Load data}
-load(here('output','analysis','out-pmc-base.RDa'))
 load(here('output','analysis','out-pmc-ses.RDa'))
-load(here('output','analysis','out-fac-base.RDa'))
 load(here('output','analysis','out-fac-ses.RDa'))
-#load(here('output','analysis','out-fac-base-ec.RDa'))
-#load(here('output','analysis','out-fac-ses-ec.RDa'))
 load(here('output','analysis','out-pmc-resid.RDa'))
@@
                "Ni", "V") 
-cmp.m2 <- c("PM2.5", "PM2.5", "Si", "Si", "Ca", "Ca", "Pb", "Pb", "Zn", "Zn",
-            "NO3", "NO3", "OC", "OC", "Se", "Se", "SO4", "SO4", "Ni", "Ni", "V", "V")
+cmp.multi.labels <- c(expression("PM"[2.5]),"Si", "Ca", "Pb", "Zn", 
+                      expression("NO"[3]^{"-"}), "OC", "Se", expression("SO"[4]^{"2-"}),
+                      "Ni", "V")
 
@@
                    "-Se", "-SO4", "-Ni", "-V")
-
-Race <- c("A", "B", "H", "W")
-AgeC <- c("LE75", "M75")
-```
-
-# Figure 1a
-```{r}
-table_fk <- function(data, cmp, cuz){
-  opts <- options(knitr.kable.NA = "0")
-  kbl(data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz)) %>% 
-  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
-  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
-  select(-(HR:HR.U)) %>% 
-  pivot_wider(names_from = "Cause",
-              values_from = "HR.Sum") %>% 
-  slice(match(cmp, Index)),
-  align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
-    group_rows("Soil", 2, 3) %>%   # same result with group 1=
-    group_rows("Metals", 4, 5) %>% 
-    group_rows("Traffic", 6, 7) %>% 
-    group_rows("Biomass", 8, 9) %>% 
-    group_rows("Coal", 10, 11) %>%
-    group_rows("Salt", 12, 13) %>% 
-    group_rows("Oil", 14, 15) %>% 
-    group_rows("Steel", 16, 17) %>% 
-    kable_styling() %>% 
-    row_spec(0, font_size = 8)
-}
-
-table_fk(data = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row)
-```
-
-# Figure 1a
-```{r}
-table_fk(data = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row)
-```
-
-# Figure 1b
-```{r}
-table_fk <- function(data, cmp, cuz){
-  opts <- options(knitr.kable.NA = "0")
-  kbl(data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz)) %>% 
-  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
-  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
-  select(-(HR:HR.U)) %>% 
-  pivot_wider(names_from = "Cause",
-              values_from = "HR.Sum") %>% 
-  slice(match(cmp, Index)),
-  align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
-    kable_styling() %>% 
-    row_spec(0, font_size = 9)
-}
-
-table_fk(data = out.fac.ses, cmp = So.main, cuz = cuz.top.row)
-```
-
-# Figure 1b
-```{r}
-table_fk(data = out.fac.ses, cmp = So.main, cuz = cuz.bot.row)
-```
-
-# Figure 2a
-```{r}
-table_fk <- function(data, cmp, cuz){
-  opts <- options(knitr.kable.NA = "0")
-  kbl(data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz)) %>% 
-  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
-  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
-  select(-(HR:HR.U)) %>% 
-  pivot_wider(names_from = "Cause",
-              values_from = "HR.Sum") %>% 
-  slice(match(cmp, Index)),
-  align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
-    group_rows("Soil", 2, 3) %>%   # same result with group 1=
-    group_rows("Metals", 4, 5) %>% 
-    group_rows("Traffic", 6, 7) %>% 
-    group_rows("Coal", 8, 9) %>%
-    group_rows("Oil", 10, 11) %>% 
-    kable_styling() %>% 
-    row_spec(0, font_size = 9)
-}
-
-table_fk(data = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row)
-```
-
-# Figure 2a
-```{r}
-table_fk(data = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row)
-```
-
-# Figure 2b
-```{r}
-table_fk <- function(data, cmp, cuz){
-  opts <- options(knitr.kable.NA = "0")
-  kbl(data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz)) %>% 
-  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
-  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
-  select(-(HR:HR.U)) %>% 
-  pivot_wider(names_from = "Cause",
-              values_from = "HR.Sum") %>% 
-  slice(match(cmp, Index)),
-  align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
-    kable_styling() %>% 
-    row_spec(0, font_size = 9)
-}
-
-table_fk(data = out.fac.resid, cmp = So.res, cuz = cuz.top.row)
-```
-
-# Figure 2b
-```{r}
-table_fk(data = out.fac.resid, cmp = So.res, cuz = cuz.bot.row)
-```
-
-# Figure x
-```{r}
-table_fk <- function(data, cmp, cuz, em){
-  opts <- options(knitr.kable.NA = "0")
-  kbl(data %>% 
-  filter(!Index %in% c("Na", "Cl")) %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz)) %>% 
-  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
-  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
-  select(-(HR:HR.U)) %>% 
-  pivot_wider(names_from = "Cause",
-              values_from = "HR.Sum") %>% 
-    arrange(factor(Index, levels = cmp), Age),
-  align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 8) %>%
-    group_rows("Soil", 3, 6) %>%   # same result with group 1=
-    group_rows("Metals", 7, 10) %>% 
-    group_rows("Traffic", 11, 14) %>% 
-    group_rows("Coal", 15, 18) %>% 
-    group_rows("Oil", 19, 22) %>%
-    kable_styling() %>% 
-    row_spec(0, font_size = 8)
-}
-
-table_fk(data = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row)
 ```
@@
 ```{r}
-table_fk(data = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row)
-```
-
-# Figure x2
-```{r}
-table_fk <- function(data, cmp, cuz){
-  opts <- options(knitr.kable.NA = "0")
-  kbl(data %>% 
-  filter(Index %in% cmp,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz)) %>% 
-  mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
-  mutate(HR.Sum = paste(HR," (", HR.L,"-", HR.U,")", sep = "")) %>% 
-  select(-(HR:HR.U)) %>% 
-  pivot_wider(names_from = "Cause",
-              values_from = "HR.Sum") %>% 
-    arrange(factor(Index, levels = cmp), Age),
-  align = "c", booktabs = TRUE) %>%
-    kable_classic_2(full_width = F, html_font = "Times New Roman", font_size = 11) %>%
-    kable_styling() %>% 
-    row_spec(0, font_size = 9)
-}
-
-table_fk(data = out.fac.age, cmp = So.multi, cuz = cuz.top.row)
+doc <- read_docx()
+doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row,
+                 cpt = "Figure 1", ftnt = "Continued ...")
+doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row,
+                 cpt = "Figure 1, Continued", ftnt = "")
 ```
@@
 ```{r}
-table_fk(data = out.fac.age, cmp = So.multi, cuz = cuz.bot.row)
+doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.top.row,
+                 cpt = "Figure 2", ftnt = "Continued ...")
+doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.bot.row,
+                 cpt = "Figure 2, Continued", ftnt = "")
 ```
+
+```{r}
+doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row,
+                 cpt = "Figure 3", ftnt = "Continued ...")
+doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row,
+                 cpt = "Figure 3, Continued", ftnt = "")
+```
+
+```{r}
+doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.top.row,
+                 cpt = "Figure 4", ftnt = "Continued ...")
+doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.bot.row,
+                 cpt = "Figure 4, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.race <- out.pmc.race %>% 
+  mutate(Race = ifelse(Race == "A", "Asian",
+                       ifelse(Race == "B", "Black",
+                              ifelse(Race == "H", "Hispanic", "White"))))
+
+doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 5", ftnt = "Continued ...")
+doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 5, Continued", ftnt = "")
+```
+
+```{r}
+out.fac.race <- out.fac.race %>% 
+  mutate(Race = ifelse(Race == "A", "Asian",
+                       ifelse(Race == "B", "Black",
+                              ifelse(Race == "H", "Hispanic", "White"))))
+
+doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.top.row,
+                 cpt = "Figure 6", ftnt = "Continued ...")
+doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 6, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.age <- out.pmc.age %>% 
+  mutate(Age = ifelse(Age == "LE75", "65-75", "> 75"),
+         Age = factor(Age, levels = c("65-75", "> 75")))
+
+doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 7", ftnt = "Continued ...")
+doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 7, Continued", ftnt = "")
+```
+
+```{r}
+out.fac.age <- out.fac.age %>% 
+  mutate(Age = ifelse(Age == "LE75", "65-75", "> 75"),
+         Age = factor(Age, levels = c("65-75", "> 75")))
+
+doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.top.row,
+                 cpt = "Figure 8", ftnt = "Continued ...")
+doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 8, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.sex <- out.pmc.sex %>% 
+  mutate(Sex = ifelse(Sex == "F", "Female", "Male"))
+
+doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 9", ftnt = "Continued ...")
+doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 9, Continued", ftnt = "")
+```
+
+```{r}
+out.fac.sex <- out.fac.sex %>% 
+  mutate(Sex = ifelse(Sex == "F", "Female", "Male"))
+
+doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.top.row,
+                 cpt = "Figure 10", ftnt = "Continued ...")
+doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 10, Continued", ftnt = "")
+```
+
+```{r}
+doc <- Table.Single(dt = out.pmc.urbanicity %>% filter(Loc.Set == "urban") %>%
+                      select(-Loc.Set),
+                    cmp = cmp.main, cuz = cuz.top.row,
+                 cpt = "Figure 11", ftnt = "Continued ...")
+doc <- Table.Single(dt = out.pmc.urbanicity%>% filter(Loc.Set == "urban") %>% 
+                      select(-Loc.Set),
+                    cmp = cmp.main, cuz = cuz.bot.row,
+                 cpt = "Figure 11, Continued", ftnt = "")
+```
+
+```{r}
+doc <- Table.Single(dt = out.fac.urbanicity %>% filter(Loc.Set == "urban") %>% 
+                      select(-Loc.Set),
+                    cmp = So.main, cuz = cuz.top.row,
+                 cpt = "Figure 12", ftnt = "Continued ...")
+doc <- Table.Single(dt = out.fac.urbanicity%>% filter(Loc.Set == "urban") %>% 
+                      select(-Loc.Set),
+                    cmp = So.main, cuz = cuz.bot.row,
+                 cpt = "Figure 12, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.sescat <- out.pmc.sescat %>% 
+  mutate(SES.Cat = ifelse(SES.Cat == "L", "Low",
+                          ifelse(SES.Cat == "M", "Middle", "High")),
+         SES.Cat = factor(SES.Cat, levels = c("Low", "Middle", "High")))
+
+doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 13", ftnt = "Continued ...")
+doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 13, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.region <- out.pmc.region %>% 
+  mutate(Region = ifelse(Region == "west", "West",
+                         ifelse(Region == "midwest", "Midwest",
+                                ifelse(Region == "south", "South", "Northeast"))),
+         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast")))
+
+doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 14", ftnt = "Continued ...")
+doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 14, Continued", ftnt = "")
+```
+
+```{r}
+out.fac.region <- out.fac.region %>% 
+  mutate(Region = ifelse(Region == "west", "West",
+                         ifelse(Region == "midwest", "Midwest",
+                                ifelse(Region == "south", "South", "Northeast"))),
+         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast")))
+
+doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.top.row,
+                 cpt = "Figure 15", ftnt = "Continued ...")
+doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 15, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.resid.region <- out.pmc.resid.region %>% 
+  mutate(Region = ifelse(Region == "west", "West",
+                         ifelse(Region == "midwest", "Midwest",
+                                ifelse(Region == "south", "South", "Northeast"))),
+         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast")))
+
+doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.top.row,
+                 cpt = "Figure 16", ftnt = "Continued ...")
+doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.bot.row,
+                 cpt = "Figure 16, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.brfss <- out.pmc.brfss %>% 
+  mutate(BRFSS = ifelse(BRFSS == "brfss0", "Base", "BRFSS-Adjusted"))
+
+doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 17", ftnt = "Continued ...")
+doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 17, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.buffer <- out.pmc.buffer %>% 
+  mutate(Buffer = ifelse(Buffer == "6", "6-miles",
+                         ifelse(Buffer == "12", "12-miles", "24-miles")),
+         Buffer = factor(Buffer, levels = c("6-miles", "12-miles", "24-miles")))
+
+doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 18", ftnt = "Continued ...")
+doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 18, Continued", ftnt = "")
+```
+
+```{r}
+out.pmc.expo <- out.pmc.expo %>% 
+  mutate(Window = ifelse(Window == "1", "1-yr",
+                         ifelse(Window == "2", "2-yr",
+                                ifelse(Window == "3", "3-yr",
+                                       ifelse(Window == "4", "4-yr", "5-yr")))))
+
+doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Figure 19", ftnt = "Continued ...")
+doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Figure 19, Continued", ftnt = "")
+```
+
+```{r}
+print(doc, target = here('output','table','supplement-tables.docx'))
+```

### 2021-06-03 code/data-viz/forest-plot-functions.R

@@ -21,7 +21,7 @@ library(ggpubr)
 Plot.Single.lab <- function(dt, ggtheme){
   p <- ggplot(dt, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
     geom_vline(xintercept = 1, linetype = 2, color = "black") +
-    labs(x = "", y = "") +
+    labs(x = "Hazard Ratio (95% CI) \n Solid shapes (point estimates) indicate statistically significant results at the 0.05 level", y = "") +
     geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
                  color = plot.cols, size = 0.25, show.legend = F) + 
     geom_point(aes(x = HR, y = Index, shape = sig), 
@@ -41,7 +41,7 @@ Plot.Single.lab <- function(dt, ggtheme){
 Plot.Single <- function(dt, ggtheme){
   p <- ggplot(dt, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
     geom_vline(xintercept = 1, linetype = 2, color = "black") +
-    labs(x = "", y = "") +
+    labs(x = "Hazard Ratio (95% CI) \n Solid shapes (point estimates) indicate statistically significant results at the 0.05 level", y = "") +
     geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
                  color = plot.cols, size = 0.25, show.legend = F) + 
     geom_point(aes(x = HR, y = Index, shape = sig), 
@@ -96,7 +96,7 @@ Plot.Multi.lab <- function(dt, ggtheme, n) {
   p2 <- ggplot(data = filter(dt, Cause %in% cuz.bot.row),
                aes(x = HR, xmin = HR.L, xmax = HR.U, y = Tag)) +
     geom_vline(xintercept = 1, linetype = 2, color = "black") +
-    labs(x = "", y = "") +
+    labs(x = "Hazard Ratio (95% CI) \n Solid shapes (point estimates) indicate statistically significant results at the 0.05 level", y = "") +
     geom_segment(aes(x = HR.L, xend = HR.U, y = Tag, yend = Tag, color = Tag),
                  size = 0.25, show.legend = T) + 
     geom_point(aes(x = HR, y = Tag, color = Tag, shape = sig, size = size.m), 
@@ -150,7 +150,7 @@ Plot.Multi <- function(dt, ggtheme, n) {
[…]

### 2021-06-03 code/data-viz/manuscript-table-functions.R

@@ -1,0 +1,327 @@
+### Author: Fatemeh Kazemi - 05-31-2021
+
+# Functions for making table results of exposure ~ outcome analysis
+# Hazard Ratio (HR) and 95% CI (HR.L, HR.U) (HR.Lower and HR.Upper)
+
+library(tidyverse)
+library(here)
+library(flextable)
+library(officer)
+
+
+
+
+
+# Single Group Table Function ---------------------------------------------
+Table.Single <- function(dt, cmp, cuz, cpt, ftnt){
+  dt <- dt %>% 
+    filter(Index %in% cmp,
+           Cause %in% cuz) %>% 
+    mutate(Index = factor(Index, levels = cmp),
+           Cause = factor(Cause, levels = cuz)) %>% 
+    mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
+    mutate(HR.Sum = paste(HR," (", HR.L,", ", HR.U,")", sep = "")) %>% 
+    select(-(HR:HR.U)) %>% 
+    pivot_wider(names_from = "Cause",
+                values_from = "HR.Sum") %>% 
+    slice(match(cmp, Index))
+  
+  ft <- flextable(dt)
+  ft <- theme_vanilla(ft)
+  ft <- vline(ft, j = c('Index'))
+  ft <- padding(ft, padding = 0)
+  ft <- fontsize(ft, size = 12)
+  ft <- set_caption(ft, caption = cpt)
+  ft <- fontsize(ft, i = 1, size = 12, part = "header")
+  ft <- autofit(ft)
+  
+  doc <- body_add_flextable(doc, value = ft, split = T)
+  doc <- body_add_par(doc, ftnt, style = "Normal")
+  body_add(doc, run_pagebreak())
+  
+  return(doc)
+}
+
+
+# Age Group Table Function ------------------------------------------------
+Table.Multi.age <- function(dt, cmp, cuz, cpt, ftnt){
+  dt <- dt %>% 
+    filter(Index %in% cmp,
+           Cause %in% cuz) %>% 
+    mutate(Index = factor(Index, levels = cmp),
+           Cause = factor(Cause, levels = cuz)) %>% 
+    mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
[…]

### 2021-06-04 code/data-viz/manuscript-figures.Rmd
main and sup tables and figures

@@
 author: "Fatemeh Kazemi"
-date: "02-13-2021"
+date: "06-03-2021"
 ---
@@
 
-### Components Age
-```{r - Components Age, fig.dim = c(7.5, 7.5)}
-data <- out.pmc.age %>% 
-  filter(Index %in% cmp.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp.multi),
-         Tag = ifelse(Age == "LE75", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Age == "M75"), 1,
-                      ifelse((sig == 15 & Age == "M75"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-levels(data$Index) <- cmp.multi.labels
-
-plot.labs <- c("> 75 years", "65-75 years")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-Index.labels <- cmp.multi.labels
-
-Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-age.jpeg'), width = 7.5, height = 7.5, dpi = 600)
-```
-
-<br>
-
-### Factors Age
-```{r - Factor Age, fig.dim = c(7.5, 6.5)}
-data <- out.fac.age %>% 
-  filter(Index %in% So.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So.multi),
-         Tag = ifelse(Age == "LE75", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Age == "M75"), 1,
-                      ifelse((sig == 15 & Age == "M75"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-plot.labs <- c("> 75 years", "65-75 years")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-age.jpeg'), width = 7.5, height = 6.5, dpi = 600)
-```
-
-<br>
-
-### Components Sex
-```{r - Components Sex, fig.dim = c(7.5, 7.5)}
-data <- out.pmc.sex %>% 
-  filter(Index %in% cmp.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp.multi),
-         Tag = ifelse(Sex == "F", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Sex == "M"), 1,
-                      ifelse((sig == 15 & Sex == "M"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-levels(data$Index) <- cmp.multi.labels
-
-plot.labs <- c("Male", "Female")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-Index.labels <- cmp.multi.labels
-
-Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-sex.jpeg'), width = 7.5, height = 7.5, dpi = 600)
-```
-
-<br>
-
-### Factors Sex
-```{r - Factor Sex, fig.dim = c(7.5, 6.5)}
-data <- out.fac.sex %>% 
-  filter(Index %in% So.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So.multi),
-         Tag = ifelse(Sex == "F", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Sex == "M"), 1,
-                      ifelse((sig == 15 & Sex == "M"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-plot.labs <- c("Male", "Female")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-sex.jpeg'), width = 7.5, height = 6.5, dpi = 600)
-```
-
-<br>
-
-### Figure x - Components Race
+### Figure 5 - Components Race
 ```{r - Components Race, fig.dim = c(7.5, 8.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n =1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure 5.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Factors Race
+### Figure 6 - Factors Race
 ```{r - Factor Race, fig.dim = c(7.5, 6.5)}
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+ggsave(here('output', 'plot','Figure 6.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Urban
-```{r - Components urban, fig.dim = c(7.5, 6.5)}
-data <- out.pmc.urbanicity %>% 
-  filter(Loc.Set == "urban") %>% 
+### Figure 7 - Components Age
+```{r - Components Age, fig.dim = c(7.5, 7.5)}
+data <- out.pmc.age %>% 
   filter(Index %in% cmp.multi,
@@
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = rev(cmp.multi)),
-         sig = ifelse(HR.U < 1 , 16, #16-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+         Index = factor(Index, levels = cmp.multi),
+         Tag = ifelse(Age == "LE75", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Age == "M75"), 1,
+                      ifelse((sig == 15 & Age == "M75"),16, sig)),
+         sig = as.integer(sig)
   )
 
-plot.cols <- c("#EB2226")
-Index.labels <- rev(cmp.multi.labels)
+levels(data$Index) <- cmp.multi.labels
 
-Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+plot.labs <- c("> 75 years", "65-75 years")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
+
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','Figure 7.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
 
-### Figure x - Factors Urban
-```{r - Factor Urban, fig.dim = c(7.5, 6.5)}
-data <- out.fac.urbanicity %>%
-  filter(Loc.Set == "urban") %>% 
+### Figure 8 - Factors Age
+```{r - Factor Age, fig.dim = c(7.5, 6.5)}
+data <- out.fac.age %>% 
   filter(Index %in% So.multi,
@@
   mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So.main),
-         sig = ifelse(HR.U < 1 , 16, #16-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Age == "LE75", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Age == "M75"), 1,
+                      ifelse((sig == 15 & Age == "M75"),16, sig)),
+         sig = as.integer(sig)
   )
 
-plot.cols <- c("#EB2226")
+plot.labs <- c("> 75 years", "65-75 years")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
 
-Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
+ggsave(here('output', 'plot','Figure 8.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 
-### Figure x - Components SES-urban
+### Figure 9 - Components Sex
+```{r - Components Sex, fig.dim = c(7.5, 7.5)}
+data <- out.pmc.sex %>% 
+  filter(Index %in% cmp.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp.multi),
+         Tag = ifelse(Sex == "F", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Sex == "M"), 1,
+                      ifelse((sig == 15 & Sex == "M"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+levels(data$Index) <- cmp.multi.labels
+
+plot.labs <- c("Male", "Female")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
+
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','Figure 9.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+```
+
+<br>
+
+### Figure 10 - Factors Sex
+```{r - Factor Sex, fig.dim = c(7.5, 6.5)}
+data <- out.fac.sex %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Sex == "F", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Sex == "M"), 1,
+                      ifelse((sig == 15 & Sex == "M"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+plot.labs <- c("Male", "Female")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
+
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
+ggsave(here('output', 'plot','Figure 10.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### Figure 11 - Components SES-urban
 ```{r Components SES-Urban, fig.dim = c(7.5, 7.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+ggsave(here('output', 'plot','Figure 11.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Region
+### Figure S3 - Components Urban
+```{r - Components urban, fig.dim = c(7.5, 6.5)}
+data <- out.pmc.urbanicity %>% 
+  filter(Loc.Set == "urban") %>% 
+  filter(Index %in% cmp.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = rev(cmp.multi)),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+Index.labels <- rev(cmp.multi.labels)
+
+Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','Figure S3.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### Figure S4 - Factors Urban
+```{r - Factor Urban, fig.dim = c(7.5, 6.5)}
+data <- out.fac.urbanicity %>%
+  filter(Loc.Set == "urban") %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','Figure S4.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### Figure S5 - Components Region
 ```{r - Components Region, fig.dim = c(7.5, 8.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S5.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Factors Region
+### Figure S6 - Factors Region
 ```{r - Factor Region, fig.dim = c(7.5, 6.5)}
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S6.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Residual Region
+### Figure S7 - Components Residual Region
 ```{r - Components Residual Region, fig.dim = c(7.5, 8.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'),width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S7.jpeg'),width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Components BRFSS
+### Figure S8 - Components BRFSS
 ```{r - Components BRFSS, fig.dim = c(7.5, 7.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S8.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Buffer
+### Figure S9 - Components Buffer
 ```{r Components Buffer, fig.dim = c(7.5, 8.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S9.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Exposure Window
+### Figure S10 - Components Exposure Window
 ```{r Components Exposure window, fig.dim = c(7.5, 9.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 9.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S10.jpeg'), width = 7.5, height = 9.5, dpi = 600)
 ```

### 2021-06-04 code/data-viz/manuscript-tables.Rmd
main and sup tables and figures

@@
                "Ni", "V")
-cmp.multi.labels <- c(expression("PM"[2.5]),"Si", "Ca", "Pb", "Zn", 
-                      expression("NO"[3]^{"-"}), "OC", "Se", expression("SO"[4]^{"2-"}),
-                      "Ni", "V")
 
@@
 
+### Figure 1 - Components SES
 ```{r}
@@
 doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row,
-                 cpt = "Figure 1", ftnt = "Continued ...")
+                 cpt = "Table S2.
+Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row,
-                 cpt = "Figure 1, Continued", ftnt = "")
+                 cpt = "Table S2.
+Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 2 - Factors SES
 ```{r}
 doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.top.row,
-                 cpt = "Figure 2", ftnt = "Continued ...")
+                 cpt = "Table S3.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.bot.row,
-                 cpt = "Figure 2, Continued", ftnt = "")
+                 cpt = "Table S3.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 3 - PM-Components Residual
 ```{r}
 doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row,
-                 cpt = "Figure 3", ftnt = "Continued ...")
+                 cpt = "Table S4.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row,
-                 cpt = "Figure 3, Continued", ftnt = "")
+                 cpt = "Table S4.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 4 - PM-Factors Residual
 ```{r}
 doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.top.row,
-                 cpt = "Figure 4", ftnt = "Continued ...")
+                 cpt = "Table S5.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.bot.row,
-                 cpt = "Figure 4, Continued", ftnt = "")
+                 cpt = "Table S5.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 5 - Components Race
 ```{r}
@@
 doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 5", ftnt = "Continued ...")
+                 cpt = "Table S6.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 5, Continued", ftnt = "")
+                 cpt = "Table S6.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 6 - Factors Race
 ```{r}
@@
 doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Figure 6", ftnt = "Continued ...")
+                 cpt = "Table S7.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 6, Continued", ftnt = "")
+                 cpt = "Table S7.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 7 - Components Age
 ```{r}
@@
 doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 7", ftnt = "Continued ...")
+                 cpt = "Table S8.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 7, Continued", ftnt = "")
+                 cpt = "Table S8.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 8 - Factors Age
 ```{r}
@@
 doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Figure 8", ftnt = "Continued ...")
+                 cpt = "Table S9.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 8, Continued", ftnt = "")
+                 cpt = "Table S9.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 9 - Components Sex
 ```{r}
@@
 doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 9", ftnt = "Continued ...")
+                 cpt = "Table S10.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 9, Continued", ftnt = "")
+                 cpt = "Table S10.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure 10 - Factors Sex
 ```{r}
@@
 doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Figure 10", ftnt = "Continued ...")
+                 cpt = "Table S11.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 10, Continued", ftnt = "")
+                 cpt = "Table S11.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
-```{r}
-doc <- Table.Single(dt = out.pmc.urbanicity %>% filter(Loc.Set == "urban") %>%
-                      select(-Loc.Set),
-                    cmp = cmp.main, cuz = cuz.top.row,
-                 cpt = "Figure 11", ftnt = "Continued ...")
-doc <- Table.Single(dt = out.pmc.urbanicity%>% filter(Loc.Set == "urban") %>% 
-                      select(-Loc.Set),
-                    cmp = cmp.main, cuz = cuz.bot.row,
-                 cpt = "Figure 11, Continued", ftnt = "")
-```
-
-```{r}
-doc <- Table.Single(dt = out.fac.urbanicity %>% filter(Loc.Set == "urban") %>% 
-                      select(-Loc.Set),
-                    cmp = So.main, cuz = cuz.top.row,
-                 cpt = "Figure 12", ftnt = "Continued ...")
-doc <- Table.Single(dt = out.fac.urbanicity%>% filter(Loc.Set == "urban") %>% 
-                      select(-Loc.Set),
-                    cmp = So.main, cuz = cuz.bot.row,
-                 cpt = "Figure 12, Continued", ftnt = "")
-```
-
+### Figure 11 - Components SES-urban
 ```{r}
@@
 doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 13", ftnt = "Continued ...")
+                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas.", ftnt = "Continued ...")
 doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 13, Continued", ftnt = "")
+                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas., Continued", ftnt = "")
 ```
 
+### Figure S3 - Components Urban
+```{r}
+doc <- Table.Single(dt = out.pmc.urbanicity %>% filter(Loc.Set == "urban") %>%
+                      select(-Loc.Set),
+                    cmp = cmp.main, cuz = cuz.top.row,
+                 cpt = "Table S13.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+doc <- Table.Single(dt = out.pmc.urbanicity%>% filter(Loc.Set == "urban") %>% 
+                      select(-Loc.Set),
+                    cmp = cmp.main, cuz = cuz.bot.row,
+                 cpt = "Table S13.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+```
+
+### Figure S4 - factors Urban
+```{r}
+doc <- Table.Single(dt = out.fac.urbanicity %>% filter(Loc.Set == "urban") %>% 
+                      select(-Loc.Set),
+                    cmp = So.main, cuz = cuz.top.row,
+                 cpt = "Table S14.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+doc <- Table.Single(dt = out.fac.urbanicity%>% filter(Loc.Set == "urban") %>% 
+                      select(-Loc.Set),
+                    cmp = So.main, cuz = cuz.bot.row,
+                 cpt = "Table S14.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+```
+
+### Figure S5 - Components Region
 ```{r}
@@
 doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 14", ftnt = "Continued ...")
+                 cpt = "Table S15.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 14, Continued", ftnt = "")
+                 cpt = "Table S15.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure S6 - Factors Region
 ```{r}
@@
 doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Figure 15", ftnt = "Continued ...")
+                 cpt = "Table S16.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 15, Continued", ftnt = "")
+                 cpt = "Table S16.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure S7 - Components Residual Region
 ```{r}
@@
 doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.top.row,
-                 cpt = "Figure 16", ftnt = "Continued ...")
+                 cpt = "Table S17.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.bot.row,
-                 cpt = "Figure 16, Continued", ftnt = "")
+                 cpt = "Table S17.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure S8 - Components BRFSS
 ```{r}
@@
 doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 17", ftnt = "Continued ...")
+                 cpt = "Table S18.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 17, Continued", ftnt = "")
+                 cpt = "Table S18.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure S9 - Components Buffer
 ```{r}
@@
 doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 18", ftnt = "Continued ...")
+                 cpt = "Table S19.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its components exposures.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 18, Continued", ftnt = "")
+                 cpt = "Table S19.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its components exposures., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
+### Figure S10 - Components Exposure Window
 ```{r}
@@
 doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Figure 19", ftnt = "Continued ...")
+                 cpt = "Table S20.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its components for the subset of the monitors with complete data of 1 to 5 year moving average.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Figure 19, Continued", ftnt = "")
+                 cpt = "Table S20.
+Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its components for the subset of the monitors with complete data of 1 to 5 year moving average., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```

### 2021-06-06 code/data-processors/air-data-processor.Rmd
main text tables

@@
 ```
-
-```{r}
-load(here('data','processed', 'pmc-daily.RDa'))
-load(here('data','processed','pmc-site-ndi.RDa'))
-
-dt.pmc <- dt.pmc.site.ndi %>% 
-  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
-         Region = ifelse(Region.IV == 1, "W",
-                         ifelse(Region.IV == 2, "MW",
-                                ifelse(Region.IV == 3, "S", "NE")))) %>% 
-    select(Site.ID, Region, Loc.Set) %>% 
-  merge(dt.pmc.daily) %>% 
-  pivot_longer(AS:PM,
-               names_to = "Parameter",
-               values_to = "Value")
-
-table.region <- dt.pmc %>% 
-  group_by(Parameter, Region) %>% 
-  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
-            STD = sprintf("%0.2f", sd(Value*1000)))
-
-table.urban <- dt.pmc %>% 
-  group_by(Parameter, Loc.Set) %>% 
-  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
-            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
-  rename(Region = Loc.Set)
-
-table <- dt.pmc %>% 
-  group_by(Parameter) %>% 
-  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
-            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
-  mutate(Region = "US") %>% 
-  as.data.frame() %>% 
-  add_row(table.region) %>% 
-  add_row(table.urban) %>% 
-  pivot_wider(names_from = c(Region),
-              values_from = c(Mean, STD))
-
-write.csv(table,
-          file = here('output','table', 'pmc-daily-summary.csv'),
-          row.names = F)
-
-```

### 2021-06-06 code/data-viz/manuscript-tables.Rmd
main text tables

@@
 ```{r Load data}
+load(here('data','processed', 'pmc-daily.RDa'))
+load(here('data','processed','pmc-site-ndi.RDa'))
+
 load(here('output','analysis','out-pmc-ses.RDa'))
@@
                    "-Se", "-SO4", "-Ni", "-V")
+```
+
+### Table 2
+```{r}
+dt.pmc <- dt.pmc.site.ndi %>% 
+  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
+         Region = ifelse(Region.IV == 1, "West",
+                         ifelse(Region.IV == 2, "Midwest",
+                                ifelse(Region.IV == 3, "South", "Northeast"))),
+         Region = factor(Region, levels = c("West", "Midwest", "South", "Northeast"))) %>%
+  select(Site.ID, Region, Loc.Set) %>% 
+  merge(dt.pmc.daily) %>% 
+  pivot_longer(AS:PM,
+               names_to = "Parameter",
+               values_to = "Value")
+
+table.region <- dt.pmc %>% 
+  group_by(Parameter, Region) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
+            STD = sprintf("%0.2f", sd(Value*1000)))
+
+table.urban <- dt.pmc %>% 
+  group_by(Parameter, Loc.Set) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
+            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
+  mutate(Region = Loc.Set,
+         Region = factor(Region, levels = c("Urban", "Rural"))) %>% 
+  select(-Loc.Set) %>% 
+  arrange(Region)
+
+cmp <- c("PM", "AS", "CA", "CL", "CU", "FE", "K", "MG", "MN", "NA", "NI",
+         "NO3", "OC", "PB", "SE", "SI", "SO4", "V", "ZN")
+
+table <- dt.pmc %>% 
+  group_by(Parameter) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
+            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
+  mutate(Region = "US",
+         Region = factor(Region, levels = c("US"))) %>% 
+  as.data.frame() %>% 
+  add_row(table.region) %>% 
+  add_row(table.urban) %>% 
+  filter(Parameter != "EC") %>% 
+  mutate(test = paste(Mean,"±",STD, sep = " ")) %>% 
+  select(-Mean, -STD) %>% 
+  pivot_wider(names_from = "Region",
+              values_from = "test",
+              names_sort = F) %>% 
+  mutate(Parameter = factor(Parameter, levels = cmp)) %>% 
+  arrange(Parameter) %>% 
+  rename(Component = Parameter)
+
+ft <- flextable(table)
+ft <- theme_booktabs(ft)
+ft <- vline(ft, j = c('Component', 'US', 'Northeast'))
+ft <- hline(ft, i = c(1, 4, 7, 10, 13, 16))
+ft <- padding(ft, padding = 0)
+ft <- fontsize(ft, size = 10)
+ft <- set_caption(ft, caption = "Table 2. Daily concentrations of PM2.5 and its components, mean ± standard deviation, nationwide, by region and urbanicity.")
+ft <- fontsize(ft, i = 1, size = 12, part = "header")
+ft <- autofit(ft)
+
+doc <- read_docx()
+doc <- body_add_flextable(doc, value = ft, split = T)
+doc <- body_add_par(doc, "Units are ng/m3 unless specified", style = "Normal")
+body_add(doc, run_pagebreak())
+```
+
+### Table 3
+```{r}
+fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
+factor.loadings <- rbind(fit$loadings) %>% as.data.frame()
+factor.loadings <- rownames_to_column(factor.loadings, "Component")
+
+colnames(factor.loadings) <- c("Component", "Soil", "Metals", "Traffic", 
+                               "Biomass Combustion", "Coal combustion", "Salt", 
+                               "Residual Oil Combustion", "Steel Industry") 
+factor.loadings <- factor.loadings %>% 
+  mutate_at(.vars = c("Soil", "Metals", "Traffic", "Biomass Combustion", 
+                      "Coal combustion", "Salt", "Residual Oil Combustion", 
+                      "Steel Industry"), ~sprintf('%.2f', .x))
+
+ft <- flextable(factor.loadings)
+ft <- theme_booktabs(ft)
+ft <- vline(ft, j = c('Component'))
+ft <- hline(ft, i = c(3, 6, 9, 12, 15))
+ft <- padding(ft, padding = 0)
+ft <- fontsize(ft, size = 10)
+ft <- set_caption(ft, caption = "Table 3. Loadings of each component for eight identified factors.")
+ft <- fontsize(ft, i = 1, size = 12, part = "header")
+ft <- autofit(ft)
+
+doc <- body_add_flextable(doc, value = ft, split = T)
+body_add(doc, run_pagebreak())
+
+print(doc, target = here('output','table','main-tables.docx'))
 ```

### 2021-06-25 code/data-viz/manuscript-tables.Rmd
IQRs

@@
 ```{r Load data}
-load(here('data','processed', 'pmc-daily.RDa'))
+load(here('data','processed','pmc-daily.RDa'))
 load(here('data','processed','pmc-site-ndi.RDa'))
+load(here('data','processed','pmc-1yr.RDa'))
+load(here('data','processed','fac-1yr.RDa'))
 
@@
 
+```{r - Parameter/Factor to Index}
+### Components
+Para.to.Index <- tribble(
+  ~Index, ~Parameter,
+   "As", "AS",
+   "Ca", "CA",
+   "Cu", "CU",
+   "Cl", "CL",
+   "Fe", "FE",
+   "Pb", "PB",
+   "Mn", "MN",
+   "Ni", "NI",
+   "Mg", "MG",
+   "Se", "SE",
+   "V", "V",
+   "Si", "SI",
+   "Zn", "ZN",
+   "K", "K",
+   "Na", "NA",
+   "NO3", "NO3",
+   "SO4", "SO4",
+   "OC", "OC",
+   "EC", "EC",
+   "PM2.5", "PM"
+   ) %>% 
+  mutate(Index = as.factor(Index),
+         Parameter = as.factor(Parameter))
+
+### Factors 
+Factor.to.Index <- tribble(
+  ~Index, ~Parameter,
+   "Soil", "Factor1",
+   "Metals", "Factor2",
+   "Traffic", "Factor3",
+   "Biomass", "Factor4",
+   "Coal", "Factor5",
+   "Salt", "Factor6",
+   "Oil", "Factor7",
+   "Steel", "Factor8"
+   ) %>% 
+  mutate(Index = as.factor(Index),
+         Parameter = as.factor(Parameter))
+```
+
 ### Table 2
@@
 table.region <- dt.pmc %>% 
+   mutate(
+    Value = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), Value, Value * 1000)) %>%
   group_by(Parameter, Region) %>% 
-  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
-            STD = sprintf("%0.2f", sd(Value*1000)))
+  summarise(Mean = sprintf("%0.2f", mean(Value)),
+            STD = sprintf("%0.2f", sd(Value)))
 
 table.urban <- dt.pmc %>% 
+   mutate(
+    Value = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), Value, Value * 1000)) %>%
   group_by(Parameter, Loc.Set) %>% 
-  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
-            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value)),
+            STD = sprintf("%0.2f", sd(Value))) %>% 
   mutate(Region = Loc.Set,
@@
 table <- dt.pmc %>% 
+   mutate(
+    Value = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), Value, Value * 1000)) %>%
   group_by(Parameter) %>% 
-  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
-            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
+  summarise(Mean = sprintf("%0.2f", mean(Value)),
+            STD = sprintf("%0.2f", sd(Value))) %>% 
   mutate(Region = "US",
@@
   arrange(Parameter) %>% 
-  rename(Component = Parameter)
+  merge(Para.to.Index) %>% 
+  rename(Component = Index) %>% 
+  select(Component, everything(), -Parameter)
 
@@
 factor.loadings <- rbind(fit$loadings) %>% as.data.frame()
-factor.loadings <- rownames_to_column(factor.loadings, "Component")
+factor.loadings <- rownames_to_column(factor.loadings, "Parameter")
 
-colnames(factor.loadings) <- c("Component", "Soil", "Metals", "Traffic", 
+colnames(factor.loadings) <- c("Parameter", "Soil", "Metals", "Traffic", 
                                "Biomass Combustion", "Coal combustion", "Salt", 
@@
                       "Coal combustion", "Salt", "Residual Oil Combustion", 
-                      "Steel Industry"), ~sprintf('%.2f', .x))
+                      "Steel Industry"), ~sprintf('%.2f', .x)) %>% 
+  merge(Para.to.Index) %>% 
+  rename(Component = Index) %>% 
+  select(Component, everything(), -Parameter)
 
@@
 
-print(doc, target = here('output','table','main-tables.docx'))
+print(doc, target = here('output','table','main-tables-2.docx'))
+```
+
+### Table S2
+```{r}
+cmp <- c("PM2.5", "Si", "Ca", "Pb", "Zn", "NO3", "OC", "K", "Cu", "Se", "SO4",
+         "Na", "Cl", "Ni", "V", "Fe", "Mn")
+
+### Components
+pmc.1yr.iqr <- dt.pmc.site.ndi %>% 
+  select(Site.ID) %>% 
+  inner_join(dt.pmc.1yr) %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(
+    IQR = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), IQR, IQR * 1000),
+    IQR = sprintf("%0.2f", IQR),
+    Parameter = as.factor(Parameter)) %>% 
+  merge(Para.to.Index) %>% 
+  rename(Component = Index) %>% 
+  select(Component, everything(), -Parameter) %>% 
+  filter(Component %in% cmp) %>% 
+  mutate(Component = factor(Component, levels = cmp)) %>% 
+  arrange(Component) %>% 
+  mutate(Source = ifelse(Component == "PM2.5", "PM2.5",
+                         ifelse(Component %in% c("Si", "Ca"), "Soil",
+                                ifelse(Component %in% c("Pb", "Zn"), "Metals",
+                                       ifelse(Component %in% c("NO3", "OC"), "Traffic",
+                         ifelse(Component %in% c("K", "Cu"), "Biomass",
+                                ifelse(Component %in% c("Se", "SO4"), "Coal",
+                                       ifelse(Component %in% c("Na", "Cl"), "Salt",
+                         ifelse(Component %in% c("Ni", "V"), "Oil", "Steel")))))))))
+
+### Factors excluding EC
+fac.1yr.iqr <- dt.pmc.site.ndi %>% 
+  select(Site.ID) %>% 
+  inner_join(dt.fac.1yr) %>% 
+  summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
+  pivot_longer(cols = Factor1:Factor8,
+               names_to = "Parameter",
+               values_to = "IQR.2")%>% 
+  mutate(IQR.2 = sprintf("%0.2f", IQR.2)) %>% 
+  mutate(Parameter = as.factor(Parameter)) %>% 
+  merge(Factor.to.Index) %>% 
+  rename(Source = Index) %>% 
+  select(Source, everything(), -Parameter)
+
+table <- full_join(pmc.1yr.iqr, fac.1yr.iqr) %>% 
+  select(Source, IQR.2, Component, IQR)
+
+ft <- flextable(table)
+ft <- merge_v(ft, j = c("Source", "IQR.2"))
+ft <- theme_vanilla(ft)
+ft <- vline(ft, j = c('IQR.2'))
+ft <- padding(ft, padding = 0)
+ft <- fontsize(ft, size = 10)
+ft <- set_caption(ft, caption = "Table S2. IQR for 1-year moving average of source factors, PM2.5 and its components")
+ft <- fontsize(ft, i = 1, size = 12, part = "header")
+ft <- autofit(ft)
+
+doc <- read_docx()
+doc <- body_add_flextable(doc, value = ft, split = T)
+doc <- body_add_par(doc, "a Source factors are unitless b Units are ng/m3 unless specified", style = "Normal")
+body_add(doc, run_pagebreak())
 ```
@@
 ```{r}
-doc <- read_docx()
 doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.top.row,
-                 cpt = "Table S2.
+                 cpt = "Table S3.
 Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components.", ftnt = "Continued ...
@@
 doc <- Table.Single(dt = out.pmc.ses, cmp = cmp.main, cuz = cuz.bot.row,
-                 cpt = "Table S2.
+                 cpt = "Table S3.
 Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.top.row,
-                 cpt = "Table S3.
+                 cpt = "Table S4.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors.", ftnt = "Continued ...
@@
 doc <- Table.Single(dt = out.fac.ses, cmp = So.main, cuz = cuz.bot.row,
-                 cpt = "Table S3.
+                 cpt = "Table S4.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.top.row,
-                 cpt = "Table S4.
+                 cpt = "Table S5.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components.", ftnt = "Continued ...
@@
 doc <- Table.Single(dt = out.pmc.resid, cmp = cmp.res, cuz = cuz.bot.row,
-                 cpt = "Table S4.
+                 cpt = "Table S5.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.top.row,
-                 cpt = "Table S5.
+                 cpt = "Table S6.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores.", ftnt = "Continued ...
@@
 doc <- Table.Single(dt = out.fac.resid, cmp = So.res, cuz = cuz.bot.row,
-                 cpt = "Table S5.
+                 cpt = "Table S6.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from source-related factor scores., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S6.
+                 cpt = "Table S7.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race.", ftnt = "Continued ...
@@
 doc <- Table.Multi.race(dt = out.pmc.race, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S6.
+                 cpt = "Table S7.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Table S7.
+                 cpt = "Table S8.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race.", ftnt = "Continued ...
@@
 doc <- Table.Multi.race(dt = out.fac.race, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Table S7.
+                 cpt = "Table S8.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S8.
+                 cpt = "Table S9.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age.", ftnt = "Continued ...
@@
 doc <- Table.Multi.age(dt = out.pmc.age, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S8.
+                 cpt = "Table S9.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Table S9.
+                 cpt = "Table S10.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age.", ftnt = "Continued ...
@@
 doc <- Table.Multi.age(dt = out.fac.age, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Table S9.
+                 cpt = "Table S10.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S10.
+                 cpt = "Table S11.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex.", ftnt = "Continued ...
@@
 doc <- Table.Multi.sex(dt = out.pmc.sex, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S10.
+                 cpt = "Table S11.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Table S11.
+                 cpt = "Table S12.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex.", ftnt = "Continued ...
@@
 doc <- Table.Multi.sex(dt = out.fac.sex, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Table S11.
+                 cpt = "Table S12.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas.", ftnt = "Continued ...")
+                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas.", ftnt = "Continued ...")
 doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S12. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas., Continued", ftnt = "")
+                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas., Continued", ftnt = "")
 ```
@@
                     cmp = cmp.main, cuz = cuz.top.row,
-                 cpt = "Table S13.
+                 cpt = "Table S14.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas.", ftnt = "Continued ...
@@
                     cmp = cmp.main, cuz = cuz.bot.row,
-                 cpt = "Table S13.
+                 cpt = "Table S14.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                     cmp = So.main, cuz = cuz.top.row,
-                 cpt = "Table S14.
+                 cpt = "Table S15.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas.", ftnt = "Continued ...
@@
                     cmp = So.main, cuz = cuz.bot.row,
-                 cpt = "Table S14.
+                 cpt = "Table S15.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S15.
+                 cpt = "Table S16.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region.", ftnt = "Continued ...
@@
 doc <- Table.Multi.region(dt = out.pmc.region, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S15.
+                 cpt = "Table S16.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.top.row,
-                 cpt = "Table S16.
+                 cpt = "Table S17.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region.", ftnt = "Continued ...
@@
 doc <- Table.Multi.region(dt = out.fac.region, cmp = So.multi, cuz = cuz.bot.row,
-                 cpt = "Table S16.
+                 cpt = "Table S17.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in source factors: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.top.row,
-                 cpt = "Table S17.
+                 cpt = "Table S18.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region.", ftnt = "Continued ...
@@
 doc <- Table.Multi.region(dt = out.pmc.resid.region, cmp = cmp.multi.res, cuz = cuz.bot.row,
-                 cpt = "Table S17.
+                 cpt = "Table S18.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S18.
+                 cpt = "Table S19.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data.", ftnt = "Continued ...
@@
 doc <- Table.Multi.brfss(dt = out.pmc.brfss, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S18.
+                 cpt = "Table S19.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S19.
+                 cpt = "Table S20.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its components exposures.", ftnt = "Continued ...
@@
 doc <- Table.Multi.buffer(dt = out.pmc.buffer, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S19.
+                 cpt = "Table S20.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its components exposures., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S20.
+                 cpt = "Table S21.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its components for the subset of the monitors with complete data of 1 to 5 year moving average.", ftnt = "Continued ...
@@
 doc <- Table.Multi.expo(dt = out.pmc.expo, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S20.
+                 cpt = "Table S21.
 Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its components for the subset of the monitors with complete data of 1 to 5 year moving average., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
 ```{r}
-print(doc, target = here('output','table','supplement-tables.docx'))
+print(doc, target = here('output','table','supplement-tables-2.docx'))
 ```

### 2021-10-07 code/data-analysis/config-file-generator.Rmd
plot, table, map
revision

@@
 title: "Config File Generator"
-output: 
+author: "Fatemeh Kazemi"
+date: "01-18-2021"
 ---
@@
              "Yr_PB","Yr_PM","Yr_SI","Yr_SO4","Yr_V","Yr_ZN")
+```
+
+```{r List of Major PM Components Yr Sub}
+pmc.major.yr <- c("Yr1_SI","Yr1_NO3","Yr1_SO4",
+                "Yr2_SI","Yr2_NO3","Yr2_SO4",
+                "Yr3_SI","Yr3_NO3","Yr3_SO4",
+                "Yr4_SI","Yr4_NO3","Yr4_SO4",
+                "Yr5_SI","Yr5_NO3","Yr5_SO4")
 ```
@@
 
-```{r ses adj. model for components - bz 6}
+```{r ses adj. model for components - bz6}
 dataname <- "ndi-pmc-bz6.csv"
@@
 
-```{r ses adj. model for components - bz 12}
+```{r ses adj. model for components - bz12}
 dataname <- "ndi-pmc-bz12.csv"
@@
 
-```{r ses adj. model for components - bz 24}
+```{r ses adj. model for components - bz24}
 dataname <- "ndi-pmc-bz24.csv"
@@
       writeLines(w, here('config-files','mass-ses', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - bz6 & 1-5yr}
+dataname <- "ndi-pmc-bz6-15yr.csv"
+expo <- pmc.major.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','pmc-bz6-15yr', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - bz12 & 1-5yr}
+dataname <- "ndi-pmc-bz12-15yr.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','pmc-bz12-15yr', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
+```{r ses adj. model for components - bz 24 & 1-5yr}
+dataname <- "ndi-pmc-bz24.csv"
+expo <- pmc.sub.yr
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','pmc-bz24-15yr', paste(k,'.txt', sep = "")))
     }

### 2021-10-07 code/data-analysis/factor-analysis.Rmd
revision

@@
 
-### Last Edit: 12-31-2020
-
 ### This program:
   (1) Run factor analysis
+
+# Notes
+  1. Combination2 is better for mass app
 
@@
 load(here('data','processed', 'aqs-sites.RDa'))
-load(here('data','processed', 'mass-apportioned.RDa'))
+#load(here('data','processed', 'mass-apportioned-c1.RDa'))
 ```
@@
 source(here('code','data-processors','air-data-smooth-mvavg-function.R'))
+
+so.coef <- function(model, cmp){
+  source = as.numeric(summary(model)$coefficients[,1][cmp])
+  return(source)
+}
 ```
@@
 factor.scores <- factor.scores(dt.pmc.daily %>% select(AS:OC), fit)
-dt.fac.daily <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores) 
+dt.fac.ec.daily <- cbind(dt.pmc.daily %>% select(Site.ID, Date), factor.scores$scores) 
 save(dt.fac.ec.daily, file = here('data', 'processed', 'fac-ec-daily.RDa'))
@@
 
-```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
+```{r Smoothing Factors & Caluculating 1-yr mvavg for each month}
 dt.air <- dt.fac.daily %>% 
@@
 
-```{r Smoothing Data & Caluculating 1-yr mvavg for each month with EC}
-dt.air <- dt.fac.daily.ec %>% 
+```{r Smoothing Factors & Caluculating 1-yr mvavg for each month with EC}
+dt.air <- dt.fac.ec.daily %>% 
   pivot_longer(cols = Factor1:Factor8,
@@
 
-```{r Smoothing Data & Caluculating 1-yr mvavg for each month}
+```{r Smoothing Factors Residuals & Caluculating 1-yr mvavg for each month}
 dt.air <- dt.fac.residual %>% 
@@
 
+```
+
+```{r}
+Factor.to.Index <- tribble(
+  ~Index, ~Parameter,
+   "Soil", "Factor1",
+   "Metals", "Factor2",
+   "Traffic", "Factor3",
+   "Biomass", "Factor4",
+   "Coal", "Factor5",
+   "Salt", "Factor6",
+   "Oil", "Factor7",
+   "Steel", "Factor8"
+   ) %>% 
+  mutate(Index = as.factor(Index),
+         Parameter = as.factor(Parameter))
+```
+
+```{r Factor Score Mass Apportionment}
+dt.pm.daily <- dt.pmc.daily %>% 
+  select(Site.ID, Date, PM)
+
+dt.fac.pm.daily <- dt.fac.daily %>% 
+  merge(dt.pm.daily) %>% 
+  rename("Soil" = Factor1,
+         "Metals" = Factor2,
+         "Traffic" = Factor3,
+         "Biomass" = Factor4,
+         "Coal" = Factor5,
+         "Salt" = Factor6,
+         "Oil" = Factor7,
+         "Steel" = Factor8)
+
+factor.mass <- lmer(data = dt.fac.pm.daily,
+              PM ~ Soil + Metals + Traffic + Biomass + Coal + Salt + Oil + Steel+ (1|Site.ID))
+
+tab_model(factor.mass, show.se = T, show.ci = F, show.aic = T,
+          show.re.var = F, show.icc = T, show.obs = T, show.ngroups = T,
+          title = "Factor Related PM Mass")
+```
+
+```{r Smoothing Source mass & Caluculating 1-yr mvavg for each month}
+dt.air <- dt.fac.pm.daily %>%
+  mutate(Soil.mass = so.coef(factor.mass, 'Soil') * Soil,
+         Metals.mass = so.coef(factor.mass, 'Metals') * Metals,
+         Traffic.mass = so.coef(factor.mass, 'Traffic') * Traffic,
+         Biomass.mass = so.coef(factor.mass, 'Biomass') * Biomass,
+         Coal.mass = so.coef(factor.mass, 'Coal') * Coal,
+         Salt.mass = so.coef(factor.mass, 'Salt') * Salt,
+         Oil.mass = so.coef(factor.mass, 'Oil') * Oil,
+         Steel.mass = so.coef(factor.mass, 'Steel') * Steel) %>% 
+  select(Site.ID, Date, Soil.mass:Steel.mass) %>% 
+  pivot_longer(cols = c(Soil.mass:Steel.mass),
+               names_to = "Parameter.Symbol",
+               values_to = "Value") %>% 
+  arrange(Site.ID, Parameter.Symbol, Date)
+
+site.para <- dt.air %>% 
+  distinct(Site.ID, Parameter.Symbol)
+
+#using smoothed.yr function
+smooth.out <- mapply(Smoothed.Year, 
+                     site.para$Site.ID, site.para$Parameter.Symbol, 0.99, 350)
+para.monthly <- data.frame(Site.ID=unlist(smooth.out[1,]),
+                           Parameter.Symbol=unlist(smooth.out[2,]),
+                           Date=unlist(smooth.out[3,]), 
+                           para.1yr=unlist(smooth.out[4,]))
+
+dt.mass.app.1yr.fac <- para.monthly %>% 
+  mutate(Parameter.Symbol = sub("\\..*", "", Parameter.Symbol),
+         Year = floor(Date -0.01),
+         Month = round((Date - Year)*12)) %>% 
+  select(-Date) %>% 
+  pivot_wider(names_sort = T,
+              names_from = c(Parameter.Symbol),
+              values_from = c(para.1yr)) %>% 
+  arrange(Site.ID, Year, Month)
+
+save(dt.mass.app.1yr.fac, file = here('data', 'processed', 'mass-app-1yr-fac.RDa'))
+write.csv(dt.mass.app.1yr.fac, file = here('data', 'processed', 'mass-app-1yr-fac.csv'), row.names = F)
+```
+
+```{r IQR test}
+Soil  <-  so.coef(factor.mass, 'Soil') * 0.38
+Metals <- so.coef(factor.mass, 'Metals') * 0.16
+Traffic <- so.coef(factor.mass, 'Traffic') * 1.18
+Biomass <- so.coef(factor.mass, 'Biomass') * 0.18
+Coal <- so.coef(factor.mass, 'Coal') * 1.03
+Salt <- so.coef(factor.mass, 'Salt') * 0.18
+Oil <- so.coef(factor.mass, 'Oil') * 0.09
+Steel <- so.coef(factor.mass, 'Steel') * 0.15
+
+# Second way
+dt.mass.app.1yr.fac %>% summarise_at(vars(Biomass:Traffic), ~IQR(.x))
 ```
@@
 
-```{r - Single Tracer Mass Apportionment - function}
+```{r - Single Tracer Mass Apportionment}
 dt.sites <- dt.aqs.sites %>% 
@@
 Sources <- c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Salt", "Oil", "Steel")
-
-so.coef <- function(model, cmp){
-  source = as.numeric(summary(model)$coefficients[,1][cmp])
-  return(source)
-}
 ```
@@
 
-```{r - Single Tracer Mass Apportionment - Combination 2}
+```{r - Single Tracer Mass Apportionment - Combination 2 - Preferred}
 dt.mass.app.c2 <- dt.pmc.daily %>% 

### 2021-10-07 code/data-analysis/output-cleaning.Rmd
plot, table, map
revision

@@
 title: "Analysis Output files"
+author: "Fatemeh Kazemi"
+date: "01-30-2021"
 ---
@@
 load(here('data','processed','mass-app-1yr-c2.RDa'))
+load(here('data','processed','site-urban-ses-cat.RDa'))
 ```
@@
 ```{r - Parameter/Factor to Index}
+cmp <- c("PM2.5", "Si", "Ca", "Pb", "Zn", "NO3", "OC", "K", "Cu", "Se", "SO4",
+         "Na", "Cl", "Ni", "V", "Fe", "Mn")
+
 ### Components
@@
 ### Components
-pmc.1yr.iqr <- dt.pmc.site.ndi %>% 
-  select(Site.ID) %>% 
-  inner_join(dt.pmc.1yr) %>% 
+pmc.1yr.iqr <- dt.pmc.1yr %>% 
   summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
@@
 ### Factors excluding EC
-fac.1yr.iqr <- dt.pmc.site.ndi %>% 
-  select(Site.ID) %>% 
-  inner_join(dt.fac.1yr) %>% 
+fac.1yr.iqr <- dt.fac.1yr %>% 
   summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
@@
 ### Factors Inc EC
-fac.ec.1yr.iqr <- dt.pmc.site.ndi %>% 
-  select(Site.ID) %>% 
-  inner_join(dt.fac.ec.1yr) %>% 
+fac.ec.1yr.iqr <- dt.fac.ec.1yr %>% 
   summarise_at(vars(Factor1:Factor8), ~IQR(.x)) %>% 
@@
 ### Source Apportioned PM Mass
-mass.1yr.iqr <- dt.pmc.site.ndi %>% 
-  select(Site.ID) %>% 
-  inner_join(dt.mass.app.1yr.c2) %>% 
+mass.1yr.iqr <- dt.mass.app.1yr.c2 %>% 
   summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
@@
 
-carbon.1yr.iqr <- dt.site %>% 
-  select(Site.ID) %>% 
-  inner_join(dt.carbon) %>% 
+carbon.1yr.iqr <- dt.carbon %>% 
   summarise_at(vars(EC:OC), ~IQR(.x)) %>% 
@@
 
+table <- pmc.xyr.5yr.iqr %>% 
+  mutate(IQR = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), IQR, IQR * 1000),
+         IQR = sprintf("%0.2f", IQR)) %>% 
+  pivot_wider(names_from = "Window",
+              values_from = "IQR",
+              names_sort = T) %>% 
+  merge(Para.to.Index) %>% 
+  rename(Component = Index) %>% 
+  select(Component, everything(), -Parameter) %>% 
+  filter(Component %in% cmp) %>% 
+  mutate(Component = factor(Component, levels = cmp)) %>% 
+  arrange(Component)
+
+write.csv(table,
+          file = here('output','table', '1to5iqr.csv'))
+
+### Components - SES urban
+pmc.1yr.sescat.iqr <- dt.site.urban.ses.cat %>% 
+  inner_join(dt.pmc.1yr) %>% 
+  group_by(ses.cat) %>% 
+  summarise_at(vars(AS:ZN), ~IQR(.x)) %>% 
+  pivot_longer(cols = AS:ZN,
+               names_to = "Parameter",
+               values_to = "IQR") %>% 
+  mutate(Parameter = as.factor(Parameter),
+         SES.Cat = substr(ses.cat,1,1)) %>% 
+  select(-ses.cat)
 ```
@@
 
-out.pmc.sescat <- out.pmc.sescat %>% 
+out.pmc.sescat.upd <- out.pmc.sescat %>% 
   mutate(Parameter = gsub(".*Yr_", "", Predictor),
          Parameter = as.factor(Parameter)) %>% 
-  merge(pmc.1yr.iqr) %>% 
+  merge(pmc.1yr.sescat.iqr) %>% #pmc.1yr.iqr
   merge(Para.to.Index) %>% 
@@
 
-save(out.pmc.sescat, file = here('output','analysis','out-pmc-sescat.RDa'))
+save(out.pmc.sescat.upd, file = here('output','analysis','out-pmc-sescat-upd.RDa'))
 ```
@@
 ```
+
+```{r Output PMC Bufferzone and Exposure window}
+out.pmc.buffer.expo = data.frame()
+for (i in c("6", "12", "24")){
+  dt <- read.csv(here('output','analysis',paste('pmc-bz',i,'-15yr.csv', sep= ""))) %>% 
+    mutate(Buffer = i,
+           Window = substr(Predictor, 3,3))
+  out.pmc.buffer.expo  <-  rbind(out.pmc.buffer.expo, dt)
+}
+
+out.pmc.buffer.expo <- out.pmc.buffer.expo %>% 
+  mutate(Parameter = gsub(".*_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>% 
+  merge(pmc.xyr.5yr.iqr) %>% 
+  merge(Para.to.Index) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3)) %>% 
+  arrange(Config, Buffer) %>% 
+  select(Index, Cause, Buffer, Window, HR, HR.L, HR.U)
+
+save(out.pmc.buffer.expo, file = here('output','analysis','out-pmc-buffer-expo.RDa'))
+```

### 2021-10-07 code/data-processors/cms-data-processor.Rmd
revision

@@
 load(here('data','processed','mass-app-1yr-c2.RDa'))
+load(here('data','processed','mass-app-1yr-fac.RDa'))
 ```
@@
 
+save(dt.site.urban.ses.cat, file = here('data', 'processed', 'site-urban-ses-cat.RDa'))
+
+dt.site.urban.ses.cat %>% 
+  distinct(Site.ID) %>% 
+  group_by(ses.cat) %>% 
+  summarise(n = n())
+
+dt.site.urban.ses.cat %>% 
+  group_by(ses.cat) %>% 
+  summarise(n = n())
+
 cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
@@
 
+```{r PM Apportioned Mass with Factors}
+dt.mass <- dt.mass.app.1yr.fac %>% 
+  rename_at(vars(Biomass: Traffic), ~paste("Yr", .x, sep = "_"))
+
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.mass.fac <- dt.master.ndi.pmc %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
+  inner_join(dt.mass) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.mass.fac, 
+          file = here('data', 'processed', 'ndi-mass-fac.csv'),
+          row.names = F)
+```
+
 ```{r PM Apportioned Mass}
@@
 ```
+
+```{r}
+cmp.major <- c("SI", "NO3", "SO4")
+
+dt.pmc5 <- dt.pmc.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr5", .x, sep = "_"))
+
+dt.pmc4 <- dt.pmc.4yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr4", .x, sep = "_"))
+
+dt.pmc3 <- dt.pmc.3yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr3", .x, sep = "_"))
+
+dt.pmc2 <- dt.pmc.2yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr2", .x, sep = "_"))
+
+dt.pmc1 <- dt.pmc.1yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr1", .x, sep = "_"))
+
+dt.pmc.major <- dt.pmc1 %>% 
+  merge(dt.pmc2) %>% merge(dt.pmc3) %>% 
+  merge(dt.pmc4) %>% merge(dt.pmc5)
+
+```
+
+```{r PMC BZ6 - 1-5yr}
+dt.ses <- dt.ses.site.bz6 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.bz6.15yr <- dt.master.ndi.pmc.bz6 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc.major) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz6.15yr, 
+          file = here('data', 'processed', 'ndi-pmc-bz6-15yr.csv'),
+          row.names = F)
+```
+
+```{r PMC BZ 12 - 1-5yr}
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.bz12.15yr <- dt.master.ndi.pmc.bz12 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc.major) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz12.15yr, 
+          file = here('data', 'processed', 'ndi-pmc-bz12-15yr.csv'),
+          row.names = F)
+```
+
+```{r PMC BZ 24 - 1-5yr}
+dt.ses <- dt.ses.site.bz24 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.bz24.15yr <- dt.master.ndi.pmc.bz24 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc.major) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz24.15yr, 
+          file = here('data', 'processed', 'ndi-pmc-bz24-15yr.csv'),
+          row.names = F)
+```

### 2021-10-07 code/data-viz/forest-plots-color-shape.Rmd
revision

@@
 load(here('output','analysis','out-mass-ses.RDa'))
+load(here('output','analysis','out-mass-fac-ses.RDa'))
 #load(here('output','analysis','out-fac-base-ec.RDa'))
@@
 load(here('output','analysis','out-pmc-expo.RDa'))
+load(here('output','analysis','out-pmc-buffer-expo.RDa'))
 ```
@@
         strip.background = element_rect(fill = "#B9CFED"),
+        axis.title.x = element_text(size = 10, color = 'black'),
         axis.text.x = element_text(size = 8, color = 'black'),
-        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
+        axis.text.y = element_text(size = 8, color = 'black')
   )
@@
         strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
-        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
+        strip.text.y = element_text(size = 10, color = "black", angle = 180),
         strip.text.y.left = element_text(angle = 0),
         strip.background = element_rect(fill = "#B9CFED"),
+        axis.title.x = element_text(size = 10, color = 'black'),
         axis.text.x = element_text(size = 8, color = 'black'),
@@
         legend.key.width = unit(0.25, units = 'in'))
+```
+
+```{r set theme 4 - matrix plots}
+ggtheme.matrix <- theme_bw() + 
+  theme(panel.spacing.x = unit(0.25, 'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, face = 'bold', color = "black"),
+        strip.background = element_rect(fill = "#B9CFED"),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_text(size = 9, color = 'black'),
+        legend.position = 'right',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 9, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in')
+  )
 ```
@@
 
-```{r - Components Base}
+<br>
+
+### Components Base
+```{r - Components Base, fig.dim = c(7.5, 6.5)}
 data <- out.pmc.base %>% 
@@
 
-```{r - Components SES-Adj}
+<br>
+
+### Components SES
+```{r - Components SES-Adj, fig.dim = c(7.5, 6.5)}
 data <- out.pmc.ses %>% 
@@
 
-```{r - Factor Base}
+<br>
+
+### Factors Base
+```{r - Factor Base, fig.dim = c(7.5, 6.5)}
 data <- out.fac.base %>% 
@@
 
-```{r - Factor SES-Adj}
+<br>
+
+### Factors SES
+```{r - Factor SES-Adj, fig.dim = c(7.5, 6.5)}
 data <- out.fac.ses %>% 
@@
 
-```{r - App Mass SES-Adj}
+<br>
+
+### Mass
+```{r - App Mass SES-Adj, fig.dim = c(7.5, 6.5)}
 data <- out.mass.ses %>% 
@@
 
-```{r - Components - PM Residual}
+<br>
+
+### Mass Factor
+```{r - App Mass Factor SES-Adj, fig.dim = c(7.5, 6.5)}
+data <- out.mass.fac.ses %>% 
+  filter(Index %in% So.main,
+         Cause %in% cuz,
+         HR < 5,
+         HR.U < 5) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','mass-fac-ses.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### PM-Components Residual
+```{r - Components - PM Residual, fig.dim = c(7.5, 6.5)}
 data <- out.pmc.resid %>% 
@@
 
-```{r - Factor - PM Residual}
+<br>
+
+### PM-Factors Residual
+```{r - Factor - PM Residual, fig.dim = c(7.5, 6.5)}
 data <- out.fac.resid %>% 
@@
 
-```{r - Components Age}
+<br>
+
+### Components Age
+```{r - Components Age, fig.dim = c(7.5, 7.5)}
 data <- out.pmc.age %>% 
@@
 
-```{r - Factor Age}
+<br>
+
+### Factors Age
+```{r - Factor Age, fig.dim = c(7.5, 6.5)}
 data <- out.fac.age %>% 
@@
 
-```{r - Components Sex}
+<br>
+
+### Components Sex
+```{r - Components Sex, fig.dim = c(7.5, 7.5)}
 data <- out.pmc.sex %>% 
@@
 
-```{r - Factor Sex}
+<br>
+
+### Factors Sex
+```{r - Factor Sex, fig.dim = c(7.5, 6.5)}
 data <- out.fac.sex %>% 
@@
 
-```{r - Components Race}
+<br>
+
+### Components Race
+```{r - Components Race, fig.dim = c(7.5, 8.5)}
 data <- out.pmc.race %>% 
@@
 
-```{r - Factor Race}
+<br>
+
+### Factors Race
+```{r - Factor Race, fig.dim = c(7.5, 6.5)}
 data <- out.fac.race %>% 
@@
 
-```{r Components Urbanicity}
+<br>
+
+### Components Urbanicity
+```{r Components Urbanicity, fig.dim = c(7.5, 7.5)}
 data <- out.pmc.urbanicity %>% 
@@
 
-```{r - Factor Urbanicity}
+<br>
+
+### Factors Urbanicity
+```{r - Factor Urbanicity, fig.dim = c(7.5, 6.5)}
 data <- out.fac.urbanicity %>% 
@@
 
-```{r - Components urban}
+<br>
+
+### Components Urban
+```{r - Components urban, fig.dim = c(7.5, 6.5)}
 data <- out.pmc.urbanicity %>% 
@@
 
-```{r Components SES-Urban}
-data <- out.pmc.sescat %>% 
+<br>
+
+### Factors Urban
+```{r - Factor Urban, fig.dim = c(7.5, 6.5)}
+data <- out.fac.urbanicity %>%
+  filter(Loc.Set == "urban") %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+Plot.Single(dt = data, ggtheme = ggtheme.single) +
+ggsave(here('output','plot','fac-urban.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### Components SES-urban
+```{r Components SES-Urban, fig.dim = c(7.5, 7.5)}
+data <- out.pmc.sescat.upd %>% 
   filter(Index %in% cmp.multi,
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-sescat.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+ggsave(here('output', 'plot','pmc-sescat-upd.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
 
-```{r - Components Region}
+<br>
+
+### Components Region
+```{r - Components Region, fig.dim = c(7.5, 8.5)}
 data <- out.pmc.region %>% 
@@
 
-```{r - Factor Region}
+<br>
+
+### Factors Region
+```{r - Factor Region, fig.dim = c(7.5, 6.5)}
 data <- out.fac.region %>% 
@@
 
-```{r - Components Residual Region}
+<br>
+
+### Components Residual Region
+```{r - Components Residual Region, fig.dim = c(7.5, 8.5)}
 data <- out.pmc.resid.region %>% 
@@
 
-```{r - Components BRFSS}
+<br>
+
+### Components BRFSS
+```{r - Components BRFSS, fig.dim = c(7.5, 7.5)}
 data <- out.pmc.brfss %>% 
@@
 
-```{r Components Buffer}
+<br>
+
+### Components Buffer
+```{r Components Buffer, fig.dim = c(7.5, 8.5)}
 data <- out.pmc.buffer %>% 
@@
 
-```{r Components Exposure window}
+<br>
+
+### Components Exposure Window
+```{r Components Exposure window, fig.dim = c(7.5, 9.5)}
 data <- out.pmc.expo %>% 
@@
 ```
+
+```{r Components Buffer & Exposure window}
+dt <- out.pmc.buffer.expo %>% 
+  arrange(Buffer, Window) %>% 
+  mutate(Cause = factor(Cause, levels = rev(cuz)),
+         Buffer = ifelse(Buffer == 6, "6-mile",
+                         ifelse(Buffer == 12, "12-mile", "24-mile")),
+         Buffer = factor(Buffer, levels = c("6-mile", "12-mile", "24-mile")),
+         Window = ifelse(Window == 1, "1-yr",
+                         ifelse(Window == 2, "2-yr",
+                                ifelse(Window == 3, "3-yr",
+                                       ifelse(Window == 4, "4-yr", "5-yr")))),
+         Window = as.factor(Window),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16))) #1-null # 16-sigpos
+
+Plot.Matrix(dt = dt, cmp = "SO4", title = expression(SO[4]^"2-"), 
+            ggtheme = ggtheme.matrix) +
+ggsave(here('output', 'plot','SO4-buffer-expo.png'), width = 9, height = 8)
+
+Plot.Matrix(dt = dt, cmp = "NO3", title = expression(NO[3]^"-"), 
+            ggtheme = ggtheme.matrix) +
+ggsave(here('output', 'plot','NO3-buffer-expo.png'), width = 9, height = 8)
+
+Plot.Matrix(dt = dt, cmp = "Si", title = "Si", 
+            ggtheme = ggtheme.matrix) +
+ggsave(here('output', 'plot','Si-buffer-expo.png'), width = 9, height = 8)
+```

### 2021-10-07 code/data-viz/forest-plots-color.Rmd
revision

@@
 
-plot.labs <- c("24-miles", "12-miles", "6-miles") 
+plot.labs <- c("24-mile", "12-mile", "6-mile") 
 plot.cols <- c("#EB2226", "#075AAA", "#01742F")

### 2021-10-07 code/data-viz/manuscript-figures.Rmd
revision

--- 2021-06-03 code/data-viz/manuscript-figures.Rmd
@@
 
-### Components Age
-```{r - Components Age, fig.dim = c(7.5, 7.5)}
-data <- out.pmc.age %>% 
-  filter(Index %in% cmp.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp.multi),
-         Tag = ifelse(Age == "LE75", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Age == "M75"), 1,
-                      ifelse((sig == 15 & Age == "M75"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-levels(data$Index) <- cmp.multi.labels
-
-plot.labs <- c("> 75 years", "65-75 years")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-Index.labels <- cmp.multi.labels
-
-Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-age.jpeg'), width = 7.5, height = 7.5, dpi = 600)
-```
-
-<br>
-
-### Factors Age
-```{r - Factor Age, fig.dim = c(7.5, 6.5)}
-data <- out.fac.age %>% 
-  filter(Index %in% So.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So.multi),
-         Tag = ifelse(Age == "LE75", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Age == "M75"), 1,
-                      ifelse((sig == 15 & Age == "M75"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-plot.labs <- c("> 75 years", "65-75 years")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-age.jpeg'), width = 7.5, height = 6.5, dpi = 600)
-```
-
-<br>
-
-### Components Sex
-```{r - Components Sex, fig.dim = c(7.5, 7.5)}
-data <- out.pmc.sex %>% 
-  filter(Index %in% cmp.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = cmp.multi),
-         Tag = ifelse(Sex == "F", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Sex == "M"), 1,
-                      ifelse((sig == 15 & Sex == "M"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-levels(data$Index) <- cmp.multi.labels
-
-plot.labs <- c("Male", "Female")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-Index.labels <- cmp.multi.labels
-
-Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','pmc-sex.jpeg'), width = 7.5, height = 7.5, dpi = 600)
-```
-
-<br>
-
-### Factors Sex
-```{r - Factor Sex, fig.dim = c(7.5, 6.5)}
-data <- out.fac.sex %>% 
-  filter(Index %in% So.multi,
-         Cause %in% cuz) %>% 
-  mutate(Cause = factor(Cause, levels = cuz),
-         Index = factor(Index, levels = So.multi),
-         Tag = ifelse(Sex == "F", "b", "a"),
-         Tag = as.factor(Tag),
-         sig = ifelse(HR.U < 1 , 15, #15-prtc
-                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
-         sig = ifelse((sig == 0 & Sex == "M"), 1,
-                      ifelse((sig == 15 & Sex == "M"),16, sig)),
-         sig = as.integer(sig)
-  )
-
-plot.labs <- c("Male", "Female")
-plot.cols <- c("#EB2226", "#075AAA")
-guide.shapes <- c(15,16)
-
-Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','fac-sex.jpeg'), width = 7.5, height = 6.5, dpi = 600)
-```
-
-<br>
-
-### Figure x - Components Race
+### Figure S3 - Components Race
 ```{r - Components Race, fig.dim = c(7.5, 8.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n =1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S3.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Factors Race
+### Figure S4 - Factors Race
 ```{r - Factor Race, fig.dim = c(7.5, 6.5)}
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S4.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Urban
+### Figure S5 - Components Age
+```{r - Components Age, fig.dim = c(7.5, 7.5)}
+data <- out.pmc.age %>% 
+  filter(Index %in% cmp.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp.multi),
+         Tag = ifelse(Age == "LE75", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Age == "M75"), 1,
+                      ifelse((sig == 15 & Age == "M75"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+levels(data$Index) <- cmp.multi.labels
+
+plot.labs <- c("> 75 years", "65-75 years")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
+
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','Figure S5.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+```
+
+<br>
+
+### Figure S6 - Factors Age
+```{r - Factor Age, fig.dim = c(7.5, 6.5)}
+data <- out.fac.age %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Age == "LE75", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Age == "M75"), 1,
+                      ifelse((sig == 15 & Age == "M75"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+plot.labs <- c("> 75 years", "65-75 years")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
+
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
+ggsave(here('output', 'plot','Figure S6.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### Figure S7 - Components Sex
+```{r - Components Sex, fig.dim = c(7.5, 7.5)}
+data <- out.pmc.sex %>% 
+  filter(Index %in% cmp.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = cmp.multi),
+         Tag = ifelse(Sex == "F", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Sex == "M"), 1,
+                      ifelse((sig == 15 & Sex == "M"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+levels(data$Index) <- cmp.multi.labels
+
+plot.labs <- c("Male", "Female")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
+Index.labels <- cmp.multi.labels
+
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
+ggsave(here('output', 'plot','Figure S7.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+```
+
+<br>
+
+### Figure S8 - Factors Sex
+```{r - Factor Sex, fig.dim = c(7.5, 6.5)}
+data <- out.fac.sex %>% 
+  filter(Index %in% So.multi,
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.multi),
+         Tag = ifelse(Sex == "F", "b", "a"),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Sex == "M"), 1,
+                      ifelse((sig == 15 & Sex == "M"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+plot.labs <- c("Male", "Female")
+plot.cols <- c("#EB2226", "#075AAA")
+guide.shapes <- c(15,16)
+
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
+ggsave(here('output', 'plot','Figure S8.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### Figure S9 - Components Urban
 ```{r - Components urban, fig.dim = c(7.5, 6.5)}
@@
 Plot.Single.lab(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+ggsave(here('output','plot','Figure S9.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 
-### Figure x - Factors Urban
+### Figure S10 - Factors Urban
 ```{r - Factor Urban, fig.dim = c(7.5, 6.5)}
@@
 Plot.Single(dt = data, ggtheme = ggtheme.single) +
-ggsave(here('output','plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+ggsave(here('output','plot','Figure S10.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 
-### Figure x - Components SES-urban
+### Figure S11 - Components SES-urban
 ```{r Components SES-Urban, fig.dim = c(7.5, 7.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S11.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Region
+### Figure S12 - Components Region
 ```{r - Components Region, fig.dim = c(7.5, 8.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S12.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Factors Region
+### Figure S13 - Factors Region
 ```{r - Factor Region, fig.dim = c(7.5, 6.5)}
@@
 Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S13.jpeg'), width = 7.5, height = 6.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Residual Region
+### Figure S14 - Components Residual Region
 ```{r - Components Residual Region, fig.dim = c(7.5, 8.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'),width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S14.jpeg'),width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Components BRFSS
+### Figure S15 - Components BRFSS
 ```{r - Components BRFSS, fig.dim = c(7.5, 7.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 7.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S15.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Buffer
+### Figure S16 - Components Buffer
 ```{r Components Buffer, fig.dim = c(7.5, 8.5)}
@@
 
-plot.labs <- c("24-miles", "12-miles", "6-miles")
+plot.labs <- c("24-mile", "12-mile", "6-mile")
 plot.cols <- c("#EB2226", "#075AAA", "#01742F")
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 8.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S16.jpeg'), width = 7.5, height = 8.5, dpi = 600)
 ```
@@
 
-### Figure x - Components Exposure Window
+### Figure S17 - Components Exposure Window
 ```{r Components Exposure window, fig.dim = c(7.5, 9.5)}
@@
 Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) + 
-ggsave(here('output', 'plot','Figure x.jpeg'), width = 7.5, height = 9.5, dpi = 600)
+ggsave(here('output', 'plot','Figure S17.jpeg'), width = 7.5, height = 9.5, dpi = 600)
 ```
+
+### Figure S18 & S19 & S20
+```{r Components Buffer & Exposure window}
+dt <- out.pmc.buffer.expo %>% 
+  arrange(Buffer, Window) %>% 
+  mutate(Cause = factor(Cause, levels = rev(cuz)),
+         Buffer = ifelse(Buffer == 6, "6-mile",
+                         ifelse(Buffer == 12, "12-mile", "24-mile")),
+         Buffer = factor(Buffer, levels = c("6-mile", "12-mile", "24-mile")),
+         Window = ifelse(Window == 1, "1-yr",
+                         ifelse(Window == 2, "2-yr",
+                                ifelse(Window == 3, "3-yr",
+                                       ifelse(Window == 4, "4-yr", "5-yr")))),
+         Window = as.factor(Window),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16))) #1-null # 16-sigpos
+
+Plot.Matrix(dt = dt, cmp = "SO4", title = expression(SO[4]^"2-"), 
+            ggtheme = ggtheme.matrix) +
+ggsave(here('output', 'plot','Figure S18.jpeg'), width = 9, height = 8)
+
+Plot.Matrix(dt = dt, cmp = "NO3", title = expression(NO[3]^"-"), 
+            ggtheme = ggtheme.matrix) +
+ggsave(here('output', 'plot','Figure S19.jpeg'), width = 9, height = 8)
+
+Plot.Matrix(dt = dt, cmp = "Si", title = "Si", 
+            ggtheme = ggtheme.matrix) +
+ggsave(here('output', 'plot','Figure S20.jpeg'), width = 9, height = 8)
+```

### 2021-10-07 code/data-viz/manuscript-tables.Rmd
revision

@@
 ---
-title: "Tables for PM2.5 Components Paper Manuscript"
+title: "Tables for PM2.5 constituents Paper Manuscript"
 author: "Fatemeh Kazemi"
@@
 ```{r - Parameter/Factor to Index}
-### Components
+### constituents
 Para.to.Index <- tribble(
@@
 ft <- fontsize(ft, size = 10)
-ft <- set_caption(ft, caption = "Table 2. Daily concentrations of PM2.5 and its components, mean ± standard deviation, nationwide, by region and urbanicity.")
+ft <- set_caption(ft, caption = "Table 2. Daily concentrations of PM2.5 and its constituents, mean ± standard deviation, nationwide, by region and urbanicity.")
 ft <- fontsize(ft, i = 1, size = 12, part = "header")
@@
 
-### Components
+### constituents
 pmc.1yr.iqr <- dt.pmc.site.ndi %>% 
@@
 
-### Factors excluding EC
+### Factors
 fac.1yr.iqr <- dt.pmc.site.ndi %>% 
@@
 
-table <- full_join(pmc.1yr.iqr, fac.1yr.iqr) %>% 
-  select(Source, IQR.2, Component, IQR)
+### Factors Mass
+fac.mass.1yr.iqr <- dt.pmc.site.ndi %>% 
+  select(Site.ID) %>% 
+  inner_join(dt.mass.app.1yr.fac) %>% 
+  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
+  pivot_longer(cols = Biomass:Traffic,
+               names_to = "Parameter",
+               values_to = "IQR.2")%>% 
+  mutate(IQR.2 = sprintf("%0.2f", IQR.3)) %>% 
+  mutate(Parameter = as.factor(Parameter)) %>% 
+  rename(Source = Index) %>% 
+  select(Source, everything(), -Parameter)
+
+table <- full_join(pmc.1yr.iqr, fac.1yr.iqr, fac.mass.1yr.iqr) %>% 
+  select(Source, IQR.2, IQR.3, Component, IQR)
 
 ft <- flextable(table)
-ft <- merge_v(ft, j = c("Source", "IQR.2"))
+ft <- merge_v(ft, j = c("Source", "IQR.2", "IQR.3"))
 ft <- theme_vanilla(ft)
-ft <- vline(ft, j = c('IQR.2'))
+ft <- vline(ft, j = c('IQR.2', 'IQR.3'))
 ft <- padding(ft, padding = 0)
 ft <- fontsize(ft, size = 10)
-ft <- set_caption(ft, caption = "Table S2. IQR for 1-year moving average of source factors, PM2.5 and its components")
+ft <- set_caption(ft, caption = "Table S2. IQR for 1-year moving average of source factors, PM2.5 and its constituents")
 ft <- fontsize(ft, i = 1, size = 12, part = "header")
@@
 
-### Figure 1 - Components SES
+### Figure 1 - constituents SES
 ```{r}
@@
                  cpt = "Table S3.
-Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components.", ftnt = "Continued ...
+Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S3.
-Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 
-### Figure 3 - PM-Components Residual
+### Figure 3 - PM-constituents Residual
 ```{r}
@@
                  cpt = "Table S5.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S5.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 
-### Figure 5 - Components Race
+### Figure 5 - constituents Race
 ```{r}
@@
                  cpt = "Table S7.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by race.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S7.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by race., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 
-### Figure 7 - Components Age
+### Figure 7 - constituents Age
 ```{r}
@@
                  cpt = "Table S9.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: By age.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S9.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: By age., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 
-### Figure 9 - Components Sex
+### Figure 9 - constituents Sex
 ```{r}
@@
                  cpt = "Table S11.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by sex.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S11.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by sex., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 
-### Figure 11 - Components SES-urban
+### Figure 11 - constituents SES-urban
 ```{r}
@@
 doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.top.row,
-                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas.", ftnt = "Continued ...")
+                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by income category in urban areas.", ftnt = "Continued ...")
 doc <- Table.Multi.sescat(dt = out.pmc.sescat, cmp = cmp.multi, cuz = cuz.bot.row,
-                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by income category in urban areas., Continued", ftnt = "")
+                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by income category in urban areas., Continued", ftnt = "")
 ```
 
-### Figure S3 - Components Urban
+### Figure S3 - constituents Urban
 ```{r}
@@
                  cpt = "Table S14.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents in urban areas.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S14.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents in urban areas., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 
-### Figure S5 - Components Region
+### Figure S5 - constituents Region
 ```{r}
@@
                  cpt = "Table S16.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by region.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S16.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 
-### Figure S7 - Components Residual Region
+### Figure S7 - constituents Residual Region
 ```{r}
@@
                  cpt = "Table S18.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents: by region.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S18.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents: by region., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
-### Figure S8 - Components BRFSS
+### Figure S8 - constituents BRFSS
 ```{r}
@@
                  cpt = "Table S19.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S19.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents: Base versus BRFSS-adjusted models for the subset of monitors with BRFSS data., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
-### Figure S9 - Components Buffer
+### Figure S9 - constituents Buffer
 ```{r}
@@
                  cpt = "Table S20.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its components exposures.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its constituents exposures.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S20.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific components: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its components exposures., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in total PM2.5 and in PM2.5 minus variability from specific constituents: using 6-, 12- and 24-mile buffer zones to assess PM2.5 and its constituents exposures., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
 
-### Figure S10 - Components Exposure Window
+### Figure S10 - constituents Exposure Window
 ```{r}
@@
                  cpt = "Table S21.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its components for the subset of the monitors with complete data of 1 to 5 year moving average.", ftnt = "Continued ...
+Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its constituents for 2005-2008 with complete data of 1 to 5 year moving average.", ftnt = "Continued ...
 Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
@@
                  cpt = "Table S21.
-Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its components for the subset of the monitors with complete data of 1 to 5 year moving average., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+Mortality Hazard ratios (95% CI) associated with an IQR increase in 1- to 5- years PM2.5 moving average exposure and its constituents for 2005-2008 with complete data of 1 to 5 year moving average., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
 ```
@@
 ```
+
+### Figure S18, S19, S20 - constituents Buffer & Expsoure Window
+```{r}
+doc <- read_docx()
+cmp.major <- c("Si", "NO3", "SO4")
+out.pmc.buffer.expo <- out.pmc.buffer.expo %>% 
+  mutate(Buffer = ifelse(Buffer == "6", "6-mile",
+                         ifelse(Buffer == "12", "12-mile", "24-mile")),
+         Buffer = factor(Buffer, levels = c("6-mile", "12-mile", "24-mile")),
+         Window = ifelse(Window == "1", "1-yr",
+                         ifelse(Window == "2", "2-yr",
+                                ifelse(Window == "3", "3-yr",
+                                       ifelse(Window == "4", "4-yr", "5-yr")))))
+
+doc <- Table.Multi.buffer.expo(dt = out.pmc.buffer.expo, cmp = cmp.major, cuz = cuz.top.row,
+                 cpt = "Table S22.
+Mortality Hazard ratiosa (95% CI) associated with an IQR increase in 1- to 5- years Si, NO3 and SO42- moving average exposure for 2005 to 2008 with complete data of 1 to 5 year moving average: using 6-, 12- and 24-mile buffer zones to assess exposures.", ftnt = "Continued ...
+Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+doc <- Table.Multi.buffer.expo(dt = out.pmc.buffer.expo, cmp = cmp.major, cuz = cuz.bot.row,
+                 cpt = "Table S22.
+Mortality Hazard ratiosa (95% CI) associated with an IQR increase in 1- to 5- years Si, NO3 and SO42- moving average exposure for 2005 to 2008 with complete data of 1 to 5 year moving average: using 6-, 12- and 24-mile buffer zones to assess exposures., Continued", ftnt = "Hazard ratios are age, sex, race and site stratified and adjusted for SES.")
+```
+
+```{r}
+print(doc, target = here('output','table','supplement-tables-revision.docx'))
+```

### 2021-10-07 code/data-viz/forest-plot-functions.R

@@ -229,3 +229,45 @@ Plot.Multi.Color <- function(dt, ggtheme, n) {
   return(p)
 }
 
+
+
+
+###############################################################################
+############################  Plot.Matrix  ###############################
+###############################################################################
+
+### Function *** Plot.Matrix ***
+# Plots subgroups with different colors
+# Function Arguments: 
+# dt : dataset that contains the HRs for each exposure, outcome and subgroups
+# cmp : component of interest
+# title : 
+# ggtheme : customized theme
+
+
+### Matrix Plot Function
+Plot.Matrix <- function(dt, cmp, title, ggtheme) {
+  
+  p <- ggplot(data = dt %>%  filter(Index == cmp),
+              aes(x = HR, xmin = HR.L, xmax = HR.U, y = Cause)) +
+    geom_vline(xintercept = 1, linetype = 2, color = "black") +
+    geom_segment(aes(x = HR.L, xend = HR.U, y = Cause, yend = Cause, color = Cause),
+                 size = 0.25, show.legend = T) + 
+    geom_point(aes(x = HR, y = Cause, shape = sig, color = Cause),
+               size = 2, show.legend = T) + 
+    scale_shape_identity() +
+    #scale_size_identity() +
+    #scale_color_manual(
+    # labels = plot.labs, 
+    #values = plot.cols) +
+    scale_color_tableau(palette = "Tableau 10") +
+    labs(x = "Hazard Ratio (95% CI) \n Solid shapes (point estimates) indicate statistically significant results at the 0.05 level", y = "") +
+    ggtitle(title) +
+    facet_grid(Buffer ~ Window,  scales = "fixed", switch = 'y',
+               shrink = T, space = 'fixed') +
+    ggtheme.matrix + 
+    guides(color = guide_legend(ncol = 1, byrow = T, reverse = T,
+                                direction = "vertical"))
+  return(p)
+}
+

### 2021-10-07 code/data-viz/manuscript-table-functions.R

@@ -325,3 +325,39 @@ Table.Multi.expo <- function(dt, cmp, cuz, cpt, ftnt){
   
   return(doc)
 }
+
+
+
+
+
+
+
+# Buffer & Exposure Group Table Function ------------------------------------------------
+Table.Multi.buffer.expo <- function(dt, cmp, cuz, cpt, ftnt){
+  dt <- dt %>% 
+    mutate(Index = factor(Index, levels = cmp),
+           Cause = factor(Cause, levels = cuz)) %>% 
+    mutate_at(.vars = c("HR", "HR.L", "HR.U"), ~sprintf('%.3f', .x)) %>% 
+    mutate(HR.Sum = paste(HR," (", HR.L,", ", HR.U,")", sep = "")) %>% 
+    select(-(HR:HR.U)) %>% 
+    drop_na() %>% 
+    pivot_wider(names_from = "Cause",
+                values_from = "HR.Sum") %>% 
+    arrange(factor(Index, levels = cmp), Buffer, Window)
+  
+  ft <- flextable(dt)
+  ft <- merge_v(ft, j = c('Index', 'Buffer', 'Window'))
+  ft <- theme_vanilla(ft)
+  ft <- vline(ft, j = c('Index', 'Buffer', 'Window'))
+  ft <- padding(ft, padding = 0)
+  ft <- fontsize(ft, size = 12)
+  ft <- set_caption(ft, caption = cpt)
+  ft <- fontsize(ft, i = 1, size = 12, part = "header")
+  ft <- autofit(ft)
+  
+  doc <- body_add_flextable(doc, value = ft, split = T)
+  doc <- body_add_par(doc, ftnt, style = "Normal")
+  body_add(doc, run_pagebreak())
+  
+  return(doc)
+}

### 2021-10-07 code/data-analysis/config-file-generator.Rmd
Revision

@@
 ```{r List of Sources}
-so <- c("Yr_Biomass","Yr_Coal","Yr_Metal","Yr_Oil",
+so <- c("Yr_Biomass","Yr_Coal","Yr_Metals","Yr_Oil",
          "Yr_Salt","Yr_Soil","Yr_Steel","Yr_Traffic")
@@
 
+```{r ses adj. model for apportioned mass factor}
+dataname <- "ndi-mass-fac.csv"
+expo <- so
+
+for (i in seq(1,length(expo),1)){
+  filenames <- c( tempfile())
+  for( f in  filenames ){
+    cat(config.ses, file=f)
+    x <- readLines(f)
+    y <- gsub("dataset", dataname, x)
+    z <- gsub("exposure", expo[i], y)
+    for (j in seq(1,length(cuz.sub),1)){
+      w <- gsub("outcome", cuz.sub[j], z)
+      cat(w, file=f, sep="\n")
+      k=j+length(cuz.sub)*(i-1)
+      writeLines(w, here('config-files','mass-fac-ses', paste(k,'.txt', sep = "")))
+    }
+  }
+  file.remove(f)
+  }
+```
+
 ```{r ses adj. model for components - bz6 & 1-5yr}

### 2021-10-07 code/data-analysis/output-cleaning.Rmd
Revision

@@
 load(here('data','processed','pmc-sub-5yr.RDa'))
-load(here('data','processed','mass-app-1yr-c2.RDa'))
+#load(here('data','processed','mass-app-1yr-c2.RDa'))
+load(here('data','processed','mass-app-1yr-fac.RDa'))
 load(here('data','processed','site-urban-ses-cat.RDa'))
@@
 mass.1yr.iqr <- dt.mass.app.1yr.c2 %>% 
+  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
+  pivot_longer(cols = Biomass:Traffic,
+               names_to = "Parameter",
+               values_to = "IQR")%>% 
+  mutate(Parameter = as.factor(Parameter))
+
+### Source Apportioned PM Mass with Factors
+mass.fac.1yr.iqr <- dt.mass.app.1yr.fac %>% 
   summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
@@
 
-```{r Output Factors Ex. EC Base}
+```{r Output Factors Base}
 out.fac.base <- read.csv(here('output','analysis','fac-base.csv')) %>% 
@@
 
-```{r Output Factors Ex. EC SES-Adj}
+```{r Output Factors SES-Adj}
 out.fac.ses <- read.csv(here('output','analysis','fac-ses.csv')) %>% 
@@
 
-```{r Output Factors Base}
+```{r Output Factors Inc. EC Base}
 out.fac.ec.base <- read.csv(here('output','analysis','fac-ec-base.csv')) %>% 
@@
 
-```{r Output Factors SES-Adj}
+```{r Output Factors Factors Inc. EC SES-Adj}
 out.fac.ec.ses <- read.csv(here('output','analysis','fac-ec-ses.csv')) %>% 
@@
 save(out.mass.ses, file = here('output','analysis','out-mass-ses.RDa'))
+```
+
+```{r Output App Mass Factor SES-Adj}
+out.mass.fac.ses <- read.csv(here('output','analysis','mass-fac-ses.csv')) %>%
+  mutate(Parameter = gsub(".*Yr_", "", Predictor),
+         Parameter = as.factor(Parameter)) %>%  
+  merge(mass.fac.1yr.iqr) %>% 
+  merge(Outcome.to.Cause) %>% 
+  mutate(HR = round(exp(Coef * IQR),3),
+         HR.L = round(exp((Coef-1.96*std) * IQR),3),
+         HR.U = round(exp((Coef+1.96*std) * IQR),3),
+         Index = Parameter) %>% 
+  arrange(Config) %>% 
+  select(Index, Cause, HR, HR.L, HR.U)
+
+save(out.mass.fac.ses, file = here('output','analysis','out-mass-fac-ses.RDa'))
 ```
@@
 ```{r Output Factor Region}
-out.fac.region = data.frame()
+out.fac.region.2 = data.frame()
 for (i in c("west", "midwest", "south", "northeast")){
@@
     mutate(Region = i)
-  out.fac.region  <-  rbind(out.fac.region, dt)
+  out.fac.region.2  <-  rbind(out.fac.region.2, dt)
 }
 
-out.fac.region <- out.fac.region %>% 
+out.fac.region.2 <- out.fac.region.2 %>% 
   rename(Parameter = Predictor) %>% 

### 2021-10-17 code/data-analysis/output-cleaning.Rmd
Revision

@@
   select(-ses.cat)
+
+table.ses <- pmc.1yr.sescat.iqr %>% 
+  mutate(IQR = ifelse(Parameter %in% c("PM", "NO3", "OC", "SO4"), IQR, IQR * 1000),
+         IQR = sprintf("%0.2f", IQR)) %>% 
+  pivot_wider(names_from = "SES.Cat",
+              values_from = "IQR",
+              names_sort = T) %>% 
+  merge(Para.to.Index) %>% 
+  rename(Component = Index) %>% 
+  select(Component, everything(), -Parameter) %>% 
+  filter(Component %in% cmp) %>% 
+  mutate(Component = factor(Component, levels = cmp)) %>% 
+  arrange(Component) %>% 
+  select(Component, L, M, H)
+
+write.csv(table.ses,
+          file = here('output','table', 'sescatiqr.csv'))
 ```

### 2021-10-17 code/data-processors/cms-data-processor.Rmd
Revision

--- 2021-02-22 code/data-processors/cms-data-processor.Rmd
@@
 cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
-             "PB", "PM", "SI", "SO4", "V", "ZN")
+             "PB", "PM", "SI", "SO4", "V", "ZN", "K")
 
@@
 ```
+
+```{r}
+cmp.major <- c("SI", "NO3", "SO4")
+
+dt.pmc5 <- dt.pmc.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr5", .x, sep = "_"))
+
+dt.pmc4 <- dt.pmc.4yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr4", .x, sep = "_"))
+
+dt.pmc3 <- dt.pmc.3yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr3", .x, sep = "_"))
+
+dt.pmc2 <- dt.pmc.2yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr2", .x, sep = "_"))
+
+dt.pmc1 <- dt.pmc.1yr.5yr %>% 
+  select(Site.ID, Year, Month, cmp.major) %>% 
+  rename_at(cmp.major, ~paste("Yr1", .x, sep = "_"))
+
+dt.pmc.major <- dt.pmc1 %>% 
+  merge(dt.pmc2) %>% merge(dt.pmc3) %>% 
+  merge(dt.pmc4) %>% merge(dt.pmc5)
+
+```
+
+```{r PMC BZ6 - 1-5yr}
+dt.ses <- dt.ses.site.bz6 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.bz6.15yr <- dt.master.ndi.pmc.bz6 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc.major) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz6.15yr, 
+          file = here('data', 'processed', 'ndi-pmc-bz6-15yr.csv'),
+          row.names = F)
+```
+
+```{r PMC BZ 12 - 1-5yr}
+dt.ses <- dt.ses.site.bz12 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.bz12.15yr <- dt.master.ndi.pmc.bz12 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc.major) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+write.csv(dt.ndi.pmc.bz12.15yr, 
+          file = here('data', 'processed', 'ndi-pmc-bz12-15yr.csv'),
+          row.names = F)
+```
+
+```{r PMC BZ 24 - 1-5yr}
+dt.ses <- dt.ses.site.bz24 %>% 
+  mutate(ses = SES.Zip.Norm) %>% 
+  select(Site.ID, Year, ses)
+
+dt.ndi.pmc.bz24.15yr <- dt.master.ndi.pmc.bz24 %>% 
+  mutate(StrID = paste(age, sex, race)) %>% 
+  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc) %>% 
+  inner_join(dt.pmc.major) %>% 
+  inner_join(dt.ses) %>% 
+  rename(SiteID = Site.ID)
+
+view(dt.ndi.pmc.bz24.15yr)
+write.csv(dt.ndi.pmc.bz24.15yr, 
+          file = here('data', 'processed', 'ndi-pmc-bz24-15yr.csv'),
+          row.names = F)
+```

### 2021-10-17 code/data-viz/forest-plots-color-shape.Rmd
Revision

@@
 
-```{r set theme 4 - matrix plots}
+```{r set theme 4 - components - effect modification, subgroups, multiple groups plots}
+ggtheme.multi.3 <- theme_classic() + 
+  theme(panel.spacing.x = unit(0.5,'lines'),
+        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0,0.25),'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
+        strip.text.y = element_text(size = 10, color = "black", angle = 180),
+        strip.text.y.left = element_text(angle = 0),
+        strip.background = element_rect(fill = "#B9CFED"),
+        axis.title.x = element_text(size = 10, color = 'black'),
+        axis.text.x = element_text(size = 8, color = 'black'),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = 'bottom',
+        legend.title = element_blank(),
+        legend.text = element_text(size = 10, face = "bold"),
+        legend.key.width = unit(0.25, units = 'in'))
+```
+
+```{r set theme 5 - matrix plots}
 ggtheme.matrix <- theme_bw() + 
@@
 
+cuz.g.abs <- c("All-Cause", "Cardiovascular", "Respiratory", "Lung Cancer")
+
 cmp.main <- c("Mn", "Fe", "V", "Ni", "Cl", "Na", "SO4", "Se", 
@@
          "Biomass", "Traffic", "Metals", "Soil")
+
 So.multi <- c("Soil", "Metals", "Traffic",
@@
                           expression("-SO"[4]^{"2-"}), "-Ni", "-V")
+```
+
+<br>
+
+# Ghraphical Abs
+```{r - Factor SES-Adj, fig.dim = c(7.5, 6.5)}
+data <- out.fac.ses %>% 
+  filter(Index %in% So.main,
+         Cause %in% cuz.g.abs) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = So.main),
+         sig = ifelse(HR.U < 1 , 16, #16-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
+  )
+
+plot.cols <- c("#EB2226")
+
+p <- ggplot(data, aes(x = HR, xmin = HR.L, xmax = HR.U, y = Index)) +
+    geom_vline(xintercept = 1, linetype = 2, color = "black") +
+    geom_segment(aes(x = HR.L, xend = HR.U, y = Index, yend = Index),
+                 color = plot.cols, size = 0.25, show.legend = F) + 
+    geom_point(aes(x = HR, y = Index, shape = sig), 
+               color = plot.cols, size = 1.5, show.legend = F) +
+  labs(x = "HR (95% CI) per IQR Increase", y = expression(paste("Source-Related ", PM[2.5])),
+       title = expression(paste("Association of Long-Term Source-Related ", PM[2.5], " Exposure and Cause-Specific Mortality"))) +
+    scale_shape_identity() +
+    facet_wrap( ~ Cause, ncol = 5, scales = "fixed") +
+   theme_bw() + 
+    theme(panel.spacing.x = unit(0.5, 'lines'),
+        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
+        strip.text.x = element_text(face = 'bold', color = "black"),
+        strip.background = element_rect(fill = "#B9CFED"),
+        axis.title = element_text(size = 12, color = 'black'),
+        axis.text = element_text(size = 9, color = 'black'),
+        plot.title = element_text(size = 12, face = 'bold', color = 'black', hjust = 0.5, vjust = 2))
+
+annotate_figure(p, 
+                bottom = text_grob(expression(paste("IQRs in μg/",m^3, ": Soil = 0.29, Metals = 0.07, Traffic = 4.09, Biomass = 0.13, Coal = 4.36, Salt = 0.03, Oil = 0.03, Steel = 0.03")), size = 8)) +
+  ggsave(here('output','plot','graphical-abstract.jpeg'), width = 9.5, height = 4, dpi = 600)
 ```
@@
 
+### Components Region
+```{r - Components Region, fig.dim = c(7.5, 8.5)}
+data <- out.pmc.region %>% 
+  filter(Index %in% c(cmp.multi, "K"),
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = c(cmp.multi, "K")),
+         Tag = ifelse(Region == "west", "d",
+                      ifelse(Region == "midwest", "c",
+                             ifelse(Region == "south", "b", "a"))),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Region == "northeast"), 5,
+                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
+         sig = ifelse((sig == 0 & Region == "south"), 2,
+                      ifelse((sig == 15 & Region == "south"),17, sig)),
+         sig = ifelse((sig == 0 & Region == "midwest"), 1,
+                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+levels(data$Index) <- c(cmp.multi.labels, "K")
+
+plot.labs <- c("Northeast", "South", "Midwest", "West")
+plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
+guide.shapes <- c(15,16,17,18)
+Index.labels <- cmp.multi.labels
+
+Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.3, n = 1) +
+ggsave(here('output', 'plot','pmc-region-with-K.jpeg'), width = 7.5, height = 9.5, dpi = 600)
+```
+
+<br>
+
 ### Factors Region
@@
 ggsave(here('output', 'plot','fac-region.jpeg'), width = 7.5, height = 6.5, dpi = 600)
+```
+
+<br>
+
+### Factors Region
+```{r - Factor Region, fig.dim = c(7.5, 6.5)}
+data <- out.fac.region %>% 
+  filter(Index %in% c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Oil"),
+         Cause %in% cuz) %>% 
+  mutate(Cause = factor(Cause, levels = cuz),
+         Index = factor(Index, levels = c("Soil", "Metals", "Traffic", "Biomass", "Coal", "Oil")),
+  Tag = ifelse(Region == "west", "d",
+               ifelse(Region == "midwest", "c",
+                      ifelse(Region == "south", "b", "a"))),
+         Tag = as.factor(Tag),
+         sig = ifelse(HR.U < 1 , 15, #15-prtc
+                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
+         sig = ifelse((sig == 0 & Region == "northeast"), 5,
+                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
+         sig = ifelse((sig == 0 & Region == "south"), 2,
+                      ifelse((sig == 15 & Region == "south"),17, sig)),
+         sig = ifelse((sig == 0 & Region == "midwest"), 1,
+                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
+         sig = as.integer(sig)
+  )
+
+plot.labs <- c("Northeast", "South", "Midwest", "West")
+plot.cols <- c("#FF8200", "#075AAA", "#EB2226", "#01742F")
+guide.shapes <- c(15,16,17,18)
+
+Plot.Multi(dt = data, ggtheme = ggtheme.multi.2, n = 1) +
+ggsave(here('output', 'plot','fac-region-with-Biomass.jpeg'), width = 7.5, height = 7.5, dpi = 600)
 ```

### 2021-10-17 code/data-viz/manuscript-tables.Rmd
Revision

@@
 load(here('output','analysis','out-pmc-sescat.RDa'))
+load(here('output','analysis','out-pmc-sescat-upd.RDa'))
 load(here('output','analysis','out-pmc-region.RDa'))
@@
 
+### Figure 11 - constituents SES-urban - updated
+```{r}
+out.pmc.sescat.upd <- out.pmc.sescat.upd %>% 
+  mutate(SES.Cat = ifelse(SES.Cat == "L", "Low",
+                          ifelse(SES.Cat == "M", "Middle", "High")),
+         SES.Cat = factor(SES.Cat, levels = c("Low", "Middle", "High")))
+
+doc <- Table.Multi.sescat(dt = out.pmc.sescat.upd, cmp = cmp.multi, cuz = cuz.top.row,
+                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by income category in urban areas.", ftnt = "Continued ...")
+doc <- Table.Multi.sescat(dt = out.pmc.sescat.upd, cmp = cmp.multi, cuz = cuz.bot.row,
+                 cpt = "Table S13. Mortality Hazard ratios (95% CI) associated with an IQR increase in PM2.5 and its constituents: by income category in urban areas., Continued", ftnt = "")
+```
+
 ### Figure S3 - constituents Urban
@@
 ```{r}
-print(doc, target = here('output','table','supplement-tables-revision.docx'))
+print(doc, target = here('output','table','supplement-tables-revision-sescatupd.docx'))
 ```

### 2021-10-17 code/data-viz/forest-plot-functions.R

@@ -5,6 +5,7 @@
 
 library(tidyverse)
 library(ggpubr)
+library(RColorBrewer)
 
 
 ###############################################################################
@@ -260,7 +261,8 @@ Plot.Matrix <- function(dt, cmp, title, ggtheme) {
     #scale_color_manual(
     # labels = plot.labs, 
     #values = plot.cols) +
-    scale_color_tableau(palette = "Tableau 10") +
+    scale_color_manual(values = brewer.pal(n=10, "Paired")) +
+    #scale_color_tableau(palette = "Tableau 10") +
     labs(x = "Hazard Ratio (95% CI) \n Solid shapes (point estimates) indicate statistically significant results at the 0.05 level", y = "") +
     ggtitle(title) +
     facet_grid(Buffer ~ Window,  scales = "fixed", switch = 'y',

### 2021-11-08 code/data-analysis/config-file-generator.Rmd
Revision
2nd Rev - Mortality Rate - ExpoBuffer PM results

--- 2021-10-07 code/data-analysis/config-file-generator.Rmd
@@
 author: "Fatemeh Kazemi"
-date: "01-18-2021"
+date: "11-07-2021"
 ---
@@
                 "Yr4_SI","Yr4_NO3","Yr4_SO4",
-                "Yr5_SI","Yr5_NO3","Yr5_SO4")
+                "Yr5_SI","Yr5_NO3","Yr5_SO4",
+                "Yr1_PM", "Yr2_PM", "Yr3_PM", "Yr4_PM", "Yr5_PM")
 ```
@@
 dataname <- "ndi-pmc-bz12-15yr.csv"
-expo <- pmc.sub.yr
+expo <- pmc.major.yr
 
@@
 ```{r ses adj. model for components - bz 24 & 1-5yr}
-dataname <- "ndi-pmc-bz24.csv"
-expo <- pmc.sub.yr
+dataname <- "ndi-pmc-bz24-15yr.csv"
+expo <- pmc.major.yr
 

### 2021-11-08 code/data-analysis/output-cleaning.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results

@@
 author: "Fatemeh Kazemi"
-date: "01-30-2021"
+date: "11-07-2021"
 ---
@@
 ### Source Apportioned PM Mass
-mass.1yr.iqr <- dt.mass.app.1yr.c2 %>% 
-  summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
-  pivot_longer(cols = Biomass:Traffic,
-               names_to = "Parameter",
-               values_to = "IQR")%>% 
-  mutate(Parameter = as.factor(Parameter))
+# mass.1yr.iqr <- dt.mass.app.1yr.c2 %>% 
+#   summarise_at(vars(Biomass:Traffic), ~IQR(.x)) %>% 
+#   pivot_longer(cols = Biomass:Traffic,
+#                names_to = "Parameter",
+#                values_to = "IQR")%>% 
+#   mutate(Parameter = as.factor(Parameter))
 

### 2021-11-08 code/data-processors/cms-data-processor.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results

@@
 author: "Fatemeh Kazemi"
-date: "1/18/2021"
+date: "11/07/2021"
 output: html_document
@@
 load(here('data','processed','pmc-sub-1yr-5yr.RDa'))
-load(here('data','processed','mass-app-1yr-c2.RDa'))
+#load(here('data','processed','mass-app-1yr-c2.RDa'))
 ```
@@
 ```{r}
-cmp.major <- c("SI", "NO3", "SO4")
+cmp.major <- c("SI", "NO3", "SO4", "PM")
 
@@
   merge(dt.pmc4) %>% merge(dt.pmc5)
-
 ```

### 2021-11-08 code/data-viz/manuscript-tables.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results

@@
 author: "Fatemeh Kazemi"
-date: "05/31/2021"
+date: "11/07/2021"
 output:
@@
 cuz.bot.row <- c ("Respiratory", "COPD", "Pneumonia", "Cancer", "Lung Cancer")
+
+grp <- c('Main', 'Age', 'Sex', 'Race', 'Urbanicity', 'SES.Cat', 'Region', 'BRFSS')
+
+subgrp <- c('Main', '65-75', '> 75', 'Female', 'Male',
+            'Asian', 'Black', 'Hispanic', 'White',
+            'Urban', 'Rural', 'Low', 'Middle', 'High',
+            'West', 'Midwest', 'South', 'Northeast', 'BRFSS')
 
@@
 body_add(doc, run_pagebreak())
+```
+
+### Table S3
+```{r}
+dt.mort.rate <- read.csv(here('output','table','pmc-mortality-rate.csv')) %>% 
+  `colnames<-`(c("Group", "Subgroup", cuz)) %>% 
+  mutate_at(.vars = cuz, ~as.integer(.x)) %>% 
+  mutate(Group = factor(Group, levels = grp),
+         Subgroup = factor(Subgroup, levels = subgrp)) %>% 
+  arrange(factor(Group, levels = grp), Subgroup)
+
+doc3 <- read_docx()
+
+ft <- flextable(dt.mort.rate)
+ft <- merge_v(ft, j = c('Group', 'Subgroup'))
+ft <- theme_vanilla(ft)
+ft <- vline(ft, j = c('Group', 'Subgroup'))
+ft <- padding(ft, padding = 0)
+ft <- fontsize(ft, size = 12)
+ft <- set_caption(ft, caption = "Table S3. Average monthly cause-specific mortality rate per 100,000 of Medicare enrollees for entire population and by subgroup, US 2000 - 2008.")
+ft <- fontsize(ft, i = 1, size = 12, part = "header")
+ft <- autofit(ft)
+
+doc3 <- body_add_flextable(doc3, value = ft, split = T)
+doc3 <- body_add_par(doc3, "Abbreviations: IHD= Ischemic heart disease; CBV= Cerebrovascular disease; CHF = Congestive heart failure; COPD = chronic obstructive pulmonary disease.", style = "Normal")
+body_add(doc3, run_pagebreak())
+
+print(doc3, target = here('output','table','supplement-tables-revision-2nd-mort-rate.docx'))
 ```
@@
 doc <- read_docx()
-cmp.major <- c("Si", "NO3", "SO4")
+cmp.major <- c("PM2.5", "Si", "NO3", "SO4")
 out.pmc.buffer.expo <- out.pmc.buffer.expo %>% 
@@
 ```{r}
-print(doc, target = here('output','table','supplement-tables-revision-sescatupd.docx'))
+print(doc, target = here('output','table','supplement-tables-revision-2nd.docx'))
 ```

### 2021-11-08 code/data-viz/forest-plot-functions.R

@@ -1,4 +1,4 @@
-### Author: Fatemeh Kazemi - 01-30-2021
+### Author: Fatemeh Kazemi - 10-06-2021
 
 # Functions for plotting results of exposure ~ outcome analysis
 # Hazard Ratio (HR) and 95% CI (HR.L, HR.U) (HR.Lower and HR.Upper)

### 2021-11-08 code/data-viz/manuscript-table-functions.R

@@ -1,4 +1,4 @@
-### Author: Fatemeh Kazemi - 05-31-2021
+### Author: Fatemeh Kazemi - 11-07-2021
 
 # Functions for making table results of exposure ~ outcome analysis
 # Hazard Ratio (HR) and 95% CI (HR.L, HR.U) (HR.Lower and HR.Upper)
@@ -41,6 +41,9 @@ Table.Single <- function(dt, cmp, cuz, cpt, ftnt){
   
   return(doc)
 }
+
+
+
 
 
 # Age Group Table Function ------------------------------------------------

### 2021-11-09 code/data-viz/forest-plots-color-shape.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results
graphical abs revise

@@
 author: "Fatemeh Kazemi"
-date: "02-13-2021"
+date: "10-17-2021"
 ---
@@
                color = plot.cols, size = 1.5, show.legend = F) +
-  labs(x = "HR (95% CI) per IQR Increase", y = expression(paste("Source-Related ", PM[2.5])),
+  labs(x = "HR (95% CI) per IQR Increase", y = "",
+       #expression(paste("Source-Related ", PM[2.5]))
        title = expression(paste("Association of Long-Term Source-Related ", PM[2.5], " Exposure and Cause-Specific Mortality"))) +
@@
         strip.background = element_rect(fill = "#B9CFED"),
-        axis.title = element_text(size = 12, color = 'black'),
+        axis.title = element_text(size = 10, color = 'black'),
         axis.text = element_text(size = 9, color = 'black'),

### 2022-02-03 code/data-processors/air-data-processor.Rmd
2nd Rev - Mortality Rate - ExpoBuffer PM results
Notes for smoothing function

@@
 author: "Fatemeh Kazemi"
-date: "12-27-2020"
+date: "06-06-2021"
 output:
@@
 
+# dt.air : "Site.ID", "Date", "Parameter.Symbol", "Value"
+
 site.para <- dt.air %>% 

### 2022-02-03 code/data-processors/air-data-smooth-mvavg-function.R

@@ -16,6 +16,16 @@ library(mgcv)
 #    Value:
 #    Date:
 
+# Function Paramaeters:
+# si : list of sites
+# pr : list of parameters for each site
+# s  : 0.99 for 1-yr
+#      1.99 for 2-yr
+#      2.99 for 3-yr
+#      3.99 for 4-yr
+#      4.99 for 5-yr
+# n  : minimum number of days needed for calculating the x-year moving average
+
 Smoothed.Year <- function(si, pr, s, n){ 
 
     dt <- dt.air %>% 
